### 2020-08-03 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
Adding Journal

\section{Introduction}\label{Sec:Intro}

Time Series carry valuable information about the system which produces the data.
Their analysis is usually based on two approaches \cite{TimeSeriesAnalysisCryerChan}: in the (natural) time and transformed domains (for instance, frequency and wavelet).

In the context of time-domain analysis, a new methodology was proposed by \citeauthor{Bandt2002Permutation}~\citeyear{Bandt2002Permutation}.
Its approach is non-parametric and based on descriptors of Information Theory.
Through this, the time series is transformed into ordinal patterns, with which a histogram is formed.
Using such patterns, the resulting distribution becomes less sensitive to outliers and, as it does not depend on any model, can be applied to a variety of situations.

The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{2500} citations, according to the Journal of Citation Records.
We found works using such an approach in multiple areas of scientific knowledge such as, for example,
the study of electroencephalography signals using wavelet decomposition~\cite{EEGAnalysisWaveletInformationTools},
characterization of household appliances through their energy consumption~\cite{CharacterizationElectricLoadInformationTheoryQuantifiers},
 online signature classification and verification~\cite{ClassificationVerificationOnlineHandwrittenSignatures}
 %, and characterization of SAR image textures~\cite{DudaLAGIRS}
 .

Each time series is described by a point in the range of $\mathbbm R^2$, the entropy complexity plane.
Two points are well known in this plane: those of white noise and a completely deterministic sequence.
Through these references, we can characterize time series according to the dynamics of its generating process.
Based on this premise, studies with different applications managed to obtain relevant results from time series through information on the nature of the data provided by the  $H \times C$ plane.
Examples include the work of \citeauthor{ComplexNetworksEvolution}~\citeyear{ComplexNetworksEvolution} analyzed the evolution of dynamic networks by trajectories in the $H \times C$ plane,
\citeauthor{InformationTheoryPerspectiveNetworkRobustness}~\citeyear{InformationTheoryPerspectiveNetworkRobustness} checked the effect of attacks to complex networks by the displacement of their points in the $H \times C$ plane,
\citeauthor{CharacterizationVehicleBehaviorInformationTheory}~\citeyear{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles as a function of the topology of cities, and
\citeauthor{StructuralChangesDataCommunicationWSN}~\citeyear{StructuralChangesDataCommunicationWSN} employ Information-Theoretic measures to describe the evolution of wireless sensors networks.

Many results in this regard have been provided through the analysis and study of chaotic components.
We can cite as highlights:
\citeauthor{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties}~\citeyear{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
\citeauthor{De_Micco_2009}~\citeyear{De_Micco_2009} studied chaotic components in pseudo-random number generators.
\citeauthor{DistinguishingNoiseFromChaos}~\citeyear{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
\citeauthor{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach}~\citeyear{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.

With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
Some preliminary results can already be found in the literature.
\citeauthor{Larrondo2006Random}~\citeyear{Larrondo2006Random} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
\citeauthor{De_Micco_2008}~\citeyear{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
\citeauthor{LiborInvisibleHand}~\citeyear{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.

This paper advances the state-of-the-art by providing confidence regions for points in the $H\times C$ plane for a diversity of situations of interest.
%Such regions are obtained using a Monte Carlo approach.
The input is a sequence of actual random observations generated by a physical procedure, and these regions are obtained by the application of PCA in space of Entropy-Complexity Plane.
We emphasize that this study aims at providing confidence regions for sequences of the size that usually appear in the literature, not tests for randomness of PRNGs.

The paper is structured as follows: Section~\ref{Sec:Intro} introduces the elements of the study (the Bandt and Pompe methodology, the random deviates, and model).
The confidence regions are presented in Section~\ref{Sec:Results} with some analysis of this application, and the conclusions are discussed in Section~\ref{Sec:Conclusions}.

### 2020-08-03 Reports/JOURNAL - Confidence Regions/Chapters/Methodology.tex
Adding Journal

\section{Methodology}\label{Sec:Method}

\subsection{The Bandt-Pompe Methodology}

Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real valued time series of length $T$, without ties. 
As stated
by~\citeauthor{Bandt2002Permutation}~\citeyear{Bandt2002Permutation}in their seminal work:  
\begin{quote}
``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
\end{quote}
Also, as stressed by these authors, 
\begin{quote}
``The corresponding symbol sequence must come 
naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
\end{quote}

Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm Z}$) be the symmetric group of order $D!$ formed by all 
possible permutation of order $D$, and the symbol component vector 
${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
($\pi_j \neq \pi_k~\forall~j \neq k$). 
Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
with embedding dimension $D \geq 2$ ($D \in {\mathbbm Z}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm Z}$, also called ``embedding time''):
\begin{equation} 
\label{eq:time-delay}
{\mathbf X}^{(D,\tau)}_t ~=~( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) \ ,
\end{equation} 
for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
Then the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol vector ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
This mapping should be defined in a way that preserves the desired relation between the elements 
$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called motif) have to mapped to the same 
${\bm \pi}^{(D)}$. 
The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
\begin{enumerate}[a)]
\item ordering the ranks of the $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
       (\textit{Rank Permutation}) or,
\item ordering the time indexes according to the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$  
       (\textit{Chronological Index Permutation});
\end{enumerate}
       see details in \citeauthor{Traversaro2018Bandt}~\ycite{Traversaro2018Bandt}.
Without loss of generality, in the following we will only use the latter.

Consider, for instance, the time series $\mathcal X = (1.8, 1.2, 3.2, 4.8, 4.2, 4.5, 2.3, 3.7, 1.2, .5)$ depicted in Fig.~\ref{Fig:IntroBP}.
Assume we are using patterns of length $D=5$ with unitary time lag $\tau=1$.
The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(3.2, 4.8, 4.2, 4.5, 2.3)$, shown in black, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.

The dash-dot line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
In this case, $\mathbf X_{1}^{(5,2)}= (1.8, 3.2, 4.2, 2.3, 1.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.

\begin{figure}[H]
\centering
\includegraphics[width=.7\linewidth]{IntroBP}
\caption{Illustration of the Bandt and Pompe coding}
\label{Fig:IntroBP}
\end{figure}

Once all symbols have been computed, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
This is an estimate of the (unknown, in general) probability distribution function of these patterns.
The next step into the characterization of the time series is computing descriptors from this histogram.

The first descriptor is a measure of the disorder of the system.
The most frequently used feature for this is the Normalized Shannon entropy, defined as
\begin{equation}
H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
\end{equation}
with the convention that terms in the summation for which $h(j)=0$ are null.
This quantity is bounded in the unit interval, and is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citeauthor{LopezRuiz1995}~\citeyear{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
A time series can then be mapped into a point in the $H\times C$ plane.

\subsection{The Entropy-Complexity Plane}

We illustrate the use of the Entropy-Complexity ($H\times C$) with the following time series:
\begin{itemize}
\item Colored $k$-noise: white ($k=0$), $k=-1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $=5/2$, and $k=3$;
\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
\end{itemize}
In all cases, we used $D=6$ and $\tau=1$.
Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.

\begin{figure}[H]
\centering
	\subfloat[Logistic map $r=3.6$]{\includegraphics[width=.3\linewidth]{h36}}\quad
	\subfloat[Logistic map $r=4$]{\includegraphics[width=.3\linewidth]{h4}}\quad
	\subfloat[$f^{-3}$ noise]{\includegraphics[width=.3\linewidth]{h3}}\quad
	\subfloat[$f^{-5/2}$ noise]{\includegraphics[width=.3\linewidth]{h25}}\quad
	\subfloat[$f^{-2}$ noise]{\includegraphics[width=.3\linewidth]{h2}}\quad
	\subfloat[$f^{-1.5}$ noise]{\includegraphics[width=.3\linewidth]{h15}}\quad
	\subfloat[$f^{-1}$ noise]{\includegraphics[width=.3\linewidth]{h1}}\quad
	\subfloat[$f^{-1/2}$ noise]{\includegraphics[width=.3\linewidth]{h05}}\quad
	\subfloat[White noise]{\includegraphics[width=.3\linewidth]{h0}}
	\caption{Patterns histograms of selected time series, with $D=6$ and $\tau=1$\label{fig:Histograms}}
\end{figure}

Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series and the points they were mapped onto.
The points due to $f^{-k}$ noises appear joined by dotted segments.
It is noticeable that deterministic patterns have more complexity than random ones.
Also, points related to $f^{-k}$ noises tend to clutter for $k<1$.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{AllSystems}
\caption{Eleven systems and their points in the $H\times C$ plane}\label{fig:AllSystems}
\end{figure}

Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=-1/2$, and pink ($k=1$) noises.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{RightMostCorner}
\caption{White Noise, $f^{-1/2}$ and $f^{-1}$ noise points}\label{fig:RightMostCorner}
\end{figure}

The focus of our study is the empirical distribution of points produced by White and selected $f^{-k}$ noises, with this, providing confidence regions in the $H\times C$ plane.
In particular, we are interested in assessing pure randomness with this technique.

\subsection{The $H\times C$ plane in the literature}

Table~\ref{Tab:Literature} presents references in which the authors analyze time series of size $N$ and embedding dimension $D$.
The authors also attest whether the time series is white noise or not, according to its $(h,c)$ feature.

The following widely used non-chaotic algorithmic generators are analyzed:
\begin{itemize}
    \item[$-$] RNG available in Intel fortran compiler (FOR)
    \item[$-$] RNG available in Borland C++ compiler (CCC)
    \item[$-$] Matlab RAND function (MAT)
    \item[$-$] Mother RNG, available in Marsaglia website~\cite{marsaglia1994yet} (MOT)
    \item[$-$] Multiple with carry RNG (MWC)~\cite{marsaglia1994yet}
    \item[$-$] Combo RNG (COM)~\cite{marsaglia1994yet}
    \item[$-$] Lehmer RNG (LEH)~\cite{payne1969coding}
    \item[$-$] Fractional Gaussian noise with $\alpha = 0$ (fGn)
    \item[$-$] Fractional Brownian motion with $\alpha = 1.2$ (fBm)
    \item[$-$] $f^{-k}$ noise with $k = 0$
    \item[$-$] Linear Congruential Generator (LCG)~\cite{knuth1997sorting}
\end{itemize}

\begin{table}[H]
    \caption{References which attest whether a time series of size $N$ is white noise according to its $(h,c)$ feature, and the empirical $p$-value of such hypothesis according to our results}
    \label{Tab:Literature}
    \centering
    \begin{tabular}{llcccccc}
    \toprule
Reference & PRNG & $N$ & $D$ & $H$ & $C$ & Is white noise? & $p$-value\\ 
\midrule
\citeauthor{larrondo2002statistical} (\citeyear{larrondo2002statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no & NA\\
 &  FOR & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
 &  CCC & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
 &  MAT & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
\cmidrule(lr){1-8}
\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
 &  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
 &  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{Larrondo2006Random} (\citeyear{Larrondo2006Random}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
 &  MOT & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
 &  MWC & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{olivares2012contrasting} (\citeyear{olivares2012contrasting}) &  fGn & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.998$ & NA & yes & NA\\
 & fBm & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.993$ & NA & yes & NA\\
 & $f^{-k}$ & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.997$ & NA & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no & NA\\
\cmidrule(lr){1-8}
\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
 & $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
\bottomrule
    \end{tabular}
\end{table}

%The mathematical theory of markets states that fairness is characterized by white noise.

\subsection{True Random Numbers}

\textcolor{red}{Gerador - Marcelo e Heitor}

Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavihor. 
Pseudo randomic results can be achieved by software in a deterministic way. 
But, some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
Randomness can be observed in unpredictable real world phenomena like cathodic radiation or atmospheric noise.
In this study we used two sources of real random numbers. 
The first is based on vacuum states to generate random quantum numbers described by \citeauthor{Wittmann2010generator}~(\citeyear{Wittmann2010generator}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.

%Deixei as URLs pois não tenho o .bib ...

%The colored $k$-noise mentioned in the previous section, also known as ``correlated noise'', is such that its power spectrum has shape $f^{-k}$.
%When $k=0$, we have white noise, i.e., independent deviates.
%The larger $k$ is, the more correlated the observations are.

\subsection{Empirical Confidence Regions}

As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible at this first moment.
Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.

The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\cite{martin2006generalized}.
Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
A classic proposal in these categories of problems is the principal component analysis (PCA) algorithm~\cite{wold1987principal}.

Let $ {\mathcal P} = \{p_n \}_{n = 1}^{N} $ be a set of $N$ observations in the $H \times C$ plane, where ${p_n} = (h_n, c_n)$ corresponds to a time series.
We apply a principal component analysis to these points and obtain $\{(u_n,v_n)\}_{n=1}^N$.
This transformation yields uncorrelated observations in the $\Omega_1\times\Omega_2$ plane.

We will find the empirical confidence regions on the $\Omega_1\times\Omega_2$ plane, and then they will be mapped back to the $H \times C$ plane.
For simplicity, and without loss of generality, assume $N$ odd; we find a parallelepiped that contains 
\SI{100}{\minusalphapercent} of the points in the $\Omega_1\times\Omega_2$ as
\begin{enumerate}
    \item Find the ranks that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
    \item Find point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
    \item Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
    \item Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
    \item The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
    \item The top and bottom bounds of the box are the minimum and maximum values of the second principal component of the points whose first principal component is at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$; denote these values $v_{\min}$ and $v_{\max}$, respectively.
    %\item The lower-left and upper-right corners of the box are $(u_{r_{[N\alpha/2]}}, v_{\min})$, and $(u_{r_{[N\alpha/2]}},v_{\max})$, respectively.
    \item The corners of the box are 
    $(u_{r_{[N\alpha/2]}}, v_{\min})$, 
    $(u_{r_{[N\alpha/2]}}, v_{\max})$, 
    $(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
    $(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
    %\item Apply the inverse PCA transform to these corners obtaining $(h_1^{\SI{100}{\minusalphapercent}}, c_1^{\SI{100}{\minusalphapercent}})$, $(h_2^{\SI{100}{\minusalphapercent}}, c_2^{\SI{100}{\minusalphapercent}})$, $(h_1^{\SI{100}{\alphapercent}}, c_1^{\SI{100}{\alphapercent}})$ and $(h_2^{\SI{100}{\alphapercent}},c_2^{\SI{100}{\alphapercent}})$.
    \item Apply the inverse PCA transform to these corners obtaining $(h_{v_1}, c_{v_1})$, $(h_{v_2}, h_{v_2})$, $(h_{v_3}, c_{v_3})$ and $(h_{v_4},c_{v_4})$.
\end{enumerate}
These steps are also depicted in Fig.~\ref{fig:methodology}.

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/methodology.pdf}
    \caption{Outline of the methodology used for the construction of confidence regions.}
    \label{fig:methodology}
\end{figure}

\begin{sidewaystable}
    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{5 e4}$ in the $H \times C$ plane obtained by the proposed methodology}
    \label{Tab:Regions50k}
    \centering
    \begin{tabular}{cccccc}
    \toprule
Confidence Regions & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
\midrule
\SI{90}{\percent} & 3 & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$\\
\SI{95}{\percent} & 3 & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$\\
\SI{99}{\percent} & 3 & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$\\
\SI{99.9}{\percent} & 3 & $(0.9998625, 0.0001361)$ & $(0.9998622, 0.0001358)$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 4 & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9998075, 0.0002508)$ & $(0.9998087, 0.0002524)$\\
\SI{95}{\percent} & 4 & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9998506, 0.0001942)$ & $(0.9998518, 0.0001958)$\\
\SI{99}{\percent} & 4 & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9998756, 0.0001615)$ & $(0.9998768, 0.000163)$\\
\SI{99.9}{\percent} & 4 & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ & $(0.9998889, 0.000144)$ & $(0.9998901, 0.0001456)$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 5 & $(0.9998172, 0.0003232)$ & $(0.9998194, 0.0003273)$ & $(0.9994812, 0.0009246)$ & $(0.9994834, 0.0009286)$\\
\SI{95}{\percent} & 5 & $(0.9998259, 0.0003075)$ & $(0.9998282, 0.0003116)$ & $(0.9996371, 0.0006455)$ & $(0.9996394, 0.0006495)$\\
\SI{99}{\percent} & 5 & $(0.9998428, 0.0002774)$ & $(0.999845, 0.0002814)$ & $(0.9996703, 0.0005862)$ & $(0.9996725, 0.0005901)$\\
\SI{99.9}{\percent} & 5 & $(0.9998573, 0.0002517)$ & $(0.9998593, 0.0002553)$ & $(0.9996884, 0.000554)$ & $(0.9996904, 0.0005576)$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 6 & $(0.9990169, 0.002336)$ & $(0.9990249, 0.0023554)$ & $(0.9978983, 0.0050219)$ & $(0.9979064, 0.0050413)$\\
\SI{95}{\percent} & 6 & $(0.9990368, 0.002288)$ & $(0.9990449, 0.0023074)$ & $(0.998714, 0.0030633)$ & $(0.998722, 0.0030827)$\\
\SI{99}{\percent} & 6 & $(0.9990736, 0.0021997)$ & $(0.9990817, 0.0022191)$ & $(0.998765, 0.0029407)$ & $(0.9987731, 0.0029601)$\\
\SI{99.9}{\percent} & 6 & $(0.9991069, 0.0021197)$ & $(0.999115, 0.0021392)$ & $(0.9987884, 0.0028845)$ & $(0.9987965, 0.0029039)$\\
\bottomrule
    \end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{1 e3}$ in the $H \times C$ plane obtained by the proposed methodology}
    \label{Tab:Regions1000}
    \centering
    \begin{tabular}{cccccc}
    \toprule
Confidence Region & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
\midrule
\SI{90}{\percent} & 3 & $(0.9973334, 0.0025601)$ & $(0.9974047, 0.0026304)$ & $(0.9999497, 0)$ & $(1, \num[scientific-notation=true]{5.17e-05})$\\
\SI{95}{\percent} & 3 & $(0.9967311, 0.0031343)$ & $(0.9968219, 0.0032238)$ & $(0.9999398, 0)$ & $(1, \num[scientific-notation=true]{6.12e-05})$\\
\SI{99}{\percent} & 3 & $(0.9953009, 0.0045054)$ & $(0.9954349, 0.0046375)$ & $(0.9999203, 0)$ & $(1, \num[scientific-notation=true]{8.45e-05})$\\
\SI{99.9}{\percent} & 3 & $(0.9931825, 0.0065387)$ & $(0.9933704, 0.006724)$ & $(0.9998925, 0)$ & $(1, 0.0001104)$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 4 & $(0.994364, 0.0081246)$ & $(0.9939234, 0.0075452)$ & $(0.9994791, 0.0013982)$ & $(0.9990385, 0.0008188)$\\
\SI{95}{\percent} & 4 & $(0.9937138, 0.0089796)$ & $(0.9932534, 0.0083741)$ & $(0.9991609, 0.0018166)$ & $(0.9987005, 0.0012111)$\\
\SI{99}{\percent} & 4 & $(0.9922575, 0.0108947)$ & $(0.9917308, 0.0102022)$ & $(0.9987924, 0.0023012)$ & $(0.9982658, 0.0016087)$\\
\SI{99.9}{\percent} & 4 & $(0.9902578, 0.0135243)$ & $(0.9897312, 0.0128318)$ & $(0.9985727, 0.0025901)$ & $(0.9980461, 0.0018976)$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 5 & $(0.9811818, 0.0321294)$ & $(0.9827429, 0.0350291)$ & $(0.9919707, 0.0120896)$ & $(0.9935319, 0.0149893)$\\
\SI{95}{\percent} & 5 & $(0.9801289, 0.0340045)$ & $(0.9817117, 0.0369446)$ & $(0.9909376, 0.0139279)$ & $(0.9925204, 0.016868)$\\
\SI{99}{\percent} & 5 & $(0.977917, 0.0377295)$ & $(0.9796031, 0.0408613)$ & $(0.9898161, 0.0156277)$ & $(0.9915021, 0.0187595)$\\
\SI{99.9}{\percent} & 5 & $(0.9753326, 0.0425299)$ & $(0.9770187, 0.0456617)$ & $(0.9892599, 0.0166608)$ & $(0.9909459, 0.0197926)$\\
\cmidrule(lr){1-6}
\SI{90}{\percent} & 6 & $(0.9121895, 0.2201993)$ & $(0.9146048, 0.2260776)$ & $(0.9443868, 0.1418373)$ & $(0.9468021, 0.1477156)$\\
\SI{95}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9419202, 0.1476904)$ & $(0.9443663, 0.1536439)$\\
\SI{99}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9396577, 0.1531967)$ & $(0.9421039, 0.1591502)$\\
\SI{99.9}{\percent} & 6 & $(0.9077672, 0.2305874)$ & $(0.9102595, 0.2366531)$ & $(0.9383611, 0.1561279)$ & $(0.9408534, 0.1621937)$\\
\bottomrule
    \end{tabular}
\end{sidewaystable}

### 2020-08-03 Reports/JOURNAL - Confidence Regions/Chapters/Results.tex
Adding Journal

\section{Results}\label{Sec:Results}

In this section, we describe the descriptive analysis of representative points in relation to the confidence regions, as well as revisiting hypotheses of white noise present in the literature.
Empirical experiments on the behavior of an emblematic sample when injecting correlation structures are also presented.

We employed the following factors in this study:
\begin{itemize}
\item Time series length $T\in\mathcal T=\{10^3, \num[scientific-notation=true]{5 e4}\}$,
\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$,and
\item Exponent of the $f^{-k}$ noise $k\in\mathcal K=\{0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.5, 1,\\ 1.5, 2, 2.5, 3\}$.
\item Time delay $\tau=\{1,10,30,50\}$.
\end{itemize}
%There were no significant differences in data in repeated experiments with time delays $\tau=\{1,10,30,50\}$. 
%Therefore, we obtained $1000$ independent series for each point in the factors set $\mathcal T\times \mathcal D\times \mathcal K$.

The data generation and analyses were performed using the \texttt R platform \cite{Rmanual} v.~3.6.3.
We used the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.

\subsection{Descriptive analysis of representative data}

For the construction of the confidence regions presented in this work we use:
\begin{itemize}
    \item An set of $104596$ points in the $H \times C$ plane, referring to sequences of length $T = 1000$, for each combination of the factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$, and
    \item  An another set of $2093$ points in the $H \times C$ plane, referring to sequences of length $T = 50000$, for each combination of factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$.
\end{itemize}
Since the results involving the variation of the time delay parameter did not show a significant difference in repeated experiments, we don't consider it as a determinating factor during the execution of the algorithm.
On the other hand, we consider two determining variables during the generation of such sub-spaces: the embedding dimension and the length of the sequence.

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/Points-PDF.png}
    \caption{White noise samples considered during the construction of the proposed confidence regions.}
    \label{fig:white-noise}
\end{figure}

In Fig.~\ref{fig:HC-PCA} we show the results obtained for $T = 50000$ in the scenarios of $D = 3$ and $D = 6$ in the new space defined by the PCA, together with the quantiles of $90\%$, $95\%$, $99\%$ and $99.9\%$.
We also show the projection of the $H \times C$ plane limits in this new representation space, as well as identifying the median of each data set, the latter being represented as the red dots present in the graphs.

\begin{figure}[H]
	\centering
	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D3N50k.png}
	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D6N50k.png}
	\caption{}
	\label{fig:HC-PCA}
\end{figure}

As we can see in Fig.~\ref{fig:PCA-Hist} in the new representation space produced by the PCA, the data are not evenly distributed among the axes of the first main component, maintaining the character presented in the $H \times C$ plane, since such points tend to be concentrated close to the point $(1, 0)$.

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{PCA-hist-50k}
    \caption{Histogram of the PCA first component }
    \label{fig:PCA-Hist}
\end{figure}

%\textcolor{red}{An\'alise descritiva: alguns pontos de $\Theta$ representativos:} 
\subsection{Testing White Noise in the confidence regions}

To test the efficiency of the confidence region calculated, we tested its applicability on a set of truly random data generated physically not used by the algorithm during its construction. 
The results can be seen in Fig.~\ref{fig:RNG}.

For small series, $N = 1000$, and $D = 3$ we managed to maintain exactly $99\%$ of the data in the confidence region of the same value, and as the dimension increased reach $96\%$ of the points.
On the other hand, there was a very large loss of points located in the region with $95\%$ confidence as the dimension increased.
A reasonable explanation for this event is given in the choice of the parameter itself.
It is known by definition that $D! << N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
For larger series, $N = 50000$, although we observed a small drop in the percentage of data present in the region with $99\%$ confidence, there was a significant increase in points in the region with $95\%$ confidence, showing between $90\%$ and $88\%$ of the points when we vary the embedding dimension.

\begin{table}[H]
	\centering
	\caption{Results found it for samples of true random numbers}
	\label{tab:result1}
	\begin{tabular}{c*{3}rr}
		\toprule
		Algorithm & \multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		\cmidrule(lr){5-5}
		True-Random & 1000 & 3 & $0.98$ & $1$\\
		&  & 4 & $0.98$ & $0.96$\\
		&  & 5 & $1$ & $0.94$\\
		&  & 6 & $0.97$ & $0.87$\\
		\cmidrule(lr){1-5}
		True-Random & 50000 & 3 & $0.97$ & $0.96$\\
		&  & 4 & $0.94$ & $0.95$\\
		&  & 5 & $0.97$ & $0.96$\\
		&  & 6 & $0.98$ & $0.99$\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
    \includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
    \caption{White Noise in HC Plane}
    \label{fig:RNG}
\end{figure}

\begin{comment}
\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/fk-descriptive-analysis.pdf}
    \caption{$f^{-k}$ noises in HC Plane}
    \label{fig:fk}
\end{figure}

\end{comment}

%\textcolor{red}{Justificar o tipo de an\'alise: regressão? bivariada clássica? não-paramétrica?}

%\textcolor{red}{Regi\~oes de confian\c ca}

\begin{comment}

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/N50kBoxes95.png}
    \caption{}
    \label{fig:region95}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{Figures/N50kBoxes99.png}
    \caption{}
    \label{fig:region99}
\end{figure}

\end{comment}

%\subsection{Analysis of the Empirical Confidence Regions}

\subsection{Analyzing of the Empirical Confidence Regions Injecting Correlation}
% k=0 white
% k=1 pink
% k=2 brown
% T = 1000, T = 5 10^5
% D= 3, D = 6

Fig.~\ref{fig:AllSystems} shows the behavior of random time series with different levels of correlation (by means of the $f^{-k}$ model) in the $(h,c)$ plane.
Knowing that such plane can discriminate between different system dynamics, several studies in the literature have used this approach in the investigation of methods of identification and characterization of randomness.
Although this same strategy can be used to characterize different levels of correlation structures, in our case, we want to analyze the impact of injecting such dynamics into noise under the aspect of confidence regions.

For carrying out the experiment, we used an ''emblematic'' time series as a basis.
This series consists of the sample corresponding to the median of the $(h,c)$ points used to build the confidence regions, thus expressing a representative sample of the dataset.
Fig.~\ref{fig:correlation}a. illustrates, respectively, the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
As we can observe in the plane as the correlation between the observations increases, that is, $k > 0$, the randomness decreases and the entropy presented decreases, informing the loss of its stochastic characteristic.

Fig.~\ref{fig:correlation}b. illustrates the degree of limit correlation structure that can be added in white noise to eliminate it from the regions of confidence, where the red dot represents the original "emblematic" series.
When we have $k = 0$, the features of the sequence have a small variation, corroborating the premise that series of noise $f^{-k} = 0$ have a minimum correlation measure, not significantly changing the dynamics of the system.

\begin{figure}[H]
    \centering
	\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}
    \includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}
    \caption{Correlation Structure Analysis
    }
    \label{fig:correlation}
\end{figure}
%In the following, we will present how the $(h,c)$ point of the ``emblematic'' sequence alters when injecting temporal correlation (by means of the $f^{-k}$ model).
%, and determinism (by a convex combination with a sine function).
%The $f^{-k}$: simulation

\begin{comment}
\subsection{Injecting Determinism}
Consider the emblematic sequence $\bm x=(x_1,\dots,x_N)$, which is mapped onto the point $(h,c)$.
In order to inject determinism in this sequence, we will analyze the effect of $\xi\in[0,1]$, by checking how the point $\big(h,c\big)(\xi)$ evolves in the $(H,C)$ plane, in which
\begin{equation}
\bm x'(j) = \xi \sin(10 \pi j/N) +(1-\xi) x_j.    
\label{Eq:DeterminismXi}
\end{equation}
With this, when $\xi=0$ we have the original sequence $\bm x$ and, thus, the original emblematic point $(h,c)$;
when $\xi=1$, we have pure determinism: five sine functions.
\end{comment}

\subsection{Revisiting the White Noise Hypothesis in the Literature}

\begin{table}[H]
	\centering
	\caption{Points inside the confidence regions}
	\label{tab:resultFinal}
	\begin{tabular}{c*{3}r}
		\toprule
		Algorithm & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		Wichmann-Hill & 3 & 0.97 & 0.96\\ 
		Wichmann-Hill & 4 & 0.9675 & 0.9675\\ 
		Wichmann-Hill & 5 & 0.9725 & 0.965\\ 
		Wichmann-Hill & 6 & 0.97 & 0.97\\ 
		%\cmidrule(lr){1-4}
		%Marsaglia-Multicarry & 3 & 0.97 & 0.9625\\ 
		%Marsaglia-Multicarry & 4 & 0.97 & 0.9825\\ 
		%Marsaglia-Multicarry & 5 & 0.9625 & 0.9625\\ 
		%Marsaglia-Multicarry & 6 & 0.9675 & 0.9625\\ 
		\cmidrule(lr){1-4}
		Super-Duper & 3 & 0.9675 & 0.975\\ 
		Super-Duper & 4 & 0.9775 & 0.9725\\ 
		Super-Duper & 5 & 0.9675 & 0.985\\ 
		Super-Duper & 6 & 0.9825 & 0.965\\ 
		\cmidrule(lr){1-4}
		Knuth-TAOCP-2002 & 3 & 0.9775 & 0.9625\\ 
		Knuth-TAOCP-2002 & 4 & 0.965 & 0.98\\ 
		Knuth-TAOCP-2002 & 5 & 0.9625 & 0.9825\\ 
		Knuth-TAOCP-2002 & 6 & 0.9725 & 0.96\\  
		\cmidrule(lr){1-4}
		Knuth-TAOCP & 3 & 0.975 & 0.9775\\ 
		Knuth-TAOCP & 4 & 0.965 & 0.9725\\ 
		Knuth-TAOCP & 5 & 0.9875 & 0.985\\ 
		Knuth-TAOCP & 6 & 0.9725 & 0.975\\ 
		\cmidrule(lr){1-4}
		LEcuyer-CMRG & 3 & 0.98 & 0.98\\ 
		LEcuyer-CMRG & 4 & 0.9675 & 0.9725\\ 
		LEcuyer-CMRG & 5 & 0.965 & 0.9725\\ 
		LEcuyer-CMRG & 6 & 0.9625 & 0.97\\ 
		\cmidrule(lr){1-4}
		pcg64 & 3 & 0.97 & 0.9675\\ 
		pcg64 & 4 & 0.97 & 0.97\\ 
		pcg64 & 5 & 0.9775 & 0.9625\\ 
		pcg64 & 6 & 0.9575 & 0.9575\\ 
		\cmidrule(lr){1-4}
		Threefry & 3 & 0.9625 & 0.97\\ 
		Threefry & 4 & 0.975 & 0.97\\ 
		Threefry & 5 & 0.96 & 0.9625\\ 
		Threefry & 6 & 0.965 & 0.955\\ 
		\cmidrule(lr){1-4}
		Xoroshiro128+ & 3 & 0.975 & 0.9825\\ 
		Xoroshiro128+ & 4 & 0.995 & 0.9825\\ 
		Xoroshiro128+ & 5 & 0.98 & 0.9725\\ 
		Xoroshiro128+ & 6 & 0.9725 & 0.955\\ 
		\cmidrule(lr){1-4}
		MWC & 3 & 1 & 0.75\\
		MWC & 4 & 0.25 & 0.25\\ 
		MWC & 5 & 1 & 1\\ 
		MWC & 6 & 0 & 0\\ 
		\cmidrule(lr){1-4}
		MOT & 3 & 1 & 1\\ 
		MOT & 4 & 1 & 1\\ 
		MOT & 5 & 1 & 1\\ 
		MOT & 6 & 0.75 & 1\\ 
		\bottomrule 
	\end{tabular}
	\begin{tabular}{c*{3}r}
		\toprule
		Algorithm & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		Xoshiro256+ (FOR) & 3 & 0.98 & 0.98\\ 
		Xoshiro256+ (FOR) & 4 & 0.9675 & 0.965\\ 
		Xoshiro256+ (FOR) & 5 & 0.9525 & 0.96\\ 
		Xoshiro256+ (FOR) & 6 & 0.9775 & 0.975\\
		\cmidrule(lr){1-4} 
		Mersenne-Twister & 3 & 0.9725 & 0.97\\ 
		Mersenne-Twister & 4 & 0.98 & 0.97\\ 
		Mersenne-Twister & 5 & 0.9725 & 0.9775\\ 
		Mersenne-Twister & 6 & 0.975 & 0.9725\\ 
		\cmidrule(lr){1-4}
		Randu & 3 & 0.2275 & 0.42\\ 
		Randu & 4 & 0 & 0\\ 
		Randu & 5 & 0 & 0\\ 
		Randu & 6 & 0 & 0\\ 
		\cmidrule(lr){1-4}
		LCG & 3 & 0.07 & 0.09\\ 
		LCG & 4 & 0 & 0\\ 
		LCG & 5 & 0 & 0\\ 
		LCG & 6 & 0 & 0\\ 
		\cmidrule(lr){1-4}
		LEH & 3 & 0.9825 & 0.98\\ 
		LEH & 4 & 0.9675 & 0.9775\\ 
		LEH & 5 & 0.9725 & 0.9775\\ 
		LEH & 6 & 0.9775 & 0.9825\\ 
		\cmidrule(lr){1-4}
		fBm & 3 & 0 & 0\\ 
		fBm & 4 & 0 & 0\\ 
		fBm & 5 & 0 & 0\\ 
		fBm & 6 & 0 & 0\\ 
		\cmidrule(lr){1-4}
		fGn & 3 & 0.9722 & 0.9874\\ 
		fGn & 4 & 0.9798 & 0.9773\\ 
		fGn & 5 & 0.9646 & 0.9773\\ 
		fGn & 6 & 0.9722 & 0.9545\\
		\cmidrule(lr){1-4}
		$f^{-k}$ & 3 & 0.9525 & 0.96\\ 
		$f^{-k}$ & 4 & 0.975 & 0.9725\\ 
		$f^{-k}$ & 5 & 0.98 & 0.9675\\ 
		$f^{-k}$ & 6 & 0.9775 & 0.975\\
		\cmidrule(lr){1-4}
		COM & 3 & 0.25 & 0.5\\ 
		COM & 4 & 0 & 0\\ 
		COM & 5 & 0 & 0\\ 
		COM & 6 & 0 & 0\\ 
		\cmidrule(lr){1-4}
		CCC & 3 & 0 & 0\\ 
		CCC & 4 & 0 & 0\\ 
		CCC & 5 & 0 & 0\\ 
		CCC & 6 & 0 & 0\\
		\bottomrule
	\end{tabular}
\end{table}

### 2020-08-03 Code/PNRG-Analysis.R

@@ -559,7 +559,7 @@ generator.all <- function(){
 test.all <- function(){
   #registerDoParallel(cores = 6)
   table.code = ""
-  for(i in 15:17){
+  for(i in 18){
     table.code = PNRG.test.confidence.regions(D = 3, N = 50000, generator = i, table.code)
     table.code = PNRG.test.confidence.regions(D = 4, N = 50000, generator = i, table.code)
     table.code = PNRG.test.confidence.regions(D = 5, N = 50000, generator = i, table.code)
@@ -568,7 +568,7 @@ test.all <- function(){
   return(table.code)
 }
 
-generator.all()
+test.all()
 
 #pdf("pcg64-50000.pdf", width = 24, height = 16)
 #p = plot.PNRG.analysis(N = 50000, generator = 'pcg64')

### 2020-08-03 Reports/JOURNAL - Confidence Regions/Code-Heitor/plots.R

@@ -1,0 +1,45 @@
+library(ggplot2)
+setwd('Marcelo/paper/')
+elmacho=read.csv('../Data/results.csv', header=T)
+
+elmacho$X=NULL
+#dEuclid=sqrt(elmacho$H^2+elmacho$C^2)
+
+#elmacho=cbind(elmacho,dEuclid)
+
+#cotas
+
+read_cotas = function(D=3){
+  cont_name = paste('limits/continua-N',factorial(D),'.q1', sep='')
+  trozos_name = paste('limits/trozos-N',factorial(D),'.q1', sep='')
+  continua = read.table(cont_name, skip=7)
+  trozos = read.table(trozos_name, skip=7)
+  cotas = list(continua,trozos)
+  return(cotas)
+}
+
+plot_confidence = function(DD,TNN){
+  #D=3, TN=1000, K=0
+  out1 = subset(elmacho,D==DD&TN==TNN)
+  cot = read_cotas(DD)
+  xmax=max(out1$H)
+  ymax=max(out1$C)
+  xmin=min(out1$H)
+  ymin=min(out1$C)
+  ymin=0
+  ggplot() +
+    geom_point(aes(H,C,colour = K),data=out1, alpha=.3) +
+    scale_colour_gradient(low = "yellow", high = "black") +
+    geom_line(aes(V1,V2),data=cot[[1]])+
+    geom_line(aes(V1,V2),data=cot[[2]])+
+    scale_x_continuous(limits=c(xmin,xmax)) +
+    scale_y_continuous(limits=c(ymin,ymax))+
+    theme_light() 
+}
+plot_confidence(3,1e3)
+plot_confidence(3,5e5)
+
+plot_confidence(6,1e3)
+plot_confidence(6,5e5)
+
+

### 2020-08-03 Code/PNRG-Analysis.R
matlab

@@ -277,6 +277,8 @@ PNRG <- function(n.series, size.series, generator = 'randu'){
       random.vector[i,] = rand.borland[(((i-1)*n.series) + 1):(n.series*i)]
       print(i)
     }
+  }else if(generator == 'matlab'){
+    random.vector = read.csv("../../matlab-rand.csv")
   }
   return(random.vector)
 }
@@ -288,7 +290,7 @@ PNRG.HC.generator <- function(i){
   GNR.models = c('Wichmann-Hill', 'Marsaglia-Multicarry', 'Super-Duper', 
                  'Knuth-TAOCP-2002', 'Knuth-TAOCP', 'LEcuyer-CMRG',
                  'pcg64', 'Threefry', 'Xoroshiro128+', 'Xoshiro256+', 
-                 'mersenne', 'randu', 'lcg', 'Lehmer', 'mwc', 'mother', 'combo', 'borland')
+                 'mersenne', 'randu', 'lcg', 'Lehmer', 'mwc', 'mother', 'combo', 'borland', 'matlab')
   
   i = GNR.models[i]
   
@@ -321,7 +323,7 @@ PNRG.test.confidence.regions <- function(D = 3, N = 50000, generator = 1, table.
   GNR.models = c('Wichmann-Hill', 'Marsaglia-Multicarry', 'Super-Duper', 
                  'Knuth-TAOCP-2002', 'Knuth-TAOCP', 'LEcuyer-CMRG',
                  'pcg64', 'Threefry', 'Xoroshiro128+', 'Xoshiro256+', 
-                 'mersenne', 'randu', 'lcg', 'Lehmer', 'mwc', 'mother', 'combo', 'borland')
+                 'mersenne', 'randu', 'lcg', 'Lehmer', 'mwc', 'mother', 'combo', 'borland', 'matlab')
   
   generator = GNR.models[generator]
   
@@ -365,6 +367,8 @@ PNRG.test.confidence.regions <- function(D = 3, N = 50000, generator = 1, table.
     hc.data = read.csv("../Data/PRNG/HC-combo-50k.csv")[2:5]
   }else if(generator == 'borland'){
     hc.data = read.csv("../Data/PRNG/HC-borland-50k.csv")[2:5]
+  }else if(generator == 'matlab'){
+    hc.data = read.csv("../Data/PRNG/HC-matlab-50k.csv")[2:5]
   }
[…]

### 2020-08-04 Code/PNRG-Analysis.R
matlab generator

@@ -285,6 +285,33 @@ PNRG <- function(n.series, size.series, generator = 'randu'){
 
 # Analysis functions -----------------------------------------------------------------------------------
 
+matlab.generator <- function(){
+  
+  # N = 50000 -------------------
+  a = -99
+  N = 50000
+  D = c(3, 4, 5, 6)
+  tau = c(1, 10, 30, 50)
+  random.series = PNRG(100, N, 'matlab')
+  hc.50k = data.frame(H = numeric(1584), C = numeric(1584), D = numeric(1584), tau = numeric(1584))
+  
+  for(t in tau){
+    for(d in D){
+      a = a + 99
+      for(j in 1:99){
+        cat("N: ", N, " D: ", d, " tau: ", t, " series: ", j, '\n')
+        probs = bandt.pompe(random.series[j,], d, t)
+        hc.50k$H[j + a] = shannon.entropy.normalized(probs)
+        hc.50k$C[j + a] = Ccomplexity(probs)
+        hc.50k$D[j + a] = d
+        hc.50k$tau[j + a] = t
+      }
+    }
+  }
+  write.csv(hc.50k, file = "../Data/PRNG/HC-matlab-50k.csv")
+}
+
+
 PNRG.HC.generator <- function(i){
   
   GNR.models = c('Wichmann-Hill', 'Marsaglia-Multicarry', 'Super-Duper', 
@@ -576,7 +603,7 @@ test.all <- function(){
   return(table.code)
 }
 
-generator.all()
+matlab.generator()
 
 #pdf("pcg64-50000.pdf", width = 24, height = 16)
 #p = plot.PNRG.analysis(N = 50000, generator = 'pcg64')

### 2020-08-04 Code/PNRG-Analysis.R
matlab generator

@@ -292,7 +292,7 @@ matlab.generator <- function(){
   N = 50000
   D = c(3, 4, 5, 6)
   tau = c(1, 10, 30, 50)
-  random.series = PNRG(100, N, 'matlab')
+  random.series = PNRG(100, N, 'matlab')[1:99,]
   hc.50k = data.frame(H = numeric(1584), C = numeric(1584), D = numeric(1584), tau = numeric(1584))
   
   for(t in tau){
@@ -300,7 +300,7 @@ matlab.generator <- function(){
       a = a + 99
       for(j in 1:99){
         cat("N: ", N, " D: ", d, " tau: ", t, " series: ", j, '\n')
-        probs = bandt.pompe(random.series[j,], d, t)
+        probs = bandt.pompe(unlist(random.series[j,]), d, t)
         hc.50k$H[j + a] = shannon.entropy.normalized(probs)
         hc.50k$C[j + a] = Ccomplexity(probs)
         hc.50k$D[j + a] = d

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/Background.tex
Journal confidence regions

--- 2020-08-03 Reports/JOURNAL - Confidence Regions/Chapters/Methodology.tex
@@
-\section{Methodology}\label{Sec:Method}
+\section{Bandt-Pompe Symbolization: A Background}
+
+In our work, we consider that ordinal patterns are formed from white noise sequences using Bandt-Pompe symbolization and mapped in the two-dimensional plane of information theory descriptors, permutation entropy and statistical complexity.
+Through the space formed by this tuple of features, we were able to obtain regions of confidence and a test statistic that can discriminating random series.
 
@@
 Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real valued time series of length $T$, without ties. 
-As stated
-by~\citeauthor{Bandt2002Permutation}~\citeyear{Bandt2002Permutation}in their seminal work:  
+As stated by \citeauthor{PermutationEntropyBandtPompe}~\ycite{PermutationEntropyBandtPompe} in their seminal work:  
 \begin{quote}
@@
 \end{enumerate}
-       see details in \citeauthor{Traversaro2018Bandt}~\ycite{Traversaro2018Bandt}.
+       see details in \citeauthor{BPRepeatedValuesChaos}~\ycite{BPRepeatedValuesChaos}.
 Without loss of generality, in the following we will only use the latter.
@@
 In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citeauthor{LopezRuiz1995}~\citeyear{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
+To this aim, \citeauthor{LopezRuiz1995}~\ycite{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
 They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
@@
 \begin{figure}[H]
+    \includegraphics[width=\linewidth]{Figures/h.pdf}
+	\caption{Patterns histograms of selected time series, with $D=6$ and $\tau=1$}
+	\label{fig:Histograms}
+\end{figure}
+
+\begin{comment}
+\begin{figure}[H]
 \centering
@@
 \end{figure}
+\end{comment}
 
@@
 It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$.
+Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
 
@@
 
-The focus of our study is the empirical distribution of points produced by White and selected $f^{-k}$ noises, with this, providing confidence regions in the $H\times C$ plane.
-In particular, we are interested in assessing pure randomness with this technique.
-
-\subsection{The $H\times C$ plane in the literature}
-
-Table~\ref{Tab:Literature} presents references in which the authors analyze time series of size $N$ and embedding dimension $D$.
-The authors also attest whether the time series is white noise or not, according to its $(h,c)$ feature.
-
-The following widely used non-chaotic algorithmic generators are analyzed:
-\begin{itemize}
-    \item[$-$] RNG available in Intel fortran compiler (FOR)
-    \item[$-$] RNG available in Borland C++ compiler (CCC)
-    \item[$-$] Matlab RAND function (MAT)
-    \item[$-$] Mother RNG, available in Marsaglia website~\cite{marsaglia1994yet} (MOT)
-    \item[$-$] Multiple with carry RNG (MWC)~\cite{marsaglia1994yet}
-    \item[$-$] Combo RNG (COM)~\cite{marsaglia1994yet}
-    \item[$-$] Lehmer RNG (LEH)~\cite{payne1969coding}
-    \item[$-$] Fractional Gaussian noise with $\alpha = 0$ (fGn)
-    \item[$-$] Fractional Brownian motion with $\alpha = 1.2$ (fBm)
-    \item[$-$] $f^{-k}$ noise with $k = 0$
-    \item[$-$] Linear Congruential Generator (LCG)~\cite{knuth1997sorting}
-\end{itemize}
-
-\begin{table}[H]
-    \caption{References which attest whether a time series of size $N$ is white noise according to its $(h,c)$ feature, and the empirical $p$-value of such hypothesis according to our results}
-    \label{Tab:Literature}
-    \centering
-    \begin{tabular}{llcccccc}
-    \toprule
-Reference & PRNG & $N$ & $D$ & $H$ & $C$ & Is white noise? & $p$-value\\ 
-\midrule
-\citeauthor{larrondo2002statistical} (\citeyear{larrondo2002statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no & NA\\
- &  FOR & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
- &  CCC & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
- &  MAT & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{Larrondo2006Random} (\citeyear{Larrondo2006Random}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MOT & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MWC & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{olivares2012contrasting} (\citeyear{olivares2012contrasting}) &  fGn & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.998$ & NA & yes & NA\\
- & fBm & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.993$ & NA & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.997$ & NA & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
-\bottomrule
-    \end{tabular}
-\end{table}
-
-%The mathematical theory of markets states that fairness is characterized by white noise.
-
-\subsection{True Random Numbers}
-
-\textcolor{red}{Gerador - Marcelo e Heitor}
-
-Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavihor. 
-Pseudo randomic results can be achieved by software in a deterministic way. 
-But, some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real world phenomena like cathodic radiation or atmospheric noise.
-In this study we used two sources of real random numbers. 
-The first is based on vacuum states to generate random quantum numbers described by \citeauthor{Wittmann2010generator}~(\citeyear{Wittmann2010generator}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-%Deixei as URLs pois não tenho o .bib ...
-
-%The colored $k$-noise mentioned in the previous section, also known as ``correlated noise'', is such that its power spectrum has shape $f^{-k}$.
-%When $k=0$, we have white noise, i.e., independent deviates.
-%The larger $k$ is, the more correlated the observations are.
-
-\subsection{Empirical Confidence Regions}
-
-As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible at this first moment.
-Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
-
-The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\cite{martin2006generalized}.
-Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-A classic proposal in these categories of problems is the principal component analysis (PCA) algorithm~\cite{wold1987principal}.
-
-Let $ {\mathcal P} = \{p_n \}_{n = 1}^{N} $ be a set of $N$ observations in the $H \times C$ plane, where ${p_n} = (h_n, c_n)$ corresponds to a time series.
-We apply a principal component analysis to these points and obtain $\{(u_n,v_n)\}_{n=1}^N$.
-This transformation yields uncorrelated observations in the $\Omega_1\times\Omega_2$ plane.
-
-We will find the empirical confidence regions on the $\Omega_1\times\Omega_2$ plane, and then they will be mapped back to the $H \times C$ plane.
-For simplicity, and without loss of generality, assume $N$ odd; we find a parallelepiped that contains 
-\SI{100}{\minusalphapercent} of the points in the $\Omega_1\times\Omega_2$ as
-\begin{enumerate}
-    \item Find the ranks that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-    \item Find point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-    \item Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-    \item Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-    \item The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-    \item The top and bottom bounds of the box are the minimum and maximum values of the second principal component of the points whose first principal component is at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$; denote these values $v_{\min}$ and $v_{\max}$, respectively.
-    %\item The lower-left and upper-right corners of the box are $(u_{r_{[N\alpha/2]}}, v_{\min})$, and $(u_{r_{[N\alpha/2]}},v_{\max})$, respectively.
-    \item The corners of the box are 
-    $(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-    $(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-    $(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-    $(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-    %\item Apply the inverse PCA transform to these corners obtaining $(h_1^{\SI{100}{\minusalphapercent}}, c_1^{\SI{100}{\minusalphapercent}})$, $(h_2^{\SI{100}{\minusalphapercent}}, c_2^{\SI{100}{\minusalphapercent}})$, $(h_1^{\SI{100}{\alphapercent}}, c_1^{\SI{100}{\alphapercent}})$ and $(h_2^{\SI{100}{\alphapercent}},c_2^{\SI{100}{\alphapercent}})$.
-    \item Apply the inverse PCA transform to these corners obtaining $(h_{v_1}, c_{v_1})$, $(h_{v_2}, h_{v_2})$, $(h_{v_3}, c_{v_3})$ and $(h_{v_4},c_{v_4})$.
-\end{enumerate}
-These steps are also depicted in Fig.~\ref{fig:methodology}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/methodology.pdf}
-    \caption{Outline of the methodology used for the construction of confidence regions.}
-    \label{fig:methodology}
-\end{figure}
-
-\begin{sidewaystable}
-    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{5 e4}$ in the $H \times C$ plane obtained by the proposed methodology}
-    \label{Tab:Regions50k}
-    \centering
-    \begin{tabular}{cccccc}
-    \toprule
-Confidence Regions & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
-\midrule
-\SI{90}{\percent} & 3 & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$\\
-\SI{95}{\percent} & 3 & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$\\
-\SI{99}{\percent} & 3 & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$\\
-\SI{99.9}{\percent} & 3 & $(0.9998625, 0.0001361)$ & $(0.9998622, 0.0001358)$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 4 & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9998075, 0.0002508)$ & $(0.9998087, 0.0002524)$\\
-\SI{95}{\percent} & 4 & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9998506, 0.0001942)$ & $(0.9998518, 0.0001958)$\\
-\SI{99}{\percent} & 4 & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9998756, 0.0001615)$ & $(0.9998768, 0.000163)$\\
-\SI{99.9}{\percent} & 4 & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ & $(0.9998889, 0.000144)$ & $(0.9998901, 0.0001456)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 5 & $(0.9998172, 0.0003232)$ & $(0.9998194, 0.0003273)$ & $(0.9994812, 0.0009246)$ & $(0.9994834, 0.0009286)$\\
-\SI{95}{\percent} & 5 & $(0.9998259, 0.0003075)$ & $(0.9998282, 0.0003116)$ & $(0.9996371, 0.0006455)$ & $(0.9996394, 0.0006495)$\\
-\SI{99}{\percent} & 5 & $(0.9998428, 0.0002774)$ & $(0.999845, 0.0002814)$ & $(0.9996703, 0.0005862)$ & $(0.9996725, 0.0005901)$\\
-\SI{99.9}{\percent} & 5 & $(0.9998573, 0.0002517)$ & $(0.9998593, 0.0002553)$ & $(0.9996884, 0.000554)$ & $(0.9996904, 0.0005576)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 6 & $(0.9990169, 0.002336)$ & $(0.9990249, 0.0023554)$ & $(0.9978983, 0.0050219)$ & $(0.9979064, 0.0050413)$\\
-\SI{95}{\percent} & 6 & $(0.9990368, 0.002288)$ & $(0.9990449, 0.0023074)$ & $(0.998714, 0.0030633)$ & $(0.998722, 0.0030827)$\\
-\SI{99}{\percent} & 6 & $(0.9990736, 0.0021997)$ & $(0.9990817, 0.0022191)$ & $(0.998765, 0.0029407)$ & $(0.9987731, 0.0029601)$\\
-\SI{99.9}{\percent} & 6 & $(0.9991069, 0.0021197)$ & $(0.999115, 0.0021392)$ & $(0.9987884, 0.0028845)$ & $(0.9987965, 0.0029039)$\\
-\bottomrule
-    \end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{1 e3}$ in the $H \times C$ plane obtained by the proposed methodology}
-    \label{Tab:Regions1000}
-    \centering
-    \begin{tabular}{cccccc}
-    \toprule
-Confidence Region & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
-\midrule
-\SI{90}{\percent} & 3 & $(0.9973334, 0.0025601)$ & $(0.9974047, 0.0026304)$ & $(0.9999497, 0)$ & $(1, \num[scientific-notation=true]{5.17e-05})$\\
-\SI{95}{\percent} & 3 & $(0.9967311, 0.0031343)$ & $(0.9968219, 0.0032238)$ & $(0.9999398, 0)$ & $(1, \num[scientific-notation=true]{6.12e-05})$\\
-\SI{99}{\percent} & 3 & $(0.9953009, 0.0045054)$ & $(0.9954349, 0.0046375)$ & $(0.9999203, 0)$ & $(1, \num[scientific-notation=true]{8.45e-05})$\\
-\SI{99.9}{\percent} & 3 & $(0.9931825, 0.0065387)$ & $(0.9933704, 0.006724)$ & $(0.9998925, 0)$ & $(1, 0.0001104)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 4 & $(0.994364, 0.0081246)$ & $(0.9939234, 0.0075452)$ & $(0.9994791, 0.0013982)$ & $(0.9990385, 0.0008188)$\\
-\SI{95}{\percent} & 4 & $(0.9937138, 0.0089796)$ & $(0.9932534, 0.0083741)$ & $(0.9991609, 0.0018166)$ & $(0.9987005, 0.0012111)$\\
-\SI{99}{\percent} & 4 & $(0.9922575, 0.0108947)$ & $(0.9917308, 0.0102022)$ & $(0.9987924, 0.0023012)$ & $(0.9982658, 0.0016087)$\\
-\SI{99.9}{\percent} & 4 & $(0.9902578, 0.0135243)$ & $(0.9897312, 0.0128318)$ & $(0.9985727, 0.0025901)$ & $(0.9980461, 0.0018976)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 5 & $(0.9811818, 0.0321294)$ & $(0.9827429, 0.0350291)$ & $(0.9919707, 0.0120896)$ & $(0.9935319, 0.0149893)$\\
-\SI{95}{\percent} & 5 & $(0.9801289, 0.0340045)$ & $(0.9817117, 0.0369446)$ & $(0.9909376, 0.0139279)$ & $(0.9925204, 0.016868)$\\
-\SI{99}{\percent} & 5 & $(0.977917, 0.0377295)$ & $(0.9796031, 0.0408613)$ & $(0.9898161, 0.0156277)$ & $(0.9915021, 0.0187595)$\\
-\SI{99.9}{\percent} & 5 & $(0.9753326, 0.0425299)$ & $(0.9770187, 0.0456617)$ & $(0.9892599, 0.0166608)$ & $(0.9909459, 0.0197926)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 6 & $(0.9121895, 0.2201993)$ & $(0.9146048, 0.2260776)$ & $(0.9443868, 0.1418373)$ & $(0.9468021, 0.1477156)$\\
-\SI{95}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9419202, 0.1476904)$ & $(0.9443663, 0.1536439)$\\
-\SI{99}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9396577, 0.1531967)$ & $(0.9421039, 0.1591502)$\\
-\SI{99.9}{\percent} & 6 & $(0.9077672, 0.2305874)$ & $(0.9102595, 0.2366531)$ & $(0.9383611, 0.1561279)$ & $(0.9408534, 0.1621937)$\\
-\bottomrule
-    \end{tabular}
-\end{sidewaystable}
+The focus of our study is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences, providing regions of confidence in the $H \times C$ plane.

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/Conclusions.tex
Journal confidence regions

\section{Conclusions}\label{Sec:Conclusions}

We present and evaluate a new method of building empirical confidence regions in the Entropy-Complexity plane for the analysis of white noise.
The following proposal consists of two stages:
(1)~the construction of empirical confidence regions obtained through the mapping of points in the latent space formed by the application of the principal components analysis under the reference points,
(2) ~ the application of a hypothesis test to measure the similarity of new sequences to the reference points.
Sequences of true random samples were used to calculate theses empirical regions.

Experiments with true random samples showed that the presented methodology can represent them with good performance.
Although the present work focuses on the study of short sequences, we were able to capture the random behavior of PRNGs already analyzed in the literature and we verified the robustness of our technique and the correlation structure present in the sequences.

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/ExperimentalSetup.tex
Journal confidence regions

\section{Experimental Settings}

We evaluated the performance of the proposed method in relation to a large set of random sequences provided by state-of-the-art pseudo-random number generators.
In this section, we present the settings of the parameters that we use as a reference, the true random physical generators used to calculate the empirical distribution, and descriptive analysis of representative points in relation to the confidence regions.

\subsection{Parameters Settings and Dataset}

In the calculation of the ordinal symbol histogram, we employed the following factors in this study:
\begin{itemize}
\item Sequence length $T\in\mathcal T=\{10^3, \num[scientific-notation=true]{5 e4}\}$,
\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$,and
\item Time delay $\tau=\{1, 10, 30, 50\}$.
\end{itemize}

For the construction of the confidence regions presented, we use:
\begin{itemize}
    \item Set of $104596$ points in the $H \times C$ plane, referring to sequences of length $T = 1000$, for each combination of the factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$, and
    \item  Another set of $2093$ points in the $H \times C$ plane, referring to sequences of length $T = 50000$, for each combination of factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$.
\end{itemize}
Since the results involving the variation of the time delay parameter did not show a significant difference in repeated experiments, we don't consider it as a determinating factor during the execution of the algorithm.
On the other hand, we consider two determining variables during the generation of such sub-spaces: the embedding dimension and the length of the sequence.
%\todo[inline]{Justificar o porquê da ausência do tau nos experimentos}

The data generation and analyses were performed using the \texttt R platform \cite{Rmanual} v.~3.6.3.
We used the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.

\subsection{True Random Numbers}

\todo[inline]{Gerador - Marcelo}

Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavihor. 
Pseudo randomic results can be achieved by software in a deterministic way. 
But, some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
Randomness can be observed in unpredictable real world phenomena like cathodic radiation or atmospheric noise.
In this study we used two sources of real random numbers. 
The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.

%Deixei as URLs pois não tenho o .bib ...

%The colored $k$-noise mentioned in the previous section, also known as ``correlated noise'', is such that its power spectrum has shape $f^{-k}$.
%When $k=0$, we have white noise, i.e., independent deviates.
%The larger $k$ is, the more correlated the observations are.
\begin{comment}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Figures/Points-PDF.png}
    \caption{White noise samples considered during the construction of the proposed confidence regions.}
    \label{fig:white-noise}
\end{figure}

\end{comment}

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
Journal confidence regions

@@
 Their analysis is usually based on two approaches \cite{TimeSeriesAnalysisCryerChan}: in the (natural) time and transformed domains (for instance, frequency and wavelet).
-
-In the context of time-domain analysis, a new methodology was proposed by \citeauthor{Bandt2002Permutation}~\citeyear{Bandt2002Permutation}.
+In the context of time-domain analysis, a new methodology was proposed by \citeauthor{PermutationEntropyBandtPompe}~\ycite{PermutationEntropyBandtPompe}.
 Its approach is non-parametric and based on descriptors of Information Theory.
@@
 characterization of household appliances through their energy consumption~\cite{CharacterizationElectricLoadInformationTheoryQuantifiers},
- online signature classification and verification~\cite{ClassificationVerificationOnlineHandwrittenSignatures}
- %, and characterization of SAR image textures~\cite{DudaLAGIRS}
- .
+ online signature classification and verification~\cite{ClassificationVerificationOnlineHandwrittenSignatures}.
 
@@
 Two points are well known in this plane: those of white noise and a completely deterministic sequence.
-Through these references, we can characterize time series according to the dynamics of its generating process.
+Through these references, we can characterize the time series according to the dynamics of its generating process.
 Based on this premise, studies with different applications managed to obtain relevant results from time series through information on the nature of the data provided by the $H \times C$ plane.
-Examples include the work of \citeauthor{ComplexNetworksEvolution}~\citeyear{ComplexNetworksEvolution} analyzed the evolution of dynamic networks by trajectories in the $H \times C$ plane,
-\citeauthor{InformationTheoryPerspectiveNetworkRobustness}~\citeyear{InformationTheoryPerspectiveNetworkRobustness} checked the effect of attacks to complex networks by the displacement of their points in the $H \times C$ plane,
-\citeauthor{CharacterizationVehicleBehaviorInformationTheory}~\citeyear{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles as a function of the topology of cities, and
-\citeauthor{StructuralChangesDataCommunicationWSN}~\citeyear{StructuralChangesDataCommunicationWSN} employ Information-Theoretic measures to describe the evolution of wireless sensors networks.
+Examples include the analysis of \citeauthor{echegoyen2020permutation}~\ycite{echegoyen2020permutation} in magnetoencephalography recordings of individuals suffering from mild cognitive impairment and individuals diagnosed with Alzheimer's disease by trajectories in the $H \times C$ plane,
+\citeauthor{InformationTheoryPerspectiveNetworkRobustness}~\ycite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by displacing their points in the $H \times C$ plane,
+\citeauthor{CharacterizationVehicleBehaviorInformationTheory}~\ycite{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles depending on the topology of cities, and
+\citeauthor{Chagas2020Characterization}~\ycite{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing SAR texture images, making characterization, and classification of them.
 
-Many results in this regard have been provided through the analysis and study of chaotic components.
-We can cite as highlights:
-\citeauthor{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties}~\citeyear{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
-\citeauthor{De_Micco_2009}~\citeyear{De_Micco_2009} studied chaotic components in pseudo-random number generators.
-\citeauthor{DistinguishingNoiseFromChaos}~\citeyear{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
-\citeauthor{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach}~\citeyear{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
+%and \citeauthor{StructuralChangesDataCommunicationWSN}~\ycite{StructuralChangesDataCommunicationWSN} employ Information-Theoretic measures to describe the evolution of wireless sensors networks.
 
+In the context of theoretical work, chaotic and random component analysis has been developed with the aim of improving the understanding of the plane's properties. We can cite as highlights:
+\citeauthor{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties}~\ycite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
+\citeauthor{De_Micco_2009}~\ycite{De_Micco_2009} studied chaotic components in pseudo-random number generators.
+\citeauthor{DistinguishingNoiseFromChaos}~\ycite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
+\citeauthor{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach}~\ycite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
 With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
 Some preliminary results can already be found in the literature.
-\citeauthor{Larrondo2006Random}~\citeyear{Larrondo2006Random} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
-\citeauthor{De_Micco_2008}~\citeyear{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-\citeauthor{LiborInvisibleHand}~\citeyear{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
+\citeauthor{RandomNumberGeneratorsCausality}~\ycite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
+\citeauthor{De_Micco_2008}~\ycite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
+\citeauthor{LiborInvisibleHand}~\ycite{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
 
-This paper advances the state-of-the-art by providing confidence regions for points in the $H\times C$ plane for a diversity of situations of interest.
-%Such regions are obtained using a Monte Carlo approach.
-The input is a sequence of actual random observations generated by a physical procedure, and these regions are obtained by the application of PCA in space of Entropy-Complexity Plane.
-We emphasize that this study aims at providing confidence regions for sequences of the size that usually appear in the literature, not tests for randomness of PRNGs.
+Motivated by such works, in this paper we advance the state-of-the-art providing confidence regions for white noise points in the $H\times C$ plane.
+In the proposed approach, the input is a sequence of true random observations generated by a physical procedure, and the confidence regions are obtained by performing an orthogonal projection of the data onto a space of principal components analysis (PCA), thus eliminating the restrictions imposed by the curvilinear space of the Entropy-Complexity Plane.
+Our contributions can be summarized as follows:
+\begin{itemize}
+    \item Provide the first contribution in construction that confidence regions in Entropy-Complexity Plane.
+    \item Evaluate the discrimination power of these regions in the analysis of small random sequences generated by physical procedures and pseudorandom generators (PRNGs).
+\end{itemize}
 

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/Methodology.tex
Journal confidence regions

@@
-\section{Methodology}\label{Sec:Method}
+\section{Proposed Method}
 
-\subsection{The Bandt-Pompe Methodology}
+In this section, we formalize the task of building a confidence region in the Entropy-Complexity manifold.
+Then, we present our proposal to change space through the algorithm of the principal components analysis.
+Our goal is to find a latent space representative of the data, without the restrictions of a curvilinear space.
+Through this new representation of the data, we calculate empirical regions with different levels of confidence.
+Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
 
-Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real valued time series of length $T$, without ties. 
-As stated
-by~\citeauthor{Bandt2002Permutation}~\citeyear{Bandt2002Permutation}in their seminal work:  
-\begin{quote}
-``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
-$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
-\end{quote}
-Also, as stressed by these authors, 
-\begin{quote}
-``The corresponding symbol sequence must come 
-naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
-\end{quote}
+%\subsection{Problem Formalization}
 
-Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm Z}$) be the symmetric group of order $D!$ formed by all 
-possible permutation of order $D$, and the symbol component vector 
-${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
-Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
-with embedding dimension $D \geq 2$ ($D \in {\mathbbm Z}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm Z}$, also called ``embedding time''):
-\begin{equation} 
-\label{eq:time-delay}
-{\mathbf X}^{(D,\tau)}_t ~=~( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) \ ,
-\end{equation} 
-for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
-Then the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol vector ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
-This mapping should be defined in a way that preserves the desired relation between the elements 
-$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called motif) have to mapped to the same 
-${\bm \pi}^{(D)}$. 
-The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[a)]
-\item ordering the ranks of the $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
-       (\textit{Rank Permutation}) or,
-\item ordering the time indexes according to the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$  
-       (\textit{Chronological Index Permutation});
-\end{enumerate}
-       see details in \citeauthor{Traversaro2018Bandt}~\ycite{Traversaro2018Bandt}.
-Without loss of generality, in the following we will only use the latter.
+\subsection{Overall Framework}
 
-Consider, for instance, the time series $\mathcal X = (1.8, 1.2, 3.2, 4.8, 4.2, 4.5, 2.3, 3.7, 1.2, .5)$ depicted in Fig.~\ref{Fig:IntroBP}.
-Assume we are using patterns of length $D=5$ with unitary time lag $\tau=1$.
-The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(3.2, 4.8, 4.2, 4.5, 2.3)$, shown in black, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
-With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
-
-The dash-dot line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
-In this case, $\mathbf X_{1}^{(5,2)}= (1.8, 3.2, 4.2, 2.3, 1.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
+The structure of our proposal is shown in Fig.~\ref{fig:methodology}. 
+It consists of two steps:
+\begin{itemize}
+    \item \textbf{Empirical confidence region}: With the data present in a Euclidean plane, we can easily calculate empirical regions that involve the data with a certain level of confidence.
+    \item \textbf{Construction of a test statistic}: To measure the similarity of new data sequences with the empirical points, a test statistic was proposed. 
+    By acquiring a p-value less than 0.5, we can reject the null hypothesis, which states that such data belong to the empirical probability distribution used for the construction of the confidence region.
+\end{itemize}
 
@@
     \centering
-\includegraphics[width=.7\linewidth]{IntroBP}
-\caption{Illustration of the Bandt and Pompe coding}
-\label{Fig:IntroBP}
+    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
+    \caption{Outline of the methodology used for the construction of confidence regions.}
+    \label{fig:methodology}
 \end{figure}
 
-Once all symbols have been computed, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
-This is an estimate of the (unknown, in general) probability distribution function of these patterns.
-The next step into the characterization of the time series is computing descriptors from this histogram.
+\subsection{Empirical Confidence Regions}\label{confidenceRegions}
 
-The first descriptor is a measure of the disorder of the system.
-The most frequently used feature for this is the Normalized Shannon entropy, defined as
-\begin{equation}
-H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
-\end{equation}
-with the convention that terms in the summation for which $h(j)=0$ are null.
-This quantity is bounded in the unit interval, and is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
-
-Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
-In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citeauthor{LopezRuiz1995}~\citeyear{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
-They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-
-With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
-A time series can then be mapped into a point in the $H\times C$ plane.
-
-\subsection{The Entropy-Complexity Plane}
-
-We illustrate the use of the Entropy-Complexity ($H\times C$) with the following time series:
-\begin{itemize}
-\item Colored $k$-noise: white ($k=0$), $k=-1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $=5/2$, and $k=3$;
-\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
-\end{itemize}
-In all cases, we used $D=6$ and $\tau=1$.
-Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
-we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
-
-\begin{figure}[H]
-\centering
-	\subfloat[Logistic map $r=3.6$]{\includegraphics[width=.3\linewidth]{h36}}\quad
-	\subfloat[Logistic map $r=4$]{\includegraphics[width=.3\linewidth]{h4}}\quad
-	\subfloat[$f^{-3}$ noise]{\includegraphics[width=.3\linewidth]{h3}}\quad
-	\subfloat[$f^{-5/2}$ noise]{\includegraphics[width=.3\linewidth]{h25}}\quad
-	\subfloat[$f^{-2}$ noise]{\includegraphics[width=.3\linewidth]{h2}}\quad
-	\subfloat[$f^{-1.5}$ noise]{\includegraphics[width=.3\linewidth]{h15}}\quad
-	\subfloat[$f^{-1}$ noise]{\includegraphics[width=.3\linewidth]{h1}}\quad
-	\subfloat[$f^{-1/2}$ noise]{\includegraphics[width=.3\linewidth]{h05}}\quad
-	\subfloat[White noise]{\includegraphics[width=.3\linewidth]{h0}}
-	\caption{Patterns histograms of selected time series, with $D=6$ and $\tau=1$\label{fig:Histograms}}
-\end{figure}
-
-Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series and the points they were mapped onto.
-The points due to $f^{-k}$ noises appear joined by dotted segments.
-It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=\linewidth]{AllSystems}
-\caption{Eleven systems and their points in the $H\times C$ plane}\label{fig:AllSystems}
-\end{figure}
-
-Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=-1/2$, and pink ($k=1$) noises.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=\linewidth]{RightMostCorner}
-\caption{White Noise, $f^{-1/2}$ and $f^{-1}$ noise points}\label{fig:RightMostCorner}
-\end{figure}
-
-The focus of our study is the empirical distribution of points produced by White and selected $f^{-k}$ noises, with this, providing confidence regions in the $H\times C$ plane.
-In particular, we are interested in assessing pure randomness with this technique.
-
-\subsection{The $H\times C$ plane in the literature}
-
-Table~\ref{Tab:Literature} presents references in which the authors analyze time series of size $N$ and embedding dimension $D$.
-The authors also attest whether the time series is white noise or not, according to its $(h,c)$ feature.
-
-The following widely used non-chaotic algorithmic generators are analyzed:
-\begin{itemize}
-    \item[$-$] RNG available in Intel fortran compiler (FOR)
-    \item[$-$] RNG available in Borland C++ compiler (CCC)
-    \item[$-$] Matlab RAND function (MAT)
-    \item[$-$] Mother RNG, available in Marsaglia website~\cite{marsaglia1994yet} (MOT)
-    \item[$-$] Multiple with carry RNG (MWC)~\cite{marsaglia1994yet}
-    \item[$-$] Combo RNG (COM)~\cite{marsaglia1994yet}
-    \item[$-$] Lehmer RNG (LEH)~\cite{payne1969coding}
-    \item[$-$] Fractional Gaussian noise with $\alpha = 0$ (fGn)
-    \item[$-$] Fractional Brownian motion with $\alpha = 1.2$ (fBm)
-    \item[$-$] $f^{-k}$ noise with $k = 0$
-    \item[$-$] Linear Congruential Generator (LCG)~\cite{knuth1997sorting}
-\end{itemize}
-
-\begin{table}[H]
-    \caption{References which attest whether a time series of size $N$ is white noise according to its $(h,c)$ feature, and the empirical $p$-value of such hypothesis according to our results}
-    \label{Tab:Literature}
-    \centering
-    \begin{tabular}{llcccccc}
-    \toprule
-Reference & PRNG & $N$ & $D$ & $H$ & $C$ & Is white noise? & $p$-value\\ 
-\midrule
-\citeauthor{larrondo2002statistical} (\citeyear{larrondo2002statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no & NA\\
- &  FOR & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
- &  CCC & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
- &  MAT & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{Larrondo2006Random} (\citeyear{Larrondo2006Random}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MOT & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MWC & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{olivares2012contrasting} (\citeyear{olivares2012contrasting}) &  fGn & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.998$ & NA & yes & NA\\
- & fBm & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.993$ & NA & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.997$ & NA & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
-\bottomrule
-    \end{tabular}
-\end{table}
-
-%The mathematical theory of markets states that fairness is characterized by white noise.
-
-\subsection{True Random Numbers}
-
-\textcolor{red}{Gerador - Marcelo e Heitor}
-
-Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavihor. 
-Pseudo randomic results can be achieved by software in a deterministic way. 
-But, some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real world phenomena like cathodic radiation or atmospheric noise.
-In this study we used two sources of real random numbers. 
-The first is based on vacuum states to generate random quantum numbers described by \citeauthor{Wittmann2010generator}~(\citeyear{Wittmann2010generator}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-%Deixei as URLs pois não tenho o .bib ...
-
-%The colored $k$-noise mentioned in the previous section, also known as ``correlated noise'', is such that its power spectrum has shape $f^{-k}$.
-%When $k=0$, we have white noise, i.e., independent deviates.
-%The larger $k$ is, the more correlated the observations are.
-
-\subsection{Empirical Confidence Regions}
-
-As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible at this first moment.
+As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
 Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
@@
 In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-A classic proposal in these categories of problems is the principal component analysis (PCA) algorithm~\cite{wold1987principal}.
+A classic proposal in these categories of problems is the principal component analysis algorithm~\cite{wold1987principal}.
 
-Let $ {\mathcal P} = \{p_n \}_{n = 1}^{N} $ be a set of $N$ observations in the $H \times C$ plane, where ${p_n} = (h_n, c_n)$ corresponds to a time series.
-We apply a principal component analysis to these points and obtain $\{(u_n,v_n)\}_{n=1}^N$.
-This transformation yields uncorrelated observations in the $\Omega_1\times\Omega_2$ plane.
-
-We will find the empirical confidence regions on the $\Omega_1\times\Omega_2$ plane, and then they will be mapped back to the $H \times C$ plane.
-For simplicity, and without loss of generality, assume $N$ odd; we find a parallelepiped that contains 
-\SI{100}{\minusalphapercent} of the points in the $\Omega_1\times\Omega_2$ as
+Let ${\mathcal P} = \{p_n\}_{n = 1}^{N}$ be a set of $N$ observations in the $H \times C$ plane, where ${p_n} = (h_n, c_n)$ corresponds to a time series.
+We propose in this work the use of a latent space $\Omega_1 \times \Omega_2$ obtained by the PCA for the construction of empirical confidence regions, which hereinafter referred to we call HC-PCA regions.
+Let $\{(u_n, v_n)\}_{n = 1}^N$ uncorrelated observations obtained by the representation of ${\mathcal P}$ in the latent space $\Omega_1 \times \Omega_2$.
+For simplicity, and without loss of generality, assume $N$ odd; 
+in the proposed methodology, we find a parallelepiped that contains \SI{100}{\minusalphapercent} of the points in the $H \times C$ plane with the following steps:
+%We apply a principal component analysis to these points and obtain $\{(u_n,v_n)\}_{n=1}^N$.
+%This transformation yields uncorrelated observations in the $\Omega_1\times\Omega_2$ plane.
+%We will find the empirical confidence regions on the $\Omega_1\times\Omega_2$ plane, and then they will be mapped back to the $H \times C$ plane.
 \begin{enumerate}
@@
     \item The top and bottom bounds of the box are the minimum and maximum values of the second principal component of the points whose first principal component is at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$; denote these values $v_{\min}$ and $v_{\max}$, respectively.
-    %\item The lower-left and upper-right corners of the box are $(u_{r_{[N\alpha/2]}}, v_{\min})$, and $(u_{r_{[N\alpha/2]}},v_{\max})$, respectively.
     \item The corners of the box are 
@@
     $(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-    %\item Apply the inverse PCA transform to these corners obtaining $(h_1^{\SI{100}{\minusalphapercent}}, c_1^{\SI{100}{\minusalphapercent}})$, $(h_2^{\SI{100}{\minusalphapercent}}, c_2^{\SI{100}{\minusalphapercent}})$, $(h_1^{\SI{100}{\alphapercent}}, c_1^{\SI{100}{\alphapercent}})$ and $(h_2^{\SI{100}{\alphapercent}},c_2^{\SI{100}{\alphapercent}})$.
     \item Apply the inverse PCA transform to these corners obtaining $(h_{v_1}, c_{v_1})$, $(h_{v_2}, h_{v_2})$, $(h_{v_3}, c_{v_3})$ and $(h_{v_4},c_{v_4})$.
 \end{enumerate}
-These steps are also depicted in Fig.~\ref{fig:methodology}.
+The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/methodology.pdf}
-    \caption{Outline of the methodology used for the construction of confidence regions.}
-    \label{fig:methodology}
-\end{figure}
+\subsection{Construction of a test statistic}\label{test}
 
-\begin{sidewaystable}
-    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{5 e4}$ in the $H \times C$ plane obtained by the proposed methodology}
-    \label{Tab:Regions50k}
-    \centering
-    \begin{tabular}{cccccc}
-    \toprule
-Confidence Regions & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
-\midrule
-\SI{90}{\percent} & 3 & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$\\
-\SI{95}{\percent} & 3 & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$\\
-\SI{99}{\percent} & 3 & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$\\
-\SI{99.9}{\percent} & 3 & $(0.9998625, 0.0001361)$ & $(0.9998622, 0.0001358)$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 4 & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9998075, 0.0002508)$ & $(0.9998087, 0.0002524)$\\
-\SI{95}{\percent} & 4 & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9998506, 0.0001942)$ & $(0.9998518, 0.0001958)$\\
-\SI{99}{\percent} & 4 & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9998756, 0.0001615)$ & $(0.9998768, 0.000163)$\\
-\SI{99.9}{\percent} & 4 & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ & $(0.9998889, 0.000144)$ & $(0.9998901, 0.0001456)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 5 & $(0.9998172, 0.0003232)$ & $(0.9998194, 0.0003273)$ & $(0.9994812, 0.0009246)$ & $(0.9994834, 0.0009286)$\\
-\SI{95}{\percent} & 5 & $(0.9998259, 0.0003075)$ & $(0.9998282, 0.0003116)$ & $(0.9996371, 0.0006455)$ & $(0.9996394, 0.0006495)$\\
-\SI{99}{\percent} & 5 & $(0.9998428, 0.0002774)$ & $(0.999845, 0.0002814)$ & $(0.9996703, 0.0005862)$ & $(0.9996725, 0.0005901)$\\
-\SI{99.9}{\percent} & 5 & $(0.9998573, 0.0002517)$ & $(0.9998593, 0.0002553)$ & $(0.9996884, 0.000554)$ & $(0.9996904, 0.0005576)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 6 & $(0.9990169, 0.002336)$ & $(0.9990249, 0.0023554)$ & $(0.9978983, 0.0050219)$ & $(0.9979064, 0.0050413)$\\
-\SI{95}{\percent} & 6 & $(0.9990368, 0.002288)$ & $(0.9990449, 0.0023074)$ & $(0.998714, 0.0030633)$ & $(0.998722, 0.0030827)$\\
-\SI{99}{\percent} & 6 & $(0.9990736, 0.0021997)$ & $(0.9990817, 0.0022191)$ & $(0.998765, 0.0029407)$ & $(0.9987731, 0.0029601)$\\
-\SI{99.9}{\percent} & 6 & $(0.9991069, 0.0021197)$ & $(0.999115, 0.0021392)$ & $(0.9987884, 0.0028845)$ & $(0.9987965, 0.0029039)$\\
-\bottomrule
-    \end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-    \caption{Empirical confidence regions for time series of length $T = \num[scientific-notation=true]{1 e3}$ in the $H \times C$ plane obtained by the proposed methodology}
-    \label{Tab:Regions1000}
-    \centering
-    \begin{tabular}{cccccc}
-    \toprule
-Confidence Region & $D$ & $(h_{v_1}, c_{v_1})$ & $(h_{v_2}, h_{v_2})$ & $(h_{v_3}, c_{v_3})$ & $(h_{v_4},c_{v_4})$\\ 
-\midrule
-\SI{90}{\percent} & 3 & $(0.9973334, 0.0025601)$ & $(0.9974047, 0.0026304)$ & $(0.9999497, 0)$ & $(1, \num[scientific-notation=true]{5.17e-05})$\\
-\SI{95}{\percent} & 3 & $(0.9967311, 0.0031343)$ & $(0.9968219, 0.0032238)$ & $(0.9999398, 0)$ & $(1, \num[scientific-notation=true]{6.12e-05})$\\
-\SI{99}{\percent} & 3 & $(0.9953009, 0.0045054)$ & $(0.9954349, 0.0046375)$ & $(0.9999203, 0)$ & $(1, \num[scientific-notation=true]{8.45e-05})$\\
-\SI{99.9}{\percent} & 3 & $(0.9931825, 0.0065387)$ & $(0.9933704, 0.006724)$ & $(0.9998925, 0)$ & $(1, 0.0001104)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 4 & $(0.994364, 0.0081246)$ & $(0.9939234, 0.0075452)$ & $(0.9994791, 0.0013982)$ & $(0.9990385, 0.0008188)$\\
-\SI{95}{\percent} & 4 & $(0.9937138, 0.0089796)$ & $(0.9932534, 0.0083741)$ & $(0.9991609, 0.0018166)$ & $(0.9987005, 0.0012111)$\\
-\SI{99}{\percent} & 4 & $(0.9922575, 0.0108947)$ & $(0.9917308, 0.0102022)$ & $(0.9987924, 0.0023012)$ & $(0.9982658, 0.0016087)$\\
-\SI{99.9}{\percent} & 4 & $(0.9902578, 0.0135243)$ & $(0.9897312, 0.0128318)$ & $(0.9985727, 0.0025901)$ & $(0.9980461, 0.0018976)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 5 & $(0.9811818, 0.0321294)$ & $(0.9827429, 0.0350291)$ & $(0.9919707, 0.0120896)$ & $(0.9935319, 0.0149893)$\\
-\SI{95}{\percent} & 5 & $(0.9801289, 0.0340045)$ & $(0.9817117, 0.0369446)$ & $(0.9909376, 0.0139279)$ & $(0.9925204, 0.016868)$\\
-\SI{99}{\percent} & 5 & $(0.977917, 0.0377295)$ & $(0.9796031, 0.0408613)$ & $(0.9898161, 0.0156277)$ & $(0.9915021, 0.0187595)$\\
-\SI{99.9}{\percent} & 5 & $(0.9753326, 0.0425299)$ & $(0.9770187, 0.0456617)$ & $(0.9892599, 0.0166608)$ & $(0.9909459, 0.0197926)$\\
-\cmidrule(lr){1-6}
-\SI{90}{\percent} & 6 & $(0.9121895, 0.2201993)$ & $(0.9146048, 0.2260776)$ & $(0.9443868, 0.1418373)$ & $(0.9468021, 0.1477156)$\\
-\SI{95}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9419202, 0.1476904)$ & $(0.9443663, 0.1536439)$\\
-\SI{99}{\percent} & 6 & $(0.9105951, 0.2239294)$ & $(0.9130413, 0.2298829)$ & $(0.9396577, 0.1531967)$ & $(0.9421039, 0.1591502)$\\
-\SI{99.9}{\percent} & 6 & $(0.9077672, 0.2305874)$ & $(0.9102595, 0.2366531)$ & $(0.9383611, 0.1561279)$ & $(0.9408534, 0.1621937)$\\
-\bottomrule
-    \end{tabular}
-\end{sidewaystable}
+Using the method of construction of confidence regions described in subsection~\ref{confidenceRegions} in $M$ reference points in the $H \times C$ plane produced by sequences obtained from true-random generators of length $T$ and embedding dimension $D$, we formulate a hypothesis test that we hereinafter referred the HC-PCA test.
+Whether $\bm x'$ is a sequence of length $T$ and embedding dimension $D$, the  main idea of the HC-PCA test is based on the following null hypothesis:
+\begin{description}
+    \item[$\mathcal{H}_0$]: $\bm x'$ consists of a sequence of independent uniform random variables.
+\end{description}
+The empirical $p$-value of $\bm x'$ with respect to the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
+Therefore, it can be achieved by the following steps:
+\begin{enumerate}
+    \item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
+    \item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
+    \item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
+\end{enumerate}
+Thus, we can verify that:
+\begin{itemize}
+    \item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the the point produced by the emblematic sequence, that is, point whose first principal component is the median of the $M$ reference points, and
+    \item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
+\end{itemize}
+Assuming the critical value $\alpha = 0.05$, we obtain:
+\begin{equation*}
+    p-\text{value} \geq \alpha, \text{ the null hypothesis not can be reject}.
+\end{equation*}

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/Results.tex
Journal confidence regions

@@
 
-In this section, we describe the descriptive analysis of representative points in relation to the confidence regions, as well as revisiting hypotheses of white noise present in the literature.
-Empirical experiments on the behavior of an emblematic sample when injecting correlation structures are also presented.
+\subsection{Descriptive analysis of empirical confidence regions}
 
-We employed the following factors in this study:
-\begin{itemize}
-\item Time series length $T\in\mathcal T=\{10^3, \num[scientific-notation=true]{5 e4}\}$,
-\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$,and
-\item Exponent of the $f^{-k}$ noise $k\in\mathcal K=\{0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.5, 1,\\ 1.5, 2, 2.5, 3\}$.
-\item Time delay $\tau=\{1,10,30,50\}$.
-\end{itemize}
-%There were no significant differences in data in repeated experiments with time delays $\tau=\{1,10,30,50\}$. 
-%Therefore, we obtained $1000$ independent series for each point in the factors set $\mathcal T\times \mathcal D\times \mathcal K$.
-
-The data generation and analyses were performed using the \texttt R platform \cite{Rmanual} v.~3.6.3.
-We used the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
-
-\subsection{Descriptive analysis of representative data}
-
-For the construction of the confidence regions presented in this work we use:
-\begin{itemize}
-    \item An set of $104596$ points in the $H \times C$ plane, referring to sequences of length $T = 1000$, for each combination of the factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$, and
-    \item  An another set of $2093$ points in the $H \times C$ plane, referring to sequences of length $T = 50000$, for each combination of factors $\mathcal T \times \mathcal D \times \mathcal{\tau}$.
-\end{itemize}
-Since the results involving the variation of the time delay parameter did not show a significant difference in repeated experiments, we don't consider it as a determinating factor during the execution of the algorithm.
-On the other hand, we consider two determining variables during the generation of such sub-spaces: the embedding dimension and the length of the sequence.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/Points-PDF.png}
-    \caption{White noise samples considered during the construction of the proposed confidence regions.}
-    \label{fig:white-noise}
-\end{figure}
-
-In Fig.~\ref{fig:HC-PCA} we show the results obtained for $T = 50000$ in the scenarios of $D = 3$ and $D = 6$ in the new space defined by the PCA, together with the quantiles of $90\%$, $95\%$, $99\%$ and $99.9\%$.
+The regions used as a reference in this work are obtained through true random sequences, where we extract the empirical distribution of white noises in the Entropy-Complexity plane.
+In Fig.~\ref{fig:HC-PCA} we show the results obtained for $T = 50000$ in the scenarios of $D = 3$ and $D = 6$ in the new space defined by the PCA, together with the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
 We also show the projection of the $H \times C$ plane limits in this new representation space, as well as identifying the median of each data set, the latter being represented as the red dots present in the graphs.
 
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D6N50k.png}
-	\caption{}
+	\caption{Representation of truly random sequences with length $T = 50.000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
 	\label{fig:HC-PCA}
@@
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 
-%\textcolor{red}{An\'alise descritiva: alguns pontos de $\Theta$ representativos:} 
 \subsection{Testing White Noise in the confidence regions}
 
-To test the efficiency of the confidence region calculated, we tested its applicability on a set of truly random data generated physically not used by the algorithm during its construction. 
+To analyze the efficiency of the confidence region calculated, we tested its applicability on a set of true random data generated physically not used by the algorithm during its construction. 
 The results can be seen in Fig.~\ref{fig:RNG}.
 
-For small series, $N = 1000$, and $D = 3$ we managed to maintain exactly $99\%$ of the data in the confidence region of the same value, and as the dimension increased reach $96\%$ of the points.
-On the other hand, there was a very large loss of points located in the region with $95\%$ confidence as the dimension increased.
+For small series, $T = 1000$, and $D = 3$ we managed to maintain exactly $\SI{99}{\percent}$ of the data in the confidence region of the same value, and as the dimension increased reach $\SI{96}{\percent}$ of the points.
+On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
 A reasonable explanation for this event is given in the choice of the parameter itself.
 It is known by definition that $D! << N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-For larger series, $N = 50000$, although we observed a small drop in the percentage of data present in the region with $99\%$ confidence, there was a significant increase in points in the region with $95\%$ confidence, showing between $90\%$ and $88\%$ of the points when we vary the embedding dimension.
+For larger series, $T = 50000$, although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
 
-\begin{table}[H]
-	\centering
-	\caption{Results found it for samples of true random numbers}
-	\label{tab:result1}
-	\begin{tabular}{c*{3}rr}
-		\toprule
-		Algorithm & \multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		\cmidrule(lr){5-5}
-		True-Random & 1000 & 3 & $0.98$ & $1$\\
-		&  & 4 & $0.98$ & $0.96$\\
-		&  & 5 & $1$ & $0.94$\\
-		&  & 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-5}
-		True-Random & 50000 & 3 & $0.97$ & $0.96$\\
-		&  & 4 & $0.94$ & $0.95$\\
-		&  & 5 & $0.97$ & $0.96$\\
-		&  & 6 & $0.98$ & $0.99$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
     \includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-    \caption{White Noise in HC Plane}
+    \caption{Results of the analysis behavior of true random noises in the regions of confidence built.}
     \label{fig:RNG}
@@
 
-\begin{comment}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/fk-descriptive-analysis.pdf}
-    \caption{$f^{-k}$ noises in HC Plane}
-    \label{fig:fk}
-\end{figure}
-
-\end{comment}
-
-%\textcolor{red}{Justificar o tipo de an\'alise: regressão? bivariada clássica? não-paramétrica?}
-
-%\textcolor{red}{Regi\~oes de confian\c ca}
-
-\begin{comment}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/N50kBoxes95.png}
-    \caption{}
-    \label{fig:region95}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{Figures/N50kBoxes99.png}
-    \caption{}
-    \label{fig:region99}
-\end{figure}
-
-\end{comment}
-
-%\subsection{Analysis of the Empirical Confidence Regions}
-
-\subsection{Analyzing of the Empirical Confidence Regions Injecting Correlation}
+\subsection{Analyzing Robustness to Correlation Structures}
 % k=0 white
@@
     \includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}
-    \caption{Correlation Structure Analysis
-    }
+    \caption{Correlation Structure Analysis}
     \label{fig:correlation}
 \end{figure}
-%In the following, we will present how the $(h,c)$ point of the ``emblematic'' sequence alters when injecting temporal correlation (by means of the $f^{-k}$ model).
-%, and determinism (by a convex combination with a sine function).
-%The $f^{-k}$: simulation
-
-\begin{comment}
-\subsection{Injecting Determinism}
-Consider the emblematic sequence $\bm x=(x_1,\dots,x_N)$, which is mapped onto the point $(h,c)$.
-In order to inject determinism in this sequence, we will analyze the effect of $\xi\in[0,1]$, by checking how the point $\big(h,c\big)(\xi)$ evolves in the $(H,C)$ plane, in which
-\begin{equation}
-\bm x'(j) = \xi \sin(10 \pi j/N) +(1-\xi) x_j.    
-\label{Eq:DeterminismXi}
-\end{equation}
-With this, when $\xi=0$ we have the original sequence $\bm x$ and, thus, the original emblematic point $(h,c)$;
-when $\xi=1$, we have pure determinism: five sine functions.
-\end{comment}
 
@@
 
-\begin{table}[H]
+In this section, we evaluate the quality of the confidence regions preceded by HC-PCA with sequences of previously analyze generators in the literature with the Entropy-Complexity plane.
+For this, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator present in table~\ref{Tab:Literature} and calculated the respective p-values for each configuration of $D = \{3, 4, 5, 6\}$.
+The results obtained can be seen in table~\ref{Tab:LiteratureComparations}, where we categorize the sets of sequences among those that did not reject (NR) the null hypothesis presented in the HC-PCA test and those that rejected (R).
+
+Performing a comparative analysis of the results produced by tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we can see that the proposed methodology of confidence regions can capture the random dynamics of the sequences produced by most of the analyzed generators well, although in our experiments we consider only short sequences.
+
+However, two results deserve special attention: the sequences produced by the generators fBm and Combo RNG.
+The first one, although it was not rejected by the analysis of~\cite{olivares2012contrasting}, presented low p-values, due to the characteristic point in the $H \times C$ plane where its sequences belong.
+For the case analyzed in~\cite{olivares2012contrasting} with $D = 6$, we verified that the produced sequences present an average of $H = 0.997$, therefore they do not belong to the empirical $\SI{95}{\percent}$ confidence region produced by HC-PCA.
+Analyzing the results produced by the Combo RNG, we can verify that only for $D = 3$ the proposed method can characterize the sequences produced as random.
+This is due to the fact that by presenting higher dimension values, we were able to analyze a greater number of ordinal patterns, which may not be presented in their entirety in short sequences.
+
+\begin{table}
+    \caption{Results of the sequences generated by the main PRNGs in the literature. 
+    The analyzed sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+    \label{Tab:LiteratureComparations}
     \centering
-	\caption{Points inside the confidence regions}
-	\label{tab:resultFinal}
-	\begin{tabular}{c*{3}r}
+    \begin{tabular}{cccc}
     \toprule
-		Algorithm & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
 		\cmidrule(lr){1-1}
@@
 		\cmidrule(lr){4-4}
-		Wichmann-Hill & 3 & 0.97 & 0.96\\ 
-		Wichmann-Hill & 4 & 0.9675 & 0.9675\\ 
-		Wichmann-Hill & 5 & 0.9725 & 0.965\\ 
-		Wichmann-Hill & 6 & 0.97 & 0.97\\ 
-		%\cmidrule(lr){1-4}
-		%Marsaglia-Multicarry & 3 & 0.97 & 0.9625\\ 
-		%Marsaglia-Multicarry & 4 & 0.97 & 0.9825\\ 
-		%Marsaglia-Multicarry & 5 & 0.9625 & 0.9625\\ 
-		%Marsaglia-Multicarry & 6 & 0.9675 & 0.9625\\ 
+        MOT & 3 & 0.305 & NR\\
+		& 4 & 0.572 & NR\\ 
+		& 5 & 0.455 & NR\\ 
+		& 6 & 0.508 & NR\\ 
 		\cmidrule(lr){1-4}
-		Super-Duper & 3 & 0.9675 & 0.975\\ 
-		Super-Duper & 4 & 0.9775 & 0.9725\\ 
-		Super-Duper & 5 & 0.9675 & 0.985\\ 
-		Super-Duper & 6 & 0.9825 & 0.965\\ 
+        MWC & 3 & 0.501 & NR\\
+        & 4 & 0.477 & NR\\ 
+        & 5 & 0.496 & NR\\ 
+        & 6 & 0.496 & NR\\ 
 		\cmidrule(lr){1-4}
-		Knuth-TAOCP-2002 & 3 & 0.9775 & 0.9625\\ 
-		Knuth-TAOCP-2002 & 4 & 0.965 & 0.98\\ 
-		Knuth-TAOCP-2002 & 5 & 0.9625 & 0.9825\\ 
-		Knuth-TAOCP-2002 & 6 & 0.9725 & 0.96\\  
+		COM & 3 & 0.123 & NR\\
+		& 4 & 0.002 & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
 		\cmidrule(lr){1-4}
-		Knuth-TAOCP & 3 & 0.975 & 0.9775\\ 
-		Knuth-TAOCP & 4 & 0.965 & 0.9725\\ 
-		Knuth-TAOCP & 5 & 0.9875 & 0.985\\ 
-		Knuth-TAOCP & 6 & 0.9725 & 0.975\\ 
-		\cmidrule(lr){1-4}
-		LEcuyer-CMRG & 3 & 0.98 & 0.98\\ 
-		LEcuyer-CMRG & 4 & 0.9675 & 0.9725\\ 
-		LEcuyer-CMRG & 5 & 0.965 & 0.9725\\ 
-		LEcuyer-CMRG & 6 & 0.9625 & 0.97\\ 
-		\cmidrule(lr){1-4}
-		pcg64 & 3 & 0.97 & 0.9675\\ 
-		pcg64 & 4 & 0.97 & 0.97\\ 
-		pcg64 & 5 & 0.9775 & 0.9625\\ 
-		pcg64 & 6 & 0.9575 & 0.9575\\ 
-		\cmidrule(lr){1-4}
-		Threefry & 3 & 0.9625 & 0.97\\ 
-		Threefry & 4 & 0.975 & 0.97\\ 
-		Threefry & 5 & 0.96 & 0.9625\\ 
-		Threefry & 6 & 0.965 & 0.955\\ 
-		\cmidrule(lr){1-4}
-		Xoroshiro128+ & 3 & 0.975 & 0.9825\\ 
-		Xoroshiro128+ & 4 & 0.995 & 0.9825\\ 
-		Xoroshiro128+ & 5 & 0.98 & 0.9725\\ 
-		Xoroshiro128+ & 6 & 0.9725 & 0.955\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 1 & 0.75\\
-		MWC & 4 & 0.25 & 0.25\\ 
-		MWC & 5 & 1 & 1\\ 
-		MWC & 6 & 0 & 0\\ 
-		\cmidrule(lr){1-4}
-		MOT & 3 & 1 & 1\\ 
-		MOT & 4 & 1 & 1\\ 
-		MOT & 5 & 1 & 1\\ 
-		MOT & 6 & 0.75 & 1\\ 
+		LEH & 3 & 0.531 & NR\\
+		& 4 & 0.515 & NR\\ 
+		& 5 & 0.495 & NR\\ 
+		& 6 & 0.501 & NR\\ 
     \bottomrule
     \end{tabular}
-	\begin{tabular}{c*{3}r}
+    \begin{tabular}{|cccc}
     \toprule
-		Algorithm & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
 		\cmidrule(lr){1-1}
@@
 		\cmidrule(lr){4-4}
-		Xoshiro256+ (FOR) & 3 & 0.98 & 0.98\\ 
-		Xoshiro256+ (FOR) & 4 & 0.9675 & 0.965\\ 
-		Xoshiro256+ (FOR) & 5 & 0.9525 & 0.96\\ 
-		Xoshiro256+ (FOR) & 6 & 0.9775 & 0.975\\
+		fGn & 3 & 0.521 & NR\\
+		& 4 & 0.519 & NR\\ 
+		& 5 & 0.498 & NR\\ 
+		& 6 & 0.470 & NR\\
 		\cmidrule(lr){1-4}
-		Mersenne-Twister & 3 & 0.9725 & 0.97\\ 
-		Mersenne-Twister & 4 & 0.98 & 0.97\\ 
-		Mersenne-Twister & 5 & 0.9725 & 0.9775\\ 
-		Mersenne-Twister & 6 & 0.975 & 0.9725\\ 
+		fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
 		\cmidrule(lr){1-4}
-		Randu & 3 & 0.2275 & 0.42\\ 
-		Randu & 4 & 0 & 0\\ 
-		Randu & 5 & 0 & 0\\ 
-		Randu & 6 & 0 & 0\\ 
+		$f^{-k}$ & 3 & 0.482 & NR\\
+		& 4 & 0.520 & NR\\ 
+		& 5 & 0.513 & NR\\ 
+		& 6 & 0.508 & NR\\
 		\cmidrule(lr){1-4}
-		LCG & 3 & 0.07 & 0.09\\ 
-		LCG & 4 & 0 & 0\\ 
-		LCG & 5 & 0 & 0\\ 
-		LCG & 6 & 0 & 0\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.9825 & 0.98\\ 
-		LEH & 4 & 0.9675 & 0.9775\\ 
-		LEH & 5 & 0.9725 & 0.9775\\ 
-		LEH & 6 & 0.9775 & 0.9825\\ 
-		\cmidrule(lr){1-4}
-		fBm & 3 & 0 & 0\\ 
-		fBm & 4 & 0 & 0\\ 
-		fBm & 5 & 0 & 0\\ 
-		fBm & 6 & 0 & 0\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.9722 & 0.9874\\ 
-		fGn & 4 & 0.9798 & 0.9773\\ 
-		fGn & 5 & 0.9646 & 0.9773\\ 
-		fGn & 6 & 0.9722 & 0.9545\\
-		\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.9525 & 0.96\\ 
-		$f^{-k}$ & 4 & 0.975 & 0.9725\\ 
-		$f^{-k}$ & 5 & 0.98 & 0.9675\\ 
-		$f^{-k}$ & 6 & 0.9775 & 0.975\\
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.25 & 0.5\\ 
-		COM & 4 & 0 & 0\\ 
-		COM & 5 & 0 & 0\\ 
-		COM & 6 & 0 & 0\\ 
-		\cmidrule(lr){1-4}
-		CCC & 3 & 0 & 0\\ 
-		CCC & 4 & 0 & 0\\ 
-		CCC & 5 & 0 & 0\\ 
-		CCC & 6 & 0 & 0\\
+		LCG & 3 & 0.009 & R\\ 
+		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
     \bottomrule
@@
 \end{table}
+
+\begin{comment}
+\begin{table}
+    \caption{Results of literature PRNG references for time series of size $T = 50000$}
+    \label{Tab:LiteratureComparations}
+    \centering
+    \begin{tabular}{c*{3}rcccc}
+    \toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}} & 
+		$p$-value &
+		HC-PCA & 
+		Literature Results & 
+		TestU01\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		\cmidrule(lr){5-5}
+		\cmidrule(lr){6-6}
+		\cmidrule(lr){7-7}
+		\cmidrule(lr){8-8}
+        MOT & 3 & 1 & 1 & 0.305 & NR & NR & \\
+		& 4 & 1 & 1 & 0.572  & & & \\ 
+		& 5 & 1 & 1 & 0.455 & & & \\ 
+		& 6 & 0.75 & 1 & 0.508 & & & \\ 
+		\cmidrule(lr){1-8}
+        MWC & 3 & 0.97 & 0.9625 & 0.501  & NR & NR & R\\
+        & 4 & 0.97 & 0.9825 & 0.477 & & & \\ 
+        & 5 & 0.9625 & 0.9625 & 0.496 & & & \\ 
+        & 6 & 0.9675 & 0.9625 & 0.496  & & & \\ 
+		\cmidrule(lr){1-8}
+		COM & 3 & 0.25 & 0.5 & 0.123 & NR & NR & \\
+		& 4 & 0 & 0 & 0.002 & R & & \\ 
+		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16}  & & & \\ 
+		\cmidrule(lr){1-8}
+		LEH & 3 & 0.9825 & 0.98 & 0.531 & NR & NR & NR\\
+		& 4 & 0.9675 & 0.9775 &  0.515  & & & \\ 
+		& 5 & 0.9725 & 0.9775 &  0.495 & & & \\ 
+		& 6 & 0.9775 & 0.9825 & 0.501 & & & \\ 
+		\cmidrule(lr){1-8}
+		fGn & 3 & 0.9722 & 0.9874 & 0.521 & NR & NR & \\
+		& 4 & 0.9798 & 0.9773 & 0.519 & & & \\ 
+		& 5 & 0.9646 & 0.9773 & 0.498 & & & \\ 
+		& 6 & 0.9722 & 0.9545 & 0.470 & & & \\
+		\cmidrule(lr){1-8}
+		fBm & 3 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & R & NR & \\ 
+		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		\cmidrule(lr){1-8}
+		$f^{-k}$ & 3 & 0.9525 & 0.96 & 0.482 & NR & NR &\\
+		& 4 & 0.975 & 0.9725 & 0.520 & & & \\ 
+		& 5 & 0.98 & 0.9675 & 0.513 & & & \\ 
+		& 6 & 0.9775 & 0.975 & 0.508 & & & \\
+		\cmidrule(lr){1-8}
+		LCG & 3 & 0.07 & 0.09 & 0.009 & R & R & R \\ 
+		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
+\end{comment}
+
+\begin{comment}
+\begin{table}
+	\centering
+	\caption{Results of analysis of PRNGs with the proposed methodology}
+	\label{tab:resultFinal}
+	\begin{tabular}{c*{3}rccc}
+		\toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		\multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}} &  
+		$p$-value &
+		HC-PCA &   
+		TestU01\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		\cmidrule(lr){5-5}
+		\cmidrule(lr){6-6}
+		\cmidrule(lr){7-7}
+		Wichmann-Hill & 3 & 0.97 & 0.96 & 0.478 & NR & R\\ 
+		& 4 & 0.9675 & 0.9675 & 0.513 & & \\ 
+		& 5 & 0.9725 & 0.965 & 0.501 & & \\ 
+		& 6 & 0.97 & 0.97 & 0.491 & & \\ 
+		\cmidrule(lr){1-7}
+		Super-Duper & 3 & 0.9675 & 0.975 & 0.496 & NR & R\\
+		& 4 & 0.9775 & 0.9725 & 0.512 & &\\ 
+		& 5 & 0.9675 & 0.985 & 0.525 & &\\ 
+		& 6 & 0.9825 & 0.965 & 0.507 & &\\ 
+		\cmidrule(lr){1-7}
+		Knuth-TAOCP-2002 & 3 & 0.9775 & 0.9625 & 0.513 & NR & NR\\ 
+		& 4 & 0.965 & 0.98 & 0.481 & &\\ 
+		& 5 & 0.9625 & 0.9825 & 0.494 & &\\ 
+		& 6 & 0.9725 & 0.96 & 0.479 & &\\  
+		\cmidrule(lr){1-7}
+		Knuth-TAOCP & 3 & 0.975 & 0.9775 & 0.480 & NR & NR\\
+		& 4 & 0.965 & 0.9725 & 0.519 & &\\ 
+		& 5 & 0.9875 & 0.985 & 0.531 & &\\ 
+		& 6 & 0.9725 & 0.975 & 0.515 & &\\ 
+		\cmidrule(lr){1-7}
+		LEcuyer-CMRG & 3 & 0.98 & 0.98 & 0.505 & NR & NR\\ 
+		& 4 & 0.9675 & 0.9725 & 0.490 & &\\ 
+		& 5 & 0.965 & 0.9725 & 0.512 & &\\ 
+		& 6 & 0.9625 & 0.97 & 0.524 & &\\ 
+		\cmidrule(lr){1-7}
+		Mersenne-Twister & 3 & 0.9725 & 0.97 & 0.506 & NR & NR\\ 
+		& 4 & 0.98 & 0.97 & 0.499 & &\\ 
+		& 5 & 0.9725 & 0.9775 & 0.524 & &\\ 
+		& 6 & 0.975 & 0.9725 & 0.502 & &\\ 
+		\cmidrule(lr){1-7}
+		Randu & 3 & 0.2275 & 0.42 & 0.032 & R & R\\ 
+		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\ 
+		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\ 
+		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\  
+		\cmidrule(lr){1-7}
+		pcg64 & 3 & 0.97 & 0.9675 & 0.510 & NR & NR\\
+		& 4 & 0.97 & 0.97 & 0.503 & &\\ 
+		& 5 & 0.9775 & 0.9625 & 0.508 & &\\ 
+		& 6 & 0.9575 & 0.9575 & 0.502 & &\\ 
+		\cmidrule(lr){1-7}
+		Threefry & 3 & 0.9625 & 0.97 & 0.491 & NR & NR\\ 
+		& 4 & 0.975 & 0.97 & 0.506 & &\\ 
+		& 5 & 0.96 & 0.9625 & 0.506 & &\\ 
+		& 6 & 0.965 & 0.955 & 0.473 & &\\ 
+		\cmidrule(lr){1-7}
+		Xoroshiro128+ & 3 & 0.975 & 0.9825 & 0.501 & NR & R\\ 
+		& 4 & 0.995 & 0.9825 & 0.493 & &\\ 
+		& 5 & 0.98 & 0.9725 & 0.503 & &\\ 
+		& 6 & 0.9725 & 0.955 & 0.513 & &\\
+		\cmidrule(lr){1-7}
+		Xoshiro256+ & 3 & 0.98 & 0.98 & 0.502 & NR & NR\\ 
+		& 4 & 0.9675 & 0.965 & 0.489 & &\\ 
+		& 5 & 0.9525 & 0.96 & 0.492 & &\\ 
+		& 6 & 0.9775 & 0.975 & 0.513 & &\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+\end{comment}

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex
Journal confidence regions

\section{Entropy-Complexity plane in the literature}

The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cites{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cites{larrondo2002statistical, gonzalez2005statistical}.

Table~\ref{Tab:Literature} presents a summary of the main works in the literature that perform analysis of non-chaotic algorithmic generators, according to their features $(h, c)$.
For this, we also provide the length $T$ and embedding dimension $D$ applied in the analysis of the time series.
The following algorithmic generators were analyzed:
\begin{itemize}
    %\item[$-$] RNG available in Intel fortran compiler (FOR)
    %\item[$-$] RNG available in Borland C++ compiler (CCC)
    %\item[$-$] Matlab RAND function (MAT)
    \item Mother RNG, available in Marsaglia website~\cite{marsaglia1994yet} (MOT);
    \item Multiple with carry RNG (MWC)~\cite{marsaglia1994yet};
    \item Combo RNG (COM)~\cite{marsaglia1994yet};
    \item Lehmer RNG (LEH)~\cite{payne1969coding};
    \item Fractional Gaussian noise with $\alpha = 0$ (fGn);
    \item Fractional Brownian motion with $\alpha = 1.2$ (fBm);
    \item $f^{-k}$ noise with $k = 0$;
    \item Linear Congruential Generator (LCG)~\cite{knuth1997sorting}.
\end{itemize}

\begin{table}[H]
    \caption{Result of the main works of white noise sequences analysis in the $H \times C$ plane.}
    \label{Tab:Literature}
    \centering
    \begin{tabular}{llcccccc}
    \toprule
Reference & PRNG & $T$ & $D$ & $H$ & $C$ & Is white noise? & $p$-value\\ 
\midrule
\citeauthor{larrondo2002statistical} (\citeyear{larrondo2002statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no & NA\\
%&  FOR & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
%&  CCC & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
%&  MAT & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
\cmidrule(lr){1-8}
\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
 &  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
 &  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{RandomNumberGeneratorsCausality} (\citeyear{RandomNumberGeneratorsCausality}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
 &  MOT & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
 &  MWC & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{olivares2012contrasting} (\citeyear{olivares2012contrasting}) &  fGn & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.998$ & NA & yes & NA\\
 & fBm & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.993$ & NA & yes & NA\\
 & $f^{-k}$ & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.997$ & NA & yes & NA\\
\cmidrule(lr){1-8}
\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no & NA\\
\cmidrule(lr){1-8}
\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
 & $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
\bottomrule
    \end{tabular}
\end{table}

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Conversa.tex
Journal confidence regions

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amsthm,amssymb,bm,bbm}

\begin{document}

Empirical $p$-value of the sequence $\bm x'$ of length $N$ and embedding dimension $D$:
\begin{description}
    \item[Input: a sequence $\bm x'$ of length $N$ and  embedding dimension $D$]
    \item[Setup: $M$ reference points in the $H \times C$ plane produced by sequences of length $N$ and embedding dimension $D$]
    \begin{enumerate}
        \item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$
        \item Compute $b_{N,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points
            \begin{itemize}
                \item the smallest $b_{N,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the the point produced by the emblematic sequence;
                \item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points
            \end{itemize}
        \item The empirical $p$-value of $\bm x'$ wrt the null hypothesis blablabla is the percentage of reference points outside $b_{N,D}(\bm x')$
    \end{enumerate}
\end{description}

Why one decision per configuration, and not a collective decision based on several values of $D$?

Imagine the situation of having a sample $\bm x$ and checking if the mean of the underlying distribution that produced the data is zero.
The simplest test statistic that we may use is a Student's-t Test.
But we could also use a test based on the median (the notches of the boxplot).
How do we integrate both evidences?
It is difficult!
It would lead us to Bonferroni-type tests, because we are using a single sample for several tests.

The focus of this paper is \textbf{not} assessing the quality of PRNG.
We are testing sequences in the configuration that appear in the literature.

The data either provide evidence to \textbf{reject} the null hypothesis, or not.
In the last case, we \textbf{do not} accept the null hypothesis; we just do not have enough evidence to reject it.

About the textures.
We assessed the trajectory of points $(h,c)$ computed over $z=\alpha w \cdot (1-\alpha) n_L$.
It will be interesting to see 
$z = m_\alpha (w) \cdot n_L$, where 
$m_\alpha$ is the function that maps $[0,1]\mapsto [\alpha,1]$.

\end{document}

### 2020-09-15 Code/Osvaldo.R

@@ -1,65 +1,0 @@
-source("Bandt-Pompe.R")
-
-series.generator.map <- function(r, x_0, n, n_0){
-  series = vector(mode = "numeric", length = n)
-  series[1] = x_0
-  j = 0
-  for(i in 2:(n+n_0)){
-    if(i > n_0 + 1){
-      j = j + 1
-      series[j + 1] <- r*series[j]*(1 - series[j])
-    }
-  }
-  return(series)
-}
-
-## Logistic Map --------------------------------------------------------------------------------------------
-x.0 = 0.1
-n.0 = 10^5
-n.series = 15
-r = c(3.73, 3.70, 3.68, 3.67, 3.83, 4.00)
-names.series = rep(r, n.series)
-
-j = 1
-series.map.1 = matrix(nrow = 10^5, ncol = length(r) * n.series)
-for(i in 1:n.series){
-  for(rr in r){
-    series.map.1[,j] = series.generator.map(rr, x.0, 10^5, n.0)
-    j = j + 1
-    print(j)
-  } 
-}
-
-j = 1
-series.map.2 = matrix(nrow = 10^6, ncol = length(r) * n.series)
-for(i in 1:n.series){
-  for(rr in r){
-    series.map.2[,j] = series.generator.map(rr, x.0, 10^6, n.0)
-    j = j + 1
-    print(j)
-  } 
-}
-
-HC.values = data.frame(H = numeric(n.series * length(r) * 2), 
-                       C = numeric(n.series * length(r) * 2),  
-                       A = rep(names.series, 2),
-                       N = c(rep(10^5, n.series * length(r)), rep(10^6, n.series * length(r))))
-
-j = 1
-for(i in 1:(n.series * length(r))){
-  probs = bandt.pompe(series.map.1[,i], 4, 1)
-  HC.values$H[j] = shannon.entropy.normalized(probs)
-  HC.values$C[j] = Ccomplexity(probs)
-  j = j + 1
-  cat("Series: ", j, "\n")
-}
-
-for(i in 1:(n.series * length(r))){
-    probs = bandt.pompe(series.map.2[,i], 4, 1)
-    HC.values$H[j] = shannon.entropy.normalized(probs)
-    HC.values$C[j] = Ccomplexity(probs)
-    j = j + 1
-    cat("Series: ", j, "\n")
-}
-
-write.csv(HC.values, "HC-Logistic-Map-2.csv")

### 2020-09-15 Code/Plot-Osvaldo.R

@@ -1,99 +1,0 @@
-source("Bandt-Pompe.R")
-if(!require(reshape2)){
-  install.packages("reshape2")
-  require(reshape2)
-}
-if(!require(ggplot2)){
-  install.packages("ggplot2")
-  require(ggplot2)
-}
-if(!require(ggthemes)){
-  install.packages("ggthemes")
-  require(ggthemes)
-}
-if(!require(ggpubr)){
-  install.packages("ggpubr")
-  require(ggpubr)
-}
-HC.values = read.csv('HC-Logistic-Map-Rosso.csv')
-r = c(3.73, 3.70, 3.68, 3.67, 3.83, 4.00)
-rainbow_colors = palette(c("#fca311",#amarelo
-                           "#000000", #preto
-                           "#ff006e", #rosa
-                           "#40916c", #verde
-                           "#6a040f", #vermelho
-                           "#eb5e28", #laranja
-                           "#6a4c93", #roxo
-                           "#50514f", #cinza
-                           "#5e3023", #marrom
-                           "#3f88c5", #azul
-                           "#60d394"))
-color.series = rep(rainbow_colors[1:6], 50)
-
-
-hc.4 = HC.values[which(HC.values$D == 4),]
-hc.4$color = color.series
-hc.4$A = as.factor(hc.4$A)
-
-cotas.sup = data.frame("c1x" = numeric(9582), "c1y" = numeric(9582), "D" = as.factor(rep(4, 9582)))
-cotas.sup$c1x = readingMPR(4, 1)
-cotas.sup$c1y = readingMPR(4, 2)
-
-cotas.inf = data.frame("c1x" = numeric(27753), "c1y" = numeric(27753), "D" = as.factor(rep(4, 27753)))
-cotas.inf$c1x = readingMPR(4, 3)
-cotas.inf$c1y = readingMPR(4, 4)
-
-ggplot(data = hc.4, aes(x = H, y = C, color = A)) +
-  geom_point(size = 2.5, alpha = .8) +
-  geom_line(data = cotas.sup, aes(x = c1x, y = c1y), color="gray") +
-  geom_line(data = cotas.inf, aes(x = c1x, y = c1y), color="gray") + 
-  ggtitle(expression(italic(D == 4))) +
-  xlab(expression(italic(H))) + ylab(expression(italic(C))) + 
[…]

### 2020-09-15 Code/p-value-test.R

@@ -1,6 +1,6 @@
 ########################################################################################################
 # Author: Eduarda Chagas
-# Date : Aug 5, 2020
+# Date : Sep 15, 2020
 # Contact: eduarda.chagas@dcc.ufmg.br
 ########################################################################################################
 
@@ -32,11 +32,9 @@ calculate.p.value.samples <- function(samples, N, D){
   
   p.values = rep(0, dim(samples)[1])
   
-  
   attach(PC)
   for(i in 1:dim(samples)[1]){
-    print(i)
-    
+    #print(i)
     test = TRUE
     step.loop = 0
     region.test = 1.001

### 2020-09-15 Reports/JOURNAL - Confidence Regions/Code-Heitor/plots.R

@@ -1,45 +1,0 @@
-library(ggplot2)
-setwd('Marcelo/paper/')
-elmacho=read.csv('../Data/results.csv', header=T)
-
-elmacho$X=NULL
-#dEuclid=sqrt(elmacho$H^2+elmacho$C^2)
-
-#elmacho=cbind(elmacho,dEuclid)
-
-#cotas
-
-read_cotas = function(D=3){
-  cont_name = paste('limits/continua-N',factorial(D),'.q1', sep='')
-  trozos_name = paste('limits/trozos-N',factorial(D),'.q1', sep='')
-  continua = read.table(cont_name, skip=7)
-  trozos = read.table(trozos_name, skip=7)
-  cotas = list(continua,trozos)
-  return(cotas)
-}
-
-plot_confidence = function(DD,TNN){
-  #D=3, TN=1000, K=0
-  out1 = subset(elmacho,D==DD&TN==TNN)
-  cot = read_cotas(DD)
-  xmax=max(out1$H)
-  ymax=max(out1$C)
-  xmin=min(out1$H)
-  ymin=min(out1$C)
-  ymin=0
-  ggplot() +
-    geom_point(aes(H,C,colour = K),data=out1, alpha=.3) +
-    scale_colour_gradient(low = "yellow", high = "black") +
-    geom_line(aes(V1,V2),data=cot[[1]])+
-    geom_line(aes(V1,V2),data=cot[[2]])+
-    scale_x_continuous(limits=c(xmin,xmax)) +
-    scale_y_continuous(limits=c(ymin,ymax))+
-    theme_light() 
-}
-plot_confidence(3,1e3)
-plot_confidence(3,5e5)
-
-plot_confidence(6,1e3)
-plot_confidence(6,5e5)
-
-

### 2020-10-31 Reports/JOURNAL - Confidence Regions/Chapters/Background.tex
subsection true random numbers

@@
 Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real valued time series of length $T$, without ties. 
-As stated by \citeauthor{PermutationEntropyBandtPompe}~\ycite{PermutationEntropyBandtPompe} in their seminal work:  
+As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
 \begin{quote}
@@
 The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[a)]
+\begin{enumerate}[label=\alph*)]
 \item ordering the ranks of the $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
@@
 \end{enumerate}
-       see details in \citeauthor{BPRepeatedValuesChaos}~\ycite{BPRepeatedValuesChaos}.
+       see details in \Mycite{BPRepeatedValuesChaos}.
 Without loss of generality, in the following we will only use the latter.
@@
 In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citeauthor{LopezRuiz1995}~\ycite{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
+To this aim, \Mycite{LopezRuiz1995} proposed using $Q$, the disequilibrium, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
 They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

### 2020-10-31 Reports/JOURNAL - Confidence Regions/Chapters/ExperimentalSetup.tex
subsection true random numbers

@@
 
-\todo[inline]{Gerador - Marcelo}
-
-Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavihor. 
+Random numbers are used in many fields, from gambling to criptography, aiming to guarantee a secure, realistic or unpredictable behavior. 
 Pseudo randomic results can be achieved by software in a deterministic way. 
@@
 Randomness can be observed in unpredictable real world phenomena like cathodic radiation or atmospheric noise.
-In this study we used two sources of real random numbers. 
-The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
+%In this study we used two sources of real random numbers. 
+%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
+
+In this study we used two sources of random numbers, here called true random, both from physical phenomena observation and measurement.
+The first is based on vacuum states to generate random quantum numbers, the setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
+The probability distribution of the vacuum state is binned into $2^n$ equal parts (bins of same size), than, assigning a fixed bit combination of length \textit{n} to each sample point in a given bin \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}).
+The second one is based on atmospheric noise captured by a cheap radio receiver, started as a gambling engine, the randomness comes from an ordinary radio receiver that has no filter for static unwanted sounds caused by atmospheric noise, but perfect for random purposes, developed over a distributed setup with some radios located at different geographical locations sending random bits to a cloud server who process data and hosts random.org, the history, and some other information could be found at \cite{RandomOrg}.
 

### 2020-10-31 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
subsection true random numbers

@@
 Their analysis is usually based on two approaches \cite{TimeSeriesAnalysisCryerChan}: in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, a new methodology was proposed by \citeauthor{PermutationEntropyBandtPompe}~\ycite{PermutationEntropyBandtPompe}.
+In the context of time-domain analysis, a new methodology was proposed by \Mycite{PermutationEntropyBandtPompe}.
 Its approach is non-parametric and based on descriptors of Information Theory.
@@
 Based on this premise, studies with different applications managed to obtain relevant results from time series through information on the nature of the data provided by the $H \times C$ plane.
-Examples include the analysis of \citeauthor{echegoyen2020permutation}~\ycite{echegoyen2020permutation} in magnetoencephalography recordings of individuals suffering from mild cognitive impairment and individuals diagnosed with Alzheimer's disease by trajectories in the $H \times C$ plane,
-\citeauthor{InformationTheoryPerspectiveNetworkRobustness}~\ycite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by displacing their points in the $H \times C$ plane,
-\citeauthor{CharacterizationVehicleBehaviorInformationTheory}~\ycite{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles depending on the topology of cities, and
-\citeauthor{Chagas2020Characterization}~\ycite{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing SAR texture images, making characterization, and classification of them.
+Examples include the analysis of \Mycite{echegoyen2020permutation} in magnetoencephalography recordings of individuals suffering from mild cognitive impairment and individuals diagnosed with Alzheimer's disease by trajectories in the $H \times C$ plane,
+\Mycite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by displacing their points in the $H \times C$ plane,
+\Mycite{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles depending on the topology of cities, and
+\Mycite{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing SAR texture images, making characterization, and classification of them.
 
@@
 In the context of theoretical work, chaotic and random component analysis has been developed with the aim of improving the understanding of the plane's properties. We can cite as highlights:
-\citeauthor{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties}~\ycite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
-\citeauthor{De_Micco_2009}~\ycite{De_Micco_2009} studied chaotic components in pseudo-random number generators.
-\citeauthor{DistinguishingNoiseFromChaos}~\ycite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
-\citeauthor{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach}~\ycite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
+\Mycite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.~\citeyear{De_Micco_2009} studied chaotic components in pseudo-random number generators.
+\Mycite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
+\Mycite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
 With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
 Some preliminary results can already be found in the literature.
-\citeauthor{RandomNumberGeneratorsCausality}~\ycite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
-\citeauthor{De_Micco_2008}~\ycite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-\citeauthor{LiborInvisibleHand}~\ycite{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
+\Mycite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
+\Mycite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
+\Mycite{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
 

### 2020-10-31 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex
subsection true random numbers

@@
 
-The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cites{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
-However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cites{larrondo2002statistical, gonzalez2005statistical}.
+The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cite{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
+However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cite{larrondo2002statistical, gonzalez2005statistical}.
 

### 2020-11-02 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
Intro revisada

@@
 Time Series carry valuable information about the system which produces the data.
-Their analysis is usually based on two approaches \cite{TimeSeriesAnalysisCryerChan}: in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, a new methodology was proposed by \Mycite{PermutationEntropyBandtPompe}.
-Its approach is non-parametric and based on descriptors of Information Theory.
+Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: in the (natural) time and transformed domains (for instance, frequency and wavelet).
+In the context of time-domain analysis, a new methodology was proposed by \cite{PermutationEntropyBandtPompe}.
+Such approach is non-parametric and based on descriptors of Information Theory.
 Through this, the time series is transformed into ordinal patterns, with which a histogram is formed.
@@
 
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{2500} citations, according to the Journal of Citation Records.
+The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{2500} citations, according to Web of Science\footnote{aqui informar a data da consulta, as palavras chave, e o valor exato}.
 We found works using such an approach in multiple areas of scientific knowledge such as, for example,
-the study of electroencephalography signals using wavelet decomposition~\cite{EEGAnalysisWaveletInformationTools},
-characterization of household appliances through their energy consumption~\cite{CharacterizationElectricLoadInformationTheoryQuantifiers},
- online signature classification and verification~\cite{ClassificationVerificationOnlineHandwrittenSignatures}.
+the study of electroencephalography signals using wavelet decomposition \citep{EEGAnalysisWaveletInformationTools},
+the characterization of household appliances through their energy consumption \citep{CharacterizationElectricLoadInformationTheoryQuantifiers},
+and online signature classification and verification \citep{ClassificationVerificationOnlineHandwrittenSignatures}.
 
-Each time series is described by a point in the range of $\mathbbm R^2$, the entropy complexity plane.
+Each time series is described by a point in a manifold of $\mathbbm R^2$, the entropy complexity plane $H\times C$.
 Two points are well known in this plane: those of white noise and a completely deterministic sequence.
-Through these references, we can characterize the time series according to the dynamics of its generating process.
-Based on this premise, studies with different applications managed to obtain relevant results from time series through information on the nature of the data provided by the $H \times C$ plane.
-Examples include the analysis of \Mycite{echegoyen2020permutation} in magnetoencephalography recordings of individuals suffering from mild cognitive impairment and individuals diagnosed with Alzheimer's disease by trajectories in the $H \times C$ plane,
-\Mycite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by displacing their points in the $H \times C$ plane,
-\Mycite{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles depending on the topology of cities, and
-\Mycite{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing SAR texture images, making characterization, and classification of them.
+Through these references, we can characterize the time series according to the dynamics that generated the observed process.
+Based on this premise, studies with different applications managed to obtain relevant information about the nature of the data.
+Examples include the work by \cite{echegoyen2020permutation} in magnetoencephalography recordings of individuals suffering from mild cognitive impairment and individuals diagnosed with Alzheimer's disease.
+\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
+\cite{CharacterizationVehicleBehaviorInformationTheory} described the behavior of vehicles depending on the topology of cities, and
+\cite{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
+\cite{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
 
@@
 
-In the context of theoretical work, chaotic and random component analysis has been developed with the aim of improving the understanding of the plane's properties. We can cite as highlights:
-\Mycite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.~\citeyear{De_Micco_2009} studied chaotic components in pseudo-random number generators.
-\Mycite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
-\Mycite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
+Although the boundaries of the $H\times C$ are well-defined, a complete characterization of its intrinsic topology is an open problem.
+Several works have used deterministic and pseudorandom sequences aiming at understanding its properties.
+\cite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
+\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
+\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
+\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
+
 With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
-Some preliminary results can already be found in the literature.
-\Mycite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
-\Mycite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-\Mycite{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
+Results in this direction can be found in the literature.
+\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of the results of Diehard tests for pseudorandom number generators.
+\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
 
 Motivated by such works, in this paper we advance the state-of-the-art providing confidence regions for white noise points in the $H\times C$ plane.
-In the proposed approach, the input is a sequence of true random observations generated by a physical procedure, and the confidence regions are obtained by performing an orthogonal projection of the data onto a space of principal components analysis (PCA), thus eliminating the restrictions imposed by the curvilinear space of the Entropy-Complexity Plane.
+In the proposed approach, the input is a sequence of true random observations generated by a physical procedure, and the confidence regions are obtained by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the curvilinear space of the Entropy-Complexity Plane.
 Our contributions can be summarized as follows:
 \begin{itemize}
-    \item Provide the first contribution in construction that confidence regions in Entropy-Complexity Plane.
-    \item Evaluate the discrimination power of these regions in the analysis of small random sequences generated by physical procedures and pseudorandom generators (PRNGs).
+    \item We provide the first contribution in construction that confidence regions in Entropy-Complexity Plane.
+    \item We evaluate the discrimination power of these regions in the analysis of small random sequences generated by physical procedures and pseudorandom generators (PRNGs).
 \end{itemize}

### 2020-11-02 Code/PCA-Histogram.R
Novos histogramas + erro bizarro

@@ -56,11 +56,16 @@ pca.histogram <- function(){
   PC = melt(data = PC, id.vars = c(1,2), variable.name = "D")
   
   pdf("PCA-hist-50k.pdf", width = 32, height = 10)
+  
   p = ggplot(PC) +
     ggtitle("First Component Histogram") +
     xlab("") +
     ylab("") +
-    geom_histogram(aes(x = PC1, y = ..density..), binwidth = 1, fill="#212529", color="#343a40", alpha=0.9) +
+    geom_histogram(aes(x = PC1, y = ..density..), 
+                   bins = nclass.FD(PC$PC1[1:8372]), 
+                   fill="white", 
+                   color="black", 
+                   alpha=0.9) +
     facet_grid(. ~ value) + 
     theme_few(base_size = 35, base_family = "serif") +  
     theme(plot.title = element_text(hjust=0.5)) +
@@ -84,10 +89,14 @@ plot.pca.histogram <- function(HC, D, N){
   median.pca = data.frame(PC1 = pca.data$xmin[5], PC2 = pca.data$ymax[5])
   
   p = ggplot(PC) +
-      ggtitle(paste0("First Component Histogram - D = ", D, " & N = ", N)) +
+      ggtitle(paste0("First Component Histogram - D = ", italic(D), " & N = ", N)) +
       xlab("") +
       ylab("") +
-      geom_histogram(aes(x = PC1, y = ..density..), binwidth = 1, fill="#69b3a2", color="#e9ecef", alpha=0.9) +
+      geom_histogram(aes(x = PC1, y = ..density..), 
+                     bins = nclass.FD(PC$PC1), 
+                     fill="white", 
+                     color="black", 
+                     alpha=0.9) +
       theme_clean() + 
       theme(plot.title = element_text(hjust=0.5)) +
       xlim(limits=c(0, 0.6)) 

### 2020-11-07 Reports/Report - Data Imputation/sbc-template.tex
Data Imputation report

\documentclass[11pt]{article}
\usepackage[english]{babel} 
\usepackage{sbc-template}

\usepackage{cite}
\usepackage{caption}  
\usepackage{bm}
\usepackage{xurl}
\usepackage{siunitx}

\hyphenation{op-tical net-works semi-conduc-tor}

\sloppy

\title{Data Imputation -- Papers analysis}
\author{Eduarda T. C. Chagas}
\address{
    Departamento de Ci\^encia da Computa\c c\~ao -- Universidade Federal de Minas Gerais\\
    Belo Horizonte -- Minas Gerais -- Brazil
    \email{eduarda.chagas@dcc.ufmg.br}
}

\begin{document}

\maketitle

\section*{\textbf{\textit{Comparing different approaches to compute Permutation Entropy with coarse time series}}~\cite{traversaro2019comparing}}

Was test the new Data-Driven Method of Imputation that cope with this type of time series without modifying the essence of the Bandt and Pompe Probability Distribution Function and compare it with the Modified Permutation Entropy, a complexity measure that assumes that equal values are not from artifacts of observations but they are typical of the data generating process. 
The Data-Driven Method of Imputation proves to outperform the Modified Permutation Entropy.

\subsection*{Numerical Analysis}

The Modified Permutation Entropy (MPE) and the Data Driven Method of Imputation (DDMI) are evaluated using data from simulated chaotic processes. 
The simulation consists in 44 time series generated by different chaotic processes in every dimension, previously analyzed by Rosso and coworkers in~\citeonline{rosso2013characterization}. 
Each original time series was truncated up to two decimal resolution, leading to a coarse version of those original time series.
This yields to quantify how well each strategy estimates the actual PE -- $H(\bm D)$ -- for the different chaotic processes using the PE estimation -- $\hat{H}(\bm D)$ -- obtained for each methodology.

Was used the initial conditions present in~\cite{sprott2003chaos} and refer to this book for a comprehensive analysis of those maps. 
Each map was simulated for a length of $\num[scientific-notation=true]{e6}$ and then starting in the position $\num[scientific-notation=true]{e5}$.
They were produced with IEEE 754 double precision floating point numbers.
For those initial condition, as the series is deterministic, the $H(\bm D)$, $D = \{ 3, 4, 5, 6 \}$ are the original PE of the processes.

For every length motiv $D$ the DDMI estimation is better that the MPE, and the variability of the Error of the DDMI is considerably lower than the MPE. 
The improvement in the estimation made by DDMI over the methodology of eliminating this patterns with ties can be seen as the gain of the information given by this methodology.
Another interesting property to notice is how well each methodology performs for different amounts of patterns $X_D(t)$ with ties.
As might be expected, the error increases with the repeated ratio, but the DDMI is always better than the MPE. 
It should be noted that for the highest level of repeated ratio, at least $\SI{20}{\percent}$ of the information is lost by eliminating this patterns and the DDMI retrieves some of this information lost improving the estimation.
\newpage

\section*{\textbf{\textit{An empirical evaluation of alternative methods of estimation for Permutation Entropy in time series with tied values}}~\cite{traversaro2017empirical}}

This contribution has a twofold objective. 
The first is to introduce a new method to deal with tied values and the second is to do an exhaustive exploration of all the methods presented.
Was review the different existing methodologies that treats this subject by classifying them according to their different strategies.

\subsection*{Extended alphabets: Modified Permutation-entropy algorithm}

If equal values may represent a feature state of the system under study, mapping equal values in {$x_t$} to equal representation in a symbol $\pi$ could be considered.
This modified order based alphabet results in more possible symbols for each embedding dimension $D$ so it characterizes more system states than the original PE method.

\subsection*{Numerical Analysis}

In order to get a reproducible set of time series, all maps presented in~\citeonline{rosso2013characterization} were simulated using the initial conditions presented therein.
Each original time series was truncated up to one decimal resolution, leading to a coarse version of those original time series.
The simulation consists in $39$ time series generated by different chaotic processes, and each one was simulated for a length of $n = (5000, 10000, 30000, 90000)$.

This yields to quantify how well each strategy estimates the actual Permutation Entropy $H(\bm P)$ comparing the result of each original time series with  heir respective Permutation Entropy calculated with all the above methodologies over the coarse version.
To quantify the behavior of the estimator, the Mean Square Error, defined as $E[\hat{H}(\bm P) - H(\bm P)^2]$, is used.

Time Order Imputation and Bayesian Imputation consistently beat the other methodologies for every embedding dimension $D$ and for all the repeated ratios as the MSE is the lowest in all the cases.
Methodologies that use extended alphabet tend to sub estimate the entropy, specially when the embedding dimension is small. 
Random Imputation methodology over estimates the entropy as it create noise and this is more evident when the imputation is made over a time series with a large number of repeated values.

\subsection*{Real Application}

We applied the presented strategies to classify using heart rate time series from a (healthy) control group and from patients suffering from Congestive Heart Failure (CHF). 
The data have been collected from internet data bases: 
\begin{itemize}
    \item NSR2DB Normal Sinus Rhythm RR interval database for the healthy patients, and
    \item CHF2DB Congestive heart failure RR interval database, for the patients suffering from CHF, from \url{http://www.physionet.org/cgi-bin/atm/ATM}.
\end{itemize}
For each database, $15$ series were taken, each one with approximately $100000$ observations.
Bayesian Imputation was an optimum classifier for this application since it does a great job separating the populations.
\newpage

\section*{\textbf{\textit{Bandt-Pompe symbolization dynamics for time series with tied values: A data-driven approach}}~\cite{traversaro2018bandt}}

The present contribution was to review the different existing methodologies for treating time series with tied values by classifying them according to their different strategies. 
In addition, a novel data-driven imputation is presented that proves to outperform the existing methodologies and avoid the false conclusions pointed by Zunino and co-workers.

\subsection*{Data-driven imputation}

This methodology uses information of the actual time series to deal with ties. 
Was assumed that there is an underlying (unobserved) time series with no ties and that the data at hand are a corrupted version. 
With this in mind, the proposal estimates the true patterns from the observed ones using the information available from the corrupted data through a suitable probability distribution. 
It can be seen as a Data-Driven methodology.

\subsection*{Numerical Analysis}

For evaluation of the randomness of the decimal expansion of irrational numbers, was analyze the temporal sequences of the decimal expansion of the irrational numbers $\pi$ , $e$, and $\sqrt{2}$ with length $T = \num[scientific-notation=true]{5 e3}$, $\num[scientific-notation=true]{e4}$, $\num[scientific-notation=true]{e5}$, and $\num[scientific-notation=true]{e6}$ of the first digits and evaluate the Bandt-Pompe PDF with embedding dimensions $D = \{3, 4, 5, 6\}$, and time lag $\tau = 1$.

With the effect of large vector effect ($D = 6$) of values in the set $\{0, 1, \dots, 9\}$, which would probably have repetitions, was is notable that Time Ordered Shannon entropy is significantly greater than that obtained by the Data-Driven technique.
The values of $H(D)[\Pi]$ evaluated with BP-PDF following the time order imputation suggest the presence of temporal complex structures in the data, for increasing values of $D \ge 4$, regardless the time series length $T$.
The same operator, when applied to Data-Driven imputed data, does not show any kind of correlation structure, indicating that the decimal expansion of the irrational numbers are compatible with uncorrelated random behavior in agreement with the results obtained by~\citeonline{luque2009horizontal}.
Note also that similar results are obtained when using BP-PDF with complete imputation, however, in this case, we have a strong reduction of the number of reconstructed vectors, implying that longer time series are necessary in order to have zero forbidden/missing patterns, as for $D = 6$.

\subsection*{Chaotic maps time series}

%Consider $\Upsilon$ an operator over a permutation pattern PDF, e.g., the Shannon Entropy. We consider four different ways of performing the mapping $\mathcal{X}$ to a symbolic alphabet, which lead to $\Pi^{(i)}$, $1 \leq i \leq 4$:
%~(1) Complete; 
%~(2) Random; 
%~(3) Time Ordered, and 
%~(4) Data-Driven.
%The hypothesis used was that the operator applied to the best symbolic imputation technique will lead to the value closest to the original value. 
%We thus want to find the technique $i$ for which:
%\begin{equation*}
%    \delta^{(i)} \Upsilon = \frac{|\Upsilon(\Pi^{(i)}) - \Upsilon(\Pi^{(*)})}{\Upsilon(\Pi^{(*)})},
%\end{equation*}
%is minimum, provided $\Upsilon(\Pi^{(*)}) \neq 0$.
%Was analyzed the behavior of $\Upsilon(\Pi^{(*)})$ for two different operators $\Upsilon$: the normalized Permutation Shannon Entropy ($H$) and the number of forbidden/missing patterns (NFMP), considering embedding dimensions $D = \{ 3, 4, 5, 6,\}$ and time lag $\tau = 1$.

Was evaluated times series $\mathcal{X^{*}}$ of $T = \num[scientific-notation=true]{e5}$ iteration data (after discarding $\num[scientific-notation=true]{e5}$ iterations for stability) from the chaotic maps considered by~\citeonline{rosso2013characterization}. 
The coarse version (low precision) time series $\mathcal{X}$ are obtained truncating the original values $x^*_t$ to two decimal digits.

Was noted that NFMP for the other methodologies present in general lower values than those for BP-PDF Data-Driven, and was conclude that Random Imputation and Complete should not be used. 
The other two techniques are competitive, but in some cases, Data-Driven outperforms Time Ordered Imputation.
\newpage

\section*{\textbf{\textit{Permutation entropy based time series analysis: Equalities in the input signal can lead to false conclusions}}~\cite{zunino2017permutation}}

In this work, was carefully study the effect that the presence of equalities has on permutation entropy estimated values when these ties are symbolized, as it is commonly done, according to their order of appearance.

\subsection*{Numerical Analysis}

To illustrate the effect that the occurrence of a high frequency of ties has on PE estimated values, we have numerically generated an ensemble of one hundred independent sequences of $N = 1.000$ pseudorandom integer values drawn from a discrete uniform distribution on the interval $[0, i]$ with $i$ ranging from $1$ to $50$ with step equal to one.
The normalized PE with different embedding dimensions, $D \in \{ 3, 4, 5, 6\}$ , and embedding delay $\tau = 1$ (consecutive data points) has been estimated.

Was is clearly observed that normalized PE values from pseudorandom discrete time series with a high frequency of occurrence of equal values are much lower than those obtained for a pseudorandom continuous time series, leading to a totally spurious identification of non-random temporal structures. 
Because of the way ties are ordered, the relative frequencies of some permutation patterns are overestimated in detriment of those associated with other motifs which are underestimated, and, consequently, a non-uniform ordinal pattern probability distribution is obtained.
Analysis by implementing the WPE has been also carried out. 
Results obtained confirm that this improved ordinal permutation quantifier also suffers from this weakness.

\subsection*{Two simple applications}

As a first application, was investigate the randomness of the decimal expansion of irrational numbers by using the PE, analyzing the ordinal pattern probability distribution of the temporal sequences obtained by picking the first $10.000$ digits of the decimal expansion of several irrational numbers such as $\pi$ , $e$, and $\sqrt{2}$.

As was is visually concluded, the different motifs are not equiprobable. 
Some of them are more probable than others, indicating, apparently, the presence of temporal complex structures in the data. 
But the results imply that the irregularly observed frequency of motifs is a totally spurious effect due to the significant number of equalities that are present in the original time series. 
Moreover, a surrogate analysis with shuffled realizations appears as a practical alternative to overcome this limitation of the PE.

Was finally developed an ordinal symbolic analysis for radioactive decay data.
A signal of plutonium-239 activity with length $N = 10.000$ has been examined.
The relative frequencies of the ordinal patterns for embedding dimension $D = 3$ and embedding delays $\tau$ between $1$ and $100$ was analyzed.
In this case, the varied the embedding delay in order to check the behavior of the experimental data for different time scales, i.e. for different sampling times.
It is concluded that, independently of the time scale, the ordinal pattern probability distribution is irregular.
\newpage

\section*{Conclusions}

In summary, we can see that the main analyzes were performed based on digits of the decimal expansion of irrational numbers such as $\pi$, and $\sqrt{2}$, and chaotic maps considered in~\cite{rosso2013characterization}.
The methods present in the literature and which have their methodologies analyzed, are:
\begin{itemize}
    \item Chronological extended alphabet;
    \item Rank extended alphabet;
    \item Complete cases;
    \item Time Ordered imputation;
    \item Random imputation;
    \item Bayesian/Data-driven Imputation.
\end{itemize}
Therefore, the variability of the Error (absolute error or mean square) between current PE and the obtained for each methodology, and the analysis of the number of forbidden/missing patterns (NFMP) are checked to see which one can more accurately represent the dynamics of the sequence generating process with repeated values.

\section*{Supplementary material}

\textbf{\textit{Characterization of chaotic maps using the permutation
Bandt-Pompe probability distribution}}

This paper provides information about the chaotic maps and our initialization parameters used in~\citeonline{traversaro2017empirical, traversaro2018bandt}, and \citeonline{traversaro2019comparing}.
Was consider 27 chaotic maps described by Sprott in the appendix of his book~\cite{sprott2003chaos}. 
These chaotic maps are grouped as:
\begin{itemize}
    \item noninvertible maps: 
    ~(1) logistic map; 
    ~(2) sine map; 
    ~(3) tent map; 
    ~(4) linear congruential generator; 
    ~(5) cubic map; 
    ~(6) Ricker’s population model; 
    ~(7) Gauss map; 
    ~(8) Cusp map; 
    ~(9) Pinchers map; 
    ~(10) Spence map; 
    ~(11) sinecircle map.
    \item  dissipative maps: 
    ~(12) Hénon map; 
    ~(13) Lozi map;
    ~(14) delayed logistic map; 
    ~(15) Tinkerbell map; 
    ~(16) Burgers’ map; 
    ~(17) Holmes cubic map; 
    ~(18) dissipative standard map; 
    ~(19) Ikeda map; 
    ~(20) Sinai map; 
    ~(21) discrete predator-prey map.
    \item conservative maps: 
    ~(22) Chirikov standard map; 
    ~(23) H´enon area-preserving quadratic map; 
    ~(24) Arnold’s cat map; 
    ~(25) Gingerbreadman map; 
    ~(26) chaotic web map; 
    ~(27) Lorenz threedimensional chaotic map.
\end{itemize}
\newpage

\newpage
\bibliographystyle{sbc}
\bibliography{sbc-template}

\end{document}

### 2020-11-07 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Research Plan

---
title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
output: html_notebook
---

The purpose of this study is describing the distribution of ties in irrational numbers when considering sequences of embedding dimension $D$ (and $\tau=1$).
The finding will help building a model for simulating such occurrences and, then, assessing imputation techniques in a Monte Carlo study.

### 2020-11-07 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Research plan - adding experiments

@@
 title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
+author: "Eduarda Chagas"
+date: "Nov 7, 2020"
 output: html_notebook
@@
 The finding will help building a model for simulating such occurrences and, then, assessing imputation techniques in a Monte Carlo study.
+
+```{r} 
+source('Bandt-Pompe.R')
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+```
+
+### Analysis of the distribution of repeated symbols for sequences with N = 1000
+
+```{r} 
+e.data = read.table('../Data/e.txt', stringsAsFactors=FALSE, fileEncoding="latin1")
+pi.data = read.table('../Data/pi.txt', stringsAsFactors=FALSE, fileEncoding="latin1")
+sqrt2.data = read.table('../Data/sqrt2.txt', stringsAsFactors=FALSE, fileEncoding="latin1")
+
+e.vector = as.numeric(strsplit(as.character(e.data), "")[[1]])[3:100011]
+pi.vector = as.numeric(strsplit(as.character(pi.data), "")[[1]])[3:100011]
+sqrt2.vector = as.numeric(strsplit(as.character(sqrt2.data), "")[[1]])[3:100030]
+
+n.series = 100
+n.elements = 1000
+e.series = asplit(array(e.vector, c(n.elements, round(length(e.vector)/n.elements))), MARGIN = 2)
+pi.series = asplit(array(pi.vector, c(n.elements, round(length(pi.vector)/n.elements))), MARGIN = 2)
+sqrt2.series = asplit(array(sqrt2.vector, c(n.elements, round(length(sqrt2.vector)/n.elements))), MARGIN = 2)
+```
+
+```{r} 
+D = 3
+Tau = 1
+e.percent.D3 = pi.percent.D3 = sqrt2.percent.D3 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D3[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D3[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D3[i] = percentual.equalities(elements)
+}
+
+data.D3 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D3, pi.percent.D3, sqrt2.percent.D3)
+)
+data.D3 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series/2) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill = "") +
+    ggtitle('D = 3') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+```{r} 
+D = 4
+Tau = 1
+e.percent.D4 = pi.percent.D4 = sqrt2.percent.D4 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D4[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D4[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D4[i] = percentual.equalities(elements)
+}
+
+data.D4 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D4, pi.percent.D4, sqrt2.percent.D4)
+)
+data.D4 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series/2) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill="") +
+    ggtitle('D = 4') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+#### Normality test for N = 1000 with Shapiro-wilk 
+```{r} 
+cat(' (D = 3 & N = 1000) -> p-values: ', 
+    shapiro.test(data.D3[1:100,]$value)$p.value, " ", 
+    shapiro.test(data.D3[101:200,]$value)$p.value, " ", 
+    shapiro.test(data.D3[201:300,]$value)$p.value, '\n',
+    '(D = 4 & N = 1000) -> p-values: ', 
+    shapiro.test(data.D4[1:100,]$value)$p.value, " ", 
+    shapiro.test(data.D4[101:200,]$value)$p.value, " ", 
+    shapiro.test(data.D4[201:300,]$value)$p.value)
+```
+### Analysis of the distribution of repeated symbols for sequences with N = 10000
+
+```{r}
+n.series = 10
+n.elements = 10000
+e.series = asplit(array(e.vector, c(n.elements, round(length(e.vector)/n.elements))), MARGIN = 2)
+pi.series = asplit(array(pi.vector, c(n.elements, round(length(pi.vector)/n.elements))), MARGIN = 2)
+sqrt2.series = asplit(array(sqrt2.vector, c(n.elements, round(length(sqrt2.vector)/n.elements))), MARGIN = 2)
+```
+
+```{r} 
+D = 3
+Tau = 1
+e.percent.D3 = pi.percent.D3 = sqrt2.percent.D3 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D3[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D3[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D3[i] = percentual.equalities(elements)
+}
+
+data.D3 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D3, pi.percent.D3, sqrt2.percent.D3)
+)
+data.D3 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill = "") +
+    ggtitle('D = 3') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+```{r} 
+D = 4
+Tau = 1
+e.percent.D4 = pi.percent.D4 = sqrt2.percent.D4 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D4[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D4[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D4[i] = percentual.equalities(elements)
+}
+
+data.D4 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D4, pi.percent.D4, sqrt2.percent.D4)
+)
+data.D4 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill="") +
+    ggtitle('D = 4') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+```{r} 
+D = 5
+Tau = 1
+e.percent.D5 = pi.percent.D5 = sqrt2.percent.D5 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D5[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D5[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D5[i] = percentual.equalities(elements)
+}
+
+data.D5 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D5, pi.percent.D5, sqrt2.percent.D5)
+)
+data.D5 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill="") +
+    ggtitle('D = 5') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+```{r} 
+D = 6
+Tau = 1
+e.percent.D6 = pi.percent.D6 = sqrt2.percent.D6 = rep(0, n.series)
+
+for(i in 1:n.series){
+  elements = formationPattern(e.series[[i]], D, Tau, 1)
+  e.percent.D6[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(pi.series[[i]], D, Tau, 1)
+  pi.percent.D6[i] = percentual.equalities(elements)
+}
+for(i in 1:n.series){
+  elements = formationPattern(sqrt2.series[[i]], D, Tau, 1)
+  sqrt2.percent.D6[i] = percentual.equalities(elements)
+}
+
+data.D6 <- data.frame(
+  type = c(rep("e", n.series), rep("pi", n.series), rep("sqrt2", n.series)),
+  value = c(e.percent.D6, pi.percent.D6, sqrt2.percent.D6)
+)
+data.D6 %>%
+    ggplot(aes(x = value, fill = type)) +
+    geom_histogram(color="#e9ecef", alpha = 3.6, position = 'identity', bins = n.series) +
+    scale_fill_manual(values=c("#69b3a2", "#404080", "#d4bf08")) +
+    theme_few(base_size = 12, base_family = "serif") +
+    labs(fill="") +
+    ggtitle('D = 6') + 
+    facet_grid(~type) +  
+    theme(plot.title = element_text(hjust=0.5))
+```
+
+#### Normality test for N = 10000 with Shapiro-wilk 
+```{r} 
+cat(' (D = 3 & N = 10000) -> p-values: ', 
+    shapiro.test(data.D3[1:10,]$value)$p.value, " ", 
+    shapiro.test(data.D3[11:20,]$value)$p.value, " ", 
+    shapiro.test(data.D3[21:30,]$value)$p.value, '\n',
+    '(D = 4 & N = 10000) -> p-values: ', 
+    shapiro.test(data.D4[1:10,]$value)$p.value, " ", 
+    shapiro.test(data.D4[11:20,]$value)$p.value, " ", 
+    shapiro.test(data.D4[21:30,]$value)$p.value, '\n',
+    '(D = 5 & N = 10000) -> p-values: ', 
+    shapiro.test(data.D5[1:10,]$value)$p.value, " ", 
+    shapiro.test(data.D5[11:20,]$value)$p.value, " ", 
+    shapiro.test(data.D5[21:30,]$value)$p.value, '\n',
+    '(D = 6 & N = 10000) -> p-values: ', 
+    shapiro.test(data.D6[1:10,]$value)$p.value, " ", 
+    shapiro.test(data.D6[11:20,]$value)$p.value, " ", 
+    shapiro.test(data.D6[21:30,]$value)$p.value)
+```

### 2020-11-07 Reports/Report - Data Imputation/Code/Bandt-Pompe.R

@@ -25,18 +25,6 @@ FP <- function(n, dimension, delay){
   return(p)
 }
 
-percentual.equalities <- function(patterns){
-  n.patterns = dim(patterns)[1]
-  n.duplicated = 0
-  for(i in 1:n.patterns){
-    if(length(which(duplicated(patterns[i,]) == TRUE))){
-      n.duplicated = n.duplicated + 1
-      print(length(which(duplicated(patterns[i,]) == TRUE)))
-    }
-  }
-  return(n.duplicated/n.patterns)
-}
-
 formationPattern <- function(series, D, tau, option){
   
   i = 1

### 2020-11-08 Reports/JOURNAL - Confidence Regions/Chapters/Conclusions.tex
Sincronizanto

@@
 (1)~the construction of empirical confidence regions obtained through the mapping of points in the latent space formed by the application of the principal components analysis under the reference points,
-(2) ~ the application of a hypothesis test to measure the similarity of new sequences to the reference points.
+(2)~the application of a hypothesis test to measure the similarity of new sequences to the reference points.
 Sequences of true random samples were used to calculate theses empirical regions.

### 2020-11-08 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
Sincronizanto

@@
 Although the boundaries of the $H\times C$ are well-defined, a complete characterization of its intrinsic topology is an open problem.
-Several works have used deterministic and pseudorandom sequences aiming at understanding its properties.
+\citet{OrdinalPatternProbabilities} obtained properties of the sample entropy under zero mean Gaussian processes.
+In particular, the joint distribution of points in this plane under typical types of time series would serve to build test statistics.
+
+Several works have used deterministic and pseudorandom sequences aiming at understanding the properties of the points they produce in the $H\times C$ plane.
 \cite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
 \cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
-\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
+\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
 \cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.

### 2020-11-08 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Sincronizanto

@@
 date: "Nov 7, 2020"
+
 output: html_notebook
@@
 ```
+
+We have produced to files with Mathematica: e.txt, pi.txt, and sqrt2.txt. They contain expansions of these irrational numbers with $100,000$ digits.
+
+The exploratory data analysis consists of
+
+1. Read the numbers, and for each number:
+2. For each value of $D\in\{3,4,5,6\}$ (or embedding dimensions employed in the literature)
+3. Compute the number of tied sequences
+4. Return binary vectors with the position of the tied sequences

### 2020-11-10 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex

@@
-\section{Entropy-Complexity plane in the literature}
+\subsection{Entropy-Complexity plane in the literature}
 
-The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cite{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
-However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cite{larrondo2002statistical, gonzalez2005statistical}.
+The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps \citep{rosso2013characterization,olivares2012contrasting, xiong2020complexity}.
+However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization \citep{larrondo2002statistical, gonzalez2005statistical}.
 

### 2020-11-10 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
new results - experimental analysis

--- 2020-11-07 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
@@
 title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
+author: "Eduarda Chagas"
+date: "Nov 10, 2020"
+
 output: html_notebook
@@
 The finding will help building a model for simulating such occurrences and, then, assessing imputation techniques in a Monte Carlo study.
+Thus, in this report we will make an exploratory analysis of the data, analyzing the percentage of tied sequences for each embedding dimension value.
+
+### Load packages and sources
+
+```{r} 
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+source('Bandt-Pompe.R')
+```
+
+### Reading the numbers
+
+We have produced to files with Mathematica: e.txt, pi.txt, and sqrt2.txt. They contain expansions of these irrational numbers with $100,000$ digits.
+
+```{r} 
+e.data = as.character(read.table('../Data/e.txt', stringsAsFactors=FALSE, fileEncoding="latin1"))
+pi.data = as.character(unlist(read.table('../Data/pi.txt', stringsAsFactors=FALSE, fileEncoding="latin1")))
+sqrt2.data = as.character(unlist(read.table('../Data/sqrt2.txt', stringsAsFactors=FALSE, fileEncoding="latin1")))
+
+e.vector = as.numeric(unlist(strsplit(e.data, ""))[3:100011])
+pi.vector = as.numeric(unlist(strsplit(pi.data, ""))[3:100011])
+sqrt2.vector = as.numeric(unlist(strsplit(sqrt2.data, ""))[3:100030])
+```
+
+### Computing the number of tied sequences for each value of $D\in\{3,4,5,6\}$
+
+```{r} 
+D = 3
+Tau = 1
+
+e.elements.D3 = formationPattern(e.vector, D, Tau, 1)
+e.percent.D3 = percentual.equalities(e.elements.D3)
+
+pi.elements.D3 = formationPattern(pi.vector, D, Tau, 1)
+pi.percent.D3 = percentual.equalities(pi.elements.D3)
+
+sqrt2.elements.D3 = formationPattern(sqrt2.vector, D, Tau, 1)
+sqrt2.percent.D3 = percentual.equalities(sqrt2.elements.D3)
+
+cat("Number of tied sequences \ne: ", round(e.percent.D3*100, 3), "%\npi: ", round(pi.percent.D3*100, 3), "%\nsqrt2: ", round(sqrt2.percent.D3*100, 3), "%\n")
+```
+
+```{r} 
+D = 4
+e.elements.D4 = formationPattern(e.vector, D, Tau, 1)
+e.percent.D4 = percentual.equalities(e.elements.D4)
+
+pi.elements.D4 = formationPattern(pi.vector, D, Tau, 1)
+pi.percent.D4 = percentual.equalities(pi.elements.D4)
+
+sqrt2.elements.D4 = formationPattern(sqrt2.vector, D, Tau, 1)
+sqrt2.percent.D4 = percentual.equalities(sqrt2.elements.D4)
+
+cat("Number of tied sequences \ne: ", round(e.percent.D4*100, 3), "%\npi: ", round(pi.percent.D4*100, 3), "%\nsqrt2: ", round(sqrt2.percent.D4*100, 3), "%\n")
+```
+
+```{r} 
+D = 5
+e.elements.D5 = formationPattern(e.vector, D, Tau, 1)
+e.percent.D5 = percentual.equalities(e.elements.D5)
+
+pi.elements.D5 = formationPattern(pi.vector, D, Tau, 1)
+pi.percent.D5 = percentual.equalities(pi.elements.D5)
+
+sqrt2.elements.D5 = formationPattern(sqrt2.vector, D, Tau, 1)
+sqrt2.percent.D5 = percentual.equalities(sqrt2.elements.D5)
+
+cat("Number of tied sequences \ne: ", round(e.percent.D5*100, 3), "%\npi: ", round(pi.percent.D5*100, 3), "%\nsqrt2: ", round(sqrt2.percent.D5*100, 3), "%\n")
+```
+
+```{r} 
+D = 6
+e.elements.D6 = formationPattern(e.vector, D, Tau, 1)
+e.percent.D6 = percentual.equalities(e.elements.D6)
+
+pi.elements.D6 = formationPattern(pi.vector, D, Tau, 1)
+pi.percent.D6 = percentual.equalities(pi.elements.D6)
+
+sqrt2.elements.D6 = formationPattern(sqrt2.vector, D, Tau, 1)
+sqrt2.percent.D6 = percentual.equalities(sqrt2.elements.D6)
+
+cat("Number of tied sequences \ne: ", round(e.percent.D6*100, 3), "%\npi: ", round(pi.percent.D6*100, 3), "%\nsqrt2: ", round(sqrt2.percent.D6*100, 3), "%\n")
+```
+### Analyzing the binary vectors with the position of the tied sequences
+
+```{r} 
+e.binary.D3 = binary.equalities(e.elements.D3)
+e.binary.D4 = binary.equalities(e.elements.D4)
+e.binary.D5 = binary.equalities(e.elements.D5)
+e.binary.D6 = binary.equalities(e.elements.D6)
+
+n.elements = 100
+
+e.binary.df = data.frame('series' = c(e.binary.D3[1:n.elements], e.binary.D4[1:n.elements], e.binary.D5[1:n.elements], e.binary.D6[1:n.elements]),
+                         'elements' = rep(c(1:n.elements), 4),
+                         'D' = as.factor(c(rep(3, n.elements), rep(4, n.elements), rep(5, n.elements), rep(6, n.elements))))
+
+ggplot(e.binary.df, mapping = aes(x = elements, y = series, group = D, color = D)) + 
+    xlab("") + ylab("") +
+    ggtitle("e number") +
+    geom_line(position = position_dodge(0.8)) +
+    theme_few(base_size = 13, base_family = "serif") + 
+    facet_grid(facets = D~.) +
+    scale_y_continuous(breaks=c(0, 1)) +
+    theme(plot.title = element_text(hjust=0.5), legend.position = "none")
+```
+
+```{r} 
+pi.binary.D3 = binary.equalities(pi.elements.D3)
+pi.binary.D4 = binary.equalities(pi.elements.D4)
+pi.binary.D5 = binary.equalities(pi.elements.D5)
+pi.binary.D6 = binary.equalities(pi.elements.D6)
+
+n.elements = 100
+
+pi.binary.df = data.frame('series' = c(pi.binary.D3[1:n.elements], pi.binary.D4[1:n.elements], pi.binary.D5[1:n.elements], pi.binary.D6[1:n.elements]),
+                         'elements' = rep(c(1:n.elements), 4),
+                         'D' = as.factor(c(rep(3, n.elements), rep(4, n.elements), rep(5, n.elements), rep(6, n.elements))))
+
+ggplot(pi.binary.df, mapping = aes(x = elements, y = series, group = D, color = D)) + 
+    xlab("") + ylab("") +
+    ggtitle("pi number") +
+    geom_line(position = position_dodge(0.8)) +
+    theme_few(base_size = 13, base_family = "serif") + 
+    facet_grid(facets = D~.) +
+    scale_y_continuous(breaks=c(0, 1)) +
+    theme(plot.title = element_text(hjust=0.5), legend.position = "none")
+```
+
+```{r} 
+sqrt2.binary.D3 = binary.equalities(sqrt2.elements.D3)
+sqrt2.binary.D4 = binary.equalities(sqrt2.elements.D4)
+sqrt2.binary.D5 = binary.equalities(sqrt2.elements.D5)
+sqrt2.binary.D6 = binary.equalities(sqrt2.elements.D6)
+
+n.elements = 100
+
+sqrt2.binary.df = data.frame('series' = c(sqrt2.binary.D3[1:n.elements], sqrt2.binary.D4[1:n.elements], sqrt2.binary.D5[1:n.elements], sqrt2.binary.D6[1:n.elements]),
+                         'elements' = rep(c(1:n.elements), 4),
+                         'D' = as.factor(c(rep(3, n.elements), rep(4, n.elements), rep(5, n.elements), rep(6, n.elements))))
+
+ggplot(sqrt2.binary.df, mapping = aes(x = elements, y = series, group = D, color = D)) + 
+    xlab("") + ylab("") +
+    ggtitle("sqrt2 number") +
+    geom_line(position = position_dodge(0.8)) +
+    theme_few(base_size = 13, base_family = "serif") + 
+    facet_grid(facets = D~.) +
+    scale_y_continuous(breaks=c(0, 1)) +
+    theme(plot.title = element_text(hjust=0.5), legend.position = "none")
+```
+
+As we can see in the graphs above, the larger the dimension used, the greater the presence of patterns with repeated elements.
+When we have $D = 3$, we see that there is a greater tendency for the existence of sequential patterns with the $label = 0$ (that is, without repeated elements).
+However, as the dimension increases, this behavior is reversed.
+This fact occurs because we are analyzing numbers within the small range $[0, 9]$, so the larger the symbol considered, the greater the probability of the existence of equal elements to be grouped.

### 2020-11-10 Reports/Report - Data Imputation/Code/Bandt-Pompe.R

@@ -183,3 +183,26 @@ histogram <- function(series, D, tau = 1){
       theme_few(base_size = 14, base_family = "serif") 
   return(p)
 }
+
+#Calculated tied sequences
+
+percentual.equalities <- function(patterns){
+  n.patterns = dim(patterns)[1]
+  n.duplicated = 0
+  for(i in 1:n.patterns){
+    if(length(which(duplicated(patterns[i,]) == TRUE)))
+      n.duplicated = n.duplicated + 1
+  }
+  return(n.duplicated/n.patterns)
+}
+
+binary.equalities <- function(patterns){
+  n.patterns = dim(patterns)[1]
+  binary = rep(0, n.patterns)
+  for(i in 1:n.patterns){
+    if(length(which(duplicated(patterns[i,]) == TRUE)))
+      binary[i] = 1
+  }
+  return(binary)
+}
+

### 2020-11-10 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
adding examples of tied sequences

@@
 This fact occurs because we are analyzing numbers within the small range $[0, 9]$, so the larger the symbol considered, the greater the probability of the existence of equal elements to be grouped.
+
+### Examples of tied patterns
+
+For illustration, follow we have presented some examples of tied sequences.
+How we can observe, the implementation used for Bandt-Pompe symbolization considers the same approach of the time-ordered algorithm.
+
+```{r} 
+sqrt2.patterns.D3 = formationPattern(sqrt2.vector, 3, 1, 0)
+sqrt2.binary.D3 = binary.equalities(sqrt2.elements.D3)
+print('Elements:')
+print(sqrt2.elements.D3[which(sqrt2.binary.D3 == 1)[1:10],])
+print('Patterns:')
+print(sqrt2.patterns.D3[which(sqrt2.binary.D3 == 1)[1:10],])
+```
+```{r} 
+e.patterns.D4 = formationPattern(e.vector, 4, 1, 0)
+e.binary.D4 = binary.equalities(e.elements.D4)
+print('Elements:')
+print(e.elements.D4[which(e.binary.D4 == 1)[1:10],])
+print('Patterns:')
+print(e.patterns.D4[which(e.binary.D4 == 1)[1:10],])
+```
+```{r} 
+pi.patterns.D6 = formationPattern(pi.vector, 6, 1, 0)
+pi.binary.D6 = binary.equalities(pi.elements.D6)
+print('Elements:')
+print(pi.elements.D6[which(pi.binary.D6 == 1)[1:10],])
+print('Patterns:')
+print(pi.patterns.D6[which(pi.binary.D6 == 1)[1:10],])
+```

### 2020-11-14 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Monte Carlo

@@
 date: "Nov 10, 2020"
-
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 ---
@@
 ```
+
+# Monte Carlo study
+
+The purpose of the study is measuring the ability of imputation methods (list here which ones we will consider: I suggest the two best ones reported in the literature) to retrieve the underlying dynamic of a time series that has been *attacked*.
+In a loose sense, we will assess the *breakdown point* of the imputation techniques (study references for "breakdown poiont").
+The **attack** consists in introducing randomly repeated values in the sequence.
+
+```{r PSEUDOCODE eval=FALSE}
+# Define imputation techniques as functions
+I1 <- function(time_series, params=...){return(imputed_time_series)}
+I2 <- function(time_series){return(imputed_time_series)}
+
+# Define attack
+# Input:  "time_series" a time series without repetitions
+#         "d" embedding dimension
+#         "p" probability of attack
+AttackTimeSeries <- function(time_series, d, p) {
+  attacked_time_series <- time_series
+  foreach(d in time_series) { # Check the package foreach
+    if (runif(1) <= p) { # attack with probability p
+      select uniformly an observation in d, say at position i
+      select uniformly a position in d different from i, say j
+      replace d[j] <- d[i] # this introduces a repetition
+    }
+  }
+  return(attacked_time_series)
+}
+
+# Define the parameter space of the Monte Carlo study
+# My suggestion: white noise, for which we already have confidence intervals in the HxC plane
+
+N <- c(N1, N2, N3, ...) # lengths of the time series to be considered
+D <- c(D1, D2, D3, ...) # embedding dimensions to be considered
+P <- c(p1, p2, p3, ...) # probabilities of attack to be considered
+
+# Store all the points in the HxC plane of the following loop
+for(n in N){
+  for(d in D) {
+    for(p in P) {
+
+      x <- white_noise_length_n # perhaps from the true noise we already have
+      hcx <- point_in_the_HC_plane(x)
+      x_attack <- AttackTimeSeries(x, d, p)
+      hcxattack <- point_in_the_HC_plane(x_attack)
+
+    }
+  }
+}
+
+# Analyze the points, for instance:
+# Measure distances between pairs
+# Count the number of points inside the confidence regions
+```

### 2021-03-17 Reports/JOURNAL - Confidence Regions/Chapters/Methodology.tex
Sincronizanto
update

@@
-\section{Proposed Method}
+\section{Proposed Method}\label{Sec:Proposal}
 
-In this section, we formalize the task of building a confidence region in the Entropy-Complexity manifold.
+In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
 Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data, without the restrictions of a curvilinear space.
+Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
 Through this new representation of the data, we calculate empirical regions with different levels of confidence.
@@
 
-%\subsection{Problem Formalization}
+\subsection{Overall Framework}\label{Sec:OverallFramework}
 
-\subsection{Overall Framework}
+Our methodology consists of the following steps:
+\begin{enumerate}
+	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
+	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
+	\item\label{item:Methodology3} Obtain the principal components of these points.
+	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
+	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
+\end{enumerate}
 
-The structure of our proposal is shown in Fig.~\ref{fig:methodology}. 
-It consists of two steps:
+\subsection{True Random Numbers}\label{Sec:TRNG}
+
+Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
+Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
+Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
+%In this study we used two sources of real random numbers. 
+%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
+
+In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
+The first uses vacuum states. 
+The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
+The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
+The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
+This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
+The history of this service and other information can be found at \citet{RandomOrg}.
+
+We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
+
+%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
+
+\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
+
+We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
+We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
+On the other hand, we found two relevant variables: 
+the length of the sequence 
+and the embedding dimension.
+We, thus, employed the following factors:
 \begin{itemize}
-    \item \textbf{Empirical confidence region}: With the data present in a Euclidean plane, we can easily calculate empirical regions that involve the data with a certain level of confidence.
-    \item \textbf{Construction of a test statistic}: To measure the similarity of new data sequences with the empirical points, a test statistic was proposed. 
-    By acquiring a p-value less than 0.5, we can reject the null hypothesis, which states that such data belong to the empirical probability distribution used for the construction of the confidence region.
+	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
+	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
+	%,and
+	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
+\end{itemize}
+and kept $\tau=1$, which is the most frequently used option.
+The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
+
+Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
+For the construction of the confidence regions presented, we used:
+\begin{itemize}
+	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
+	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
 \end{itemize}
 
-\begin{figure}[H]
+We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
+
+\begin{comment}
+
+\begin{figure}
 \centering
-    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
-    \caption{Outline of the methodology used for the construction of confidence regions.}
-    \label{fig:methodology}
+\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
+\caption{White noise samples considered during the construction of the proposed confidence regions.}
+\label{fig:white-noise}
 \end{figure}
 
-\subsection{Empirical Confidence Regions}\label{confidenceRegions}
+\end{comment}
 
-As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
-Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
+\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
 
-The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\cite{martin2006generalized}.
-Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-A classic proposal in these categories of problems is the principal component analysis algorithm~\cite{wold1987principal}.
+%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
 
-Let ${\mathcal P} = \{p_n\}_{n = 1}^{N}$ be a set of $N$ observations in the $H \times C$ plane, where ${p_n} = (h_n, c_n)$ corresponds to a time series.
-We propose in this work the use of a latent space $\Omega_1 \times \Omega_2$ obtained by the PCA for the construction of empirical confidence regions, which hereinafter referred to we call HC-PCA regions.
-Let $\{(u_n, v_n)\}_{n = 1}^N$ uncorrelated observations obtained by the representation of ${\mathcal P}$ in the latent space $\Omega_1 \times \Omega_2$.
-For simplicity, and without loss of generality, assume $N$ odd; 
-in the proposed methodology, we find a parallelepiped that contains \SI{100}{\minusalphapercent} of the points in the $H \times C$ plane with the following steps:
-%We apply a principal component analysis to these points and obtain $\{(u_n,v_n)\}_{n=1}^N$.
-%This transformation yields uncorrelated observations in the $\Omega_1\times\Omega_2$ plane.
-%We will find the empirical confidence regions on the $\Omega_1\times\Omega_2$ plane, and then they will be mapped back to the $H \times C$ plane.
+Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
+Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
+Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
+%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
+
+%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
+%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
+%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
+%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
+
+Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
+In the sequel, whenever possible, we will omit $T$ and $D$.
+For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
+Fig.~\ref{fig:Methodology1} illustrates this step.
+We will obtain confidence regions and $p$-values from $\utilde{hc}$.
+
+The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
+With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
+This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
+Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
+Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
+
+For simplicity, and without loss of generality, assume $N$ is odd.
 \begin{enumerate}
-    \item Find the ranks that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-    \item Find point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-    \item Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-    \item Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-    \item The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-    \item The top and bottom bounds of the box are the minimum and maximum values of the second principal component of the points whose first principal component is at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$; denote these values $v_{\min}$ and $v_{\max}$, respectively.
+	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
+	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
+Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
+Call the corresponding time series ``emblematic time series.''
+	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
+	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
+	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
+	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
+	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
 	\item The corners of the box are 
@@
 	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-    \item Apply the inverse PCA transform to these corners obtaining $(h_{v_1}, c_{v_1})$, $(h_{v_2}, h_{v_2})$, $(h_{v_3}, c_{v_3})$ and $(h_{v_4},c_{v_4})$.
+	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
 \end{enumerate}
-The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
 
-\subsection{Construction of a test statistic}\label{test}
+Fig.~\ref{fig:methodology} illustrates these steps.
+%
+Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
+The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
+The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
+%
+Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
+The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
+We highlighted in red the point whose first principal component is the median of the observed values.
+%
+Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
+The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
 
-Using the method of construction of confidence regions described in subsection~\ref{confidenceRegions} in $M$ reference points in the $H \times C$ plane produced by sequences obtained from true-random generators of length $T$ and embedding dimension $D$, we formulate a hypothesis test that we hereinafter referred the HC-PCA test.
-Whether $\bm x'$ is a sequence of length $T$ and embedding dimension $D$, the  main idea of the HC-PCA test is based on the following null hypothesis:
-\begin{description}
-    \item[$\mathcal{H}_0$]: $\bm x'$ consists of a sequence of independent uniform random variables.
-\end{description}
-The empirical $p$-value of $\bm x'$ with respect to the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
+\begin{figure}[hbt]
+	\centering
+	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
+	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
+	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
+	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
+	\caption{Outline of the methodology used for the construction of the confidence regions.}
+	\label{fig:methodology}
+\end{figure}
+
+Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_3, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
+We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
+
+\begin{algorithm}[hbt]
+	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+	\Input{A data base of true random values}
+	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
+	\Output{Confidence regions as points in the $H\times C$ plane}
+	\For{each $D\in \mathcal D$}{
+		\For{each $T\in \mathcal T$}{
+			\For{each $n=1,2,\dots,N$}{
+				build the time series $p_n$ with unused values from the data base\;
+				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
+			}
+			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
+			%
+			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
+			%
+			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
+			%
+			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
+			%
+			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
+			\Return{$\bm P'$}\;
+			%
+			\For{each confidence level $\alpha \in \mathcal A$}{
+				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
+				%
+				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
+				%
+				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
+				%
+				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
+				%
+				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
+				%
+				the corners of the box are 
+				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
+				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
+				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
+				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
+				%
+				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
+				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
+			}
+		}
+	}
+	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
+\end{algorithm}
+
+%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
+
+These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
+More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
+We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
+
+The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
+We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
+We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
+We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
+The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
+Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
+We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
+\begin{enumerate}
+	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
+By definition, $\eta_u\geq 1/2$.
+	%
+	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
+	%
+	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
+	%
+	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
+\end{enumerate}
+Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
+
+The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
+With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
+
+Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
+Algorithm~\ref{Algo:p-value} shows the details.
+
+\begin{figure}[hbt]
+	\centering
+	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
+	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
+	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
+	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
+	\label{fig:methodologyPvalue}
+\end{figure}
+
+\begin{comment}
+The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
 Therefore, it can be achieved by the following steps:
@@
 \begin{itemize}
-    \item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the the point produced by the emblematic sequence, that is, point whose first principal component is the median of the $M$ reference points, and
+\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
 \item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
@@
 \begin{equation*}
-    p-\text{value} \geq \alpha, \text{ the null hypothesis not can be reject}.
+p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
 \end{equation*}
+\end{comment}
+
+\begin{algorithm}[hbt]
+	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
+	\Input{The embedding dimension $D$}
+	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
+		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
+		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
+	\Output{An approximate $p$-value}
+	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
+	find the point $(h,c)$ of the sequence $\bm x$\;
+	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
+	\eIf{$u_x > u$}
+	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
+		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
+	}
+	{
+		\eIf{$u_x < u$}
+		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
+			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
+		}
+		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
+		}
+	}
+	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
+	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
+	the corners of the box $b_{\alpha}(h,c)$ are 
+	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
+	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
+	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
+	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
+	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
+	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
+	\Return{$1-n_{\bm x}/N$}
+	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
+\end{algorithm}

### 2021-03-17 Reports/JOURNAL - Confidence Regions/Chapters/Results.tex
update

@@
 
-\subsection{Descriptive analysis of empirical confidence regions}
+\subsection{Empirical confidence regions}
 
-The regions used as a reference in this work are obtained through true random sequences, where we extract the empirical distribution of white noises in the Entropy-Complexity plane.
-In Fig.~\ref{fig:HC-PCA} we show the results obtained for $T = 50000$ in the scenarios of $D = 3$ and $D = 6$ in the new space defined by the PCA, together with the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane limits in this new representation space, as well as identifying the median of each data set, the latter being represented as the red dots present in the graphs.
+Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
+of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
+for $D=3,4,5,6$ and $N=1000,50000$, .
+The points are presented counterclockwise, starting with the one with the largest complexity.
+
+\begin{comment}
+\begin{table}[hbt]
+\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
+\centering
+\begin{tabular}{rcllllllll}
+\toprule
+& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
+& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
+$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
+$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+\end{tabular}
+\end{table}
+\end{comment}
+
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 1000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
+		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
+		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
+		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
+		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
+		\midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
+		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
+		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
+		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
+		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
+		\midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
+		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
+		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
+		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
+		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
+		\midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
+		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
+		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
+		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
+		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 50000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
+		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
+		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
+		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
+		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+	\end{tabular}
+\end{table}
+
+Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
+We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
+
+\begin{figure}[hbt]
+	\centering
+	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
+	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
+	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
+	\label{fig:HC-PCA}
+\end{figure}
+
+The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
+
+Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
+They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
+As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
+Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{PCA-hist-50k}
+	\caption{Histograms of the first principal component for $D=3,4,5,6$}
+	\label{fig:PCA-Hist}
+\end{figure}
+
+\subsection{Test Size}
+
+We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
+Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
+show the results.
+
+On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
+On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
+In contrast, we expected \SI{1}{\percent} of rejection.
+This might be because, in this case, the condition $D!\ll T$ is not respected.
+Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
+
+%
+%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
+%
+%For short series, $T = 1000$, and $D = 3$ 
+%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
+%
+%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
+%A reasonable explanation for this event is given in the choice of the parameter itself.
+%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
+
+\begin{table}[hbt]
+	\centering
+	\caption{Empirical sizes of the test}
+	\label{tab:result1}
+	\begin{tabular}{*{3}rr}
+		\toprule
+		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
+		%& $p$-value\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		1000 & 3 & $0.98$ & $1.00$\\
+		& 4 & $0.98$ & $0.96$\\
+		& 5 & $1.00$ & $0.94$\\
+		& 6 & $0.97$ & $0.87$\\
+		\cmidrule(lr){1-4} 
+		50000 & 3 & $0.97$ & $0.96$\\
+		%& $0.47856$\\
+		& 4 & $0.94$ & $0.95$\\
+		%& $0.47555$\\ 
+		& 5 & $0.97$ & $0.96$\\ 
+		%& $0.48512$\\ 
+		& 6 & $0.98$ & $0.99$\\ 
+		%& $0.48058$\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
+	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
+	\caption{New $100$ TRWNS and regions of confidence.}
+	\label{fig:RNG}
+\end{figure}
+
+We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
+
+\subsection{Test Power}
+
+We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
+Several studies in the literature have used this approach for identifying and characterizing randomness.
+
+Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
+Recall that the emblematic time was chosen as the most representative of the data set.
+We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
+
+%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
+As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
+
+Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
+At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
+As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
+
+Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
+We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
+Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
+The same holds for all $k>3/10$.
 
@@
 	\centering
-	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D3N50k.png}
-	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D6N50k.png}
-	\caption{Representation of truly random sequences with length $T = 50.000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-As we can see in Fig.~\ref{fig:PCA-Hist} in the new representation space produced by the PCA, the data are not evenly distributed among the axes of the first main component, maintaining the character presented in the $H \times C$ plane, since such points tend to be concentrated close to the point $(1, 0)$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{PCA-hist-50k}
-    \caption{Histogram of the PCA first component }
-    \label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Testing White Noise in the confidence regions}
-
-To analyze the efficiency of the confidence region calculated, we tested its applicability on a set of true random data generated physically not used by the algorithm during its construction. 
-The results can be seen in Fig.~\ref{fig:RNG}.
-
-For small series, $T = 1000$, and $D = 3$ we managed to maintain exactly $\SI{99}{\percent}$ of the data in the confidence region of the same value, and as the dimension increased reach $\SI{96}{\percent}$ of the points.
-On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-A reasonable explanation for this event is given in the choice of the parameter itself.
-It is known by definition that $D! << N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-For larger series, $T = 50000$, although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-    \includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-    \caption{Results of the analysis behavior of true random noises in the regions of confidence built.}
-    \label{fig:RNG}
-\end{figure}
-
-\subsection{Analyzing Robustness to Correlation Structures}
-% k=0 white
-% k=1 pink
-% k=2 brown
-% T = 1000, T = 5 10^5
-% D= 3, D = 6
-
-Fig.~\ref{fig:AllSystems} shows the behavior of random time series with different levels of correlation (by means of the $f^{-k}$ model) in the $(h,c)$ plane.
-Knowing that such plane can discriminate between different system dynamics, several studies in the literature have used this approach in the investigation of methods of identification and characterization of randomness.
-Although this same strategy can be used to characterize different levels of correlation structures, in our case, we want to analyze the impact of injecting such dynamics into noise under the aspect of confidence regions.
-
-For carrying out the experiment, we used an ''emblematic'' time series as a basis.
-This series consists of the sample corresponding to the median of the $(h,c)$ points used to build the confidence regions, thus expressing a representative sample of the dataset.
-Fig.~\ref{fig:correlation}a. illustrates, respectively, the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane as the correlation between the observations increases, that is, $k > 0$, the randomness decreases and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:correlation}b.
-illustrates the degree of limit correlation structure that can be added in white noise to eliminate it from the regions of confidence, where the red dot represents the original "emblematic" series.
-When we have $k = 0$, the features of the sequence have a small variation, corroborating the premise that series of noise $f^{-k} = 0$ have a minimum correlation measure, not significantly changing the dynamics of the system.
-
-\begin{figure}
-    \centering
-	\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}
-    \includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}
-    \caption{Correlation Structure Analysis}
+	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
+	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
+	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
 	\label{fig:correlation}
@@
 
-In this section, we evaluate the quality of the confidence regions preceded by HC-PCA with sequences of previously analyze generators in the literature with the Entropy-Complexity plane.
-For this, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator present in table~\ref{Tab:Literature} and calculated the respective p-values for each configuration of $D = \{3, 4, 5, 6\}$.
-The results obtained can be seen in table~\ref{Tab:LiteratureComparations}, where we categorize the sets of sequences among those that did not reject (NR) the null hypothesis presented in the HC-PCA test and those that rejected (R).
-
-Performing a comparative analysis of the results produced by tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we can see that the proposed methodology of confidence regions can capture the random dynamics of the sequences produced by most of the analyzed generators well, although in our experiments we consider only short sequences.
-
-However, two results deserve special attention: the sequences produced by the generators fBm and Combo RNG.
-The first one, although it was not rejected by the analysis of~\cite{olivares2012contrasting}, presented low p-values, due to the characteristic point in the $H \times C$ plane where its sequences belong.
-For the case analyzed in~\cite{olivares2012contrasting} with $D = 6$, we verified that the produced sequences present an average of $H = 0.997$, therefore they do not belong to the empirical $\SI{95}{\percent}$ confidence region produced by HC-PCA.
-Analyzing the results produced by the Combo RNG, we can verify that only for $D = 3$ the proposed method can characterize the sequences produced as random.
-This is due to the fact that by presenting higher dimension values, we were able to analyze a greater number of ordinal patterns, which may not be presented in their entirety in short sequences.
+In this section, we compare the performance of our test with that of 
+previous analyses that employ the Entropy-Complexity plane.
+To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
+Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
+We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
 
@@
 	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-    The analyzed sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
 	\label{Tab:LiteratureComparations}
@@
 		& 4 & 0.515 & NR\\ 
-		& 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
 		\bottomrule
@@
 		\cmidrule(lr){4-4}
+		LEH & 5 & 0.495 & NR\\ 
+		& 6 & 0.501 & NR\\ 
+		\cmidrule(lr){1-4}
 		fGn & 3 & 0.521 & NR\\
@@
 		\cmidrule(lr){1-4}
-		fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
+		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%\cmidrule(lr){1-4}
 		$f^{-k}$ & 3 & 0.482 & NR\\
@@
 
-\begin{comment}
-\begin{table}
-    \caption{Results of literature PRNG references for time series of size $T = 50000$}
-    \label{Tab:LiteratureComparations}
-    \centering
-    \begin{tabular}{c*{3}rcccc}
-    \toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}} & 
-		$p$-value &
-		HC-PCA & 
-		Literature Results & 
-		TestU01\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		\cmidrule(lr){5-5}
-		\cmidrule(lr){6-6}
-		\cmidrule(lr){7-7}
-		\cmidrule(lr){8-8}
-        MOT & 3 & 1 & 1 & 0.305 & NR & NR & \\
-		& 4 & 1 & 1 & 0.572  & & & \\ 
-		& 5 & 1 & 1 & 0.455 & & & \\ 
-		& 6 & 0.75 & 1 & 0.508 & & & \\ 
-		\cmidrule(lr){1-8}
-        MWC & 3 & 0.97 & 0.9625 & 0.501  & NR & NR & R\\
-        & 4 & 0.97 & 0.9825 & 0.477 & & & \\ 
-        & 5 & 0.9625 & 0.9625 & 0.496 & & & \\ 
-        & 6 & 0.9675 & 0.9625 & 0.496  & & & \\ 
-		\cmidrule(lr){1-8}
-		COM & 3 & 0.25 & 0.5 & 0.123 & NR & NR & \\
-		& 4 & 0 & 0 & 0.002 & R & & \\ 
-		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16}  & & & \\ 
-		\cmidrule(lr){1-8}
-		LEH & 3 & 0.9825 & 0.98 & 0.531 & NR & NR & NR\\
-		& 4 & 0.9675 & 0.9775 &  0.515  & & & \\ 
-		& 5 & 0.9725 & 0.9775 &  0.495 & & & \\ 
-		& 6 & 0.9775 & 0.9825 & 0.501 & & & \\ 
-		\cmidrule(lr){1-8}
-		fGn & 3 & 0.9722 & 0.9874 & 0.521 & NR & NR & \\
-		& 4 & 0.9798 & 0.9773 & 0.519 & & & \\ 
-		& 5 & 0.9646 & 0.9773 & 0.498 & & & \\ 
-		& 6 & 0.9722 & 0.9545 & 0.470 & & & \\
-		\cmidrule(lr){1-8}
-		fBm & 3 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & R & NR & \\ 
-		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		\cmidrule(lr){1-8}
-		$f^{-k}$ & 3 & 0.9525 & 0.96 & 0.482 & NR & NR &\\
-		& 4 & 0.975 & 0.9725 & 0.520 & & & \\ 
-		& 5 & 0.98 & 0.9675 & 0.513 & & & \\ 
-		& 6 & 0.9775 & 0.975 & 0.508 & & & \\
-		\cmidrule(lr){1-8}
-		LCG & 3 & 0.07 & 0.09 & 0.009 & R & R & R \\ 
-		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & & & \\ 
-    \bottomrule
-    \end{tabular}
-\end{table}
-\end{comment}
+Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
 
-\begin{comment}
-\begin{table}
-	\centering
-	\caption{Results of analysis of PRNGs with the proposed methodology}
-	\label{tab:resultFinal}
-	\begin{tabular}{c*{3}rccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		\multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}} &  
-		$p$-value &
-		HC-PCA &   
-		TestU01\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		\cmidrule(lr){5-5}
-		\cmidrule(lr){6-6}
-		\cmidrule(lr){7-7}
-		Wichmann-Hill & 3 & 0.97 & 0.96 & 0.478 & NR & R\\ 
-		& 4 & 0.9675 & 0.9675 & 0.513 & & \\ 
-		& 5 & 0.9725 & 0.965 & 0.501 & & \\ 
-		& 6 & 0.97 & 0.97 & 0.491 & & \\ 
-		\cmidrule(lr){1-7}
-		Super-Duper & 3 & 0.9675 & 0.975 & 0.496 & NR & R\\
-		& 4 & 0.9775 & 0.9725 & 0.512 & &\\ 
-		& 5 & 0.9675 & 0.985 & 0.525 & &\\ 
-		& 6 & 0.9825 & 0.965 & 0.507 & &\\ 
-		\cmidrule(lr){1-7}
-		Knuth-TAOCP-2002 & 3 & 0.9775 & 0.9625 & 0.513 & NR & NR\\ 
-		& 4 & 0.965 & 0.98 & 0.481 & &\\ 
-		& 5 & 0.9625 & 0.9825 & 0.494 & &\\ 
-		& 6 & 0.9725 & 0.96 & 0.479 & &\\  
-		\cmidrule(lr){1-7}
-		Knuth-TAOCP & 3 & 0.975 & 0.9775 & 0.480 & NR & NR\\
-		& 4 & 0.965 & 0.9725 & 0.519 & &\\ 
-		& 5 & 0.9875 & 0.985 & 0.531 & &\\ 
-		& 6 & 0.9725 & 0.975 & 0.515 & &\\ 
-		\cmidrule(lr){1-7}
-		LEcuyer-CMRG & 3 & 0.98 & 0.98 & 0.505 & NR & NR\\ 
-		& 4 & 0.9675 & 0.9725 & 0.490 & &\\ 
-		& 5 & 0.965 & 0.9725 & 0.512 & &\\ 
-		& 6 & 0.9625 & 0.97 & 0.524 & &\\ 
-		\cmidrule(lr){1-7}
-		Mersenne-Twister & 3 & 0.9725 & 0.97 & 0.506 & NR & NR\\ 
-		& 4 & 0.98 & 0.97 & 0.499 & &\\ 
-		& 5 & 0.9725 & 0.9775 & 0.524 & &\\ 
-		& 6 & 0.975 & 0.9725 & 0.502 & &\\ 
-		\cmidrule(lr){1-7}
-		Randu & 3 & 0.2275 & 0.42 & 0.032 & R & R\\ 
-		& 4 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\ 
-		& 5 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\ 
-		& 6 & 0 & 0 & \num[scientific-notation=true]{1.11 e-16} & &\\  
-		\cmidrule(lr){1-7}
-		pcg64 & 3 & 0.97 & 0.9675 & 0.510 & NR & NR\\
-		& 4 & 0.97 & 0.97 & 0.503 & &\\ 
-		& 5 & 0.9775 & 0.9625 & 0.508 & &\\ 
-		& 6 & 0.9575 & 0.9575 & 0.502 & &\\ 
-		\cmidrule(lr){1-7}
-		Threefry & 3 & 0.9625 & 0.97 & 0.491 & NR & NR\\ 
-		& 4 & 0.975 & 0.97 & 0.506 & &\\ 
-		& 5 & 0.96 & 0.9625 & 0.506 & &\\ 
-		& 6 & 0.965 & 0.955 & 0.473 & &\\ 
-		\cmidrule(lr){1-7}
-		Xoroshiro128+ & 3 & 0.975 & 0.9825 & 0.501 & NR & R\\ 
-		& 4 & 0.995 & 0.9825 & 0.493 & &\\ 
-		& 5 & 0.98 & 0.9725 & 0.503 & &\\ 
-		& 6 & 0.9725 & 0.955 & 0.513 & &\\
-		\cmidrule(lr){1-7}
-		Xoshiro256+ & 3 & 0.98 & 0.98 & 0.502 & NR & NR\\ 
-		& 4 & 0.9675 & 0.965 & 0.489 & &\\ 
-		& 5 & 0.9525 & 0.96 & 0.492 & &\\ 
-		& 6 & 0.9775 & 0.975 & 0.513 & &\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\end{comment}
+It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
+In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.

### 2021-03-17 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex
update

--- 2020-10-31 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex
@@
-\section{Entropy-Complexity plane in the literature}
+\subsection{The Entropy-Complexity Plane in the Literature}\label{Sec:BPApplications}
 
-The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cite{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
-However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cite{larrondo2002statistical, gonzalez2005statistical}.
+Initial works on the characterization of white noises with permutation entropy arose from the need to discriminate between them and chaotic maps \citep{rosso2013characterization, xiong2020complexity}.
+Notice that the logistic map has been used for pseudorandom number generation; cf.
+\citet{AnalyzingLogisticMapPseudorandomNumberGeneratorsforPeriodicityInducedbyFinitePrecisionFloatingPointRepresentation} and the references therein.
+It was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using Information Theory descriptors with the Bandt-Pompe symbolization \citep{larrondo2013statistical, gonzalez2005statistical}.
 
-Table~\ref{Tab:Literature} presents a summary of the main works in the literature that perform analysis of non-chaotic algorithmic generators, according to their features $(h, c)$.
-For this, we also provide the length $T$ and embedding dimension $D$ applied in the analysis of the time series.
+Table~\ref{Tab:Literature} presents a summary of the main works in the literature that perform analysis of non-chaotic algorithmic generators, according to their features in the $H\times C$ plane.
+We also provide the length $T$ and embedding dimension $D$ of the time series under scrutiny.
 The following algorithmic generators were analyzed:
 \begin{itemize}
-    %\item[$-$] RNG available in Intel fortran compiler (FOR)
-    %\item[$-$] RNG available in Borland C++ compiler (CCC)
-    %\item[$-$] Matlab RAND function (MAT)
-    \item Mother RNG, available in Marsaglia website~\cite{marsaglia1994yet} (MOT);
-    \item Multiple with carry RNG (MWC)~\cite{marsaglia1994yet};
-    \item Combo RNG (COM)~\cite{marsaglia1994yet};
-    \item Lehmer RNG (LEH)~\cite{payne1969coding};
-    \item Fractional Gaussian noise with $\alpha = 0$ (fGn);
-    \item Fractional Brownian motion with $\alpha = 1.2$ (fBm);
-    \item $f^{-k}$ noise with $k = 0$;
-    \item Linear Congruential Generator (LCG)~\cite{knuth1997sorting}.
+	\item Mother RNG, available in Marsaglia's website \citep[MOT,][]{marsaglia1994yet};
+	\item Multiple with carry RNG \citep[MWC,][]{marsaglia1994yet};
+	\item Combo RNG \citep[COM,][]{marsaglia1994yet};
+	\item Lehmer RNG \citep[LEH,][]{payne1969coding};
+	\item Fractional Brownian motion (fBm) and fractional Gaussian noise (fGn); see \citet{bardet2003generators};
+	\item Colored noise with power spectrum $f^{-k}$ with $k \geq 0$~\citep{larrondo2012matlab};
+	\item Linear Congruential Generator \citep[LCG,][]{knuth1997sorting}.
 \end{itemize}
 
-\begin{table}[H]
-    \caption{Result of the main works of white noise sequences analysis in the $H \times C$ plane.}
+\begin{table}[hbt]
+	\caption{Results of the main works of white noise sequences analysis in the $H \times C$ plane.}
 	\label{Tab:Literature}
 	\centering
-    \begin{tabular}{llcccccc}
+	\begin{tabular}{llcccc b{5.4em}}
 		\toprule
-Reference & PRNG & $T$ & $D$ & $H$ & $C$ & Is white noise? & $p$-value\\ 
+		Reference & PRNG & $T$ & $D$ & $H$ & $C$ & Considered random? \\ 
 		\midrule
-\citeauthor{larrondo2002statistical} (\citeyear{larrondo2002statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no & NA\\
-%&  FOR & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
-%&  CCC & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
-%&  MAT & NA & 6 & $\cong 0.997$ & $\cong 0$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes & NA\\
- &  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{RandomNumberGeneratorsCausality} (\citeyear{RandomNumberGeneratorsCausality}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MOT & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
- &  MWC & \num[scientific-notation=true]{5 e6} & 5 & NA & $10^{-4}$ & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{olivares2012contrasting} (\citeyear{olivares2012contrasting}) &  fGn & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.998$ & NA & yes & NA\\
- & fBm & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.993$ & NA & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e15} & 6 & $\cong 0.997$ & NA & yes & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no & NA\\
-\cmidrule(lr){1-8}
-\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
- & $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes & NA\\
+		\citeauthor{larrondo2013statistical} (\citeyear{larrondo2013statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{RandomNumberGeneratorsCausality} (\citeyear{RandomNumberGeneratorsCausality}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes \\
+		&  MOT & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		&  MWC & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
+		& $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
 		\bottomrule
@@
 \end{table}
+
+None of these works provide $p$-values or hypothesis tests for their analysis.
+The focus of the articles is finding the set of descriptors that best discriminates chaos from noise.
+The authors make assessments about the randomness of sequence on ad hoc visual inspection of the point's location in the $H\times C$ plane.
+Our work fills such a gap for finite sequences of white noise and proposes a methodology that can be extended to any other situation.

### 2021-03-17 Code/Alejandro/ConfidenceRegion_p-value.R

@@ -1,0 +1,78 @@
+require(ggplot2)
+require(ggthemes)
+
+# Illustration of the confidence region
+set.seed(123456, kind="Mersenne-Twister")
+N <- 51
+a <- 0.47
+  
+u <- runif(N, min = -3, max = 3)
+v <- runif(N, min=-1, max=1)
+ru <- sort(u, index.return=TRUE)$ix
+rv <- sort(v, index.return=TRUE)$ix
+
+uv <- data.frame(u=u, v=v, ru=ru, rv=rv)
+
+
+# p-value of point X
+X <- data.frame(u=2, v=1)
+
+step1 <- ggplot(data=uv, aes(x=u, y=v)) +
+  geom_point(size=ifelse(u==median(u), 6.8, 6),
+             col=ifelse(u==median(u), "red", "seashell4")) +
+  geom_point(data=X, size=6, shape=13, col="maroon") +
+  xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
+  xlab(expression(italic(u))) +
+  ylab(expression(italic(v))) +
+  theme_clean(base_size = 30, base_family = "sans")
+
+# Confidence region at level a
+step2 <- ggplot(data=uv, aes(x=u, y=v)) +
+  geom_hline(yintercept = 0, col="gray") +
+  geom_vline(xintercept = 0, col="gray") +
+  geom_vline(xintercept = u[ru[round(N*a/2)]], linetype=2, col="red") +
+  geom_vline(xintercept = u[ru[round(N*(1-a/2))]], linetype=2, col="red") +
+  geom_point(size=ifelse(u==median(u), 6.8, 
+                         ifelse(u==u[ru[round(N*a/2)]], 6.8, 
+                                ifelse(u==u[ru[round(N*(1-a/2))]], 6.8, 6))),
+             col=ifelse(u==median(u), "red", 
+                        ifelse(u==u[ru[round(N*a/2)]], "green3", 
+                               ifelse(u==u[ru[round(N*(1-a/2))]], "green3", "seashell4")))) + 
+  geom_point(data=X, size=6, shape=13, col="maroon") +
+  geom_rug(sides = "b", 
+           col=ifelse(u==median(u), "red", "gray"),
+           size=ifelse(u==median(u), 1.2, 1)) +
+  xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
+  xlab(expression(italic(u))) +
+  ylab(expression(italic(v))) +
[…]

### 2021-03-17 Code/Bandt-Pompe.R

@@ -1,0 +1,215 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 18, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+# Packages and sources ---------------------------------------------------------------------------------
+if(!require(gtools)){
+  install.packages("gtools")
+  require(gtools)
+} 
+
+# Auxiliar Function -------------------------------------------------------------------------------------
+
+define.symbols <- function(D){
+  d = c(1:D)
+  symbol = matrix(unlist(permutations(n = D, r = D, v = d)),nrow = factorial(D), ncol = D, byrow = FALSE)
+  symbol = symbol - 1
+  symbol
+}
+
+FP <- function(n, dimension, delay){
+  dyn.load("FormationPatterns.so")
+  p <- .Call("FormationPatterns", n, dimension, delay)
+  p = t(p) + 1
+  return(p)
+}
+
+percentual.equalities <- function(patterns){
+  n.patterns = dim(patterns)[1]
+  n.duplicated = 0
+  for(i in 1:n.patterns){
+    if(length(which(duplicated(patterns[i,]) == TRUE))){
+      n.duplicated = n.duplicated + 1
+      print(length(which(duplicated(patterns[i,]) == TRUE)))
+    }
+  }
+  return(n.duplicated/n.patterns)
+}
+
+formationPattern <- function(series, D, tau, option){
+  
+  i = 1
+  n = length(series)
+  p_patterns = elements = matrix(nrow = n, ncol = D)
+  index = c(0:(D-1))
+  
+  for(s in seq(1, length(series)-(D-1)*tau, by = 1)){
+    # the indices for the subsequence
+    ind = seq(s, s+(D-1)*tau, by = tau)
+    elements[i,] = series[ind]
+    p_patterns[i,] = index[order(elements[i,])]
+    i = i + 1
+  }
+  
+  if(option == 0){
+    p_patterns = na.omit(p_patterns)
+    return(p_patterns[1:(i-1),])
+  }else if(option == 1){
+    elements = na.omit(elements)
+    return(elements[1:(i-1),])    
+  }
+}
+
+# Bandt-Pompe function ---------------------------------------------------------------------------------
+
[…]

### 2021-03-17 Code/Correlation-Analysis.R

@@ -1,0 +1,166 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 20, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+source("Bandt-Pompe.R")
+source("Level-confidence-region.R")
+if(!require(fftw)) install.packages("fftw")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+if(!require(latex2exp)) install.packages("latex2exp")
+
+# Generator of noise with power spectrum f^-k --------------------------------------------------------
+set.seed(seed = 123, kind = "Mersenne-Twister")
+
+series.generator.fk <- function(pp, y, n, k){
+  Series = vector(mode="numeric")
+  filtro = (1:n)^-(k/2)
+  filtro = filtro / sum(filtro)
+  y1 = y * filtro    
+  x1 = IFFT(y1, plan = pp)  
+  Series = c(Re(x1)) 
+  return(Series)
+}
+
+# Correlation Structure Analysis function --------------------------------------------------------------
+correlation.analysis.point <- function(){
+  
+  rainbow_colors = palette(c("#fca311",#amarelo
+                             "#000000", #preto
+                             "#ff006e", #rosa
+                             "#40916c", #verde
+                             "#6a040f", #vermelho
+                             "#eb5e28", #laranja
+                             "#6a4c93", #roxo
+                             "#50514f", #cinza
+                             "#5e3023", #marrom
+                             "#3f88c5", #azul
+                             "#60d394"))
+  D = 6
+  N = 50000
+  k = c(0, 0.1, 0.2, 0.3)
+  
+  ts = read.csv("../Data/Emblematic-series-D6-N50000.csv")[,2]
+  probs.ts = bandt.pompe(ts, 6, 1)
[…]

### 2021-03-17 Code/Deterministic-Analysis.R

@@ -1,0 +1,124 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jul 12, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+source("Bandt-Pompe.R")
+source("Level-confidence-region.R")
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+} 
+if(!require(ggrepel)){
+  install.packages("ggrepel")
+  require(ggrepel)
+} 
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+} 
+
+theme_set(theme_clean())
+
+# Trozos plot ---------------------------------------------------------------------------------------
+plot.cotas <- function(D){
+  c1x = readingMPR(D,1)
+  c1y = readingMPR(D,2)
+  c2x = readingMPR(D,3)
+  c2y = readingMPR(D,4)
+  
+  cotas.1xy = data.frame("c1x" = c1x, "c1y" = c1y)
+  cotas.2xy = data.frame("c2x" = c2x, "c2y" = c2y)
+  
+  p = ggplot(cotas.1xy, aes(c1x, c1y)) + 
+    geom_line(size = 0.5, color = "gray") +
+    geom_line(aes(x = c2x, y = c2y), cotas.2xy, size = 0.5, color = "gray") +
+    theme(plot.title = element_text(hjust = 0.5)) 
+  return(p)
+}
+
+# Ramp process -----------------------------------------------------------------------------------------
+ramp.function <- function(N, n) {
+  x <- 1:N
+  y <- (x %% n ) / n
+  return(y)
+}
+
+ramp.contamination.plot <- function(N, noise, ramp){
+  df = data.frame(x = c(1:N), noise = noise, ramp = ramp)
+  
+  pdf("Ramp-contamination-D6-N50k.pdf", width = 7, height = 7)
+  p = ggplot(df, aes(x = x, y = ramp)) +
+      geom_line(col = "gray") +
+      #geom_line(aes(x = x, y = ramp+noise), col = "red") +
[…]

### 2021-03-17 Code/Emblematic-Point-Search.R

@@ -1,0 +1,57 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 19 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+
+filenames <- list.files(path = "../Data/random.org/")
+
+## Get names without ".DAT" and store in "names"
+names <- substr(filenames, 1, 10)
+
+index <- c(1:length(names))
+j <- 0
+dados <- vector()
+
+##Loading data from files
+for(i in names){
+  j <- j + 1
+  filepath <- file.path(paste("../Data/random.org/", i,".bin",sep=""))
+  assign("Data", readBin(filepath, n = 1e8, size = "4", what ='integer'))
+  dados <- c(dados, Data)
+}
+
+dados <- abs(dados/max(dados))
+write.csv(dados[1:50000], file = "../Data/random_sample.csv")
+
+source("bandt_pompe/bandt_pompe.R")
+source("bandt_pompe/measures.R")
+source("bandt_pompe/features.R")
+source("bandt_pompe/visibility.R")
+source("bandt_pompe/helpers.R")
+
+random_50k <- readBin('data/random_50k.bin',n=1e8,size="4",what ='integer')
+seq_50k <- abs(random_50k/max(random_50k))
+split_seq <- as.matrix(split(seq_50k, ceiling(seq_along(seq_50k)/50000)))
+ts = matrix(nrow = 50000, ncol = 104)
+
+for(i in 1:104){
+  ts[,i] = split_seq[[i]]
+}
+
+for(i in 1:104){
+  probs = bandt.pompe(ts[,i], 6, 1)
+  h = shannon.entropy.normalized(probs)
+  c = Ccomplexity(probs)
+  cat("i: ", i, " H: ", h, " C: ", c, "\n")
+  
+  print(test.point(H = h, C = c, D = 6, N = 50000, region = 90))
+}
+
+#H = 0.9989109
+#C = 0.002609346
+
+write.csv(ts[,1], "Emblematic-series-D6-N50000.csv")

### 2021-03-17 Code/HCPlanePlots.R

@@ -1,0 +1,334 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Nov 22, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+require(ggplot2)
+require(ggthemes)
+require(ggpubr)
+require(reshape2)
+require(ggrepel)
+require(grid)
+require(gridExtra)
+require(fftw)
+if(!require(gtools)){
+  install.packages("gtools")
+  require(gtools)
+} 
+source("Bandt-Pompe.R")
+
+
+# Paleta montada a partir de https://coolors.co/ -------------------------------------------------------
+rainbow_colors <- palette(c("#494947", # 1
+                            "#7494EA", # 2
+                            "#B14AED", # 3
+                            "#44CCFF", # 4
+                            "#35FF69", # 5
+                            "#ED8438", # 6
+                            "#00296b", # 7
+                            "#ffff3f", # 8
+                            "#d62828", # 9
+                            "#FB4D3D", # 10
+                            "#f72585") # 11
+)
+
+#Função geradora da série f^⁻k--------------------------------------------------------------------------
+series_generator_fk <- function(pp, y, n, k){
+  Series <- vector(mode="numeric")
+  filtro <- (1:n)^-(k/2)
+  filtro <- filtro / sum(filtro)
+  y1 <- y * filtro    
+  x1 <- IFFT(y1, plan=pp)  
+  Series <- c(Re(x1)) 
+  Series
+}
+
+#Função geradora do mapa logístico----------------------------------------------------------------------
+series_generator_map <- function(r, x_0, n){
+  Series <- vector(mode="numeric",length = n)
+  Series[1] <- x_0
+  for(i in c(2:n)){
+    Series[i] <- r*Series[i-1]*(1 - Series[i-1])
+  }
+  Series
+}
+
+Entropy.complexity.values <- function(series, dimension, delay, type, rainbow_colors){
[…]

### 2021-03-17 Code/Histogram-Analysis.R

@@ -1,0 +1,150 @@
+source("Bandt-Pompe.R")
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(fftw)){
+  install.packages("fftw")
+  require(fftw)
+}
+if(!require(grid)){
+  install.packages("grid")
+  require(grid)
+}
+
+rainbow_colors <- palette(c("#494947", #DarkGreen
+                            "#7494EA", #MutedDarkBlue
+                            "#B14AED", #Violet
+                            "#44CCFF", #BrightLightBlue
+                            "#35FF69", #BrightGreen
+                            "#ED8438", #Orange
+                            "#E7AD99", #Pink
+                            "#C18C5D", #LightBrown
+                            "#BF6F00", #DarkYellow
+                            "#FB4D3D", #BrightRed
+                            "#495867") #DarkGray
+)
+
+series.generator.fk <- function(pp, y, n, k){
+  Series <- vector(mode="numeric")
+  filtro <- (1:n)^-(k/2)
+  filtro <- filtro / sum(filtro)
+  y1 <- y * filtro    
+  x1 <- IFFT(y1, plan=pp)  
+  Series <- c(Re(x1)) 
+  Series
+}
+
+series.generator.map <- function(r, x_0, n){
+  Series <- vector(mode="numeric",length = n)
+  Series[1] <- x_0
+  for(i in c(2:n)){
+    Series[i] <- r*Series[i-1]*(1 - Series[i-1])
+  }
+  Series
+}
+
+calculate.histogram <- function(ts, d, t, name.title){
+  fat = factorial(d)
+  symbol = define.symbols(d)
+  p.patterns = formationPattern(ts, d, t, 0)
+  n.symbols = dim(p.patterns)[1]
+  index.rep = array(0, n.symbols)
+  
+  for(i in 1:n.symbols){
+    for(j in 1:fat){
+      if(all(p.patterns[i,] == symbol[j, ])){
+        index.rep[i]=j
+        break
+      }
+    }
+  }
+  index.rep = data.frame(i = index.rep)
+  p = ggplot(index.rep) +
+    geom_histogram(aes(x = i, y = ..density..),
[…]

### 2021-03-17 Code/Level-confidence-region.R

@@ -1,0 +1,50 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 12, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+
+# Analysis functions -----------------------------------------------------------------------------------
+
+get.confidence.region <- function(HC, ph, pc, D, N){
+  pca_HC = prcomp(x = HC[,-3], retx = TRUE, 
+                  center=TRUE, scale. = TRUE)
+  PC = data.frame(PC1 = pca_HC$x[,1], PC2 = pca_HC$x[,2])
+  
+  test = TRUE
+  step.loop = 0
+  region.test = 1.001
+  
+  attach(PC)
+  while(test){
+    step.loop = step.loop + 0.001
+    region.test = region.test - 0.001
+    
+    (qpc1 = quantile(PC1, probs = c(step.loop, 0.5, 1-step.loop)))
+    (yqpc1 = c(max(abs(PC2[PC1 > qpc1[1] & PC1 < qpc1[3]]))))
+    rect = data.frame(xmin = qpc1[1], xmax = qpc1[3], ymin = -yqpc1[1], ymax = yqpc1[1])
+    rect = matrix(unlist(rect), nrow = 2, ncol = 2)
+    
+    my.order = c(1,2,4,3)
+    M = mesh(rect[,1], rect[,2])
+    rect = matrix(nrow = 4, ncol = 2)
+    rect[,1] = M$x
+    rect[,2] = M$y
+    rect = t(t(rect %*% t(pca_HC$rotation)) * pca_HC$scale + pca_HC$center)
+    rect = data.frame("H" = rect[my.order, 1], 
+                      "C" = rect[my.order, 2],
+                      stringsAsFactors=FALSE)
+    rect$H[rect$H < 0] = 0
+    rect$C[rect$C < 0] = 0
+    rect$H[rect$H > 1] = 1
+    rect$C[rect$C > 1] = 1
+    
+    test = point.in.polygon(ph, pc, rect$H, rect$C)
+  }
+  detach(PC)
+  cat("Level of the smallest confidence region to which it belongs this point: ", region.test*100, "%\n")
+  return(region.test)
+}

### 2021-03-17 Code/PNRG-Analysis.R

@@ -1,0 +1,611 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 22, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Bandt-Pompe.R")
+source("Test-point.R")
+if(!require(dqrng)){
+  install.packages("dqrng")
+  require(dqrng)
+}
+if(!require(gtools)){
+  install.packages("gtools")
+  require(gtools)
+}
+if(!require(latex2exp)){
+  install.packages("latex2exp")
+  require(latex2exp)
+}
+if(!require(doParallel)){
+  install.packages("doParallel")
+  require(doParallel)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+
+# Number generating functions --------------------------------------------------------------------------
+
+seed <- as.double(1)
+RANDU <- function(){
+  set.seed(123, kind = "Mersenne-Twister")
+  seed <<- ((1103515245 * seed ) + 12345 ) %% (2^31)
+  return(seed)
+}
+
+lehmer.rng <- function(n) {
+  
+  rng <- vector(length = n)
+  
+  m <- 2147483647
+  a <- 48271
+  q <- 44488
+  r <- 3399
+  
+  # Set the seed using the current system time in microseconds. 
+  # The initial seed value must be coprime to the modulus m, 
+  # which we are not really concerning ourselves with for this example.
+  d <- as.numeric(Sys.time())
+  
+  for (i in 1:n) {
+    h <- d / q
+    l <- d %% q
+    t <- a * l - r * h
+    if (t > 0) {
+      d <- t
+    }
+    else {
[…]

### 2021-03-17 Code/RNG-Analysis.R

@@ -1,0 +1,146 @@
+  ########################################################################################################
+  # Author: Eduarda Chagas
+  # Date : Jun 30, 2020
+  # Contact: eduarda.chagas@dcc.ufmg.br
+  ########################################################################################################
+  
+  # Packages and sources ---------------------------------------------------------------------------------
+  source("Test-point.R")
+  if(!require(ggpubr)){
+    install.packages("ggpubr")
+    require(ggpubr)
+  }
+  if(!require(ggplot2)){
+    install.packages("ggplot2")
+    require(ggplot2)
+  }
+  if(!require(ggthemes)){
+    install.packages("ggthemes")
+    require(ggthemes)
+  }
+  if(!require(reshape2)){
+    install.packages("reshape2")
+    require(reshape2)
+  }
+  if(!require(latex2exp)){
+    install.packages("latex2exp")
+    require(latex2exp)
+  }
+  
+  # Analysis functions -----------------------------------------------------------------------------------
+  RNG.HC.confidence.regions <- function(D = 3, N = 1000, horizontal = 1){
+    
+    if(N == 1000){
+      if(D == 3)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/5z1f01nu449d44m/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 4)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/vquh76d4kaqoxcm/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 5)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/37tygdzigybzu7u/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 6)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/0ez7bq8zn98phqg/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+    }else{
+      if(D == 3)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/9enu26i3sdd77a4/Random_", 50, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 4)
[…]

### 2021-03-17 Code/Regions-HC-table.R

@@ -1,0 +1,78 @@
+
+regions.HC.D3 = read.csv("../Data/Regions-HC/regions-hc-D3-N1000.csv")
+regions.HC.D4 = read.csv("../Data/Regions-HC/regions-hc-D4-N1000.csv")
+regions.HC.D5 = read.csv("../Data/Regions-HC/regions-hc-D5-N1000.csv")
+regions.HC.D6 = read.csv("../Data/Regions-HC/regions-hc-D6-N1000.csv")
+
+regions       = data.frame(H.90 = c(regions.HC.D3$H[1], regions.HC.D3$H[2], regions.HC.D3$H[3], regions.HC.D3$H[4],
+                                    regions.HC.D4$H[1], regions.HC.D4$H[2], regions.HC.D4$H[3], regions.HC.D4$H[4],
+                                    regions.HC.D5$H[1], regions.HC.D5$H[2], regions.HC.D5$H[3], regions.HC.D5$H[4],
+                                    regions.HC.D6$H[1], regions.HC.D6$H[2], regions.HC.D6$H[3], regions.HC.D6$H[4]),
+                           C.90 = c(regions.HC.D3$C[1], regions.HC.D3$C[2], regions.HC.D3$C[3], regions.HC.D3$C[4],
+                                    regions.HC.D4$C[1], regions.HC.D4$C[2], regions.HC.D4$C[3], regions.HC.D4$C[4],
+                                    regions.HC.D5$C[1], regions.HC.D5$C[2], regions.HC.D5$C[3], regions.HC.D5$C[4],
+                                    regions.HC.D6$C[1], regions.HC.D6$C[2], regions.HC.D6$C[3], regions.HC.D6$C[4]),
+                           H.95 = c(regions.HC.D3$H[5], regions.HC.D3$H[6], regions.HC.D3$H[7], regions.HC.D3$H[8],
+                                    regions.HC.D4$H[5], regions.HC.D4$H[6], regions.HC.D4$H[7], regions.HC.D4$H[8],
+                                    regions.HC.D5$H[5], regions.HC.D5$H[6], regions.HC.D5$H[7], regions.HC.D5$H[8],
+                                    regions.HC.D6$H[5], regions.HC.D6$H[6], regions.HC.D6$H[7], regions.HC.D6$H[8]),
+                           C.95 = c(regions.HC.D3$C[5], regions.HC.D3$C[6], regions.HC.D3$C[7], regions.HC.D3$C[8],
[…]

### 2021-03-17 Code/Trozos-HC-PCA.R

@@ -1,0 +1,179 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 30, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+source("Bandt-Pompe.R")
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(latex2exp)){
+  install.packages("latex2exp")
+  require(latex2exp)
+}
+
+plot.HC.PCA.trozos <- function(N, dim, lengend ,x.lim = NULL, y.lim = NULL){
+  if(N == 1000){
+    HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+  }else if(N == 50000){
+    HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+  }
+  
+  names(HC) <- c("H", "C", "D")
+  HC$D <- as.factor(HC$D)
+  HC.D <- subset(HC, D == dim)[,-3]
+  HC.D <- HC.D[,-3]
+  PCA.HC.D <- prcomp(x = HC.D[,-3], 
+                     retx = TRUE, 
+                     center = TRUE, 
+                     scale. = TRUE)
+  
+  # Trozos data ----------------------------
+  cotas.sup <- cotas(dim, 0)
+  cotas.sup <- data.frame("H" = cotas.sup$cx, 'C' = cotas.sup$cy)
+  cotas.inf <- cotas(dim, 1)
+  cotas.inf <- data.frame("H" = cotas.inf$cx, 'C' = cotas.inf$cy)
+  
+  index.i = which(cotas.sup$H >= min(HC.D$H) & cotas.sup$H <= 1)
+  sup = cotas.sup[index.i,]
[…]

### 2021-03-17 Code/methodology.R

@@ -1,0 +1,162 @@
+source("Bandt-Pompe.R")
+if(!require(latex2exp)){
+  install.packages("latex2exp")
+  require(latex2exp)
+}
+if(!require(ggrepel)){
+  install.packages("ggrepel")
+  require(ggrepel)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+#library(directlabels)
+#if(!require(plot3D)){
+#  install.packages("plot3D")
+#  require(plot3D)
+#} 
+
+
+D = 6
+N = 50000
+HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+index = which(HC$D == D)
+HC = HC[index[1:15], ]
+
+cotas.sup = cotas(D, 0)
+cotas.sup = data.frame("H" = cotas.sup$cx, 'C' = cotas.sup$cy)
+cotas.inf = cotas(D, 1)
+cotas.inf = data.frame("H" = cotas.inf$cx, 'C' = cotas.inf$cy)
+
+index.i = which(cotas.sup$H >= 0.9985 & cotas.sup$H <= 1)
+sup = cotas.sup[index.i,]
+sup = data.frame(H = sup$H, C = predict(lm(data = sup, formula = C ~ poly(H, 3))))
+cotas.sup = data.frame(H = c(cotas.sup[-index.i,]$H, sup$H), 
+                       C = c(cotas.sup[-index.i,]$C, sup$C))
+
+index.j = which(cotas.inf$H >= 0.9985 & cotas.inf$H <= 1)
+inf = cotas.inf[index.i,]
+inf = data.frame(H = inf$H, C = predict(lm(data = inf, formula = C ~ poly(H, 3))))
+cotas.inf = data.frame(H = c(cotas.inf[-index.i,]$H, inf$H), 
+                       C = c(cotas.inf[-index.i,]$C, inf$C))
+
+step1 <- ggplot(HC, aes(x = H, y = C)) + geom_point(size=4) +
+  geom_line(data = cotas.sup, aes(x = H, y = C), color="gray") +
+  geom_line(data = cotas.inf, aes(x = H, y = C), color="gray") + 
+  xlim(limits = c(0.9985, 1)) + 
+  ylim(limits = c(0, 0.004)) + 
[…]

### 2021-09-30 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Research proposal

\documentclass[12pt]{article}

\usepackage[binary-units]{siunitx}
\usepackage{fouriernc}
\usepackage{amsmath,amssymb}
\usepackage{natbib}
\usepackage{bm,bbm}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{{./Figures/}}

\title{Research Proposal}

\begin{document}
\maketitle

We already have purely empirical results about the confidence region of points in the $H\times C$ plane under white noise.
In this work, we propose advancing such a knowledge by using a general model for discrete distributions.

\section{Introduction}

Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
As stated by \citet{PermutationEntropyBandtPompe} in their seminal work:  
\begin{quote}
	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
\end{quote}
Also, as stressed by these authors, 
\begin{quote}
	``The corresponding symbol sequence must come 
	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
\end{quote}

Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
possible permutation of order $D$, and the symbol component vector 
${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
($\pi_j \neq \pi_k~\forall~j \neq k$). 
Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
\begin{equation} 
	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
	\label{eq:time-delay}
\end{equation} 
for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
This mapping should be defined in a way that preserves the desired relation between the elements 
$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
${\bm \pi}^{(D)}$. 
The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
\begin{enumerate}[label=\alph*)]
	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
	(\textit{Rank Permutation}) or,
	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
	(\textit{Chronological Index Permutation}).
\end{enumerate}
See details in the work by \citet{BPRepeatedValuesChaos}.
Without loss of generality, in the following, we will use the latter.

Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.

The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=.7\linewidth]{IntroBP}
	\caption{Illustration of the Bandt and Pompe coding}
	\label{Fig:IntroBP}
\end{figure}

After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
The next step into the characterization of the time series is computing descriptors from this histogram.

The first descriptor is a measure of the disorder of the system.
The most frequently used feature for this is the Normalized Shannon entropy, defined as
\begin{equation}
	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
\end{equation}
with the convention that terms in the summation for which $h(j)=0$ are null.
This quantity is bounded in the unit interval. 
It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!^2}, \dots, \frac{1}{D!^2}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
It is calculated as:
\begin{equation}
	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!^2} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
	u_\ell \log\frac{u_\ell}{h_\ell}
	\Big).
\end{equation}
This quantity is also called ``disequilibrium.''
The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.

With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
A time series can then be mapped into a point in the $H\times C$ plane.

The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
The time delay is irrelevant, and we consider infinitely long series.

Let us consider two extreme cases:
\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
	The entropy is zero, and the distance to the uniform distribution is maximal. 
	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
	The distance to the equilibrium distribution is zero. 
	Thus, such series are mapped onto the point $(1,0)$.
\end{enumerate}

\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
The upper boundary converges to a smooth curve when $D\to\infty$.

Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
The inset plot highlights the fine structure of the upper boundary inside the rectangle.
The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
\end{figure}

Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{RightMostCorner}
	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
	\label{fig:RightMostCorner}
\end{figure}

Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
In a previous work, we assessed pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.

In this work, we will use a model to achieve more general results.

\section{The Discretised Beta Distribution}

\citet{ANewVersatileDiscreteDistribution} proposes a flexible discrete model, the ``discretised beta'' law.
The probability function of such a random variable is
\begin{align}
\Pr(X & = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\}, \\
\intertext{where}
x &\in \{n_{\text{bot}}, n_{\text{bot}}+1, \dots, n_{\text{top}}\},\\
h(x) & =\frac{(n_{\text{top}} - n_{\text{bot}}+2)^2}{
(x-n_{\text{bot}}+1)	(n_{\text{top}}-x+1)	},\\
T_1(x) &= \log\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
T_2(x) &= \log\frac{n_{\text{top}}-x+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
\intertext{and}
A(\alpha,\beta) &= \log \bigg(
\sum_{i=n_{\text{bot}}}^{n_{\text{top}}} h(i) \exp\big\{ \alpha T_1(i) + \beta T_2(i)\big\}
\bigg).
\end{align}
This definition yields a model that belongs to the exponential family for any $\alpha,\beta\in\mathbbm R$.
Denote this situation $X\sim\text{dbd}(\alpha,\beta)$.

This model can also be related to the Beta distribution with parameters $\alpha$ and $\beta$.
The probability function and other utilities as, for instance, the maximum likelihood estimator for $(\alpha,\beta)$ are implemented in the \texttt{dbd} package for \texttt{R}.

\section{Proposal}

Our aim is, given a time series $\mathcal X$, computing the point $(h,c)$ and being able to assign a likelihood to the hypothesis that $\mathcal X$ is white noise.
In order to achieve that, we need the distribution of $(\mathfrak{H},\mathfrak{C})$, the bivariate random  variable that produced $(h,c)$, under $H_0:\mathcal X\text { is white noise}$.

We do not have that information, but we may approach the problem as an inferential one.
Let $S$ be any subset of the $H\times C$ plane.
We need 
\begin{equation}
\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)
\label{Eq:Problem}
\end{equation}
for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will estimate~\eqref{Eq:Problem}.

Assume that for each combination of $(T,D,\tau)$, we have access to $N_{T,D,\tau}$ (denoted as $N$ in the following) independent identically distributed sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ of white noise.
Each of these sequences produces a point in the $H\times C$ plane, namely $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$.
But let's remind how these points are produced.

The Bandt-Pompe symbolization transforms each sequence of values $\bm x_i$ into a sequence of symbols $\bm \pi_i$.
We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{dbd}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
We may then use $\text{dbd}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.

The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{dbd}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{dbd}(\alpha,\beta)$.

\bibliographystyle{agsm}
\bibliography{References}

\end{document}

### 2021-10-01 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Eu acho que é lixo, mas vou guardando...

@@
 
-\usepackage[binary-units]{siunitx}
+\usepackage{siunitx}
 \usepackage{fouriernc}
@@
 The probability function of such a random variable is
+\begin{equation}
+\Pr(X  = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\},
+\label{Eq:Probdb}
+\end{equation}
+where $\zeta=\text{TRUE}$ denotes that the support starts in zero ($n_{\text{bot}}=0$), otherwise it starts in one ($n_{\text{bot}}=1$), and
 \begin{align}
-\Pr(X & = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\}, \\
-\intertext{where}
 x &\in \{n_{\text{bot}}, n_{\text{bot}}+1, \dots, n_{\text{top}}\},\\
@@
 This definition yields a model that belongs to the exponential family for any $\alpha,\beta\in\mathbbm R$.
-Denote this situation $X\sim\text{dbd}(\alpha,\beta)$.
+Denote this situation $X\sim\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$.
 
-This model can also be related to the Beta distribution with parameters $\alpha$ and $\beta$.
-The probability function and other utilities as, for instance, the maximum likelihood estimator for $(\alpha,\beta)$ are implemented in the \texttt{dbd} package for \texttt{R}.
+If $\alpha,\beta>0$, we can relate the $\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
+\begin{equation}
+\Pr(X=x \mid \alpha, \beta, n_{\text{top}}, \zeta) = 
+\frac{1}{\kappa} f\Big(
+\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
+\Big),
+\label{Eq:Probdb}
+\end{equation}
+where
+$$
+\kappa = \sum_{i=n_{\text{bot}}}^{n_{\text{bot}}} f\Big(
+\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
+\Big),
+$$
+and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$.
+
+The probability function and other utilities as, for instance, the maximum likelihood estimator for $(\alpha,\beta)$, are implemented in the \texttt{dbd} package for \texttt{R}.
 
@@
 for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
-Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will estimate~\eqref{Eq:Problem}.
+Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will model it.
+
+Denote $\mathcal H$ the operator that transforms $\mathcal X$ into its histogram $\bm h$.
+We want to know the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$, where $X$ models the sequence $\mathcal X$.
+Unfortunately, even knowing the distribution of $X$ under the null hypothesis (a collection of iid random variables), modelling $\mathcal H(X)$ is difficult.
+
+All the patterns $(\pi_i)_{1\leq i\leq D!}$ are equally probable in the ideal white noise sequence.
+We then use the $\text{db}(\alpha,\beta)$ model, and set $\alpha=\beta=1$, $n_{\text{top}}=D!$, and $\zeta=\text{FALSE}$ to describe $\mathcal H(X)$ under white noise.
+With this, \eqref{Eq:Probdb} becomes $\Pr(\mathcal H(X)=\bm h)=(1/D!)_{1\leq i\leq D!}$ and, most importantly, given a histogram of patterns $\bm h$ we can estimate the model which produced it.
+Denote this situation $\mathcal H(X)\sim\text{db}_0$.
+
+Questions: given that $\mathcal H(X)\sim\text{db}_0$, what is the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$?
 
@@
 We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
-Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{dbd}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
+Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{db}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
 In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
-We may then use $\text{dbd}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
+We may then use $\text{db}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
 From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.
 
-The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{dbd}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
-The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{dbd}(\alpha,\beta)$.
+The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{db}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
+The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{db}(\alpha,\beta)$.
 

### 2021-10-04 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
:-) :-) :+1:

@@
 \Pr(X  = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\},
-\label{Eq:Probdb}
+\label{Eq:ProbdbExponential}
 \end{equation}
@@
 $$
-and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$.
+and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$, i.e.,
+\begin{equation}
+	f(u;\alpha, \beta) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)} u^{\alpha-1} (1-u)^{\beta-1} \mathbbm 1_{(0,1)}(u).
+	\label{Eq:DensBeta}
+\end{equation}
+Denote this situation $U\sim\text{Beta}(\alpha,\beta)$.
 
@@
 
-We do not have that information, but we may approach the problem as an inferential one.
-Let $S$ be any subset of the $H\times C$ plane.
-We need 
+\begin{itemize}
+\item[Q1:] What is the distribution of $(\mathfrak{H},\mathfrak{C})$ under $H_0:\mathcal X\text { is white noise}$?
+\begin{itemize}
+	\item $\bm X = (X_1,X_2,\dots,X_N)$ is white noise
+	\item Fix $\tau=1$ and define $D$
+	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
+	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction.
+	\item $\bm h$ is the random histogram of proportions from $\bm \pi$
+	\item $(\mathfrak{H},\mathfrak{C})$ is the random point in the Entropy-Complexity plane computed from $\bm h$
+	\begin{itemize}	
+		\item $H^*$ is the operator that transforms the random vector $\bm h$ into the random variable $\mathfrak{H}$
+		\item $C^*$ is the operator that transforms the random vector $\bm h$ in to the random variable $\mathfrak{C}$
+		\item Notice that $H^*$ does not compute the entropy of $\bm h$, which is a fixed value; it produces a random variable from the random variable $\bm h$.
+The same holds for $C^*$; it does not compute the complexity.
+	\end{itemize}
+\end{itemize}
+\item[Q1:] What is the distribution of $
+	(\mathfrak{H},\mathfrak{C}) = 
+	\big(H^*(\bm h),C^*(\bm h)\big)$?
+Under $H_0$, $\bm h$ is (?) a collection of iid random variables taking values in $\{1, 2,\dots, D!\}$ with same probability $1/D!$ but, as they form a histogram, there must be a restriction on the sum of their values.
+I don't know how to go on from this point.
+Multinomial?
+Whichever the distribution of $\bm h$, how do we compute the distribution of $H^*(\bm h)$?
+\item[$\bullet$] Alternatively, instead of considering such a flexible discrete distribution, we may use a parametric model.
+\item[Q2:] What is the distribution of $
+(\mathfrak{H},\mathfrak{C}) = 
+\big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{db}(\alpha,\beta,1, D!)$?
+\item[] But we go back to a quantity, rather than to a random variable.
+\item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{db}(\alpha,\beta,1, D!)$ model.
+\item[] We have the maximum likelihood estimator for $(\alpha,\beta)$, say $(\widehat\alpha,\widehat\beta)$.
+\item[] We know that the asymptotic distribution of $(\widehat\alpha,\widehat\beta)$ is a bivariate Gaussian law.
+\item[] How close are we to finding an approximate distribution for $
+(\mathfrak{H},\mathfrak{C})$ under $H_0$?
+\end{itemize}
+
+If $U\sim\text{Beta}(\alpha,\beta)$, then its entropy is
 \begin{equation}
-\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)
-\label{Eq:Problem}
+H(U) = \log\text{B}(\alpha,\beta) -
+(\alpha-1)\psi(\alpha) -(\beta-1) \psi(\beta) +(\alpha+\beta-2) \psi(\alpha+\beta),
+\label{Eq:HBeta}
 \end{equation}
-for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
-Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will model it.
+in which we denoted
+$$
+\text{B}(\alpha,\beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha+\beta)}.
+$$
 
-Denote $\mathcal H$ the operator that transforms $\mathcal X$ into its histogram $\bm h$.
-We want to know the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$, where $X$ models the sequence $\mathcal X$.
-Unfortunately, even knowing the distribution of $X$ under the null hypothesis (a collection of iid random variables), modelling $\mathcal H(X)$ is difficult.
+Also, if $U_1\sim\text{Beta}(\alpha_1,\beta_1)$ and
+$U_2\sim\text{Beta}(\alpha_2,\beta_2)$, then the Kullback-Leibler divergence between the models is
+\begin{multline}
+D_{\text{KL}}(U_1,U_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
+(\alpha_2-\alpha_1) \psi(\alpha) +
+(\beta_2-\beta_1) \psi(\beta) + \\
+(\alpha_2-\alpha_1+\beta_2-\beta_1) \psi(\alpha_1+\beta_1).
+\label{Eq:DKLBeta}
+\end{multline}
+With~\eqref{Eq:DKLBeta} we may obtain the Jensen-Shannon distance between $U\sim\text{Beta}(\alpha,\beta)$ and the Uniform distribution that is $V\sim\text{Beta}(1,1)$.
+The product between~\eqref{Eq:HBeta} and this Jensen-Shannon distance is the complexity.
 
-All the patterns $(\pi_i)_{1\leq i\leq D!}$ are equally probable in the ideal white noise sequence.
-We then use the $\text{db}(\alpha,\beta)$ model, and set $\alpha=\beta=1$, $n_{\text{top}}=D!$, and $\zeta=\text{FALSE}$ to describe $\mathcal H(X)$ under white noise.
-With this, \eqref{Eq:Probdb} becomes $\Pr(\mathcal H(X)=\bm h)=(1/D!)_{1\leq i\leq D!}$ and, most importantly, given a histogram of patterns $\bm h$ we can estimate the model which produced it.
-Denote this situation $\mathcal H(X)\sim\text{db}_0$.
-
-Questions: given that $\mathcal H(X)\sim\text{db}_0$, what is the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$?
-
-Assume that for each combination of $(T,D,\tau)$, we have access to $N_{T,D,\tau}$ (denoted as $N$ in the following) independent identically distributed sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ of white noise.
-Each of these sequences produces a point in the $H\times C$ plane, namely $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$.
-But let's remind how these points are produced.
-
-The Bandt-Pompe symbolization transforms each sequence of values $\bm x_i$ into a sequence of symbols $\bm \pi_i$.
-We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
-Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{db}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
-In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
-We may then use $\text{db}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
-From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.
-
-The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{db}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
-The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{db}(\alpha,\beta)$.
+%We do not have that information, but we may approach the problem as an inferential one.
+%Let $S$ be any subset of the $H\times C$ plane.
+%We need 
+%\begin{equation}
+%\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)
+%\label{Eq:Problem}
+%\end{equation}
+%for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
+%Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will model it.
+%
+%Denote $\mathcal H$ the operator that transforms $\mathcal X$ into its histogram $\bm h$.
+%We want to know the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$, where $X$ models the sequence $\mathcal X$.
+%Unfortunately, even knowing the distribution of $X$ under the null hypothesis (a collection of iid random variables), modelling $\mathcal H(X)$ is difficult.
+%
+%All the patterns $(\pi_i)_{1\leq i\leq D!}$ are equally probable in the ideal white noise sequence.
+%We then use the $\text{db}(\alpha,\beta)$ model, and set $\alpha=\beta=1$, $n_{\text{top}}=D!$, and $\zeta=\text{FALSE}$ to describe $\mathcal H(X)$ under white noise.
+%With this, \eqref{Eq:Probdb} becomes $\Pr(\mathcal H(X)=\bm h)=(1/D!)_{1\leq i\leq D!}$ and, most importantly, given a histogram of patterns $\bm h$ we can estimate the model which produced it.
+%Denote this situation $\mathcal H(X)\sim\text{db}_0$.
+%
+%Questions: given that $\mathcal H(X)\sim\text{db}_0$, what is the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$?
+%
+%Assume that for each combination of $(T,D,\tau)$, we have access to $N_{T,D,\tau}$ (denoted as $N$ in the following) independent identically distributed sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ of white noise.
+%Each of these sequences produces a point in the $H\times C$ plane, namely $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$.
+%But let's remind how these points are produced.
+%
+%
+%The Bandt-Pompe symbolization transforms each sequence of values $\bm x_i$ into a sequence of symbols $\bm \pi_i$.
+%We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
+%Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{db}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
+%In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
+%We may then use $\text{db}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
+%From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.
+%
+%The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{db}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
+%The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{db}(\alpha,\beta)$.
 

### 2021-10-05 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
:alien:

@@
 \begin{equation}
-	f(u;\alpha, \beta) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)} u^{\alpha-1} (1-u)^{\beta-1} \mathbbm 1_{(0,1)}(u).
+	f(v;\alpha, \beta) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)} v^{\alpha-1} (1-v)^{\beta-1} \mathbbm 1_{(0,1)}(v).
 	\label{Eq:DensBeta}
 \end{equation}
-Denote this situation $U\sim\text{Beta}(\alpha,\beta)$.
+Denote this situation $V\sim\text{Beta}(\alpha,\beta)$.
 
@@
 
-If $U\sim\text{Beta}(\alpha,\beta)$, then its entropy is
+If $V\sim\text{Beta}(\alpha,\beta)$, then its entropy is
 \begin{equation}
-H(U) = \log\text{B}(\alpha,\beta) -
+H(V) = \log\text{B}(\alpha,\beta) -
 (\alpha-1)\psi(\alpha) -(\beta-1) \psi(\beta) +(\alpha+\beta-2) \psi(\alpha+\beta),
@@
 $$
+We propose approximating the distribution of $\mathfrak{H}$ by the distribution of 
+\begin{equation}
+\widehat{H}(V)= \log\text{B}(\widehat\alpha,\widehat\beta) -
+(\widehat\alpha-1)\psi(\widehat\alpha) -(\widehat\beta-1) \psi(\widehat\beta) +(\widehat\alpha+\widehat\beta-2) \psi(\widehat\alpha+\widehat\beta),
+\end{equation}
+which is a transformation of a bivariate Gaussian distribution.
 
-Also, if $U_1\sim\text{Beta}(\alpha_1,\beta_1)$ and
-$U_2\sim\text{Beta}(\alpha_2,\beta_2)$, then the Kullback-Leibler divergence between the models is
+Also, if $V_1\sim\text{Beta}(\alpha_1,\beta_1)$ and
+$V_2\sim\text{Beta}(\alpha_2,\beta_2)$, then the Kullback-Leibler divergence between the models is
 \begin{multline}
-D_{\text{KL}}(U_1,U_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
+D_{\text{KL}}(V_1,V_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
 (\alpha_2-\alpha_1) \psi(\alpha) +
@@
 \end{multline}
-With~\eqref{Eq:DKLBeta} we may obtain the Jensen-Shannon distance between $U\sim\text{Beta}(\alpha,\beta)$ and the Uniform distribution that is $V\sim\text{Beta}(1,1)$.
+With~\eqref{Eq:DKLBeta} we may obtain the Jensen-Shannon distance between $V\sim\text{Beta}(\alpha,\beta)$ and the Uniform distribution that is $U\sim\text{Beta}(1,1)$.
 The product between~\eqref{Eq:HBeta} and this Jensen-Shannon distance is the complexity.
+Our proposal consists in approximating the distribution of $\mathfrak{C}$ by the distribution of $\widehat{C}(V,U)$.
 

### 2021-10-05 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Update ResearchProposal.tex

@@
 In this work, we propose advancing such a knowledge by using a general model for discrete distributions.
+The work by \citet{OrdinalPatternProbabilities} is among the few that study theoretical (distributional) properties of these points; the article proves consistency and asymptotic normality of estimators.
 
@@
 	\item Fix $\tau=1$ and define $D$
-	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
+	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D+1})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
 	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction.

### 2021-10-07 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Update ResearchProposal.tex

@@
 In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
+To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or non-informative distribution.
 They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
 
-We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!^2}, \dots, \frac{1}{D!^2}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
+We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!}, \dots, \frac{1}{D!}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
 It is calculated as:
 \begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!^2} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
+	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
 	u_\ell \log\frac{u_\ell}{h_\ell}

### 2021-10-09 Reports/Journal - Confidence Regions/Response-R1.tex
rebuttal letter

\RequirePackage{xr}
\externaldocument{paper}

\documentclass[journal,onecolumn,draftcls,11pt]{IEEEtran}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[cmex10]{amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{bm,bbm}
\usepackage{wasysym}
\usepackage{texnames}
\usepackage{url}
\usepackage[boxed]{algorithm2e}   % AAB inserido
\usepackage[listings, many]{tcolorbox}
\usepackage[binary-units]{siunitx}
\usepackage{multirow,bigstrut}
\usepackage{capt-of}
\usepackage{todonotes}
\usepackage{enumitem}

\begin{document}
\title{International Statistical Review - Response Letter of Manuscript ID ISR-OA-160-20}

\author{Eduarda~ T.~C.~Chagas,
        Marcelo Queiroz,
        Osvaldo A.\ Rosso,
        Heitor S.\ Ramos,
        Cristopher G.\ S. Freitas,
        Leonardo V.\ Pereira,
        Alejandro C.\ Frery}

\maketitle

\IEEEpeerreviewmaketitle

\section{Co-Editor-in-Chief Requirements}

\vskip3em\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=Comment \#1]
The editor has recommended a major revision, and I am inclined to agree. In particular, I would like to see a strong review component tied in with what you propose, and also a comparison of where your method stands in the literature. Substantiating the advantages through theory or simulation studies would be helpful as well. Please keep in mind that this is a review journal and that the paper must be accessible to more than the technical experts in the area.
\end{tcolorbox}

\section{Reviewer \#1}

\vskip3em\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=Comment \#1]
In this paper the authors propose a quite elaborate method to test whether a discrete-time analog signal is white noise by locating it in the entropy-complexity plane (ECP). The description is didactic, detailed and well-written. However, I missed the rationale of using the ECP. I mean, what can be done in this way that cannot be done with the entropy alone? After all, entropy (horizontal axis of the ECP) is a measure of (pseudo-)randomness. For white noise, the normalized (permutation) entropy is 1, hence complexity is automatically 0 (see the definition domain of the ECP in Figures 2, 4 and 5). In other words, why use two measures that are not independent (since entropy sets the range of complexity), instead of only one (the entropy in this case)? So, unless the authors convincingly rebut this point, I cannot recommend the publication of this paper in ISR.
\end{tcolorbox}

\section{Reviewer \#2}

\vskip3em\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=Comment \#1]
The paper address an interesting problem in time series. The manuscript presents a thorough review of the literature, and develops a proposed test for a wide array of models. Examples and simulation studies are clearly defined and their results are discussed. The paper is well written, and I have no major corrections to propose.
\end{tcolorbox}

\end{document}

### 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
rebuttal letter

\documentclass[alpha-refs]{wiley-article}

\usepackage[binary-units]{siunitx}
\usepackage{bm,bbm}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{float}
\usepackage{rotating}
\graphicspath{{./Figures/}}
\usepackage[linesnumbered,lined,boxed]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{undertilde}
\usepackage{todonotes}
\usepackage{comment}

\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
\DeclareSIUnit{\alphapercent}{\alpha\%}

\newcommand{\Mycite}[1]{%
 (\citeauthor{#1},~\citeyear{#1})}

\papertype{Original Article}

\title{A Test for White Noise in the Entropy-Complexity Plane}

\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}

\author[1]{Eduarda T.\ C.\ Chagas}
\author[2,3]{Marcelo Queiroz}
\author[4]{Osvaldo A.\ Rosso}
\author[1]{Heitor S.\ Ramos}
\author[2]{Cristopher G.\ S. Freitas}
\author[2]{Leonardo V.\ Pereira}
\author[4]{Alejandro C.\ Frery}

\contrib[]{All authors contributed equally.}

% Include full affiliation details for all authors
\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}

\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\corremail{eduarda.chagas@dcc.ufmg.br}

\fundinginfo{CNPq, Fapeal}

% Include the name of the author that should appear in the running header
\runningauthor{Eduarda T.\ C.\ Chagas et al.}

\begin{document}

% \begin{frontmatter}
\maketitle

\begin{abstract}
The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
by computing Information Theory descriptors of the histogram of ordinal patterns.
Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
Our test is based on true white noise sequences obtained from physical devices.
The proposed methodology provides consistent results, 
managing to assess sequences of true random samples as random (adequate size), 
rejecting correlated sequences (sound power), and
capturing the randomness of generators previously analyzed in the literature.
\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
\end{abstract}

\section{Introduction}\label{Sec:Intro}

Time Series carry valuable information about the system which produces the data.
Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
in the (natural) time and transformed domains (for instance, frequency and wavelet).
In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
Such an approach is non-parametric and based on descriptors of Information Theory.
The time series is transformed into ordinal patterns, with which a histogram is formed.
The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
Thus, the approach can be applied to a variety of situations.

The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
We found works using this approach in several areas of scientific knowledge such as, for example:
%
distinguishing noise from chaos~\citep{rosso2007distinguishing};
%
the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
%
description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
%
the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
%
detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
%
analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
%
online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.

With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.

The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
two in the \textit{Journal of Time Series Analysis}, 
and each of the remaining ten appeared in a different journal.
Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.

Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.

With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
Results in this direction can be found in the literature.
\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.

Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
Our contributions can be summarized as follows:
\begin{itemize}
	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
	\item We verify the test's power contrasting correlated noise time series.
\end{itemize}

The rest of this paper is structured as follows. 
Section~\ref{Sec:BP} introduces the elements of the study:
Section~\ref{Sec:BPMethodology} details the methodology,
Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
and Section~\ref{Sec:BPApplications} discusses applications of this approach.
%
Section~\ref{Sec:BPMethodology} describes our methodology:
Section~\ref{Sec:OverallFramework} gives the overall framework.
Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
%
Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.

\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}

In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
We then obtain a test statistic, using confidence regions, that can discriminate among times series.

\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}

Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
\begin{quote}
	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
\end{quote}
Also, as stressed by these authors, 
\begin{quote}
	``The corresponding symbol sequence must come 
	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
\end{quote}

Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
possible permutation of order $D$, and the symbol component vector 
${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
($\pi_j \neq \pi_k~\forall~j \neq k$). 
Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
\begin{equation} 
	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
	\label{eq:time-delay}
\end{equation} 
for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
This mapping should be defined in a way that preserves the desired relation between the elements 
$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
${\bm \pi}^{(D)}$. 
The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
\begin{enumerate}[label=\alph*)]
	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
	(\textit{Rank Permutation}) or,
	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
	(\textit{Chronological Index Permutation}).
\end{enumerate}
See details in the work by \citet{BPRepeatedValuesChaos}.
Without loss of generality, in the following, we will use the latter.

Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.

The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=.7\linewidth]{IntroBP}
	\caption{Illustration of the Bandt and Pompe coding}
	\label{Fig:IntroBP}
\end{figure}

After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
The next step into the characterization of the time series is computing descriptors from this histogram.

The first descriptor is a measure of the disorder of the system.
The most frequently used feature for this is the Normalized Shannon entropy, defined as
\begin{equation}
	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
\end{equation}
with the convention that terms in the summation for which $h(j)=0$ are null.
This quantity is bounded in the unit interval. 
It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
It is calculated as:
\begin{equation}
	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
	u(\ell) \log\frac{u(\ell)}{h(\ell)}
	\Big).
\end{equation}
This quantity is also called ``disequilibrium.''
The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.

With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
A time series can then be mapped into a point in the $H\times C$ plane.

\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}

The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
The time delay is irrelevant, and we consider infinitely long series.

Let us consider two extreme cases:
\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
	The entropy is zero, and the distance to the uniform distribution is maximal. 
	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
	The distance to the equilibrium distribution is zero. 
	Thus, such series are mapped onto the point $(1,0)$.
\end{enumerate}

\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
The upper boundary converges to a smooth curve when $D\to\infty$.

Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
The inset plot highlights the fine structure of the upper boundary inside the rectangle.
The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
\end{figure}

We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
\begin{itemize}
	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
\end{itemize}
In all cases, we used $D=6$ and $\tau=1$.
Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.

\begin{figure}[hbt]
	\includegraphics[width=\linewidth]{Figures/h.pdf}
	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
	\label{fig:Histograms}
\end{figure}

Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
The points due to $f^{-k}$ noises appear joined by dotted segments.
It is noticeable that deterministic patterns have more complexity than random ones.
Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{AllSystems}
	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
	\label{fig:AllSystems}
\end{figure}

Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{RightMostCorner}
	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
	\label{fig:RightMostCorner}
\end{figure}

Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.

\section{Proposed Method}\label{Sec:Proposal}

In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
Then, we present our proposal to change space through the algorithm of the principal components analysis.
Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
Through this new representation of the data, we calculate empirical regions with different levels of confidence.
Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.

\subsection{Overall Framework}\label{Sec:OverallFramework}

Our methodology consists of the following steps:
\begin{enumerate}
	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
	\item\label{item:Methodology3} Obtain the principal components of these points.
	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
\end{enumerate}

\subsection{True Random Numbers}\label{Sec:TRNG}

Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
%In this study we used two sources of real random numbers. 
%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.

In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
The first uses vacuum states. 
The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state. 
The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}. 
The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
The history of this service and other information can be found at \citet{RandomOrg}.

We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.

%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}

\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}

We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
On the other hand, we found two relevant variables: 
the length of the sequence 
and the embedding dimension.
We, thus, employed the following factors:
\begin{itemize}
	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
	%,and
	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
\end{itemize}
and kept $\tau=1$, which is the most frequently used option.
The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.

Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
For the construction of the confidence regions presented, we used:
\begin{itemize}
	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
\end{itemize}

We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.

\begin{comment}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
\caption{White noise samples considered during the construction of the proposed confidence regions.}
\label{fig:white-noise}
\end{figure}

\end{comment}

\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}

%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.

Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.

%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.

Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
In the sequel, whenever possible, we will omit $T$ and $D$.
For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
Fig.~\ref{fig:Methodology1} illustrates this step.
We will obtain confidence regions and $p$-values from $\utilde{hc}$.

The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.

For simplicity, and without loss of generality, assume $N$ is odd.
\begin{enumerate}
	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$. Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$. Call the corresponding time series ``emblematic time series.''
	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
	\item The corners of the box are 
	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
\end{enumerate}

Fig.~\ref{fig:methodology} illustrates these steps.
%
Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
%
Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
We highlighted in red the point whose first principal component is the median of the observed values.
%
Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.

\begin{figure}[hbt]
	\centering
	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
	\caption{Outline of the methodology used for the construction of the confidence regions.}
	\label{fig:methodology}
\end{figure}

Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.

\begin{algorithm}[hbt]
	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
	\Input{A data base of true random values}
	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
	\Output{Confidence regions as points in the $H\times C$ plane}
	\For{each $D\in \mathcal D$}{
		\For{each $T\in \mathcal T$}{
			\For{each $n=1,2,\dots,N$}{
				build the time series $p_n$ with unused values from the data base\;
				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
			}
			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
			%
			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
			%
			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
			%
			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
			%
			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
			\Return{$\bm P'$}\;
			%
			\For{each confidence level $\alpha \in \mathcal A$}{
				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
				%
				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
				%
				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
				%
				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
				%
				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
				%
				the corners of the box are 
				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
				%
				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
			}
		}
	}
	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
\end{algorithm}

%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.

These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.

The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
\begin{enumerate}
	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$. By definition, $\eta_u\geq 1/2$.
	%
	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
	%
	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
	%
	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
\end{enumerate}
Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.

The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.

Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
Algorithm~\ref{Algo:p-value} shows the details.

\begin{figure}[hbt]
	\centering
	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
	\label{fig:methodologyPvalue}
\end{figure}

\begin{comment}
The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
Therefore, it can be achieved by the following steps:
\begin{enumerate}
\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
\end{enumerate}
Thus, we can verify that:
\begin{itemize}
\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
\end{itemize}
Assuming the critical value $\alpha = 0.05$, we obtain:
\begin{equation*}
p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
\end{equation*}
\end{comment}

\begin{algorithm}[hbt]
	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
	\Input{The embedding dimension $D$}
	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
	\Output{An approximate $p$-value}
	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
	find the point $(h,c)$ of the sequence $\bm x$\;
	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
	\eIf{$u_x > u$}
	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
	}
	{
		\eIf{$u_x < u$}
		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
		}
		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
		}
	}
	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
	the corners of the box $b_{\alpha}(h,c)$ are 
	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
	\Return{$1-n_{\bm x}/N$}
	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
\end{algorithm}

\section{Results}\label{Sec:Results}

\subsection{Empirical confidence regions}

Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent}, 
for $D=3,4,5,6$ and $N=1000,50000$, .
The points are presented counterclockwise, starting with the one with the largest complexity.

\begin{comment}
\begin{table}[hbt]
\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
\centering
\begin{tabular}{rcllllllll}
\toprule
& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
\end{tabular}
\end{table}
\end{comment}

\begin{table}[hbt]
	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
	\centering
	\begin{tabular}{rccccc}
		\toprule
		%& & \multicolumn{4}{c}{$N$}\\ 
		%\cmidrule(lr){3-6}
		& & \multicolumn{4}{c}{$N = 1000$}\\ 
		\cmidrule(lr){3-6} 
		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
		\cmidrule(lr){3-3} 
		\cmidrule(lr){4-4} 
		\cmidrule(lr){5-5} 
		\cmidrule(lr){6-6} 
		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
		\midrule
		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
		\midrule
		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
		\midrule
		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[hbt]
	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
	\centering
	\begin{tabular}{rccccc}
		\toprule
		%& & \multicolumn{4}{c}{$N$}\\ 
		%\cmidrule(lr){3-6}
		& & \multicolumn{4}{c}{$N = 50000$}\\ 
		\cmidrule(lr){3-6} 
		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
		\cmidrule(lr){3-3} 
		\cmidrule(lr){4-4} 
		\cmidrule(lr){5-5} 
		\cmidrule(lr){6-6} 
		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
	\end{tabular}
\end{table}

Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.

\begin{figure}[hbt]
	\centering
	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
	\label{fig:HC-PCA}
\end{figure}

The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.

Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{PCA-hist-50k}
	\caption{Histograms of the first principal component for $D=3,4,5,6$}
	\label{fig:PCA-Hist}
\end{figure}

\subsection{Test Size}

We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
show the results.

On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$. 
In contrast, we expected \SI{1}{\percent} of rejection.
This might be because, in this case, the condition $D!\ll T$ is not respected.
Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.

%
%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
%
%For short series, $T = 1000$, and $D = 3$ 
%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
%
%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
%A reasonable explanation for this event is given in the choice of the parameter itself.
%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.

\begin{table}[hbt]
	\centering
	\caption{Empirical sizes of the test}
	\label{tab:result1}
	\begin{tabular}{*{3}rr}
		\toprule
		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
		%& $p$-value\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		1000 & 3 & $0.98$ & $1.00$\\
		& 4 & $0.98$ & $0.96$\\
		& 5 & $1.00$ & $0.94$\\
		& 6 & $0.97$ & $0.87$\\
		\cmidrule(lr){1-4} 
		50000 & 3 & $0.97$ & $0.96$\\
		%& $0.47856$\\
		& 4 & $0.94$ & $0.95$\\
		%& $0.47555$\\ 
		& 5 & $0.97$ & $0.96$\\ 
		%& $0.48512$\\ 
		& 6 & $0.98$ & $0.99$\\ 
		%& $0.48058$\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
	\caption{New $100$ TRWNS and regions of confidence.}
	\label{fig:RNG}
\end{figure}

We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.

\subsection{Test Power}

We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
Several studies in the literature have used this approach for identifying and characterizing randomness.

Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
Recall that the emblematic time was chosen as the most representative of the data set.
We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.

%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.

Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.

Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
The same holds for all $k>3/10$.

\begin{figure}
	\centering
	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
	\label{fig:correlation}
\end{figure}

\subsection{Revisiting the White Noise Hypothesis in the Literature}

In this section, we compare the performance of our test with that of 
previous analyses that employ the Entropy-Complexity plane.
To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).

\begin{table}
	\caption{Results of the sequences generated by the main PRNGs in the literature. 
		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
	\label{Tab:LiteratureComparations}
	\centering
	\begin{tabular}{cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		MOT & 3 & 0.305 & NR\\
		& 4 & 0.572 & NR\\ 
		& 5 & 0.455 & NR\\ 
		& 6 & 0.508 & NR\\ 
		\cmidrule(lr){1-4}
		MWC & 3 & 0.501 & NR\\
		& 4 & 0.477 & NR\\ 
		& 5 & 0.496 & NR\\ 
		& 6 & 0.496 & NR\\ 
		\cmidrule(lr){1-4}
		COM & 3 & 0.123 & NR\\
		& 4 & 0.002 & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\cmidrule(lr){1-4}
		LEH & 3 & 0.531 & NR\\
		& 4 & 0.515 & NR\\ 
		\bottomrule
	\end{tabular}
	\begin{tabular}{|cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		LEH & 5 & 0.495 & NR\\ 
		& 6 & 0.501 & NR\\ 
		\cmidrule(lr){1-4}
		fGn & 3 & 0.521 & NR\\
		& 4 & 0.519 & NR\\ 
		& 5 & 0.498 & NR\\ 
		& 6 & 0.470 & NR\\
		\cmidrule(lr){1-4}
		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%\cmidrule(lr){1-4}
		$f^{-k}$ & 3 & 0.482 & NR\\
		& 4 & 0.520 & NR\\ 
		& 5 & 0.513 & NR\\ 
		& 6 & 0.508 & NR\\
		\cmidrule(lr){1-4}
		LCG & 3 & 0.009 & R\\ 
		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\bottomrule
	\end{tabular}
\end{table}

Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.

It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.

\section{Conclusions}\label{Sec:Conclusions}

We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
Our proposal is based on two stages:
(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
We obtained the TWNRS with data from physical devices.

Our test has a good size, mostly with long TWNRS.
We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.

Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.

\section{Reproducibility and Replicability}\label{Sec:code}

Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.

\section{Acknowledgements}\label{Sec:acknowledgements}

This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).

\printendnotes

\bibliography{References}

\end{document}

### 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions.tex
rebuttal letter

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
 
-\section{Introduction}\label{Sec:Intro}
-
-Time Series carry valuable information about the system which produces the data.
-Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
-in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
-Such an approach is non-parametric and based on descriptors of Information Theory.
-The time series is transformed into ordinal patterns, with which a histogram is formed.
-The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
-Thus, the approach can be applied to a variety of situations.
-
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
-We found works using this approach in several areas of scientific knowledge such as, for example:
-%
-distinguishing noise from chaos~\citep{rosso2007distinguishing};
-%
-the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
-%
-description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
-%
-the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
-%
-detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
-%
-analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
-%
-online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
-\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
-\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
-\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
-\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
-\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.
-
-With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
-There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
-Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
-In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.
-
-The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
-These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
-Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-two in the \textit{Journal of Time Series Analysis}, 
-and each of the remaining ten appeared in a different journal.
-Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
-It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
-The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
-
-Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
-\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
-\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
-\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
-\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
-
-With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
-Results in this direction can be found in the literature.
-\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
-\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-
-Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
-In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
-We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
-Our contributions can be summarized as follows:
-\begin{itemize}
-	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
-	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series.
-\end{itemize}
-
-The rest of this paper is structured as follows. 
-Section~\ref{Sec:BP} introduces the elements of the study:
-Section~\ref{Sec:BPMethodology} details the methodology,
-Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
-and Section~\ref{Sec:BPApplications} discusses applications of this approach.
-%
-Section~\ref{Sec:BPMethodology} describes our methodology:
-Section~\ref{Sec:OverallFramework} gives the overall framework.
-Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
-Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
-Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
-%
-Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
-Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
-
-\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
-
-In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
-Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
-We then obtain a test statistic, using confidence regions, that can discriminate among times series.
-
-\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}
-
-Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
-As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
-\begin{quote}
-	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
-	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
-\end{quote}
-Also, as stressed by these authors, 
-\begin{quote}
-	``The corresponding symbol sequence must come 
-	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
-\end{quote}
-
-Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
-possible permutation of order $D$, and the symbol component vector 
-${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
-Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
-with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
-\begin{equation} 
-	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
-	\label{eq:time-delay}
-\end{equation} 
-for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
-Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
-This mapping should be defined in a way that preserves the desired relation between the elements 
-$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
-${\bm \pi}^{(D)}$. 
-The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[label=\alph*)]
-	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
-	(\textit{Rank Permutation}) or,
-	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
-	(\textit{Chronological Index Permutation}).
-\end{enumerate}
-See details in the work by \citet{BPRepeatedValuesChaos}.
-Without loss of generality, in the following, we will use the latter.
-
-Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
-Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
-The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
-With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
-
-The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
-In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{IntroBP}
-	\caption{Illustration of the Bandt and Pompe coding}
-	\label{Fig:IntroBP}
-\end{figure}
-
-After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
-Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
-The next step into the characterization of the time series is computing descriptors from this histogram.
-
-The first descriptor is a measure of the disorder of the system.
-The most frequently used feature for this is the Normalized Shannon entropy, defined as
-\begin{equation}
-	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
-\end{equation}
-with the convention that terms in the summation for which $h(j)=0$ are null.
-This quantity is bounded in the unit interval. 
-It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
-
-Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
-In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
-%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-It is calculated as:
-\begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
-	u(\ell) \log\frac{u(\ell)}{h(\ell)}
-	\Big).
-\end{equation}
-This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
-
-With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
-A time series can then be mapped into a point in the $H\times C$ plane.
-
-\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}
-
-The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
-The time delay is irrelevant, and we consider infinitely long series.
-
-Let us consider two extreme cases:
-\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
-	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
-	The entropy is zero, and the distance to the uniform distribution is maximal. 
-	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
-	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
-	The distance to the equilibrium distribution is zero. 
-	Thus, such series are mapped onto the point $(1,0)$.
-\end{enumerate}
-
-\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
-\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
-The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
-The upper boundary converges to a smooth curve when $D\to\infty$.
-
-Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
-The inset plot highlights the fine structure of the upper boundary inside the rectangle.
-The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
-	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
-\end{figure}
-
-We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
-\begin{itemize}
-	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
-	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
-\end{itemize}
-In all cases, we used $D=6$ and $\tau=1$.
-Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
-we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
-
-\begin{figure}[hbt]
-	\includegraphics[width=\linewidth]{Figures/h.pdf}
-	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:Histograms}
-\end{figure}
-
-Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
-The points due to $f^{-k}$ noises appear joined by dotted segments.
-It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{AllSystems}
-	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:AllSystems}
-\end{figure}
-
-Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{RightMostCorner}
-	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:RightMostCorner}
-\end{figure}
-
-Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
-Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
-
-\section{Proposed Method}\label{Sec:Proposal}
-
-In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
-Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
-Through this new representation of the data, we calculate empirical regions with different levels of confidence.
-Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
-
-\subsection{Overall Framework}\label{Sec:OverallFramework}
-
-Our methodology consists of the following steps:
-\begin{enumerate}
-	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
-	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
-	\item\label{item:Methodology3} Obtain the principal components of these points.
-	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
-	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
-\end{enumerate}
-
-\subsection{True Random Numbers}\label{Sec:TRNG}
-
-Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
-Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
-%In this study we used two sources of real random numbers. 
-%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
-The first uses vacuum states. 
-The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
-The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
-The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
-This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
-The history of this service and other information can be found at \citet{RandomOrg}.
-
-We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
-
-%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
-
-\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
-
-We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
-We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
-On the other hand, we found two relevant variables: 
-the length of the sequence 
-and the embedding dimension.
-We, thus, employed the following factors:
-\begin{itemize}
-	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
-	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
-	%,and
-	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
-\end{itemize}
-and kept $\tau=1$, which is the most frequently used option.
-The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
-
-Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
-For the construction of the confidence regions presented, we used:
-\begin{itemize}
-	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
-	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
-\end{itemize}
-
-We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
-
-\begin{comment}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
-\caption{White noise samples considered during the construction of the proposed confidence regions.}
-\label{fig:white-noise}
-\end{figure}
-
-\end{comment}
-
-\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
-
-%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
-
-Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
-Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
-Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
-%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
-
-%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
-%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
-
-Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
-In the sequel, whenever possible, we will omit $T$ and $D$.
-For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
-Fig.~\ref{fig:Methodology1} illustrates this step.
-We will obtain confidence regions and $p$-values from $\utilde{hc}$.
-
-The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
-With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
-This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
-Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
-Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
-
-For simplicity, and without loss of generality, assume $N$ is odd.
-\begin{enumerate}
-	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
-Call the corresponding time series ``emblematic time series.''
-	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
-	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
-	\item The corners of the box are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
-\end{enumerate}
-
-Fig.~\ref{fig:methodology} illustrates these steps.
-%
-Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
-The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
-The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
-%
-Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
-The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
-We highlighted in red the point whose first principal component is the median of the observed values.
-%
-Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
-The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
-
-\begin{figure}[hbt]
-	\centering
-	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
-	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
-	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
-	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
-	\caption{Outline of the methodology used for the construction of the confidence regions.}
-	\label{fig:methodology}
-\end{figure}
-
-Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
-We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{A data base of true random values}
-	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
-	\Output{Confidence regions as points in the $H\times C$ plane}
-	\For{each $D\in \mathcal D$}{
-		\For{each $T\in \mathcal T$}{
-			\For{each $n=1,2,\dots,N$}{
-				build the time series $p_n$ with unused values from the data base\;
-				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
-			}
-			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
-			%
-			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
-			%
-			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
-			%
-			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-			%
-			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
-			\Return{$\bm P'$}\;
-			%
-			\For{each confidence level $\alpha \in \mathcal A$}{
-				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
-				%
-				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
-				%
-				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
-				%
-				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
-				%
-				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
-				%
-				the corners of the box are 
-				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
-				%
-				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
-				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
-			}
-		}
-	}
-	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
-\end{algorithm}
-
-%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
-
-These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
-More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
-We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
-
-The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
-We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
-We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
-We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
-The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
-Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
-We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
-\begin{enumerate}
-	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
-By definition, $\eta_u\geq 1/2$.
-	%
-	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
-	%
-	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
-	%
-	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
-\end{enumerate}
-Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
-
-The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
-With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
-
-Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
-Algorithm~\ref{Algo:p-value} shows the details.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
-	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
-	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
-	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
-	\label{fig:methodologyPvalue}
-\end{figure}
-
-\begin{comment}
-The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
-Therefore, it can be achieved by the following steps:
-\begin{enumerate}
-\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
-\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
-\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
-\end{enumerate}
-Thus, we can verify that:
-\begin{itemize}
-\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
-\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
-\end{itemize}
-Assuming the critical value $\alpha = 0.05$, we obtain:
-\begin{equation*}
-p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
-\end{equation*}
-\end{comment}
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
-	\Input{The embedding dimension $D$}
-	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
-		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
-		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
-	\Output{An approximate $p$-value}
-	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-	find the point $(h,c)$ of the sequence $\bm x$\;
-	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
-	\eIf{$u_x > u$}
-	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
-		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
-	}
-	{
-		\eIf{$u_x < u$}
-		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
-			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
-		}
-		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
-		}
-	}
-	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
-	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
-	the corners of the box $b_{\alpha}(h,c)$ are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
-	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
-	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
-	\Return{$1-n_{\bm x}/N$}
-	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
-\end{algorithm}
-
-\section{Results}\label{Sec:Results}
-
-\subsection{Empirical confidence regions}
-
-Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
-of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
-for $D=3,4,5,6$ and $N=1000,50000$, .
-The points are presented counterclockwise, starting with the one with the largest complexity.
-
-\begin{comment}
-\begin{table}[hbt]
-\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
-\centering
-\begin{tabular}{rcllllllll}
-\toprule
-& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
-& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
-$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
-$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 1000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
-		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
-		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
-		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
-		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
-		\midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
-		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
-		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
-		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
-		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
-		\midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
-		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
-		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
-		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
-		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
-		\midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
-		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
-		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
-		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
-		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 50000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
-		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
-		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
-		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
-		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
-	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
-	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
-
-Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
-As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
-Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{PCA-hist-50k}
-	\caption{Histograms of the first principal component for $D=3,4,5,6$}
-	\label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Test Size}
-
-We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
-Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
-show the results.
-
-On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
-On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
-In contrast, we expected \SI{1}{\percent} of rejection.
-This might be because, in this case, the condition $D!\ll T$ is not respected.
-Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
-
-%
-%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-%
-%For short series, $T = 1000$, and $D = 3$ 
-%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
-%
-%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-%A reasonable explanation for this event is given in the choice of the parameter itself.
-%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-
-\begin{table}[hbt]
-	\centering
-	\caption{Empirical sizes of the test}
-	\label{tab:result1}
-	\begin{tabular}{*{3}rr}
-		\toprule
-		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		%& $p$-value\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		1000 & 3 & $0.98$ & $1.00$\\
-		& 4 & $0.98$ & $0.96$\\
-		& 5 & $1.00$ & $0.94$\\
-		& 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-4} 
-		50000 & 3 & $0.97$ & $0.96$\\
-		%& $0.47856$\\
-		& 4 & $0.94$ & $0.95$\\
-		%& $0.47555$\\ 
-		& 5 & $0.97$ & $0.96$\\ 
-		%& $0.48512$\\ 
-		& 6 & $0.98$ & $0.99$\\ 
-		%& $0.48058$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-	\caption{New $100$ TRWNS and regions of confidence.}
-	\label{fig:RNG}
-\end{figure}
-
-We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
-
-\subsection{Test Power}
-
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
-Several studies in the literature have used this approach for identifying and characterizing randomness.
-
-Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
-Recall that the emblematic time was chosen as the most representative of the data set.
-We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
-
-%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
-At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
-
-Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
-We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
-Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
-The same holds for all $k>3/10$.
-
-\begin{figure}
-	\centering
-	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
-	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
-	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
-	\label{fig:correlation}
-\end{figure}
-
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
-
-In this section, we compare the performance of our test with that of 
-previous analyses that employ the Entropy-Complexity plane.
-To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
-Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
-
-\begin{table}
-	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
-	\label{Tab:LiteratureComparations}
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		MOT & 3 & 0.305 & NR\\
-		& 4 & 0.572 & NR\\ 
-		& 5 & 0.455 & NR\\ 
-		& 6 & 0.508 & NR\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 0.501 & NR\\
-		& 4 & 0.477 & NR\\ 
-		& 5 & 0.496 & NR\\ 
-		& 6 & 0.496 & NR\\ 
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.123 & NR\\
-		& 4 & 0.002 & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.531 & NR\\
-		& 4 & 0.515 & NR\\ 
-		\bottomrule
-	\end{tabular}
-	\begin{tabular}{|cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		LEH & 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.521 & NR\\
-		& 4 & 0.519 & NR\\ 
-		& 5 & 0.498 & NR\\ 
-		& 6 & 0.470 & NR\\
-		\cmidrule(lr){1-4}
-		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.482 & NR\\
-		& 4 & 0.520 & NR\\ 
-		& 5 & 0.513 & NR\\ 
-		& 6 & 0.508 & NR\\
-		\cmidrule(lr){1-4}
-		LCG & 3 & 0.009 & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
-
-It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
-In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
-
-\section{Conclusions}\label{Sec:Conclusions}
-
-We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
-Our proposal is based on two stages:
-(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
-(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
-We obtained the TWNRS with data from physical devices.
-
-Our test has a good size, mostly with long TWNRS.
-We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
-
-Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
-With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
-
-\section{Reproducibility and Replicability}\label{Sec:code}
-
-Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
-
-\section{Acknowledgements}\label{Sec:acknowledgements}
-
-This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
+\input{Chapters/Introduction}
+\input{Chapters/Background}
+\input{Chapters/Methodology}
+\input{Chapters/Results}
+\input{Chapters/Conclusions}
+\input{Chapters/Source}
+\input{Chapters/acknowledgements}
 

### 2021-10-09 Code/Alejandro/ConfidenceRegion_p-value.R

@@ -24,7 +24,7 @@ step1 <- ggplot(data=uv, aes(x=u, y=v)) +
   xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
   xlab(expression(italic(u))) +
   ylab(expression(italic(v))) +
-  theme_clean(base_size = 30, base_family = "sans")
+  theme_clean(base_size = 30, base_family = "serif")
 
 # Confidence region at level a
 step2 <- ggplot(data=uv, aes(x=u, y=v)) +
@@ -45,7 +45,7 @@ step2 <- ggplot(data=uv, aes(x=u, y=v)) +
   xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
   xlab(expression(italic(u))) +
   ylab(expression(italic(v))) +
-  theme_clean(base_size = 30, base_family = "sans")
+  theme_clean(base_size = 30, base_family = "serif")
 
 # Confidence region at level a
 step3 <- ggplot(data=uv, aes(x=u, y=v)) +
@@ -70,7 +70,7 @@ step3 <- ggplot(data=uv, aes(x=u, y=v)) +
   xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
   xlab(expression(italic(u))) +
   ylab(expression(italic(v))) +
-  theme_clean(base_size = 30, base_family = "sans")
+  theme_clean(base_size = 30, base_family = "serif")
 
 ggsave(step1, filename = "../../Reports/JOURNAL - Confidence Regions/Figures/PvalueStep1.pdf", width = 8, height = 6)
 ggsave(step2, filename = "../../Reports/JOURNAL - Confidence Regions/Figures/PvalueStep2.pdf", width = 8, height = 6)

### 2021-10-09 Code/Attack-Experiments.R

@@ -1,0 +1,99 @@
+################################################################################
+# Author: Eduarda Chagas
+# Date : Out 7, 2021
+# Contact: eduarda.chagas@dcc.ufmg.br
+################################################################################
+
+# Packages and sources ---------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+
+# Define attack ----------------------------------------------------------------
+set.seed(123)
+AttackElement <- function(e, d, p){
+  if(runif(1) <= p){
+    i = round(runif(1, max = d-1, min = 1), digits = 0)
+    e[i+1] = e[i] 
+  }
+  return(e)
+}
+
+AttackPattern <- function(elements_ts, d, tau, p) {
+  n_elements = dim(elements_ts)[1]
+  attacked_elements = matrix(nrow = n_elements, ncol = d)
+  for(i in 1:n_elements){
+    elements = formationPattern(elements_ts[i,], d, tau, 1)
+    attacked_elements[i,] = AttackElement(elements, d, p)
+  }
+  return(attacked_elements)
+}
+
+AttackTimeSeries <- function(time_series, d, tau, p) {
+  ts_attacked = time_series
+  n.series = length(time_series)
+  for(i in 1:(n.series-1)){
+    if(runif(1) <= p){
+      ts_attacked[i+1] = ts_attacked[i] 
+    }
+  }
+  return(ts_attacked)
+}
+
+bandt.pompe.by.elements <- function(elements, dimension, delay){
+  dyn.load("BandtPompe.so")
+  element.size = dim(elements)[1]
+  probability <- .Call("BandtPompe", elements, dimension, element.size)
+  return(probability)
+}
+
+
+#Global variables --------------------------------------------------------------
+D = 3
+tau = 1
+P = c(0.001, 0.005, 0.01, 0.015, 0.02, 0.025, 0.03) 
+
+h = rep(0, length(P) + 1)
+c = rep(0, length(P) + 1)
+
+ts = read.csv("../Data/Emblematic-serie-D3-N50000.csv")[,2]
[…]

### 2021-10-09 Code/Bandt-Pompe.R

@@ -63,31 +63,31 @@ formationPattern <- function(series, D, tau, option){
 
 # Bandt-Pompe function ---------------------------------------------------------------------------------
 
-#bandt.pompe <- function(series, dimension, delay){
-#  dyn.load("BandtPompe.so")
-#  elements = formationPattern(series, dimension, delay, 1)
-#  element.size = dim(elements)[1]
-#  probability <- .Call("BandtPompe", elements, dimension, element.size)
-#  return(probability)
-#}
-
-
-bandt.pompe <- function(serie, dimension, delay){  
-  fat = factorial(dimension)
-  probability = rep(0, fat)
-  symbols = define.symbols(dimension)
-  p_patterns = formationPattern(serie, dimension, delay, 0)
-  n_symbols = dim(p_patterns)[1]
-  for(j in 1:n_symbols){
-    for(i in 1:fat){
-      if(all(p_patterns[j,] == symbols[i,])){ 
-        probability[i] = probability[i] + 1
-        break
-      }
-    }
-  }
-  return(probability/n_symbols)
+bandt.pompe <- function(series, dimension, delay){
+  dyn.load("BandtPompe.so")
+  elements = formationPattern(series, dimension, delay, 1)
+  element.size = dim(elements)[1]
+  probability <- .Call("BandtPompe", elements, dimension, element.size)
+  return(probability)
 }
+
+
+#bandt.pompe <- function(serie, dimension, delay){  
+#  fat = factorial(dimension)
+#  probability = rep(0, fat)
+#  symbols = define.symbols(dimension)
+#  p_patterns = formationPattern(serie, dimension, delay, 0)
+#  n_symbols = dim(p_patterns)[1]
+#  for(j in 1:n_symbols){
+#    for(i in 1:fat){
+#      if(all(p_patterns[j,] == symbols[i,])){ 
+#        probability[i] = probability[i] + 1
+#        break
+#      }
+#    }
+#  }
+#  return(probability/n_symbols)
+#}
 
 
 # Shannon Entropy function -------------------------------------------------------------------------------

### 2021-10-09 Code/Correlation-Analysis.R

@@ -85,13 +85,13 @@ correlation.analysis.point <- function(){
     geom_line(data = cotas.inf, aes(x = c2x, y = c2y), color="gray") + 
     geom_point(size = 1.5, alpha = .4) + 
     geom_point(data = HC.ts, aes(x = H, y = C), size = 1.5, alpha = .4, color = "red") + 
-    geom_label_repel(aes(label = paste("italic(k) ==", legend.names)),parse = TRUE, segment.size = 0.5, min.segment.length = 0, force = 18) +
+    geom_label_repel(aes(label = paste(expression(italic(k)), "==", legend.names)),parse = TRUE, segment.size = 0.5, min.segment.length = 0, force = 18) +
     scale_color_manual(values = rainbow_colors) +
     xlab(expression(italic(H))) +
     ylab(expression(italic(C))) +
     xlim(limits = c(min(HC.values$H, rect95$H, rect99$H), max(HC.values$H, rect95$H, rect99$H))) + 
     ylim(limits=c(0.002, max(HC.values$C, rect95$C, rect99$C))) + 
-    theme_few(base_size = 20, base_family = "sans")  + 
+    theme_few(base_size = 20, base_family = "serif")  + 
     theme(plot.title = element_text(hjust=0.5), legend.position="none")
   print(p)
   dev.off()
@@ -148,7 +148,7 @@ correlation.analysis.dotted <- function(){
     geom_polygon(data=rect99, aes(x = H, y = C), fill="green", alpha=0.2, inherit.aes = FALSE) +
     geom_line(data = cotas.sup, aes(x = c1x, y = c1y), color="gray") +
     geom_line(data = cotas.inf, aes(x = c2x, y = c2y), color="gray") + 
-    geom_label_repel(aes(label = paste("italic(k) ==", legend.names)),parse = TRUE, segment.size = 0.5, min.segment.length = 0, force = 18) +
+    geom_label_repel(aes(label = paste(expression(italic(k)), "==", legend.names)),parse = TRUE, segment.size = 0.5, min.segment.length = 0, force = 18) +
     geom_line(linetype="dotted") +
     geom_point(size = 1.5, alpha = .4) + 
     scale_color_manual(values = rainbow_colors) +
@@ -156,7 +156,7 @@ correlation.analysis.dotted <- function(){
     ylim(limits=c(0.002, max(HC.values$C, rect95$C, rect99$C))) + 
     xlab(expression(italic(H))) +
[…]

### 2021-10-09 Code/Emblematic-Point-Search.R

@@ -24,6 +24,7 @@ for(i in names){
   dados <- c(dados, Data)
 }
 
+dados <- readBin('../Data/random.org/random_50k.bin',n=1e8,size="4",what ='integer')
 dados <- abs(dados/max(dados))
 write.csv(dados[1:50000], file = "../Data/random_sample.csv")
 
@@ -33,7 +34,7 @@ source("bandt_pompe/features.R")
 source("bandt_pompe/visibility.R")
 source("bandt_pompe/helpers.R")
 
-random_50k <- readBin('data/random_50k.bin',n=1e8,size="4",what ='integer')
+random_50k <- readBin('../Data/random.org/random_50k.bin',n=1e8,size="4",what ='integer')
 seq_50k <- abs(random_50k/max(random_50k))
 split_seq <- as.matrix(split(seq_50k, ceiling(seq_along(seq_50k)/50000)))
 ts = matrix(nrow = 50000, ncol = 104)
@@ -43,15 +44,16 @@ for(i in 1:104){
 }
 
 for(i in 1:104){
-  probs = bandt.pompe(ts[,i], 6, 1)
+  probs = bandt.pompe(ts[,i], 3, 1)
   h = shannon.entropy.normalized(probs)
   c = Ccomplexity(probs)
-  cat("i: ", i, " H: ", h, " C: ", c, "\n")
+  cat("i: ", i, " H: ", round(h, 9), " C: ", round(c, 9), "\n")
   
-  print(test.point(H = h, C = c, D = 6, N = 50000, region = 90))
+  if(round(h, 6) == round(0.999985292278035, 6) && round(c, 6) == round(0.0000145144384709536, 6))
+    print(i)
 }
 
-#H = 0.9989109
-#C = 0.002609346
+#H = 0.999985292278035
+#C = 1.45144384709536e-05
 
-write.csv(ts[,1], "Emblematic-series-D6-N50000.csv")
+write.csv(ts[,10], "../Data/Emblematic-serie-D3-N50000.csv")

### 2021-10-09 Code/HCPlanePlots.R

@@ -20,17 +20,17 @@ source("Bandt-Pompe.R")
 
 
 # Paleta montada a partir de https://coolors.co/ -------------------------------------------------------
-rainbow_colors <- palette(c("#494947", # 1
-                            "#7494EA", # 2
-                            "#B14AED", # 3
-                            "#44CCFF", # 4
-                            "#35FF69", # 5
-                            "#ED8438", # 6
-                            "#00296b", # 7
-                            "#ffff3f", # 8
-                            "#d62828", # 9
-                            "#FB4D3D", # 10
-                            "#f72585") # 11
+rainbow_colors <- palette(c("#494947", #DarkGreen
+                            "#FB4D3D", #BrightRed
+                            "#B14AED", #Violet
+                            "#44CCFF", #BrightLightBlue
+                            "#35FF69", #BrightGreen
+                            "#ED8438", #Orange
+                            "#c41676", #Pink
+                            "#06470d", #verde escuro
+                            "#BF6F00", #DarkYellow
+                            "#7494EA", #MutedDarkBlue
+                            "#495867") #DarkGray
 )
 
 #Função geradora da série f^⁻k--------------------------------------------------------------------------
@@ -85,7 +85,7 @@ cotas <- function(dimension){
   p = qplot(xlab=expression(italic(H)), ylab=expression(italic(C))) +
     geom_line(aes(x=c2x, y=c2y), size=1.5, color="gray") +
     geom_line(aes(x=c1x, c1y), size=1.5, color="gray") + 
-    theme_few(base_size = 18, base_family = "sans")  + 
+    theme_few(base_size = 18, base_family = "serif")  + 
     theme(plot.title = element_text(hjust=0.5)) + 
     scale_colour_few("Dark")
   print(p)
@@ -236,55 +236,57 @@ p <- cotas(dimension)
 pHC <- HCPlane(p, Entropy.Complexity.fk, dimension,1)
 pHC <- HCPlane(pHC, Entropy.Complexity.map, dimension,0)
 pHC <- HCPlane(pHC, Entropy.Complexity.monotonic, dimension,0)
[…]

### 2021-10-09 Code/Histogram-Analysis.R

@@ -25,16 +25,16 @@ if(!require(grid)){
 }
 
 rainbow_colors <- palette(c("#494947", #DarkGreen
-                            "#7494EA", #MutedDarkBlue
+                            "#FB4D3D", #BrightRed
                             "#B14AED", #Violet
                             "#44CCFF", #BrightLightBlue
                             "#35FF69", #BrightGreen
                             "#ED8438", #Orange
-                            "#E7AD99", #Pink
-                            "#C18C5D", #LightBrown
-                            "#BF6F00", #DarkYellow
-                            "#FB4D3D", #BrightRed
-                            "#495867") #DarkGray
+                            "#c41676", #Pink
+                            "#06470d", #verde escuro
+                            "#BF6F00") #DarkYellow
+                            #"#7494EA", #MutedDarkBlue
+                            #"#495867") #DarkGray
 )
 
 series.generator.fk <- function(pp, y, n, k){
@@ -56,7 +56,7 @@ series.generator.map <- function(r, x_0, n){
   Series
 }
 
-calculate.histogram <- function(ts, d, t, name.title){
+calculate.histogram <- function(ts, d, t, name.title, color_plot){
   fat = factorial(d)
   symbol = define.symbols(d)
   p.patterns = formationPattern(ts, d, t, 0)
@@ -74,7 +74,7 @@ calculate.histogram <- function(ts, d, t, name.title){
   index.rep = data.frame(i = index.rep)
   p = ggplot(index.rep) +
     geom_histogram(aes(x = i, y = ..density..),
-                   binwidth = 1, color = "#212529") +
+                   binwidth = 1, color = color_plot, fill = color_plot) +
     ggtitle(name.title) +
     theme_few(base_size = 12, base_family = "serif") +
     theme(plot.title = element_text(size = 12, hjust=0.5)) + 
@@ -127,13 +127,22 @@ series.periodic = sin(2*x) * cos(2*x)
 ## Histogram ----------------------------------------------------------------------------------------------
 plots = array(list(), 11)
 series = data.frame(series.fk, series.map, series.monotonic, series.periodic)
-names.title = c("White Noise", expression(f^{-1/2}), expression(f^{-1}),
-                expression(f^{-3/2}), expression(f^{-2}), expression(f^{-5/2}),
[…]

### 2021-10-09 Code/RNG-Analysis.R

@@ -86,7 +86,7 @@
       geom_point(data = median, aes(x = H, y = C), colour = "red", size = 1) +
       #xlab("H") + ylab("C") + 
       xlab(expression(italic(H))) + ylab(expression(italic(C))) + 
-      theme_few(base_size = 25, base_family = "sans") +  
+      theme_few(base_size = 25, base_family = "serif") +  
       theme(plot.title = element_text(hjust=0.5),
             axis.text.x = element_text(angle = 30)) -> p
     
@@ -118,7 +118,7 @@
             label.x = expression(italic(H)), 
             label.y = expression(italic(C))) + 
     ggtitle(expression(italic(T)==1000)) +
-    theme_few(base_size = 30, base_family = "sans") + 
+    theme_few(base_size = 30, base_family = "serif") + 
     # theme(text=element_text(size=25, family="Times"), plot.title = element_text(hjust=0.5)) + 
     guides(colour = guide_legend(override.aes = list(size=3)))
   dev.off()
@@ -140,7 +140,7 @@
   ggarrange(p1, p2, p3, p4, ncol = 4, nrow = 1, common.legend = TRUE, legend = "right") + 
     ggtitle(expression(italic(T)==50000)) +
     xlab(expression(italic(H))) + ylab(expression(italic(C))) + 
-    theme_few(base_size = 30, base_family = "sans") + 
+    theme_few(base_size = 30, base_family = "serif") + 
     guides(colour = guide_legend(override.aes = list(size=3)))
   dev.off()
   

### 2021-10-09 Code/Trozos-HC-PCA.R

@@ -112,9 +112,9 @@ plot.HC.PCA.trozos <- function(N, dim, lengend ,x.lim = NULL, y.lim = NULL){
               fill = "yellow", alpha = 0.3, inherit.aes = FALSE) +
     #scale_color_discrete(name = expression(italic(D))) +
     #ggtitle(expression(italic(legend))) +
-    xlab(expression(PC[1])) + 
-    ylab(expression(PC[2])) + 
-    theme_few(base_size = 35, base_family = "sans") +  
+    xlab(expression(italic(PC[1]))) + 
+    ylab(expression(italic(PC[2]))) + 
+    theme_few(base_size = 35, base_family = "serif") +  
     theme(plot.title = element_text(hjust=0.5)) -> p
   
   if(is.null(x.lim)){

### 2021-10-09 Code/methodology.R

@@ -24,7 +24,7 @@ if(!require(ggthemes)){
 
 D = 6
 N = 50000
-HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+HC = read.csv("../Data/Regions-HC/HC-VALIDATION-D6-N50000.csv")[,2:4]
 index = which(HC$D == D)
 HC = HC[index[1:15], ]
 
@@ -104,7 +104,7 @@ step2 <-
             fill = "red", alpha = 0.1, inherit.aes = FALSE) +
   xlab(expression(PC[1])) +
   ylab(expression(PC[2])) + 
-  theme_clean(base_size = 50, base_family = "sans") +  
+  theme_clean(base_size = 50, base_family = "serif") +  
   theme(plot.title = element_text(hjust=0.5)) 
 
 
@@ -141,7 +141,7 @@ ggplot(HC, aes(x = H, y = C)) +
   xlab(expression(italic(H))) +
   ylab(expression(italic(C))) +
   theme(plot.title = element_text(hjust=0.5)) + 
-  theme_clean(base_size = 25, base_family = "sans") 
+  theme_clean(base_size = 25, base_family = "serif") 
 
 step3 <- ggplot(HC, aes(x = H, y = C)) +
   geom_line(data = cotas.sup, aes(x = H, y = C), color="gray") +
@@ -155,7 +155,7 @@ step3 <- ggplot(HC, aes(x = H, y = C)) +
   xlab(expression(italic(H))) +
   ylab(expression(italic(C))) +
   theme(plot.title = element_text(hjust=0.5)) + 
-  theme_clean(base_size = 50, base_family = "sans") 
+  theme_clean(base_size = 50, base_family = "serif") 
 
 ggsave(step1, filename = "../Reports/JOURNAL - Confidence Regions/Figures/step1.pdf", width = 14, height = 10)
 ggsave(step2, filename = "../Reports/JOURNAL - Confidence Regions/Figures/step2.pdf", width = 14, height = 10)

### 2021-10-10 Reports/Journal - Confidence Regions/ResearchProposal.tex
Check Research Proposal

--- 2021-10-07 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
@@
 \usepackage{fouriernc}
+\usepackage{color}
 \usepackage{amsmath,amssymb}
@@
 \graphicspath{{./Figures/}}
+
+\usepackage[indent=1cm]{parskip}
 
@@
 
-\citet{ANewVersatileDiscreteDistribution} proposes a flexible discrete model, the ``discretised beta'' law.
+\citet{ANewVersatileDiscreteDistribution} proposes a flexible discrete model, the ``discretised Beta'' law.
 The probability function of such a random variable is
@@
 This definition yields a model that belongs to the exponential family for any $\alpha,\beta\in\mathbbm R$.
-Denote this situation $X\sim\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$.
+Denote this situation $X\sim\text{dB}(\alpha,\beta, n_{\text{top}},\zeta)$.
 
-If $\alpha,\beta>0$, we can relate the $\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
+If $\alpha,\beta>0$, we can relate the $\text{dB}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
 \begin{equation}
@@
 In order to achieve that, we need the distribution of $(\mathfrak{H},\mathfrak{C})$, the bivariate random  variable that produced $(h,c)$, under $H_0:\mathcal X\text { is white noise}$.
-
+We will work with this setup, but later we will relax this null hypothesis.
+%
 \begin{itemize}
@@
 	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D+1})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
-	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction.
+	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction. \textcolor{red}{Eduarda, come up with a proposal for this.}
 	\item $\bm h$ is the random histogram of proportions from $\bm \pi$
@@
 	\big(H^*(\bm h),C^*(\bm h)\big)$? 
-Under $H_0$, $\bm h$ is (?) a collection of iid random variables taking values in $\{1, 2,\dots, D!\}$ with same probability $1/D!$ but, as they form a histogram, there must be a restriction on the sum of their values.
-I don't know how to go on from this point.
-Multinomial?
-Whichever the distribution of $\bm h$, how do we compute the distribution of $H^*(\bm h)$?
+\item[$\bullet$] If we stick to $H_0$, $\bm h$ is a collection of random variables taking values in $\{1, 2,\dots, D!\}$ with same probability $1/D!$, but they are not independent.
+\item[$\bullet$] We may use the multinomial distribution, but how do we compute the distribution of $H^*(\bm h)$?
 \item[$\bullet$] Alternatively, instead of considering such a flexible discrete distribution, we may use a parametric model.
-\item[Q2:] What is the distribution of $
+\item[Q2:] We will ask a slightly different question: What is the distribution of $
 (\mathfrak{H},\mathfrak{C}) = 
-\big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{db}(\alpha,\beta,1, D!)$?
+\big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{dB}(\alpha,\beta,1, D!)$?
 \item[] But we go back to a quantity, rather than to a random variable.
-\item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{db}(\alpha,\beta,1, D!)$ model.
+\item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{dB}(\alpha,\beta,1, D!)$ model.
 \item[] We have the maximum likelihood estimator for $(\alpha,\beta)$, say $(\widehat\alpha,\widehat\beta)$.
 \item[] We know that the asymptotic distribution of $(\widehat\alpha,\widehat\beta)$ is a bivariate Gaussian law.
-\item[] How close are we to finding an approximate distribution for $
-(\mathfrak{H},\mathfrak{C})$ under $H_0$?
+\item[] We may calculate the joint distribution of $\big(H^*(\widehat\alpha, \widehat\beta) , C(\widehat\alpha, \widehat\beta)\big)$.
 \end{itemize}
+How close are we to finding an approximate distribution for $
+(\mathfrak{H},\mathfrak{C})$?
+Quite close, I believe.
+
+Let us see another interesting ingredient.
+We need to express both the entropy and the disequilibrium with respect to the uniform distribution of a $\text{dB}(\alpha,\beta,1,D!)$ sample.
+\citet{ShannonsEntropyinExponentialFamiliesStatisticalApplications} computes the Shannon entropy for any member of the exponential family, and we know from~\eqref{Eq:ProbdbExponential} that this is the case of this discrete distribution.
+
+Just for the sake of illustration, let us see what happens if we use a continuous Beta distribution rather than its discretised version.
 
@@
 D_{\text{KL}}(V_1,V_2) = \log\frac{\text{B}(\alpha_2,\beta_2)}{\text{B}(\alpha_1,\beta_1)} +
-(\alpha_2-\alpha_1) \psi(\alpha) +
-(\beta_2-\beta_1) \psi(\beta) + \\
+(\alpha_2-\alpha_1) \psi(\alpha_1) +
+(\beta_2-\beta_1) \psi(\beta_1) + \\
 (\alpha_2-\alpha_1+\beta_2-\beta_1) \psi(\alpha_1+\beta_1).

### 2021-10-10 Reports/Journal - Confidence Regions/Chapters/Background.tex
update

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
-\documentclass[alpha-refs]{wiley-article}
-
-\usepackage[binary-units]{siunitx}
-\usepackage{bm,bbm}
-\usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{rotating}
-\graphicspath{{./Figures/}}
-\usepackage[linesnumbered,lined,boxed]{algorithm2e}
-\makeatletter
-\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
-\makeatother
-\usepackage{undertilde}
-\usepackage{todonotes}
-\usepackage{comment}
-
-\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
-\DeclareSIUnit{\alphapercent}{\alpha\%}
-
-\newcommand{\Mycite}[1]{%
- (\citeauthor{#1},~\citeyear{#1})}
-
-\papertype{Original Article}
-
-\title{A Test for White Noise in the Entropy-Complexity Plane}
-
-\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}
-
-\author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
-\author[4]{Osvaldo A.\ Rosso}
-\author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
-
-\contrib[]{All authors contributed equally.}
-
-% Include full affiliation details for all authors
-\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
-\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
-\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
-\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
-
-\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\corremail{eduarda.chagas@dcc.ufmg.br}
-
-\fundinginfo{CNPq, Fapeal}
-
-% Include the name of the author that should appear in the running header
-\runningauthor{Eduarda T.\ C.\ Chagas et al.}
-
-\begin{document}
-
-% \begin{frontmatter}
-\maketitle
-
-\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
-Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
-Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
-capturing the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
-\end{abstract}
-
-\section{Introduction}\label{Sec:Intro}
-
-Time Series carry valuable information about the system which produces the data.
-Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
-in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
-Such an approach is non-parametric and based on descriptors of Information Theory.
-The time series is transformed into ordinal patterns, with which a histogram is formed.
-The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
-Thus, the approach can be applied to a variety of situations.
-
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
-We found works using this approach in several areas of scientific knowledge such as, for example:
-%
-distinguishing noise from chaos~\citep{rosso2007distinguishing};
-%
-the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
-%
-description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
-%
-the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
-%
-detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
-%
-analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
-%
-online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
-\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
-\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
-\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
-\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
-\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.
-
-With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
-There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
-Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
-In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.
-
-The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
-These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
-Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-two in the \textit{Journal of Time Series Analysis}, 
-and each of the remaining ten appeared in a different journal.
-Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
-It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
-The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
-
-Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
-\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
-\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
-\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
-\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
-
-With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
-Results in this direction can be found in the literature.
-\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
-\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-
-Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
-In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
-We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
-Our contributions can be summarized as follows:
-\begin{itemize}
-	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
-	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series.
-\end{itemize}
-
-The rest of this paper is structured as follows. 
-Section~\ref{Sec:BP} introduces the elements of the study:
-Section~\ref{Sec:BPMethodology} details the methodology,
-Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
-and Section~\ref{Sec:BPApplications} discusses applications of this approach.
-%
-Section~\ref{Sec:BPMethodology} describes our methodology:
-Section~\ref{Sec:OverallFramework} gives the overall framework.
-Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
-Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
-Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
-%
-Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
-Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
-
 \section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
@@
 In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
-%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-It is calculated as:
-\begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
-	u(\ell) \log\frac{u(\ell)}{h(\ell)}
-	\Big).
-\end{equation}
-This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
+To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
+They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
 
@@
 
-\section{Proposed Method}\label{Sec:Proposal}
-
-In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
-Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
-Through this new representation of the data, we calculate empirical regions with different levels of confidence.
-Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
-
-\subsection{Overall Framework}\label{Sec:OverallFramework}
-
-Our methodology consists of the following steps:
-\begin{enumerate}
-	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
-	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
-	\item\label{item:Methodology3} Obtain the principal components of these points.
-	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
-	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
-\end{enumerate}
-
-\subsection{True Random Numbers}\label{Sec:TRNG}
-
-Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
-Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
-%In this study we used two sources of real random numbers. 
-%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
-The first uses vacuum states. 
-The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
-The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
-The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
-This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
-The history of this service and other information can be found at \citet{RandomOrg}.
-
-We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
-
-%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
-
-\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
-
-We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
-We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
-On the other hand, we found two relevant variables: 
-the length of the sequence 
-and the embedding dimension.
-We, thus, employed the following factors:
-\begin{itemize}
-	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
-	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
-	%,and
-	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
-\end{itemize}
-and kept $\tau=1$, which is the most frequently used option.
-The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
-
-Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
-For the construction of the confidence regions presented, we used:
-\begin{itemize}
-	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
-	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
-\end{itemize}
-
-We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
-
-\begin{comment}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
-\caption{White noise samples considered during the construction of the proposed confidence regions.}
-\label{fig:white-noise}
-\end{figure}
-
-\end{comment}
-
-\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
-
-%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
-
-Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
-Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
-Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
-%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
-
-%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
-%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
-
-Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
-In the sequel, whenever possible, we will omit $T$ and $D$.
-For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
-Fig.~\ref{fig:Methodology1} illustrates this step.
-We will obtain confidence regions and $p$-values from $\utilde{hc}$.
-
-The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
-With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
-This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
-Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
-Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
-
-For simplicity, and without loss of generality, assume $N$ is odd.
-\begin{enumerate}
-	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
-Call the corresponding time series ``emblematic time series.''
-	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
-	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
-	\item The corners of the box are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
-\end{enumerate}
-
-Fig.~\ref{fig:methodology} illustrates these steps.
-%
-Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
-The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
-The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
-%
-Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
-The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
-We highlighted in red the point whose first principal component is the median of the observed values.
-%
-Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
-The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
-
-\begin{figure}[hbt]
-	\centering
-	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
-	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
-	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
-	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
-	\caption{Outline of the methodology used for the construction of the confidence regions.}
-	\label{fig:methodology}
-\end{figure}
-
-Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
-We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{A data base of true random values}
-	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
-	\Output{Confidence regions as points in the $H\times C$ plane}
-	\For{each $D\in \mathcal D$}{
-		\For{each $T\in \mathcal T$}{
-			\For{each $n=1,2,\dots,N$}{
-				build the time series $p_n$ with unused values from the data base\;
-				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
-			}
-			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
-			%
-			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
-			%
-			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
-			%
-			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-			%
-			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
-			\Return{$\bm P'$}\;
-			%
-			\For{each confidence level $\alpha \in \mathcal A$}{
-				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
-				%
-				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
-				%
-				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
-				%
-				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
-				%
-				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
-				%
-				the corners of the box are 
-				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
-				%
-				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
-				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
-			}
-		}
-	}
-	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
-\end{algorithm}
-
-%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
-
-These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
-More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
-We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
-
-The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
-We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
-We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
-We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
-The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
-Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
-We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
-\begin{enumerate}
-	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
-By definition, $\eta_u\geq 1/2$.
-	%
-	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
-	%
-	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
-	%
-	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
-\end{enumerate}
-Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
-
-The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
-With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
-
-Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
-Algorithm~\ref{Algo:p-value} shows the details.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
-	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
-	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
-	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
-	\label{fig:methodologyPvalue}
-\end{figure}
-
-\begin{comment}
-The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
-Therefore, it can be achieved by the following steps:
-\begin{enumerate}
-\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
-\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
-\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
-\end{enumerate}
-Thus, we can verify that:
-\begin{itemize}
-\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
-\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
-\end{itemize}
-Assuming the critical value $\alpha = 0.05$, we obtain:
-\begin{equation*}
-p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
-\end{equation*}
-\end{comment}
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
-	\Input{The embedding dimension $D$}
-	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
-		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
-		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
-	\Output{An approximate $p$-value}
-	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-	find the point $(h,c)$ of the sequence $\bm x$\;
-	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
-	\eIf{$u_x > u$}
-	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
-		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
-	}
-	{
-		\eIf{$u_x < u$}
-		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
-			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
-		}
-		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
-		}
-	}
-	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
-	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
-	the corners of the box $b_{\alpha}(h,c)$ are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
-	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
-	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
-	\Return{$1-n_{\bm x}/N$}
-	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
-\end{algorithm}
-
-\section{Results}\label{Sec:Results}
-
-\subsection{Empirical confidence regions}
-
-Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
-of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
-for $D=3,4,5,6$ and $N=1000,50000$, .
-The points are presented counterclockwise, starting with the one with the largest complexity.
-
-\begin{comment}
-\begin{table}[hbt]
-\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
-\centering
-\begin{tabular}{rcllllllll}
-\toprule
-& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
-& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
-$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
-$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 1000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
-		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
-		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
-		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
-		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
-		\midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
-		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
-		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
-		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
-		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
-		\midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
-		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
-		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
-		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
-		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
-		\midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
-		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
-		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
-		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
-		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 50000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
-		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
-		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
-		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
-		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
-	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
-	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
-
-Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
-As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
-Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{PCA-hist-50k}
-	\caption{Histograms of the first principal component for $D=3,4,5,6$}
-	\label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Test Size}
-
-We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
-Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
-show the results.
-
-On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
-On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
-In contrast, we expected \SI{1}{\percent} of rejection.
-This might be because, in this case, the condition $D!\ll T$ is not respected.
-Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
-
-%
-%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-%
-%For short series, $T = 1000$, and $D = 3$ 
-%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
-%
-%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-%A reasonable explanation for this event is given in the choice of the parameter itself.
-%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-
-\begin{table}[hbt]
-	\centering
-	\caption{Empirical sizes of the test}
-	\label{tab:result1}
-	\begin{tabular}{*{3}rr}
-		\toprule
-		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		%& $p$-value\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		1000 & 3 & $0.98$ & $1.00$\\
-		& 4 & $0.98$ & $0.96$\\
-		& 5 & $1.00$ & $0.94$\\
-		& 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-4} 
-		50000 & 3 & $0.97$ & $0.96$\\
-		%& $0.47856$\\
-		& 4 & $0.94$ & $0.95$\\
-		%& $0.47555$\\ 
-		& 5 & $0.97$ & $0.96$\\ 
-		%& $0.48512$\\ 
-		& 6 & $0.98$ & $0.99$\\ 
-		%& $0.48058$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-	\caption{New $100$ TRWNS and regions of confidence.}
-	\label{fig:RNG}
-\end{figure}
-
-We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
-
-\subsection{Test Power}
-
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
-Several studies in the literature have used this approach for identifying and characterizing randomness.
-
-Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
-Recall that the emblematic time was chosen as the most representative of the data set.
-We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
-
-%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
-At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
-
-Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
-We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
-Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
-The same holds for all $k>3/10$.
-
-\begin{figure}
-	\centering
-	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
-	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
-	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
-	\label{fig:correlation}
-\end{figure}
-
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
-
-In this section, we compare the performance of our test with that of 
-previous analyses that employ the Entropy-Complexity plane.
-To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
-Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
-
-\begin{table}
-	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
-	\label{Tab:LiteratureComparations}
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		MOT & 3 & 0.305 & NR\\
-		& 4 & 0.572 & NR\\ 
-		& 5 & 0.455 & NR\\ 
-		& 6 & 0.508 & NR\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 0.501 & NR\\
-		& 4 & 0.477 & NR\\ 
-		& 5 & 0.496 & NR\\ 
-		& 6 & 0.496 & NR\\ 
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.123 & NR\\
-		& 4 & 0.002 & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.531 & NR\\
-		& 4 & 0.515 & NR\\ 
-		\bottomrule
-	\end{tabular}
-	\begin{tabular}{|cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		LEH & 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.521 & NR\\
-		& 4 & 0.519 & NR\\ 
-		& 5 & 0.498 & NR\\ 
-		& 6 & 0.470 & NR\\
-		\cmidrule(lr){1-4}
-		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.482 & NR\\
-		& 4 & 0.520 & NR\\ 
-		& 5 & 0.513 & NR\\ 
-		& 6 & 0.508 & NR\\
-		\cmidrule(lr){1-4}
-		LCG & 3 & 0.009 & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
-
-It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
-In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
-
-\section{Conclusions}\label{Sec:Conclusions}
-
-We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
-Our proposal is based on two stages:
-(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
-(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
-We obtained the TWNRS with data from physical devices.
-
-Our test has a good size, mostly with long TWNRS.
-We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
-
-Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
-With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
-
-\section{Reproducibility and Replicability}\label{Sec:code}
-
-Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
-
-\section{Acknowledgements}\label{Sec:acknowledgements}
-
-This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
-
-\printendnotes
-
-\bibliography{References}
-
-\end{document}
+\include{Chapters/relatedWork}

### 2021-10-10 Reports/Journal - Confidence Regions/Chapters/Conclusions.tex
update

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
-\documentclass[alpha-refs]{wiley-article}
-
-\usepackage[binary-units]{siunitx}
-\usepackage{bm,bbm}
-\usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{rotating}
-\graphicspath{{./Figures/}}
-\usepackage[linesnumbered,lined,boxed]{algorithm2e}
-\makeatletter
-\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
-\makeatother
-\usepackage{undertilde}
-\usepackage{todonotes}
-\usepackage{comment}
-
-\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
-\DeclareSIUnit{\alphapercent}{\alpha\%}
-
-\newcommand{\Mycite}[1]{%
- (\citeauthor{#1},~\citeyear{#1})}
-
-\papertype{Original Article}
-
-\title{A Test for White Noise in the Entropy-Complexity Plane}
-
-\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}
-
-\author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
-\author[4]{Osvaldo A.\ Rosso}
-\author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
-
-\contrib[]{All authors contributed equally.}
-
-% Include full affiliation details for all authors
-\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
-\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
-\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
-\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
-
-\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\corremail{eduarda.chagas@dcc.ufmg.br}
-
-\fundinginfo{CNPq, Fapeal}
-
-% Include the name of the author that should appear in the running header
-\runningauthor{Eduarda T.\ C.\ Chagas et al.}
-
-\begin{document}
-
-% \begin{frontmatter}
-\maketitle
-
-\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
-Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
-Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
-capturing the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
-\end{abstract}
-
-\section{Introduction}\label{Sec:Intro}
-
-Time Series carry valuable information about the system which produces the data.
-Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
-in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
-Such an approach is non-parametric and based on descriptors of Information Theory.
-The time series is transformed into ordinal patterns, with which a histogram is formed.
-The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
-Thus, the approach can be applied to a variety of situations.
-
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
-We found works using this approach in several areas of scientific knowledge such as, for example:
-%
-distinguishing noise from chaos~\citep{rosso2007distinguishing};
-%
-the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
-%
-description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
-%
-the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
-%
-detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
-%
-analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
-%
-online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
-\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
-\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
-\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
-\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
-\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.
-
-With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
-There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
-Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
-In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.
-
-The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
-These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
-Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-two in the \textit{Journal of Time Series Analysis}, 
-and each of the remaining ten appeared in a different journal.
-Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
-It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
-The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
-
-Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
-\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
-\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
-\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
-\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
-
-With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
-Results in this direction can be found in the literature.
-\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
-\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-
-Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
-In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
-We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
-Our contributions can be summarized as follows:
-\begin{itemize}
-	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
-	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series.
-\end{itemize}
-
-The rest of this paper is structured as follows. 
-Section~\ref{Sec:BP} introduces the elements of the study:
-Section~\ref{Sec:BPMethodology} details the methodology,
-Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
-and Section~\ref{Sec:BPApplications} discusses applications of this approach.
-%
-Section~\ref{Sec:BPMethodology} describes our methodology:
-Section~\ref{Sec:OverallFramework} gives the overall framework.
-Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
-Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
-Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
-%
-Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
-Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
-
-\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
-
-In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
-Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
-We then obtain a test statistic, using confidence regions, that can discriminate among times series.
-
-\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}
-
-Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
-As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
-\begin{quote}
-	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
-	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
-\end{quote}
-Also, as stressed by these authors, 
-\begin{quote}
-	``The corresponding symbol sequence must come 
-	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
-\end{quote}
-
-Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
-possible permutation of order $D$, and the symbol component vector 
-${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
-Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
-with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
-\begin{equation} 
-	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
-	\label{eq:time-delay}
-\end{equation} 
-for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
-Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
-This mapping should be defined in a way that preserves the desired relation between the elements 
-$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
-${\bm \pi}^{(D)}$. 
-The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[label=\alph*)]
-	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
-	(\textit{Rank Permutation}) or,
-	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
-	(\textit{Chronological Index Permutation}).
-\end{enumerate}
-See details in the work by \citet{BPRepeatedValuesChaos}.
-Without loss of generality, in the following, we will use the latter.
-
-Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
-Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
-The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
-With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
-
-The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
-In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{IntroBP}
-	\caption{Illustration of the Bandt and Pompe coding}
-	\label{Fig:IntroBP}
-\end{figure}
-
-After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
-Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
-The next step into the characterization of the time series is computing descriptors from this histogram.
-
-The first descriptor is a measure of the disorder of the system.
-The most frequently used feature for this is the Normalized Shannon entropy, defined as
-\begin{equation}
-	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
-\end{equation}
-with the convention that terms in the summation for which $h(j)=0$ are null.
-This quantity is bounded in the unit interval. 
-It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
-
-Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
-In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
-%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-It is calculated as:
-\begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
-	u(\ell) \log\frac{u(\ell)}{h(\ell)}
-	\Big).
-\end{equation}
-This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
-
-With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
-A time series can then be mapped into a point in the $H\times C$ plane.
-
-\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}
-
-The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
-The time delay is irrelevant, and we consider infinitely long series.
-
-Let us consider two extreme cases:
-\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
-	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
-	The entropy is zero, and the distance to the uniform distribution is maximal. 
-	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
-	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
-	The distance to the equilibrium distribution is zero. 
-	Thus, such series are mapped onto the point $(1,0)$.
-\end{enumerate}
-
-\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
-\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
-The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
-The upper boundary converges to a smooth curve when $D\to\infty$.
-
-Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
-The inset plot highlights the fine structure of the upper boundary inside the rectangle.
-The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
-	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
-\end{figure}
-
-We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
-\begin{itemize}
-	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
-	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
-\end{itemize}
-In all cases, we used $D=6$ and $\tau=1$.
-Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
-we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
-
-\begin{figure}[hbt]
-	\includegraphics[width=\linewidth]{Figures/h.pdf}
-	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:Histograms}
-\end{figure}
-
-Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
-The points due to $f^{-k}$ noises appear joined by dotted segments.
-It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{AllSystems}
-	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:AllSystems}
-\end{figure}
-
-Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{RightMostCorner}
-	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:RightMostCorner}
-\end{figure}
-
-Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
-Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
-
-\section{Proposed Method}\label{Sec:Proposal}
-
-In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
-Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
-Through this new representation of the data, we calculate empirical regions with different levels of confidence.
-Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
-
-\subsection{Overall Framework}\label{Sec:OverallFramework}
-
-Our methodology consists of the following steps:
-\begin{enumerate}
-	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
-	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
-	\item\label{item:Methodology3} Obtain the principal components of these points.
-	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
-	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
-\end{enumerate}
-
-\subsection{True Random Numbers}\label{Sec:TRNG}
-
-Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
-Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
-%In this study we used two sources of real random numbers. 
-%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
-The first uses vacuum states. 
-The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
-The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
-The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
-This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
-The history of this service and other information can be found at \citet{RandomOrg}.
-
-We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
-
-%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
-
-\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
-
-We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
-We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
-On the other hand, we found two relevant variables: 
-the length of the sequence 
-and the embedding dimension.
-We, thus, employed the following factors:
-\begin{itemize}
-	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
-	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
-	%,and
-	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
-\end{itemize}
-and kept $\tau=1$, which is the most frequently used option.
-The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
-
-Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
-For the construction of the confidence regions presented, we used:
-\begin{itemize}
-	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
-	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
-\end{itemize}
-
-We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
-
-\begin{comment}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
-\caption{White noise samples considered during the construction of the proposed confidence regions.}
-\label{fig:white-noise}
-\end{figure}
-
-\end{comment}
-
-\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
-
-%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
-
-Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
-Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
-Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
-%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
-
-%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
-%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
-
-Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
-In the sequel, whenever possible, we will omit $T$ and $D$.
-For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
-Fig.~\ref{fig:Methodology1} illustrates this step.
-We will obtain confidence regions and $p$-values from $\utilde{hc}$.
-
-The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
-With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
-This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
-Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
-Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
-
-For simplicity, and without loss of generality, assume $N$ is odd.
-\begin{enumerate}
-	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
-Call the corresponding time series ``emblematic time series.''
-	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
-	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
-	\item The corners of the box are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
-\end{enumerate}
-
-Fig.~\ref{fig:methodology} illustrates these steps.
-%
-Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
-The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
-The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
-%
-Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
-The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
-We highlighted in red the point whose first principal component is the median of the observed values.
-%
-Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
-The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
-
-\begin{figure}[hbt]
-	\centering
-	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
-	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
-	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
-	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
-	\caption{Outline of the methodology used for the construction of the confidence regions.}
-	\label{fig:methodology}
-\end{figure}
-
-Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
-We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{A data base of true random values}
-	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
-	\Output{Confidence regions as points in the $H\times C$ plane}
-	\For{each $D\in \mathcal D$}{
-		\For{each $T\in \mathcal T$}{
-			\For{each $n=1,2,\dots,N$}{
-				build the time series $p_n$ with unused values from the data base\;
-				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
-			}
-			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
-			%
-			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
-			%
-			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
-			%
-			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-			%
-			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
-			\Return{$\bm P'$}\;
-			%
-			\For{each confidence level $\alpha \in \mathcal A$}{
-				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
-				%
-				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
-				%
-				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
-				%
-				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
-				%
-				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
-				%
-				the corners of the box are 
-				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
-				%
-				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
-				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
-			}
-		}
-	}
-	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
-\end{algorithm}
-
-%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
-
-These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
-More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
-We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
-
-The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
-We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
-We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
-We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
-The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
-Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
-We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
-\begin{enumerate}
-	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
-By definition, $\eta_u\geq 1/2$.
-	%
-	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
-	%
-	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
-	%
-	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
-\end{enumerate}
-Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
-
-The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
-With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
-
-Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
-Algorithm~\ref{Algo:p-value} shows the details.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
-	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
-	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
-	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
-	\label{fig:methodologyPvalue}
-\end{figure}
-
-\begin{comment}
-The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
-Therefore, it can be achieved by the following steps:
-\begin{enumerate}
-\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
-\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
-\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
-\end{enumerate}
-Thus, we can verify that:
-\begin{itemize}
-\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
-\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
-\end{itemize}
-Assuming the critical value $\alpha = 0.05$, we obtain:
-\begin{equation*}
-p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
-\end{equation*}
-\end{comment}
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
-	\Input{The embedding dimension $D$}
-	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
-		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
-		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
-	\Output{An approximate $p$-value}
-	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-	find the point $(h,c)$ of the sequence $\bm x$\;
-	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
-	\eIf{$u_x > u$}
-	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
-		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
-	}
-	{
-		\eIf{$u_x < u$}
-		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
-			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
-		}
-		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
-		}
-	}
-	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
-	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
-	the corners of the box $b_{\alpha}(h,c)$ are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
-	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
-	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
-	\Return{$1-n_{\bm x}/N$}
-	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
-\end{algorithm}
-
-\section{Results}\label{Sec:Results}
-
-\subsection{Empirical confidence regions}
-
-Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
-of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
-for $D=3,4,5,6$ and $N=1000,50000$, .
-The points are presented counterclockwise, starting with the one with the largest complexity.
-
-\begin{comment}
-\begin{table}[hbt]
-\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
-\centering
-\begin{tabular}{rcllllllll}
-\toprule
-& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
-& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
-$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
-$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 1000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
-		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
-		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
-		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
-		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
-		\midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
-		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
-		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
-		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
-		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
-		\midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
-		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
-		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
-		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
-		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
-		\midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
-		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
-		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
-		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
-		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 50000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
-		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
-		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
-		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
-		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
-	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
-	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
-
-Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
-As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
-Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{PCA-hist-50k}
-	\caption{Histograms of the first principal component for $D=3,4,5,6$}
-	\label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Test Size}
-
-We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
-Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
-show the results.
-
-On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
-On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
-In contrast, we expected \SI{1}{\percent} of rejection.
-This might be because, in this case, the condition $D!\ll T$ is not respected.
-Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
-
-%
-%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-%
-%For short series, $T = 1000$, and $D = 3$ 
-%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
-%
-%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-%A reasonable explanation for this event is given in the choice of the parameter itself.
-%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-
-\begin{table}[hbt]
-	\centering
-	\caption{Empirical sizes of the test}
-	\label{tab:result1}
-	\begin{tabular}{*{3}rr}
-		\toprule
-		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		%& $p$-value\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		1000 & 3 & $0.98$ & $1.00$\\
-		& 4 & $0.98$ & $0.96$\\
-		& 5 & $1.00$ & $0.94$\\
-		& 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-4} 
-		50000 & 3 & $0.97$ & $0.96$\\
-		%& $0.47856$\\
-		& 4 & $0.94$ & $0.95$\\
-		%& $0.47555$\\ 
-		& 5 & $0.97$ & $0.96$\\ 
-		%& $0.48512$\\ 
-		& 6 & $0.98$ & $0.99$\\ 
-		%& $0.48058$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-	\caption{New $100$ TRWNS and regions of confidence.}
-	\label{fig:RNG}
-\end{figure}
-
-We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
-
-\subsection{Test Power}
-
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
-Several studies in the literature have used this approach for identifying and characterizing randomness.
-
-Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
-Recall that the emblematic time was chosen as the most representative of the data set.
-We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
-
-%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
-At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
-
-Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
-We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
-Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
-The same holds for all $k>3/10$.
-
-\begin{figure}
-	\centering
-	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
-	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
-	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
-	\label{fig:correlation}
-\end{figure}
-
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
-
-In this section, we compare the performance of our test with that of 
-previous analyses that employ the Entropy-Complexity plane.
-To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
-Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
-
-\begin{table}
-	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
-	\label{Tab:LiteratureComparations}
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		MOT & 3 & 0.305 & NR\\
-		& 4 & 0.572 & NR\\ 
-		& 5 & 0.455 & NR\\ 
-		& 6 & 0.508 & NR\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 0.501 & NR\\
-		& 4 & 0.477 & NR\\ 
-		& 5 & 0.496 & NR\\ 
-		& 6 & 0.496 & NR\\ 
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.123 & NR\\
-		& 4 & 0.002 & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.531 & NR\\
-		& 4 & 0.515 & NR\\ 
-		\bottomrule
-	\end{tabular}
-	\begin{tabular}{|cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		LEH & 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.521 & NR\\
-		& 4 & 0.519 & NR\\ 
-		& 5 & 0.498 & NR\\ 
-		& 6 & 0.470 & NR\\
-		\cmidrule(lr){1-4}
-		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.482 & NR\\
-		& 4 & 0.520 & NR\\ 
-		& 5 & 0.513 & NR\\ 
-		& 6 & 0.508 & NR\\
-		\cmidrule(lr){1-4}
-		LCG & 3 & 0.009 & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
-
-It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
-In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
-
 \section{Conclusions}\label{Sec:Conclusions}
@@
 With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
-
-\section{Reproducibility and Replicability}\label{Sec:code}
-
-Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
-
-\section{Acknowledgements}\label{Sec:acknowledgements}
-
-This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
-
-\printendnotes
-
-\bibliography{References}
-
-\end{document}

### 2021-10-10 Reports/Journal - Confidence Regions/Chapters/Introduction.tex
update

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
-\documentclass[alpha-refs]{wiley-article}
-
-\usepackage[binary-units]{siunitx}
-\usepackage{bm,bbm}
-\usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{rotating}
-\graphicspath{{./Figures/}}
-\usepackage[linesnumbered,lined,boxed]{algorithm2e}
-\makeatletter
-\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
-\makeatother
-\usepackage{undertilde}
-\usepackage{todonotes}
-\usepackage{comment}
-
-\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
-\DeclareSIUnit{\alphapercent}{\alpha\%}
-
-\newcommand{\Mycite}[1]{%
- (\citeauthor{#1},~\citeyear{#1})}
-
-\papertype{Original Article}
-
-\title{A Test for White Noise in the Entropy-Complexity Plane}
-
-\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}
-
-\author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
-\author[4]{Osvaldo A.\ Rosso}
-\author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
-
-\contrib[]{All authors contributed equally.}
-
-% Include full affiliation details for all authors
-\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
-\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
-\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
-\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
-
-\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\corremail{eduarda.chagas@dcc.ufmg.br}
-
-\fundinginfo{CNPq, Fapeal}
-
-% Include the name of the author that should appear in the running header
-\runningauthor{Eduarda T.\ C.\ Chagas et al.}
-
-\begin{document}
-
-% \begin{frontmatter}
-\maketitle
-
-\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
-Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
-Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
-capturing the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
-\end{abstract}
-
 \section{Introduction}\label{Sec:Intro}
@@
 Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
-
-\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
-
-In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
-Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
-We then obtain a test statistic, using confidence regions, that can discriminate among times series.
-
-\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}
-
-Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
-As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
-\begin{quote}
-	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
-	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
-\end{quote}
-Also, as stressed by these authors, 
-\begin{quote}
-	``The corresponding symbol sequence must come 
-	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
-\end{quote}
-
-Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
-possible permutation of order $D$, and the symbol component vector 
-${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
-Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
-with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
-\begin{equation} 
-	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
-	\label{eq:time-delay}
-\end{equation} 
-for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
-Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
-This mapping should be defined in a way that preserves the desired relation between the elements 
-$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
-${\bm \pi}^{(D)}$. 
-The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[label=\alph*)]
-	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
-	(\textit{Rank Permutation}) or,
-	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
-	(\textit{Chronological Index Permutation}).
-\end{enumerate}
-See details in the work by \citet{BPRepeatedValuesChaos}.
-Without loss of generality, in the following, we will use the latter.
-
-Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
-Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
-The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
-With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
-
-The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
-In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{IntroBP}
-	\caption{Illustration of the Bandt and Pompe coding}
-	\label{Fig:IntroBP}
-\end{figure}
-
-After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
-Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
-The next step into the characterization of the time series is computing descriptors from this histogram.
-
-The first descriptor is a measure of the disorder of the system.
-The most frequently used feature for this is the Normalized Shannon entropy, defined as
-\begin{equation}
-	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
-\end{equation}
-with the convention that terms in the summation for which $h(j)=0$ are null.
-This quantity is bounded in the unit interval. 
-It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
-
-Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
-In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
-%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-It is calculated as:
-\begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
-	u(\ell) \log\frac{u(\ell)}{h(\ell)}
-	\Big).
-\end{equation}
-This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
-
-With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
-A time series can then be mapped into a point in the $H\times C$ plane.
-
-\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}
-
-The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
-The time delay is irrelevant, and we consider infinitely long series.
-
-Let us consider two extreme cases:
-\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
-	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
-	The entropy is zero, and the distance to the uniform distribution is maximal. 
-	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
-	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
-	The distance to the equilibrium distribution is zero. 
-	Thus, such series are mapped onto the point $(1,0)$.
-\end{enumerate}
-
-\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
-\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
-The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
-The upper boundary converges to a smooth curve when $D\to\infty$.
-
-Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
-The inset plot highlights the fine structure of the upper boundary inside the rectangle.
-The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
-	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
-\end{figure}
-
-We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
-\begin{itemize}
-	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
-	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
-\end{itemize}
-In all cases, we used $D=6$ and $\tau=1$.
-Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
-we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
-
-\begin{figure}[hbt]
-	\includegraphics[width=\linewidth]{Figures/h.pdf}
-	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:Histograms}
-\end{figure}
-
-Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
-The points due to $f^{-k}$ noises appear joined by dotted segments.
-It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{AllSystems}
-	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:AllSystems}
-\end{figure}
-
-Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{RightMostCorner}
-	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:RightMostCorner}
-\end{figure}
-
-Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
-Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
-
-\section{Proposed Method}\label{Sec:Proposal}
-
-In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
-Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
-Through this new representation of the data, we calculate empirical regions with different levels of confidence.
-Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
-
-\subsection{Overall Framework}\label{Sec:OverallFramework}
-
-Our methodology consists of the following steps:
-\begin{enumerate}
-	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
-	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
-	\item\label{item:Methodology3} Obtain the principal components of these points.
-	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
-	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
-\end{enumerate}
-
-\subsection{True Random Numbers}\label{Sec:TRNG}
-
-Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
-Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
-Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
-%In this study we used two sources of real random numbers. 
-%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
-
-In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
-The first uses vacuum states. 
-The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
-The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
-The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
-This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
-The history of this service and other information can be found at \citet{RandomOrg}.
-
-We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
-
-%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
-
-\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
-
-We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
-We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
-On the other hand, we found two relevant variables: 
-the length of the sequence 
-and the embedding dimension.
-We, thus, employed the following factors:
-\begin{itemize}
-	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
-	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
-	%,and
-	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
-\end{itemize}
-and kept $\tau=1$, which is the most frequently used option.
-The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
-
-Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
-For the construction of the confidence regions presented, we used:
-\begin{itemize}
-	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
-	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
-\end{itemize}
-
-We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
-
-\begin{comment}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
-\caption{White noise samples considered during the construction of the proposed confidence regions.}
-\label{fig:white-noise}
-\end{figure}
-
-\end{comment}
-
-\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
-
-%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
-
-Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
-Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
-Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
-%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
-
-%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
-%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
-%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
-%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
-
-Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
-In the sequel, whenever possible, we will omit $T$ and $D$.
-For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
-Fig.~\ref{fig:Methodology1} illustrates this step.
-We will obtain confidence regions and $p$-values from $\utilde{hc}$.
-
-The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
-With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
-This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
-Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
-Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
-
-For simplicity, and without loss of generality, assume $N$ is odd.
-\begin{enumerate}
-	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
-	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
-Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
-Call the corresponding time series ``emblematic time series.''
-	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
-	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
-	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
-	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
-	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
-	\item The corners of the box are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
-	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
-\end{enumerate}
-
-Fig.~\ref{fig:methodology} illustrates these steps.
-%
-Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
-The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
-The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
-%
-Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
-The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
-We highlighted in red the point whose first principal component is the median of the observed values.
-%
-Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
-The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
-
-\begin{figure}[hbt]
-	\centering
-	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
-	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
-	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
-	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
-	\caption{Outline of the methodology used for the construction of the confidence regions.}
-	\label{fig:methodology}
-\end{figure}
-
-Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
-We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{A data base of true random values}
-	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
-	\Output{Confidence regions as points in the $H\times C$ plane}
-	\For{each $D\in \mathcal D$}{
-		\For{each $T\in \mathcal T$}{
-			\For{each $n=1,2,\dots,N$}{
-				build the time series $p_n$ with unused values from the data base\;
-				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
-			}
-			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
-			%
-			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
-			%
-			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
-			%
-			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-			%
-			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
-			\Return{$\bm P'$}\;
-			%
-			\For{each confidence level $\alpha \in \mathcal A$}{
-				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
-				%
-				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
-				%
-				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
-				%
-				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
-				%
-				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
-				%
-				the corners of the box are 
-				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
-				%
-				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
-				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
-			}
-		}
-	}
-	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
-\end{algorithm}
-
-%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
-
-These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
-More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
-We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
-
-The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
-We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
-We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
-We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
-The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
-Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
-We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
-\begin{enumerate}
-	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
-By definition, $\eta_u\geq 1/2$.
-	%
-	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
-	%
-	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
-	%
-	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
-\end{enumerate}
-Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
-
-The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
-With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
-
-Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
-Algorithm~\ref{Algo:p-value} shows the details.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
-	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
-	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
-	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
-	\label{fig:methodologyPvalue}
-\end{figure}
-
-\begin{comment}
-The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
-Therefore, it can be achieved by the following steps:
-\begin{enumerate}
-\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
-\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
-\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
-\end{enumerate}
-Thus, we can verify that:
-\begin{itemize}
-\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
-\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
-\end{itemize}
-Assuming the critical value $\alpha = 0.05$, we obtain:
-\begin{equation*}
-p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
-\end{equation*}
-\end{comment}
-
-\begin{algorithm}[hbt]
-	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
-	\Input{The embedding dimension $D$}
-	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
-		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
-		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
-	\Output{An approximate $p$-value}
-	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
-	find the point $(h,c)$ of the sequence $\bm x$\;
-	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
-	\eIf{$u_x > u$}
-	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
-		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
-	}
-	{
-		\eIf{$u_x < u$}
-		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
-			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
-		}
-		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
-		}
-	}
-	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
-	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
-	the corners of the box $b_{\alpha}(h,c)$ are 
-	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
-	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
-	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
-	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
-	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
-	\Return{$1-n_{\bm x}/N$}
-	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
-\end{algorithm}
-
-\section{Results}\label{Sec:Results}
-
-\subsection{Empirical confidence regions}
-
-Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
-of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
-for $D=3,4,5,6$ and $N=1000,50000$, .
-The points are presented counterclockwise, starting with the one with the largest complexity.
-
-\begin{comment}
-\begin{table}[hbt]
-\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
-\centering
-\begin{tabular}{rcllllllll}
-\toprule
-& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
-& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
-$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
-$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 1000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
-		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
-		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
-		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
-		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
-		\midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
-		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
-		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
-		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
-		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
-		\midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
-		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
-		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
-		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
-		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
-		\midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
-		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
-		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
-		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
-		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 50000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
-		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
-		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
-		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
-		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
-	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
-	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
-
-Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
-As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
-Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{PCA-hist-50k}
-	\caption{Histograms of the first principal component for $D=3,4,5,6$}
-	\label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Test Size}
-
-We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
-Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
-show the results.
-
-On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
-On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
-In contrast, we expected \SI{1}{\percent} of rejection.
-This might be because, in this case, the condition $D!\ll T$ is not respected.
-Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
-
-%
-%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-%
-%For short series, $T = 1000$, and $D = 3$ 
-%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
-%
-%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-%A reasonable explanation for this event is given in the choice of the parameter itself.
-%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-
-\begin{table}[hbt]
-	\centering
-	\caption{Empirical sizes of the test}
-	\label{tab:result1}
-	\begin{tabular}{*{3}rr}
-		\toprule
-		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		%& $p$-value\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		1000 & 3 & $0.98$ & $1.00$\\
-		& 4 & $0.98$ & $0.96$\\
-		& 5 & $1.00$ & $0.94$\\
-		& 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-4} 
-		50000 & 3 & $0.97$ & $0.96$\\
-		%& $0.47856$\\
-		& 4 & $0.94$ & $0.95$\\
-		%& $0.47555$\\ 
-		& 5 & $0.97$ & $0.96$\\ 
-		%& $0.48512$\\ 
-		& 6 & $0.98$ & $0.99$\\ 
-		%& $0.48058$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-	\caption{New $100$ TRWNS and regions of confidence.}
-	\label{fig:RNG}
-\end{figure}
-
-We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
-
-\subsection{Test Power}
-
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
-Several studies in the literature have used this approach for identifying and characterizing randomness.
-
-Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
-Recall that the emblematic time was chosen as the most representative of the data set.
-We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
-
-%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
-At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
-
-Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
-We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
-Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
-The same holds for all $k>3/10$.
-
-\begin{figure}
-	\centering
-	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
-	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
-	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
-	\label{fig:correlation}
-\end{figure}
-
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
-
-In this section, we compare the performance of our test with that of 
-previous analyses that employ the Entropy-Complexity plane.
-To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
-Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
-
-\begin{table}
-	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
-	\label{Tab:LiteratureComparations}
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		MOT & 3 & 0.305 & NR\\
-		& 4 & 0.572 & NR\\ 
-		& 5 & 0.455 & NR\\ 
-		& 6 & 0.508 & NR\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 0.501 & NR\\
-		& 4 & 0.477 & NR\\ 
-		& 5 & 0.496 & NR\\ 
-		& 6 & 0.496 & NR\\ 
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.123 & NR\\
-		& 4 & 0.002 & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.531 & NR\\
-		& 4 & 0.515 & NR\\ 
-		\bottomrule
-	\end{tabular}
-	\begin{tabular}{|cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		LEH & 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.521 & NR\\
-		& 4 & 0.519 & NR\\ 
-		& 5 & 0.498 & NR\\ 
-		& 6 & 0.470 & NR\\
-		\cmidrule(lr){1-4}
-		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.482 & NR\\
-		& 4 & 0.520 & NR\\ 
-		& 5 & 0.513 & NR\\ 
-		& 6 & 0.508 & NR\\
-		\cmidrule(lr){1-4}
-		LCG & 3 & 0.009 & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
-
-It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
-In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
-
-\section{Conclusions}\label{Sec:Conclusions}
-
-We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
-Our proposal is based on two stages:
-(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
-(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
-We obtained the TWNRS with data from physical devices.
-
-Our test has a good size, mostly with long TWNRS.
-We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
-
-Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
-With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
-
-\section{Reproducibility and Replicability}\label{Sec:code}
-
-Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
-
-\section{Acknowledgements}\label{Sec:acknowledgements}
-
-This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
-
-\printendnotes
-
-\bibliography{References}
-
-\end{document}

### 2021-10-10 Reports/Journal - Confidence Regions/Chapters/Methodology.tex
update

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
-\documentclass[alpha-refs]{wiley-article}
-
-\usepackage[binary-units]{siunitx}
-\usepackage{bm,bbm}
-\usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{rotating}
-\graphicspath{{./Figures/}}
-\usepackage[linesnumbered,lined,boxed]{algorithm2e}
-\makeatletter
-\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
-\makeatother
-\usepackage{undertilde}
-\usepackage{todonotes}
-\usepackage{comment}
-
-\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
-\DeclareSIUnit{\alphapercent}{\alpha\%}
-
-\newcommand{\Mycite}[1]{%
- (\citeauthor{#1},~\citeyear{#1})}
-
-\papertype{Original Article}
-
-\title{A Test for White Noise in the Entropy-Complexity Plane}
-
-\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}
-
-\author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
-\author[4]{Osvaldo A.\ Rosso}
-\author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
-
-\contrib[]{All authors contributed equally.}
-
-% Include full affiliation details for all authors
-\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
-\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
-\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
-\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
-
-\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\corremail{eduarda.chagas@dcc.ufmg.br}
-
-\fundinginfo{CNPq, Fapeal}
-
-% Include the name of the author that should appear in the running header
-\runningauthor{Eduarda T.\ C.\ Chagas et al.}
-
-\begin{document}
-
-% \begin{frontmatter}
-\maketitle
-
-\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
-Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
-Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
-capturing the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
-\end{abstract}
-
-\section{Introduction}\label{Sec:Intro}
-
-Time Series carry valuable information about the system which produces the data.
-Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
-in the (natural) time and transformed domains (for instance, frequency and wavelet).
-In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
-Such an approach is non-parametric and based on descriptors of Information Theory.
-The time series is transformed into ordinal patterns, with which a histogram is formed.
-The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
-Thus, the approach can be applied to a variety of situations.
-
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
-We found works using this approach in several areas of scientific knowledge such as, for example:
-%
-distinguishing noise from chaos~\citep{rosso2007distinguishing};
-%
-the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
-%
-description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
-%
-the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
-%
-detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
-%
-analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
-%
-online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
-\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
-\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
-\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
-\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
-\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.
-
-With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
-There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
-Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
-In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.
-
-The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
-These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
-Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-two in the \textit{Journal of Time Series Analysis}, 
-and each of the remaining ten appeared in a different journal.
-Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
-It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
-The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
-
-Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
-\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
-\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
-\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
-\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
-
-With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
-Results in this direction can be found in the literature.
-\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
-\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
-
-Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
-In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
-We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
-Our contributions can be summarized as follows:
-\begin{itemize}
-	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
-	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series.
-\end{itemize}
-
-The rest of this paper is structured as follows. 
-Section~\ref{Sec:BP} introduces the elements of the study:
-Section~\ref{Sec:BPMethodology} details the methodology,
-Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
-and Section~\ref{Sec:BPApplications} discusses applications of this approach.
-%
-Section~\ref{Sec:BPMethodology} describes our methodology:
-Section~\ref{Sec:OverallFramework} gives the overall framework.
-Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
-Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
-Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
-%
-Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
-Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
-
-\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
-
-In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
-Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
-We then obtain a test statistic, using confidence regions, that can discriminate among times series.
-
-\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}
-
-Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
-As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
-\begin{quote}
-	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
-	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
-\end{quote}
-Also, as stressed by these authors, 
-\begin{quote}
-	``The corresponding symbol sequence must come 
-	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
-\end{quote}
-
-Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
-possible permutation of order $D$, and the symbol component vector 
-${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
-Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
-with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
-\begin{equation} 
-	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
-	\label{eq:time-delay}
-\end{equation} 
-for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
-Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
-This mapping should be defined in a way that preserves the desired relation between the elements 
-$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
-${\bm \pi}^{(D)}$. 
-The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
-\begin{enumerate}[label=\alph*)]
-	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
-	(\textit{Rank Permutation}) or,
-	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
-	(\textit{Chronological Index Permutation}).
-\end{enumerate}
-See details in the work by \citet{BPRepeatedValuesChaos}.
-Without loss of generality, in the following, we will use the latter.
-
-Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
-Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
-The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
-With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
-
-The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
-In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{IntroBP}
-	\caption{Illustration of the Bandt and Pompe coding}
-	\label{Fig:IntroBP}
-\end{figure}
-
-After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
-Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
-The next step into the characterization of the time series is computing descriptors from this histogram.
-
-The first descriptor is a measure of the disorder of the system.
-The most frequently used feature for this is the Normalized Shannon entropy, defined as
-\begin{equation}
-	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
-\end{equation}
-with the convention that terms in the summation for which $h(j)=0$ are null.
-This quantity is bounded in the unit interval. 
-It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
-
-Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
-In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
-To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from equilibrium or non-informative distribution, as the uniform probability distribution function $\bm u$.
-%They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
-It is calculated as:
-\begin{equation}
-	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
-	u(\ell) \log\frac{u(\ell)}{h(\ell)}
-	\Big).
-\end{equation}
-This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
-
-With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
-A time series can then be mapped into a point in the $H\times C$ plane.
-
-\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}
-
-The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
-The time delay is irrelevant, and we consider infinitely long series.
-
-Let us consider two extreme cases:
-\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
-	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
-	The entropy is zero, and the distance to the uniform distribution is maximal. 
-	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
-	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
-	The distance to the equilibrium distribution is zero. 
-	Thus, such series are mapped onto the point $(1,0)$.
-\end{enumerate}
-
-\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
-\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
-The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
-The upper boundary converges to a smooth curve when $D\to\infty$.
-
-Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
-The inset plot highlights the fine structure of the upper boundary inside the rectangle.
-The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
-	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
-\end{figure}
-
-We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
-\begin{itemize}
-	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
-	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
-\end{itemize}
-In all cases, we used $D=6$ and $\tau=1$.
-Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
-we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
-
-\begin{figure}[hbt]
-	\includegraphics[width=\linewidth]{Figures/h.pdf}
-	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:Histograms}
-\end{figure}
-
-Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
-The points due to $f^{-k}$ noises appear joined by dotted segments.
-It is noticeable that deterministic patterns have more complexity than random ones.
-Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{AllSystems}
-	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:AllSystems}
-\end{figure}
-
-Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{RightMostCorner}
-	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
-	\label{fig:RightMostCorner}
-\end{figure}
-
-Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
-Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
-
 \section{Proposed Method}\label{Sec:Proposal}
@@
 \end{algorithm}
-
-\section{Results}\label{Sec:Results}
-
-\subsection{Empirical confidence regions}
-
-Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
-of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
-for $D=3,4,5,6$ and $N=1000,50000$, .
-The points are presented counterclockwise, starting with the one with the largest complexity.
-
-\begin{comment}
-\begin{table}[hbt]
-\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
-\centering
-\begin{tabular}{rcllllllll}
-\toprule
-& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
-& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
-$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
-$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
-& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 1000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
-		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
-		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
-		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
-		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
-		\midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
-		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
-		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
-		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
-		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
-		\midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
-		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
-		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
-		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
-		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
-		\midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
-		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
-		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
-		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
-		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[hbt]
-	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
-	\centering
-	\begin{tabular}{rccccc}
-		\toprule
-		%& & \multicolumn{4}{c}{$N$}\\ 
-		%\cmidrule(lr){3-6}
-		& & \multicolumn{4}{c}{$N = 50000$}\\ 
-		\cmidrule(lr){3-6} 
-		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
-		\cmidrule(lr){3-3} 
-		\cmidrule(lr){4-4} 
-		\cmidrule(lr){5-5} 
-		\cmidrule(lr){6-6} 
-		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
-		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
-		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
-		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
-		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
-		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
-		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
-		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
-		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
-		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
-		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
-		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
-		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
-		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
-		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
-		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
-		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
-		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
-		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
-		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
-
-\begin{figure}[hbt]
-	\centering
-	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
-	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
-	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
-	\label{fig:HC-PCA}
-\end{figure}
-
-The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
-
-Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
-As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
-Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{PCA-hist-50k}
-	\caption{Histograms of the first principal component for $D=3,4,5,6$}
-	\label{fig:PCA-Hist}
-\end{figure}
-
-\subsection{Test Size}
-
-We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
-Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
-show the results.
-
-On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
-On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
-In contrast, we expected \SI{1}{\percent} of rejection.
-This might be because, in this case, the condition $D!\ll T$ is not respected.
-Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
-
-%
-%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
-%
-%For short series, $T = 1000$, and $D = 3$ 
-%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
-%
-%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
-%A reasonable explanation for this event is given in the choice of the parameter itself.
-%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
-
-\begin{table}[hbt]
-	\centering
-	\caption{Empirical sizes of the test}
-	\label{tab:result1}
-	\begin{tabular}{*{3}rr}
-		\toprule
-		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
-		%& $p$-value\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		1000 & 3 & $0.98$ & $1.00$\\
-		& 4 & $0.98$ & $0.96$\\
-		& 5 & $1.00$ & $0.94$\\
-		& 6 & $0.97$ & $0.87$\\
-		\cmidrule(lr){1-4} 
-		50000 & 3 & $0.97$ & $0.96$\\
-		%& $0.47856$\\
-		& 4 & $0.94$ & $0.95$\\
-		%& $0.47555$\\ 
-		& 5 & $0.97$ & $0.96$\\ 
-		%& $0.48512$\\ 
-		& 6 & $0.98$ & $0.99$\\ 
-		%& $0.48058$\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}[hbt]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
-	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
-	\caption{New $100$ TRWNS and regions of confidence.}
-	\label{fig:RNG}
-\end{figure}
-
-We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
-
-\subsection{Test Power}
-
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
-Several studies in the literature have used this approach for identifying and characterizing randomness.
-
-Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
-Recall that the emblematic time was chosen as the most representative of the data set.
-We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
-
-%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
-As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
-
-Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
-At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
-
-Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
-We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
-Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
-The same holds for all $k>3/10$.
-
-\begin{figure}
-	\centering
-	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
-	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
-		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
-	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
-	\label{fig:correlation}
-\end{figure}
-
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
-
-In this section, we compare the performance of our test with that of 
-previous analyses that employ the Entropy-Complexity plane.
-To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
-Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
-
-\begin{table}
-	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
-	\label{Tab:LiteratureComparations}
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		MOT & 3 & 0.305 & NR\\
-		& 4 & 0.572 & NR\\ 
-		& 5 & 0.455 & NR\\ 
-		& 6 & 0.508 & NR\\ 
-		\cmidrule(lr){1-4}
-		MWC & 3 & 0.501 & NR\\
-		& 4 & 0.477 & NR\\ 
-		& 5 & 0.496 & NR\\ 
-		& 6 & 0.496 & NR\\ 
-		\cmidrule(lr){1-4}
-		COM & 3 & 0.123 & NR\\
-		& 4 & 0.002 & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\cmidrule(lr){1-4}
-		LEH & 3 & 0.531 & NR\\
-		& 4 & 0.515 & NR\\ 
-		\bottomrule
-	\end{tabular}
-	\begin{tabular}{|cccc}
-		\toprule
-		Algorithm & 
-		\multicolumn{1}{c}{$D$} & 
-		$p$-value &
-		HC-PCA\\
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-2}
-		\cmidrule(lr){3-3}
-		\cmidrule(lr){4-4}
-		LEH & 5 & 0.495 & NR\\ 
-		& 6 & 0.501 & NR\\ 
-		\cmidrule(lr){1-4}
-		fGn & 3 & 0.521 & NR\\
-		& 4 & 0.519 & NR\\ 
-		& 5 & 0.498 & NR\\ 
-		& 6 & 0.470 & NR\\
-		\cmidrule(lr){1-4}
-		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		%\cmidrule(lr){1-4}
-		$f^{-k}$ & 3 & 0.482 & NR\\
-		& 4 & 0.520 & NR\\ 
-		& 5 & 0.513 & NR\\ 
-		& 6 & 0.508 & NR\\
-		\cmidrule(lr){1-4}
-		LCG & 3 & 0.009 & R\\ 
-		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
-
-It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
-In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
-
-\section{Conclusions}\label{Sec:Conclusions}
-
-We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
-Our proposal is based on two stages:
-(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
-(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
-We obtained the TWNRS with data from physical devices.
-
-Our test has a good size, mostly with long TWNRS.
-We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
-
-Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
-With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
-
-\section{Reproducibility and Replicability}\label{Sec:code}
-
-Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
-
-\section{Acknowledgements}\label{Sec:acknowledgements}
-
-This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
-
-\printendnotes
-
-\bibliography{References}
-
-\end{document}

### 2021-10-10 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
My address
update

@@
 \author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
+\author[5]{Alejandro C.\ Frery}
 

### 2021-10-10 Code/Alejandro/BoundariesPlot.R

@@ -1,0 +1,99 @@
+### The boundaries for D=3, 4, 5
+
+require(readr)
+require(ggplot2)
+require(ggthemes)
+require(cowplot)
+
+# Read the data
+
+continua_N6 <- read_table2("../../Data/trozos/continuaN6.txt")
+continua_N24 <- read_table2("../../Data/trozos/continuaN24.txt")
+continua_N120 <- read_table2("../../Data/trozos/continuaN120.txt")
+
+trozos_N6 <- read_table2("../../Data/trozos/trozosN6.txt")
+trozos_N24 <- read_table2("../../Data/trozos/trozosN24.txt")
+trozos_N120 <- read_table2("../../Data/trozos/trozosN120.txt")
+
+# Names
+names(continua_N6) <- names(continua_N24) <- names(continua_N120) <- c("HT", "CJT")
+names(trozos_N6) <- names(trozos_N24) <- names(trozos_N120) <- c("HT", "CJT")
+
+# Interpolated functions for the solid areas
+H <- seq(from=0, to=1, length.out = 1000)
+
+interpCminN6 <- approxfun(x=continua_N6$HT, y=continua_N6$CJT, n=length(continua_N6$HT)/4)
+vinterpCminN6 <- interpCminN6(H)
+interpCmaxN6 <- approxfun(x=trozos_N6$HT, y=trozos_N6$CJT, n=length(trozos_N6$HT)/4)
+vinterpCmaxN6 <- interpCmaxN6(H)
+
+interpCminN24 <- approxfun(x=continua_N24$HT, y=continua_N24$CJT, n=length(continua_N24$HT)/4)
+vinterpCminN24 <- interpCminN24(H)
+interpCmaxN24 <- approxfun(x=trozos_N24$HT, y=trozos_N24$CJT, n=length(trozos_N24$HT)/4)
+vinterpCmaxN24 <- interpCmaxN24(H)
+
+interpCminN120 <- approxfun(x=continua_N120$HT, y=continua_N120$CJT, n=length(continua_N120$HT)/4)
+vinterpCminN120 <- interpCminN120(H)
+interpCmaxN120 <- approxfun(x=trozos_N120$HT, y=trozos_N120$CJT, n=length(continua_N120$HT)/4)
+vinterpCmaxN120 <- interpCmaxN120(H)
+
+Interpolated <- data.frame(H, vinterpCminN6, vinterpCmaxN6,
[…]

### 2021-10-10 Code/Alejandro/ConfidenceRegion_p-value.R

@@ -1,0 +1,78 @@
+require(ggplot2)
+require(ggthemes)
+
+# Illustration of the confidence region
+set.seed(123456, kind="Mersenne-Twister")
+N <- 51
+a <- 0.47
+  
+u <- runif(N, min = -3, max = 3)
+v <- runif(N, min=-1, max=1)
+ru <- sort(u, index.return=TRUE)$ix
+rv <- sort(v, index.return=TRUE)$ix
+
+uv <- data.frame(u=u, v=v, ru=ru, rv=rv)
+
+
+# p-value of point X
+X <- data.frame(u=2, v=1)
+
+step1 <- ggplot(data=uv, aes(x=u, y=v)) +
+  geom_point(size=ifelse(u==median(u), 6.8, 6),
+             col=ifelse(u==median(u), "red", "seashell4")) +
+  geom_point(data=X, size=6, shape=13, col="maroon") +
+  xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
+  xlab(expression(italic(u))) +
+  ylab(expression(italic(v))) +
+  theme_clean(base_size = 30, base_family = "serif")
+
+# Confidence region at level a
+step2 <- ggplot(data=uv, aes(x=u, y=v)) +
+  geom_hline(yintercept = 0, col="gray") +
+  geom_vline(xintercept = 0, col="gray") +
+  geom_vline(xintercept = u[ru[round(N*a/2)]], linetype=2, col="red") +
+  geom_vline(xintercept = u[ru[round(N*(1-a/2))]], linetype=2, col="red") +
+  geom_point(size=ifelse(u==median(u), 6.8, 
+                         ifelse(u==u[ru[round(N*a/2)]], 6.8, 
+                                ifelse(u==u[ru[round(N*(1-a/2))]], 6.8, 6))),
+             col=ifelse(u==median(u), "red", 
+                        ifelse(u==u[ru[round(N*a/2)]], "green3", 
+                               ifelse(u==u[ru[round(N*(1-a/2))]], "green3", "seashell4")))) + 
+  geom_point(data=X, size=6, shape=13, col="maroon") +
+  geom_rug(sides = "b", 
+           col=ifelse(u==median(u), "red", "gray"),
+           size=ifelse(u==median(u), 1.2, 1)) +
+  xlim(-3.5, 3.5) + ylim(-1.5, 1.5)  +
+  xlab(expression(italic(u))) +
+  ylab(expression(italic(v))) +
[…]

### 2021-10-10 Code/Attack-Experiments.R

@@ -1,0 +1,99 @@
+################################################################################
+# Author: Eduarda Chagas
+# Date : Out 7, 2021
+# Contact: eduarda.chagas@dcc.ufmg.br
+################################################################################
+
+# Packages and sources ---------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+
+# Define attack ----------------------------------------------------------------
+set.seed(123)
+AttackElement <- function(e, d, p){
+  if(runif(1) <= p){
+    i = round(runif(1, max = d-1, min = 1), digits = 0)
+    e[i+1] = e[i] 
+  }
+  return(e)
+}
+
+AttackPattern <- function(elements_ts, d, tau, p) {
+  n_elements = dim(elements_ts)[1]
+  attacked_elements = matrix(nrow = n_elements, ncol = d)
+  for(i in 1:n_elements){
+    elements = formationPattern(elements_ts[i,], d, tau, 1)
+    attacked_elements[i,] = AttackElement(elements, d, p)
+  }
+  return(attacked_elements)
+}
+
+AttackTimeSeries <- function(time_series, d, tau, p) {
+  ts_attacked = time_series
+  n.series = length(time_series)
+  for(i in 1:(n.series-1)){
+    if(runif(1) <= p){
+      ts_attacked[i+1] = ts_attacked[i] 
+    }
+  }
+  return(ts_attacked)
+}
+
+bandt.pompe.by.elements <- function(elements, dimension, delay){
+  dyn.load("BandtPompe.so")
+  element.size = dim(elements)[1]
+  probability <- .Call("BandtPompe", elements, dimension, element.size)
+  return(probability)
+}
+
+
+#Global variables --------------------------------------------------------------
+D = 3
+tau = 1
+P = c(0.001, 0.005, 0.01, 0.015, 0.02, 0.025, 0.03) 
+
+h = rep(0, length(P) + 1)
+c = rep(0, length(P) + 1)
+
+ts = read.csv("../Data/Emblematic-serie-D3-N50000.csv")[,2]
+elements = formationPattern(ts, D, tau, 1)
[…]

### 2021-10-10 Code/Bandt-Pompe.R

@@ -1,0 +1,215 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 18, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+# Packages and sources ---------------------------------------------------------------------------------
+if(!require(gtools)){
+  install.packages("gtools")
+  require(gtools)
+} 
+
+# Auxiliar Function -------------------------------------------------------------------------------------
+
+define.symbols <- function(D){
+  d = c(1:D)
+  symbol = matrix(unlist(permutations(n = D, r = D, v = d)),nrow = factorial(D), ncol = D, byrow = FALSE)
+  symbol = symbol - 1
+  symbol
+}
+
+FP <- function(n, dimension, delay){
+  dyn.load("FormationPatterns.so")
+  p <- .Call("FormationPatterns", n, dimension, delay)
+  p = t(p) + 1
+  return(p)
+}
+
+percentual.equalities <- function(patterns){
+  n.patterns = dim(patterns)[1]
+  n.duplicated = 0
+  for(i in 1:n.patterns){
+    if(length(which(duplicated(patterns[i,]) == TRUE))){
+      n.duplicated = n.duplicated + 1
+      print(length(which(duplicated(patterns[i,]) == TRUE)))
+    }
+  }
+  return(n.duplicated/n.patterns)
+}
+
+formationPattern <- function(series, D, tau, option){
+  
+  i = 1
+  n = length(series)
+  p_patterns = elements = matrix(nrow = n, ncol = D)
+  index = c(0:(D-1))
+  
+  for(s in seq(1, length(series)-(D-1)*tau, by = 1)){
+    # the indices for the subsequence
+    ind = seq(s, s+(D-1)*tau, by = tau)
+    elements[i,] = series[ind]
+    p_patterns[i,] = index[order(elements[i,])]
+    i = i + 1
+  }
+  
+  if(option == 0){
+    p_patterns = na.omit(p_patterns)
+    return(p_patterns[1:(i-1),])
+  }else if(option == 1){
+    elements = na.omit(elements)
+    return(elements[1:(i-1),])    
+  }
+}
+
+# Bandt-Pompe function ---------------------------------------------------------------------------------
+
[…]

### 2021-10-10 Code/Confidence-regions-functions.R

@@ -1,0 +1,501 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 11, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+if(!require(sp)){
+  install.packages("sp")
+  require(sp)
+} 
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(doParallel)){
+  install.packages("doParallel")
+  require(doParallel)
+}
+
+# Analysis functions -----------------------------------------------------------------------------------
+
+k.fold.confidence.regions <- function(d = 3, N = 50000){
+  
+  if(N == 1000){
+    HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+    names(HC) = c("H", "C", "D")
+    HC$D = as.factor(HC$n)
+    HC.D = subset(HC, n==D)[,-3]
+    
+    filePath = read.table(paste0("../../Random_/Random_", 1, "k_D", D, "-T1.dat"), header=TRUE)
+    HC = matrix(data = filePath$x, nrow = 100, ncol = 3, byrow = TRUE, dimnames = NULL)
+    
+    HC = data.frame(H = HC[,1], 
+                    C = HC[,2], 
+                    D = factor(c(rep(D, 100))))
+  }else{
+    HC.1 = read.csv("../Data/HC/HC_50k.csv")[,2:4] #length = 8372
+    names(HC.1) = c("H", "C", "D")
+    HC.1$D = as.factor(HC.1$D)
+    HC.1.D = subset(HC.1, D==d)[,-3]
[…]

### 2021-10-10 Code/Correlation-Analysis.R

@@ -1,0 +1,166 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 20, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+source("Bandt-Pompe.R")
+source("Level-confidence-region.R")
+if(!require(fftw)) install.packages("fftw")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+if(!require(latex2exp)) install.packages("latex2exp")
+
+# Generator of noise with power spectrum f^-k --------------------------------------------------------
+set.seed(seed = 123, kind = "Mersenne-Twister")
+
+series.generator.fk <- function(pp, y, n, k){
+  Series = vector(mode="numeric")
+  filtro = (1:n)^-(k/2)
+  filtro = filtro / sum(filtro)
+  y1 = y * filtro    
+  x1 = IFFT(y1, plan = pp)  
+  Series = c(Re(x1)) 
+  return(Series)
+}
+
+# Correlation Structure Analysis function --------------------------------------------------------------
+correlation.analysis.point <- function(){
+  
+  rainbow_colors = palette(c("#fca311",#amarelo
+                             "#000000", #preto
+                             "#ff006e", #rosa
+                             "#40916c", #verde
+                             "#6a040f", #vermelho
+                             "#eb5e28", #laranja
+                             "#6a4c93", #roxo
+                             "#50514f", #cinza
+                             "#5e3023", #marrom
+                             "#3f88c5", #azul
+                             "#60d394"))
+  D = 6
+  N = 50000
+  k = c(0, 0.1, 0.2, 0.3)
+  
+  ts = read.csv("../Data/Emblematic-series-D6-N50000.csv")[,2]
+  probs.ts = bandt.pompe(ts, 6, 1)
[…]

### 2021-10-10 Code/Descriptive-points.R

@@ -1,0 +1,98 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 26, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+source("PCA-Histogram.R")
+source("Bandt-Pompe.R")
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+
+# Analysis with N = 1000 --------------------------------------------------------------------------------
+HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+names(HC) = c("H", "C", "D")
+HC$D = as.factor(HC$D)
+
+HC.1000 <- melt(data = HC, id.vars = c(1,2), variable.name = "D")
+
+cotas.sup = data.frame("c1x" = numeric(37814), "c1y" = numeric(37814), "D" = as.factor(c(rep(3, 8332), rep(4, 9582), rep(5, 9915), rep(6, 9985))))
+cotas.sup$c1x = c(readingMPR(3, 1), readingMPR(4, 1), readingMPR(5, 1), readingMPR(6, 1))
+cotas.sup$c1y = c(readingMPR(3, 2), readingMPR(4, 2), readingMPR(5, 2), readingMPR(6, 2))
+cotas.sup = melt(data = cotas.sup, id.vars = c(1,2), variable.name = "D")
+
+cotas.inf = data.frame("c2x" = numeric(147122), "c2y" = numeric(147122), "D" = as.factor(c(rep(3, 14499), rep(4, 27753), rep(5, 43641), rep(6, 61229))))
+cotas.inf$c2x = c(readingMPR(3, 3), readingMPR(4, 3), readingMPR(5, 3), readingMPR(6, 3))
[…]

### 2021-10-10 Code/Emblematic-Point-Search.R

@@ -1,0 +1,59 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 19 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+
+filenames <- list.files(path = "../Data/random.org/")
+
+## Get names without ".DAT" and store in "names"
+names <- substr(filenames, 1, 10)
+
+index <- c(1:length(names))
+j <- 0
+dados <- vector()
+
+##Loading data from files
+for(i in names){
+  j <- j + 1
+  filepath <- file.path(paste("../Data/random.org/", i,".bin",sep=""))
+  assign("Data", readBin(filepath, n = 1e8, size = "4", what ='integer'))
+  dados <- c(dados, Data)
+}
+
+dados <- readBin('../Data/random.org/random_50k.bin',n=1e8,size="4",what ='integer')
+dados <- abs(dados/max(dados))
+write.csv(dados[1:50000], file = "../Data/random_sample.csv")
+
+source("bandt_pompe/bandt_pompe.R")
+source("bandt_pompe/measures.R")
+source("bandt_pompe/features.R")
+source("bandt_pompe/visibility.R")
+source("bandt_pompe/helpers.R")
+
+random_50k <- readBin('../Data/random.org/random_50k.bin',n=1e8,size="4",what ='integer')
+seq_50k <- abs(random_50k/max(random_50k))
+split_seq <- as.matrix(split(seq_50k, ceiling(seq_along(seq_50k)/50000)))
+ts = matrix(nrow = 50000, ncol = 104)
+
+for(i in 1:104){
+  ts[,i] = split_seq[[i]]
+}
+
+for(i in 1:104){
+  probs = bandt.pompe(ts[,i], 3, 1)
+  h = shannon.entropy.normalized(probs)
+  c = Ccomplexity(probs)
+  cat("i: ", i, " H: ", round(h, 9), " C: ", round(c, 9), "\n")
+  
+  if(round(h, 6) == round(0.999985292278035, 6) && round(c, 6) == round(0.0000145144384709536, 6))
+    print(i)
+}
+
+#H = 0.999985292278035
+#C = 1.45144384709536e-05
+
+write.csv(ts[,10], "../Data/Emblematic-serie-D3-N50000.csv")

### 2021-10-10 Code/Emblematic-point-analysis.R

@@ -1,0 +1,66 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 19, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Bandt-Pompe.R")
+
+# HC calculation function ------------------------------------------------------------------------------
+hc.series <- function(ts, D, tau){
+  
+  i = 0
+  h.values = c()
+  c.values = c()
+  match.median = FALSE
+  
+  for(i in 1:length(ts)){
+    i = i + 1
+    cat("Test: ", i, "\n")
+    
+    probs = bandt.pompe(ts[,i], D, tau)
+    h = shannon.entropy.normalized(probs)
+    c = Ccomplexity(probs)
+    
+    h.values = c(h.values, h)
+    c.values = c(c.values, c)
+    cat("H: ", h, " C: ", c, "\n")
+    HC.values = data.frame(H = h.values, C = c.values)
+    write.csv(HC.values, "../Data/HC-D3-N1000.csv")
+  }
+}
+
+# Median search function --------------------------------------------------------------------------------
+emblematic.series <- function(D, tau, N, dx = 4, dy = 4){
+  
+  i = 0
+  match.median = FALSE
+  HC = read.csv("../Data/HC-D3-N1000.csv")[2:3]
+  
+  while(i < dim(HC)[1]){
+    i = i + 1
+    index = i
+    
+    h = round(HC$H[i], digits = dx)
+    c = round(HC$C[i], digits = dy)
+    
+    cat("i: ", i , " h: ", h, " c: ", c, "\n")
+    
+    hc.points = read.csv(paste0("../Data/Regions-HC/regions-hc-D", D, "-N", N, ".csv"))[2:4]
+    ax = round(hc.points$H[17], digits = dx)
+    ay = round(hc.points$C[17], digits = dy)
+    
+    if(!is.na(h) && !is.na(c)){
+      if(h == ax && c == ay){
+        match.median = TRUE
+        break
+      }
+    }
+  }
+  
+  if(match.median)
+    return(index)
+  else
+    return(-1)
+}

### 2021-10-10 Code/HC-PCA.R

@@ -1,0 +1,103 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 11, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+source("PCA-Histogram.R")
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+
+# Hypotheses that I DID NOT USE  -----------------------------------------------------------------------
+### 1) Each confidence region must include the median (in the HxC plane) DUHHH!!!
+### 2) The shape of the confidence regions must be a simple parametric form well-suited to the shape of the points
+### 3) It is easier to make the analysis in the PCA plane, and then "translate" it to the HxC plane
+### 4) The shape of the density looks symmetric w.r.t. the first PC, i.e., it would suffice to find a shape of the form
+###    d(| PC1 |, PC2)
+
+# Analysis with N = 1000 --------------------------------------------------------------------------------
+
+HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+names(HC) = c("H", "C", "n")
+HC$n = as.factor(HC$n)
+
+HC.3 = subset(HC, n==3)[,-3]
+save.confidence.regions(HC.3, D = 3, N = 1000)
+HC.4 = subset(HC, n==4)[,-3]
+save.confidence.regions(HC.4, D = 4, N = 1000)
+HC.5 = subset(HC, n==5)[,-3]
[…]

### 2021-10-10 Code/HCPlanePlots.R

@@ -1,0 +1,337 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Nov 22, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+require(ggplot2)
+require(ggthemes)
+require(ggpubr)
+require(reshape2)
+require(ggrepel)
+require(grid)
+require(gridExtra)
+require(fftw)
+if(!require(gtools)){
+  install.packages("gtools")
+  require(gtools)
+} 
+source("Bandt-Pompe.R")
+
+
+# Paleta montada a partir de https://coolors.co/ -------------------------------------------------------
+rainbow_colors <- palette(c("#494947", #DarkGreen
+                            "#FB4D3D", #BrightRed
+                            "#B14AED", #Violet
+                            "#44CCFF", #BrightLightBlue
+                            "#35FF69", #BrightGreen
+                            "#ED8438", #Orange
+                            "#c41676", #Pink
+                            "#06470d", #verde escuro
+                            "#BF6F00", #DarkYellow
+                            "#7494EA", #MutedDarkBlue
+                            "#495867") #DarkGray
+)
+
+#Função geradora da série f^⁻k--------------------------------------------------------------------------
+series_generator_fk <- function(pp, y, n, k){
+  Series <- vector(mode="numeric")
+  filtro <- (1:n)^-(k/2)
+  filtro <- filtro / sum(filtro)
+  y1 <- y * filtro    
+  x1 <- IFFT(y1, plan=pp)  
+  Series <- c(Re(x1)) 
+  Series
+}
+
+#Função geradora do mapa logístico----------------------------------------------------------------------
+series_generator_map <- function(r, x_0, n){
+  Series <- vector(mode="numeric",length = n)
+  Series[1] <- x_0
+  for(i in c(2:n)){
+    Series[i] <- r*Series[i-1]*(1 - Series[i-1])
+  }
+  Series
+}
+
[…]

### 2021-10-10 Code/Histogram-Analysis.R

@@ -1,0 +1,159 @@
+source("Bandt-Pompe.R")
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(fftw)){
+  install.packages("fftw")
+  require(fftw)
+}
+if(!require(grid)){
+  install.packages("grid")
+  require(grid)
+}
+
+rainbow_colors <- palette(c("#494947", #DarkGreen
+                            "#FB4D3D", #BrightRed
+                            "#B14AED", #Violet
+                            "#44CCFF", #BrightLightBlue
+                            "#35FF69", #BrightGreen
+                            "#ED8438", #Orange
+                            "#c41676", #Pink
+                            "#06470d", #verde escuro
+                            "#BF6F00") #DarkYellow
+                            #"#7494EA", #MutedDarkBlue
+                            #"#495867") #DarkGray
+)
+
+series.generator.fk <- function(pp, y, n, k){
+  Series <- vector(mode="numeric")
+  filtro <- (1:n)^-(k/2)
+  filtro <- filtro / sum(filtro)
+  y1 <- y * filtro    
+  x1 <- IFFT(y1, plan=pp)  
+  Series <- c(Re(x1)) 
+  Series
+}
+
+series.generator.map <- function(r, x_0, n){
+  Series <- vector(mode="numeric",length = n)
+  Series[1] <- x_0
+  for(i in c(2:n)){
+    Series[i] <- r*Series[i-1]*(1 - Series[i-1])
+  }
+  Series
+}
+
+calculate.histogram <- function(ts, d, t, name.title, color_plot){
+  fat = factorial(d)
+  symbol = define.symbols(d)
+  p.patterns = formationPattern(ts, d, t, 0)
+  n.symbols = dim(p.patterns)[1]
+  index.rep = array(0, n.symbols)
+  
+  for(i in 1:n.symbols){
+    for(j in 1:fat){
+      if(all(p.patterns[i,] == symbol[j, ])){
+        index.rep[i]=j
+        break
+      }
+    }
+  }
+  index.rep = data.frame(i = index.rep)
+  p = ggplot(index.rep) +
+    geom_histogram(aes(x = i, y = ..density..),
[…]

### 2021-10-10 Code/PCA-Histogram.R

@@ -1,0 +1,108 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 16, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+
+# Analysis functions -----------------------------------------------------------------------------------
+
+pca.histogram <- function(){
+  
+  HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+  names(HC) = c("H", "C", "n")
+  HC$n = as.factor(HC$n)
+  
+  HC.3 = subset(HC, n==3)[,-3]
+  pca_HC.3 = prcomp(x = HC.3[,-3], 
+                    retx = TRUE, 
+                    center=TRUE, scale. = TRUE)
+  
+  HC.4 = subset(HC, n==4)[,-3]
+  pca_HC.4 = prcomp(x = HC.4[,-3], 
+                    retx = TRUE, 
+                    center=TRUE, scale. = TRUE)
+  
+  HC.5 = subset(HC, n==5)[,-3]
+  pca_HC.5 = prcomp(x = HC.5[,-3], 
+                    retx = TRUE, 
+                    center=TRUE, scale. = TRUE)
+  
+  HC.6 = subset(HC, n==6)[,-3]
+  pca_HC.6 = prcomp(x = HC.6[,-3], 
+                    retx = TRUE, 
+                    center=TRUE, scale. = TRUE)
+  
+  PC = data.frame(PC1 = c(pca_HC.3$x[,1], pca_HC.4$x[,1], pca_HC.5$x[,1], pca_HC.6$x[,1]),
+                  PC2 = c(pca_HC.3$x[,2], pca_HC.4$x[,2], pca_HC.5$x[,2], pca_HC.6$x[,2]), 
[…]

### 2021-10-10 Code/RNG-Analysis.R

@@ -1,0 +1,146 @@
+  ########################################################################################################
+  # Author: Eduarda Chagas
+  # Date : Jun 30, 2020
+  # Contact: eduarda.chagas@dcc.ufmg.br
+  ########################################################################################################
+  
+  # Packages and sources ---------------------------------------------------------------------------------
+  source("Test-point.R")
+  if(!require(ggpubr)){
+    install.packages("ggpubr")
+    require(ggpubr)
+  }
+  if(!require(ggplot2)){
+    install.packages("ggplot2")
+    require(ggplot2)
+  }
+  if(!require(ggthemes)){
+    install.packages("ggthemes")
+    require(ggthemes)
+  }
+  if(!require(reshape2)){
+    install.packages("reshape2")
+    require(reshape2)
+  }
+  if(!require(latex2exp)){
+    install.packages("latex2exp")
+    require(latex2exp)
+  }
+  
+  # Analysis functions -----------------------------------------------------------------------------------
+  RNG.HC.confidence.regions <- function(D = 3, N = 1000, horizontal = 1){
+    
+    if(N == 1000){
+      if(D == 3)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/5z1f01nu449d44m/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 4)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/vquh76d4kaqoxcm/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 5)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/37tygdzigybzu7u/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 6)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/0ez7bq8zn98phqg/Random_", 1, "k_D", D, "-T1.dat?dl=1")))
+    }else{
+      if(D == 3)
+        filePath <- read.table(url(paste0("https://www.dropbox.com/s/9enu26i3sdd77a4/Random_", 50, "k_D", D, "-T1.dat?dl=1")))
+      if(D == 4)
[…]

### 2021-10-10 Code/Test-point.R

@@ -1,0 +1,55 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 12, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+
+# Analysis functions -----------------------------------------------------------------------------------
+test.point <- function(H, C, D, N, region){
+  
+  points = points.confidence.regions(region, D, N)
+  test = point.in.polygon(H, C, points$H, points$C)
+  
+  if(test == 0){
+    result = FALSE
+    #cat("This point does not belong to the region \n")
+  }
+  else{
+    result = TRUE
+    #cat("This point is within the confidence region \n")
+  }
+  
+  return(result)
+}
+
+test.set.point <- function(HC, D, N, region){
+  
+  points = points.confidence.regions(region, D, N)
+  test = rep(FALSE, dim(HC)[1])
+  
+  for(i in 1:dim(HC)[1]){
+    test[i] = point.in.polygon(HC$H[i], HC$C[i], points$H, points$C)
+  }
+  
+  if(length(test[test == 1]) != 0)
+    cat("Points inside the regions of", region, "%: ", (length(test[test == 1])/length(test))*100, '%\n')
+  
+  return(test)
+}
+
+p.value.set.point <- function(HC, D, N, region){
+  
+  points = points.confidence.regions(region, D, N)
+  test = rep(FALSE, dim(HC)[1])
+  
+  for(i in 1:dim(HC)[1]){
+    test[i] = point.in.polygon(HC$H[i], HC$C[i], points$H, points$C)
+  }
+  
+  return((length(test[test == 1])/length(test)))
+}
+
+#test.point(H = 0.9998, C = 0.0001, D = 3, N = 1000, region = 90)

### 2021-10-10 Code/Trozos-HC-PCA.R

@@ -1,0 +1,179 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 30, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Confidence-regions-functions.R")
+source("Bandt-Pompe.R")
+if(!require(ggpubr)){
+  install.packages("ggpubr")
+  require(ggpubr)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(latex2exp)){
+  install.packages("latex2exp")
+  require(latex2exp)
+}
+
+plot.HC.PCA.trozos <- function(N, dim, lengend ,x.lim = NULL, y.lim = NULL){
+  if(N == 1000){
+    HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+  }else if(N == 50000){
+    HC = read.csv("../Data/Regions-HC/HC_50k.csv")[,2:4]
+  }
+  
+  names(HC) <- c("H", "C", "D")
+  HC$D <- as.factor(HC$D)
+  HC.D <- subset(HC, D == dim)[,-3]
+  HC.D <- HC.D[,-3]
+  PCA.HC.D <- prcomp(x = HC.D[,-3], 
+                     retx = TRUE, 
+                     center = TRUE, 
+                     scale. = TRUE)
+  
+  # Trozos data ----------------------------
+  cotas.sup <- cotas(dim, 0)
+  cotas.sup <- data.frame("H" = cotas.sup$cx, 'C' = cotas.sup$cy)
+  cotas.inf <- cotas(dim, 1)
+  cotas.inf <- data.frame("H" = cotas.inf$cx, 'C' = cotas.inf$cy)
+  
+  index.i = which(cotas.sup$H >= min(HC.D$H) & cotas.sup$H <= 1)
+  sup = cotas.sup[index.i,]
[…]

### 2021-10-10 Code/Trozos-HC-Regions.R

@@ -1,0 +1,57 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jul 5, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+
+D = 3
+N = 1000
+
+hc.points = read.csv(paste0("../Data/Regions-HC/regions-hc-D", D, "-N", N, ".csv"))[2:4]
+rect90 = data.frame(H = hc.points$H[1:4], C = hc.points$C[1:4])
+rect95 = data.frame(H = hc.points$H[5:8], C = hc.points$C[5:8])
+rect99 = data.frame(H = hc.points$H[9:12], C = hc.points$C[9:12])
+rect999 = data.frame(H = hc.points$H[13:16], C = hc.points$C[13:16])
+
+cotas.sup = cotas(D, 0)
+cotas.sup = data.frame("H" = cotas.sup$cx, 'C' = cotas.sup$cy)
+cotas.inf = cotas(D, 1)
+cotas.inf = data.frame("H" = cotas.inf$cx, 'C' = cotas.inf$cy)
+
+index.i = which(cotas.sup$H >= min(hc.points$H) & cotas.sup$H <= 1)
+sup = cotas.sup[index.i,]
+sup = data.frame(H = sup$H, C = predict(lm(data = sup, formula = C ~ poly(H, 3))))
+cotas.sup = data.frame(H = c(cotas.sup[-index.i,]$H, sup$H), 
+                       C = c(cotas.sup[-index.i,]$C, sup$C))
+
+index.j = which(cotas.inf$H >= min(hc.points$H) & cotas.inf$H <= 1)
+inf = cotas.inf[index.i,]
+inf = data.frame(H = inf$H, C = predict(lm(data = inf, formula = C ~ poly(H, 3))))
+cotas.inf = data.frame(H = c(cotas.inf[-index.i,]$H, inf$H), 
+                       C = c(cotas.inf[-index.i,]$C, inf$C))
+
+ggplot(hc.points, aes(x = H, y = C)) +
[…]

### 2021-10-10 Code/fbm-fgn-Analysis.R

@@ -1,0 +1,164 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jun 22, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(doParallel)){
+  install.packages("doParallel")
+  require(doParallel)
+}
+
+# Analysis functions -----------------------------------------------------------------------------------
+
+calculate.p.value.samples <- function(samples, N, D){
+  if(N == 1000){
+    HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+  }else if(N == 50000){
+    HC = read.csv("../Data/HC/HC_50k.csv")[,2:4]
+  }
+  names(HC) = c("H", "C", "n")
+  HC$n = as.factor(HC$n)
+  
+  HC.D = subset(HC, n == D)[,-3]
+  pca_HC = prcomp(x = HC.D[,-3], retx = TRUE, 
+                  center=TRUE, scale. = TRUE)
+  PC = data.frame(PC1 = pca_HC$x[,1], PC2 = pca_HC$x[,2])
+  
+  p.values = rep(0, dim(samples)[1])
+  
+  
+  attach(PC)
+  for(i in 1:dim(samples)[1]){
+    print(i)
+    
+    test = TRUE
+    step.loop = 0
+    region.test = 1.001
+    while(test){
+      step.loop = step.loop + 0.001
+      region.test = region.test - 0.001
+      
+      (qpc1 = quantile(PC1, probs = c((step.loop/2), 0.5, 1 - (step.loop/2))))
+      (x.pc.1 = PC1[which(min(abs(PC1- qpc1[1])) == abs(PC1- qpc1[1]))])
+      (x.pc.2 = PC1[which(min(abs(PC1- qpc1[3])) == abs(PC1- qpc1[3]))])
+      (y.pc.1 = min(PC2[PC1 > x.pc.1[1] & PC1 < x.pc.2[1]]))
+      (y.pc.2 = max(PC2[PC1 > x.pc.1[1] & PC1 < x.pc.2[1]]))
+      
+      rect = data.frame(xmin = x.pc.1, xmax = x.pc.2, ymin = y.pc.1, ymax = y.pc.2)
[…]

### 2021-10-10 Code/fbm-fgn-generator.py

@@ -1,0 +1,24 @@
+from fbm import fbm, fgn
+import numpy as np
+import csv
+
+n_series = 100
+n_size = 50000
+
+fbm_matrix = []
+fgn_matrix = []
+
+for i in range(n_series):
+	fbm_sample = fbm(n = n_size, hurst = 0.1, length=1, method = 'daviesharte')
+	fgn_sample = fgn(n = n_size, hurst = 0.5, length=1, method = 'daviesharte')
+	fbm_matrix.append(fbm_sample) 
+	fgn_matrix.append(fgn_sample) 
+	print(i)
+
+with open("../Data/fBm.csv","w+") as my_csv:
+    csvWriter = csv.writer(my_csv, delimiter=',')
+    csvWriter.writerows(fbm_matrix)
+
+with open("../Data/fGn.csv","w+") as my_csv:
+    csvWriter = csv.writer(my_csv, delimiter=',')
+    csvWriter.writerows(fgn_matrix)

### 2021-10-10 Code/fk-Analysis.R

@@ -1,0 +1,173 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Jul 17 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(fftw)){
+  install.packages("fftw")
+  require(fftw)
+}
+if(!require(reshape2)){
+  install.packages("reshape2")
+  require(reshape2)
+}
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+if(!require(doParallel)){
+  install.packages("doParallel")
+  require(doParallel)
+}
+
+# Analysis functions -----------------------------------------------------------------------------------
+calculate.p.value.samples <- function(samples, N, D){
+  if(N == 1000){
+    HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+  }else if(N == 50000){
+    HC = read.csv("../Data/HC/HC_50k.csv")[,2:4]
+  }
+  names(HC) = c("H", "C", "n")
+  HC$n = as.factor(HC$n)
+  
+  HC.D = subset(HC, n == D)[,-3]
+  pca_HC = prcomp(x = HC.D[,-3], retx = TRUE, 
+                  center=TRUE, scale. = TRUE)
+  PC = data.frame(PC1 = pca_HC$x[,1], PC2 = pca_HC$x[,2])
+  
+  p.values = rep(0, dim(samples)[1])
+  
+  
+  attach(PC)
+  for(i in 1:dim(samples)[1]){
+    print(i)
+    
+    test = TRUE
+    step.loop = 0
+    region.test = 1.001
+    while(test){
+      step.loop = step.loop + 0.001
+      region.test = region.test - 0.001
+      
+      (qpc1 = quantile(PC1, probs = c((step.loop/2), 0.5, 1 - (step.loop/2))))
[…]

### 2021-10-10 Code/methodology.R

@@ -1,0 +1,162 @@
+source("Bandt-Pompe.R")
+if(!require(latex2exp)){
+  install.packages("latex2exp")
+  require(latex2exp)
+}
+if(!require(ggrepel)){
+  install.packages("ggrepel")
+  require(ggrepel)
+}
+if(!require(ggplot2)){
+  install.packages("ggplot2")
+  require(ggplot2)
+}
+if(!require(ggthemes)){
+  install.packages("ggthemes")
+  require(ggthemes)
+}
+#library(directlabels)
+#if(!require(plot3D)){
+#  install.packages("plot3D")
+#  require(plot3D)
+#} 
+
+
+D = 6
+N = 50000
+HC = read.csv("../Data/Regions-HC/HC-VALIDATION-D6-N50000.csv")[,2:4]
+index = which(HC$D == D)
+HC = HC[index[1:15], ]
+
+cotas.sup = cotas(D, 0)
+cotas.sup = data.frame("H" = cotas.sup$cx, 'C' = cotas.sup$cy)
+cotas.inf = cotas(D, 1)
+cotas.inf = data.frame("H" = cotas.inf$cx, 'C' = cotas.inf$cy)
+
+index.i = which(cotas.sup$H >= 0.9985 & cotas.sup$H <= 1)
+sup = cotas.sup[index.i,]
+sup = data.frame(H = sup$H, C = predict(lm(data = sup, formula = C ~ poly(H, 3))))
+cotas.sup = data.frame(H = c(cotas.sup[-index.i,]$H, sup$H), 
+                       C = c(cotas.sup[-index.i,]$C, sup$C))
+
+index.j = which(cotas.inf$H >= 0.9985 & cotas.inf$H <= 1)
+inf = cotas.inf[index.i,]
+inf = data.frame(H = inf$H, C = predict(lm(data = inf, formula = C ~ poly(H, 3))))
+cotas.inf = data.frame(H = c(cotas.inf[-index.i,]$H, inf$H), 
+                       C = c(cotas.inf[-index.i,]$C, inf$C))
+
+step1 <- ggplot(HC, aes(x = H, y = C)) + geom_point(size=4) +
+  geom_line(data = cotas.sup, aes(x = H, y = C), color="gray") +
+  geom_line(data = cotas.inf, aes(x = H, y = C), color="gray") + 
+  xlim(limits = c(0.9985, 1)) + 
+  ylim(limits = c(0, 0.004)) + 
[…]

### 2021-10-10 Code/mixture-caos.R

@@ -1,0 +1,66 @@
+################################################################################
+# Author: Eduarda Chagas
+# Date : Out 9, 2021
+# Contact: eduarda.chagas@dcc.ufmg.br
+################################################################################
+
+# Packages and sources ---------------------------------------------------------
+source("Bandt-Pompe.R")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+
+series.generator.map <- function(r){
+  index = 1
+  time_series = vector(mode = "numeric", length = 50000)
+  
+  time_series[index] <- 0.1
+  for(i in 2:(10000 + 50000)){
+    time_series[index] = r * time_series[index] * (1 - time_series[index])
+    if(i > 10001){
+      index = index + 1
+      time_series[index] = r * time_series[index-1] * (1 - time_series[index-1])
+    }
+  }
+  return(time_series)
+}
+
+r = 3.56995
+D = 3
+tau = 1
+
+ts = read.csv("../Data/Emblematic-serie-D3-N50000.csv")[,2]
+logistic_map = series.generator.map(r)
+
+P = seq(from = 0.999, to = 1, length.out = 10)
+n_p = length(P)
+h = rep(0, n_p)
+c = rep(0, n_p)
+
+for(i in 1:n_p){
+  ts_mixture = (P[i] * ts) + ((1 - P[i]) * logistic_map)
+  probs_mixture = bandt.pompe(ts_mixture, D, tau)
+  h[i] = round(shannon.entropy.normalized(probs_mixture), 10)
+  c[i] = round(Ccomplexity(probs_mixture), 10)
+}
+
+hc_df = data.frame(H = h, C = c, P = P)
+legend.names = as.character(P)
+
+cotas.sup = data.frame("c1x" = readingMPR(D, 1), "c1y" = readingMPR(D, 2))
+cotas.inf = data.frame("c2x" = readingMPR(D, 3), "c2y" = readingMPR(D, 4))
+
+p = ggplot(data = hc_df, aes(x = H, y = C)) +
+  geom_line(data = cotas.sup, aes(x = c1x, y = c1y), color="gray") +
+  geom_line(data = cotas.inf, aes(x = c2x, y = c2y), color="gray") + 
[…]

### 2021-10-10 Code/p-value-test.R

@@ -1,0 +1,182 @@
+########################################################################################################
+# Author: Eduarda Chagas
+# Date : Sep 15, 2020
+# Contact: eduarda.chagas@dcc.ufmg.br
+########################################################################################################
+
+# Packages and sources ---------------------------------------------------------------------------------
+source("Test-point.R")
+if(!require(plot3D)){
+  install.packages("plot3D")
+  require(plot3D)
+}
+if(!require(doParallel)){
+  install.packages("doParallel")
+  require(doParallel)
+}
+
+# Analysis functions -----------------------------------------------------------------------------------
+calculate.p.value.samples <- function(samples, N, D){
+  if(N == 1000){
+    HC = read.csv("../Data/HC/HC_1000.csv")[,2:4]
+  }else if(N == 50000){
+    HC = read.csv("../Data/HC/HC_50k.csv")[,2:4]
+  }
+  names(HC) = c("H", "C", "n")
+  HC$n = as.factor(HC$n)
+  
+  HC.D = subset(HC, n == D)[,-3]
+  pca_HC = prcomp(x = HC.D[,-3], retx = TRUE, 
+                  center=TRUE, scale. = TRUE)
+  PC = data.frame(PC1 = pca_HC$x[,1], PC2 = pca_HC$x[,2])
+  
+  p.values = rep(0, dim(samples)[1])
+  
+  attach(PC)
+  for(i in 1:dim(samples)[1]){
+    #print(i)
+    test = TRUE
+    step.loop = 0
+    region.test = 1.001
+    while(test){
+      step.loop = step.loop + 0.001
+      region.test = region.test - 0.001
+      
+      (qpc1 = quantile(PC1, probs = c((step.loop/2), 0.5, 1 - (step.loop/2))))
+      (x.pc.1 = PC1[which(min(abs(PC1- qpc1[1])) == abs(PC1- qpc1[1]))])
+      (x.pc.2 = PC1[which(min(abs(PC1- qpc1[3])) == abs(PC1- qpc1[3]))])
+      (y.pc.1 = min(PC2[PC1 > x.pc.1[1] & PC1 < x.pc.2[1]]))
+      (y.pc.2 = max(PC2[PC1 > x.pc.1[1] & PC1 < x.pc.2[1]]))
[…]

### 2021-10-10 Code/rand-borland.cpp

@@ -1,0 +1,48 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <fstream>
+#include <iostream>
+#include <vector>
+using namespace std;
+
+unsigned int myseed = 0x015A4E36;
+const int N = 500001;
+
+int myrand(void)
+{
+  unsigned int t = myseed * 0x015A4E35 + 1;
+  myseed = t;
+  return (int)(t >> 16) & 0x7FFF;
+}
+
+void mysrand(unsigned int seed)
+{
+  myseed = seed;
+  myrand();
+}
+
+int main(void)
+{
+  unsigned t = time(NULL);
+  unsigned int i = 0;
+  vector<int> rng(N, 1);
+  
+  std::ofstream outfile;
+
+  //srand(t);
+  //mysrand(t);
+  
+  std::ofstream myfile;
+  myfile.open("../Data/PRNG/borland-50k.csv");
+  for(i = 0; i < N; i++){
+      rng.at(i) = myrand(); 
+      cout << i+1 << ": " << rng.at(i) << '\n';
+      myfile << rng.at(i) << '\n';  	
+      
+  }
+
+  // Close the file
+  myfile.close();
+  return 0;
+}

### 2021-10-15 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
Atualizando

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
 This quantity is also called ``disequilibrium.''
-The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
+The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$, and we chose to work with the uniform probability distribution function as the equilibrium law.
+\textcolor{red}{[Eduarda:] alguma referência (dentre as que já citamos) e algumas propriedades?}
 

### 2021-10-15 Reports/Journal - Confidence Regions/ResearchProposal.tex
update
Atualizando

@@
 \big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{dB}(\alpha,\beta,1, D!)$?
-\item[] But we go back to a quantity, rather than to a random variable.
 \item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{dB}(\alpha,\beta,1, D!)$ model.
@@
 (\widehat\alpha-1)\psi(\widehat\alpha) -(\widehat\beta-1) \psi(\widehat\beta) +(\widehat\alpha+\widehat\beta-2) \psi(\widehat\alpha+\widehat\beta),
+\label{eq:Hhat}
 \end{equation}
 which is a transformation of a bivariate Gaussian distribution.
+
+\textcolor{red}{Magdalena: el estimador de máxima verosimilitud de una transformación del parámetro, es la transformación del estimador de máxima verosimilitud $\widehat{\Psi(\theta)}=\Psi(\widehat\theta)$?}
+
+\textcolor{red}{¿Cuál es la distribución conjuta asintótica de $(\widehat\alpha,\widehat\beta$)? Sabemos que la media es $(\alpha,\beta)$, pero ¿cuál es la matriz de covarianza?}
+
+\textcolor{red}{Cuando la tengamos, ¿podemos resolver~\eqref{eq:Hhat}? Seguro que no. ¿Podemos aproximar la distribución?}
 

### 2021-10-17 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
R1 recuperada e em edição

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions.tex
@@
 \usepackage{undertilde}
+
 \usepackage{todonotes}
@@
 \author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
+\author[2,3]{Marcelo Queiroz-Oliveira}
 \author[4]{Osvaldo A.\ Rosso}
 \author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
+\author[2]{\mbox{Cristopher G.\ S. Freitas}}
+\author[5]{Alejandro C.\ Frery}
 
@@
 \begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
+The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series. 
+It consists of computing
+Information Theory descriptors of the histogram of ordinal patterns. 
 Such descriptors lie in a 2D manifold: the Entropy-Complexity plane. 
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
+This article provides the first proposal
+of a test in the Entropy-Complexity plane for the
+white noise hypothesis.
 Our test is based on true white noise sequences obtained from physical devices.

### 2021-10-17 Reports/Journal - Confidence Regions/Chapters/Background.tex
R1 recuperada e em edição

@@
 This quantity is bounded in the unit interval. 
-It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).
+It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability function).
 
@@
 To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
-They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.
+They employed the Euclidean distance between $\bm h$ and the uniform probability function.
+
+The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as a more adequate measure of such a distance:
+\begin{equation}
+	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
+	u(\ell) \log\frac{u(\ell)}{h(\ell)}
+	\Big).
+	\label{eq:JensenShannon}
+\end{equation}
+This has been the preferred distance function since its proposal by \citet{Lamberti2004}.
+Most works consider the uniform distribution $\bm u = (1/D!, 1/D!, \dots, 1/D!)$ as the reference model.
+
+The quantity~\eqref{eq:JensenShannon} is also called ``disequilibrium.''
+The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$, and we chose to work with the uniform probability distribution function as the equilibrium law.
+\textcolor{red}{[Eduarda:] alguma referência (dentre as que já citamos) e algumas propriedades? Alguma simplificação quando u é a uniforme?}
 

### 2021-10-17 Code/Attack-Experiments.R
test

@@ -5,6 +5,7 @@
 ################################################################################
 
 # Packages and sources ---------------------------------------------------------
+setwd("/home/eduarda/Desktop/Codes/Confidence Regions/ConfidenceRegions-master/Code")
 source("Bandt-Pompe.R")
 if(!require(ggplot2)) install.packages("ggplot2")
 if(!require(ggrepel)) install.packages("ggrepel")
@@ -15,7 +16,8 @@ set.seed(123)
 AttackElement <- function(e, d, p){
   if(runif(1) <= p){
     i = round(runif(1, max = d-1, min = 1), digits = 0)
-    e[i+1] = e[i] 
+    e[i] = e[i] - 0.002
+    e[i+1] = e[i+1] + 0.002
   }
   return(e)
 }
@@ -51,13 +53,14 @@ bandt.pompe.by.elements <- function(elements, dimension, delay){
 
 #Global variables --------------------------------------------------------------
 D = 3
+N = 50000
 tau = 1
-P = c(0.001, 0.005, 0.01, 0.015, 0.02, 0.025, 0.03) 
+P = seq(from = 0, to = 0.7, length.out = 20)
 
 h = rep(0, length(P) + 1)
 c = rep(0, length(P) + 1)
 
-ts = read.csv("../Data/Emblematic-serie-D3-N50000.csv")[,2]
+ts = read.csv("../Data/Minimum-serie-D3-N50000.csv")[,2]
 elements = formationPattern(ts, D, tau, 1)
 probs.ts = bandt.pompe(ts, D, tau)
 h[1] = shannon.entropy.normalized(probs.ts)
@@ -65,10 +68,10 @@ c[1] = Ccomplexity(probs.ts)
 
 for(i in 1:length(P)) {
   cat("i:" , i," P: ", P[i], "\n")
-  x_attack = AttackTimeSeries(ts, D, tau, P[i])
-  #x_attack = AttackPattern(elements, D, tau, P[i])
-  probs_attacks = bandt.pompe(x_attack, D, tau)
-  #probs_attacks = bandt.pompe.by.elements(x_attack, D, tau)
+  #x_attack = AttackTimeSeries(ts, D, tau, P[i])
+  x_attack = AttackPattern(elements, D, tau, P[i])
+  #probs_attacks = bandt.pompe(x_attack, D, tau)
+  probs_attacks = bandt.pompe.by.elements(x_attack, D, tau)
[…]

### 2021-10-17 Code/Emblematic-Point-Search.R

@@ -43,17 +43,23 @@ for(i in 1:104){
   ts[,i] = split_seq[[i]]
 }
 
+h = rep(0, 104)
+c = rep(0, 104)
+test_result = rep(FALSE, 104)
+
 for(i in 1:104){
+  print(i)
   probs = bandt.pompe(ts[,i], 3, 1)
-  h = shannon.entropy.normalized(probs)
-  c = Ccomplexity(probs)
-  cat("i: ", i, " H: ", round(h, 9), " C: ", round(c, 9), "\n")
-  
-  if(round(h, 6) == round(0.999985292278035, 6) && round(c, 6) == round(0.0000145144384709536, 6))
-    print(i)
+  h[i] = shannon.entropy.normalized(probs)
+  c[i] = Ccomplexity(probs)
+  test_result[i] = test.point(h[i], c[i], D, 50000, 99)
+  #cat("i: ", i, " H: ", round(h, 9), " C: ", round(c, 9), "\n")
+  #if(round(h, 6) == round(0.999985292278035, 6) && round(c, 6) == round(0.0000145144384709536, 6))
+  #  print(i)
 }
 
 #H = 0.999985292278035
 #C = 1.45144384709536e-05
 
 write.csv(ts[,10], "../Data/Emblematic-serie-D3-N50000.csv")
+write.csv(ts[,61], "../Data/Minimum-serie-D3-N50000.csv")

### 2021-10-17 Code/Mixture-caos.R

@@ -1,0 +1,99 @@
+################################################################################
+# Author: Eduarda Chagas
+# Date : Out 9, 2021
+# Contact: eduarda.chagas@dcc.ufmg.br
+################################################################################
+
+# Packages and sources ---------------------------------------------------------
+source("Bandt-Pompe.R")
+source("Test-point.R")
+if(!require(ggplot2)) install.packages("ggplot2")
+if(!require(ggrepel)) install.packages("ggrepel")
+if(!require(ggthemes)) install.packages("ggthemes")
+if(!require(nonlinearTseries)) install.packages("nonlinearTseries")
+
+
+logistic.map.generator <- function(r){
+  index = 1
+  time_series = vector(mode = "numeric", length = 50000)
+  
+  time_series[index] <- 0.1
+  for(i in 2:(10000 + 50000)){
+    time_series[index] = r * time_series[index] * (1 - time_series[index])
+    if(i > 10001){
+      index = index + 1
+      time_series[index] = r * time_series[index-1] * (1 - time_series[index-1])
+    }
+  }
+  return(time_series)
+}
+
+quadratic.map.generator <- function(c){
+  index = 1
+  time_series = vector(mode = "numeric", length = 50000)
+  
+  time_series[index] <- 0.1
+  for(i in 2:(10000 + 50000)){
+    time_series[index] = (time_series[index]^2) + c
+    if(i > 10001){
+      index = index + 1
+      time_series[index] = (time_series[index - 1]^2) + c
+    }
+  }
+  return(time_series)
+}
+
+r = 3.56995
+c = -2
+D = 3
+N = 50000
+tau = 1
+
+ts = read.csv("../Data/Minimum-serie-D3-N50000.csv")[,2]
+ts = round(ts, 6)
+logistic_map = logistic.map.generator(r)
+
+P = seq(from = 0.99, to = 1, length.out = 20)
+n_p = length(P)
+h_logistic = rep(0, n_p)
+c_logistic  = rep(0, n_p)
+
+for(i in 1:n_p){
+  ts_mixture_logistic = (P[i] * ts) + ((1 - P[i]) * logistic_map)
+  probs_mixture_logistic = bandt.pompe(ts_mixture_logistic, D, tau)
[…]

### 2021-10-17 Code/mixture-caos.R

@@ -1,66 +1,0 @@
-################################################################################
-# Author: Eduarda Chagas
-# Date : Out 9, 2021
-# Contact: eduarda.chagas@dcc.ufmg.br
-################################################################################
-
-# Packages and sources ---------------------------------------------------------
-source("Bandt-Pompe.R")
-if(!require(ggplot2)) install.packages("ggplot2")
-if(!require(ggrepel)) install.packages("ggrepel")
-if(!require(ggthemes)) install.packages("ggthemes")
-
-series.generator.map <- function(r){
-  index = 1
-  time_series = vector(mode = "numeric", length = 50000)
-  
-  time_series[index] <- 0.1
-  for(i in 2:(10000 + 50000)){
-    time_series[index] = r * time_series[index] * (1 - time_series[index])
-    if(i > 10001){
-      index = index + 1
-      time_series[index] = r * time_series[index-1] * (1 - time_series[index-1])
-    }
-  }
-  return(time_series)
-}
-
-r = 3.56995
-D = 3
-tau = 1
-
-ts = read.csv("../Data/Emblematic-serie-D3-N50000.csv")[,2]
-logistic_map = series.generator.map(r)
-
-P = seq(from = 0.999, to = 1, length.out = 10)
-n_p = length(P)
-h = rep(0, n_p)
-c = rep(0, n_p)
-
-for(i in 1:n_p){
-  ts_mixture = (P[i] * ts) + ((1 - P[i]) * logistic_map)
-  probs_mixture = bandt.pompe(ts_mixture, D, tau)
-  h[i] = round(shannon.entropy.normalized(probs_mixture), 10)
-  c[i] = round(Ccomplexity(probs_mixture), 10)
-}
-
-hc_df = data.frame(H = h, C = c, P = P)
-legend.names = as.character(P)
-
-cotas.sup = data.frame("c1x" = readingMPR(D, 1), "c1y" = readingMPR(D, 2))
-cotas.inf = data.frame("c2x" = readingMPR(D, 3), "c2y" = readingMPR(D, 4))
-
-p = ggplot(data = hc_df, aes(x = H, y = C)) +
-  geom_line(data = cotas.sup, aes(x = c1x, y = c1y), color="gray") +
-  geom_line(data = cotas.inf, aes(x = c2x, y = c2y), color="gray") + 
[…]

### 2021-10-17 Reports/JOURNAL - Confidence Regions/Chapters/Background 2.tex

--- 2021-10-10 Reports/Journal - Confidence Regions/Chapters/Background.tex
@@
 
+We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!^2}, \dots, \frac{1}{D!^2}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
+It is calculated as:
+\begin{equation}
+	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!^2} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
+	u_\ell \log\frac{u_\ell}{h_\ell}
+	\Big).
+\end{equation}
+This quantity is also called ``disequilibrium.''
+The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
+
 With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.

### 2021-10-21 Code/Container_function.R
incremental plot_points_confidence_regions

@@ -26,7 +26,7 @@ cotas <- function(dimension){
 }
 
 # Função que exibe o ponto no plano HC, suas cotas e região de confiança especificada
-plot_points_confidence_regions <- function(point, D=6, N=1000, interval=99){
+plot_points_confidence_regions <- function(p, point, D=6, N=1000, interval=99, zoom_x, zoom_y){
   
   hc.points = read.csv(paste0("../Data/Regions-HC/regions-hc-D", D, "-N", N, ".csv"))[2:4]
   
@@ -35,13 +35,11 @@ plot_points_confidence_regions <- function(point, D=6, N=1000, interval=99){
   }else if(interval == 95){
     rect = data.frame(H = hc.points$H[5:8], C = hc.points$C[5:8])
   }
-  
-  p = cotas(D)
   p = p +
     geom_point(data = point, aes(x = H, y = C), size = 4) +
     geom_polygon(data = rect, aes(x = H, y = C), fill = "green", alpha=0.2, inherit.aes = FALSE) +
-    xlim(limits = c(min(min(rect$H), min(point$H)), max(max(rect$H), max(point$H)))) +
-    ylim(limits = c(min(min(rect$C), min(point$C)), max(max(rect$C), max(point$C)))) +
+    xlim(limits = c(min(min(rect$H), min(point$H)) - zoom_x, max(max(rect$H), max(point$H)) +  zoom_x)) +
+    ylim(limits = c(min(min(rect$C), min(point$C)) - zoom_y, max(max(rect$C), max(point$C)) + zoom_y)) +
     xlab(expression(italic(H))) + ylab(expression(italic(C))) + 
     theme_minimal(base_size = 25, base_family = "serif")  
   
@@ -68,13 +66,15 @@ tau = 1
 N = 1000
 interval = 95
 
-# Obtenção da sequência e seu respectivo ponto no plano HC ---------------------
+# Obtenção da série e seu respectivo ponto no plano HC ---------------------
 ts = get_white_noise(N)
-probs.ts = bandt.pompe(ts[1,], D, tau)
+probs.ts = bandt.pompe(ts[2,], D, tau)
 h = shannon.entropy.normalized(probs.ts)
 c = Ccomplexity(probs.ts)
 point = data.frame(H = h, C = c)
 
 # Obtenção do plot -------------------------------------------------------------
-p = plot_points_confidence_regions(point, D, N)
+
+p = cotas(D)
[…]

### 2021-10-22 Code/Container_function.R
Update Container_function.R

@@ -68,9 +68,10 @@ interval = 95
 
 # Obtenção da série e seu respectivo ponto no plano HC ---------------------
 ts = get_white_noise(N)
-probs.ts = bandt.pompe(ts[2,], D, tau)
-h = shannon.entropy.normalized(probs.ts)
-c = Ccomplexity(probs.ts)
+x <- ts[2,]
+probs.ts = bandt.pompe(x, D, tau)
+(h = shannon.entropy.normalized(probs.ts))
+(c = Ccomplexity(probs.ts))
 point = data.frame(H = h, C = c)
 
 # Obtenção do plot -------------------------------------------------------------
@@ -78,3 +79,86 @@ point = data.frame(H = h, C = c)
 p = cotas(D)
 p = plot_points_confidence_regions(p, point, D, N, zoom_x = 0.1, zoom_y = 0.1)
 print(p)
+
+# Here begins the disaster by Alejandro
+
+## New point 1: reverse the time series
+rev.ts <- rev(x)
+probs.rev.ts <- bandt.pompe(rev.ts, D, tau)
+(hrev = shannon.entropy.normalized(probs.rev.ts))
+(crev = Ccomplexity(probs.rev.ts))
+### The point did not change (that's good)
+
+## New point 2: add logistic map
+
+logistic.map <- function(r, x, N, M){
+  ## r: bifurcation parameter
+  ## x: initial value
+  ## N: number of iteration
+  ## M: number of iteration points to be returned
+  z <- 1:N
+  z[1] <- x
+  for(i in c(1:(N-1))){
+    z[i+1] <- r *z[i]  * (1 - z[i])
+  }
+  ## Return the last M iterations 
+  z[c((N-M):N)]
+}
+
+x.logistic.map <- logistic.map(2.9, .5, 5000, 999)
+
+p.logistic.map <- bandt.pompe(x.logistic.map, D, tau)
+(h.logistic.map = shannon.entropy.normalized(p.logistic.map))
+(c.logistic.map = Ccomplexity(p.logistic.map))
+### Yes! We're far fom (h,c)
+
+
+## Now begins the fun; let's mix x (ts[2,]) and x.logistic.map
+
+alpha <- 1- 11*.Machine$double.eps
+x.mix <- (1-alpha)*x+alpha*x.logistic.map
+
+probs.mix = bandt.pompe(x.mix, D, tau)
+(hmix = shannon.entropy.normalized(probs.mix))
+(cmix = Ccomplexity(probs.mix))
[…]

### 2021-10-22 Code/Container_function.R
Update Container_function.R

@@ -6,6 +6,7 @@
 
 # Packages and sources ---------------------------------------------------------
 source("Bandt-Pompe.R")
+source("p-value-test.R")
 if(!require(ggplot2)) install.packages("ggplot2")
 if(!require(ggthemes)) install.packages("ggthemes")
 
@@ -161,4 +162,8 @@ p +
              col="red", size=2) + 
   xlim(.91, .945) +
   ylim(.05, .25)
+#### Calcular o p-valor de x.patched
+
+
+
 

### 2021-10-22 Reports/Journal - Confidence Regions/Chapters/Introduction.tex
Starting R1

@@
 
-The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{1800} citations, according to the Web of Science.
+The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{2,160} citations, according to the Web of Science\footnote{Checked on 23 October 2021}.
 We found works using this approach in several areas of scientific knowledge such as, for example:
@@
 
-The \num{1820} citations received by the seminal paper appeared in \num{684} journals indexed by the Web of Science.
-These journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-There are \num{17} citing articles from journals that belong to the Statistics \& Probability category.
+The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
+Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
 Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-two in the \textit{Journal of Time Series Analysis}, 
+two in the \textit{Journal of Time Series Analysis} and in 
+\textit{Theory and Applications of Time Series Analysis},
 and each of the remaining ten appeared in a different journal.

### 2021-10-22 Code/Container_function.R
Add p-value test in analysis

@@ -89,6 +89,7 @@ probs.rev.ts <- bandt.pompe(rev.ts, D, tau)
 (hrev = shannon.entropy.normalized(probs.rev.ts))
 (crev = Ccomplexity(probs.rev.ts))
 ### The point did not change (that's good)
+calculate.p.value.samples(data.frame(H = hrev, C = crev), N, D)
 
 ## New point 2: add logistic map
 
@@ -112,12 +113,13 @@ p.logistic.map <- bandt.pompe(x.logistic.map, D, tau)
 (h.logistic.map = shannon.entropy.normalized(p.logistic.map))
 (c.logistic.map = Ccomplexity(p.logistic.map))
 ### Yes! We're far fom (h,c)
+calculate.p.value.samples(data.frame(H = h.logistic.map, C = c.logistic.map), N, D)
 
 
 ## Now begins the fun; let's mix x (ts[2,]) and x.logistic.map
 
 alpha <- 1- 11*.Machine$double.eps
-x.mix <- (1-alpha)*x+alpha*x.logistic.map
+x.mix <- (1-alpha) * x + alpha * x.logistic.map
 
 probs.mix = bandt.pompe(x.mix, D, tau)
 (hmix = shannon.entropy.normalized(probs.mix))
@@ -130,6 +132,7 @@ p +
   xlim(.91, .945) +
   ylim(0.05, .25)
 ### Close to getting something interesting here
+calculate.p.value.samples(data.frame(H = hmix, C = cmix), N, D)
 
 ## Now begins the fun 2; let's add a sine
 
@@ -147,6 +150,7 @@ p +
              aes(x=hmix, y=cmix), 
              col="red", size=2)
 ### Nothing interesting adding the sine: the point walks through a line
+calculate.p.value.samples(data.frame(H = hmix, C = cmix), N, D)
 
 ## Now a patch from the chaotic map
 
@@ -163,6 +167,7 @@ p +
   xlim(.91, .945) +
   ylim(.05, .25)
 #### Calcular o p-valor de x.patched
+calculate.p.value.samples(data.frame(H = h.logistic.map, C = c.logistic.map), N, D)
 
 
 

### 2021-10-22 Code/p-value-test.R

@@ -179,4 +179,3 @@ p.value.all.rng <- function(){
   return(table.code)
 }
 
-p.value.all.prng()

### 2021-10-22 Reports/Journal - Confidence Regions/Response-R1.tex

@@
-\RequirePackage{xr}
-\externaldocument{paper}
+\documentclass[alpha-refs]{wiley-article}
 
-\documentclass[journal,onecolumn,draftcls,11pt]{IEEEtran}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage[binary-units]{siunitx}
+\usepackage{bm,bbm}
 \usepackage{booktabs}
-\usepackage[T1]{fontenc}
-\usepackage[cmex10]{amsmath}
-\usepackage{amsfonts}
-\usepackage{color}
-\usepackage{bm,bbm}
-\usepackage{wasysym}
-\usepackage{texnames}
-\usepackage{url}
-\usepackage[boxed]{algorithm2e}   % AAB inserido
-\usepackage[listings, many]{tcolorbox}
-\usepackage[binary-units]{siunitx}
-\usepackage{multirow,bigstrut}
-\usepackage{capt-of}
+\usepackage{subfig}
+\usepackage{float}
+\usepackage{rotating}
+\graphicspath{{./Figures/}}
+\usepackage[linesnumbered,lined,boxed]{algorithm2e}
+\makeatletter
+\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
+\makeatother
+\usepackage{undertilde}
+\usepackage{tcolorbox}
 \usepackage{todonotes}
-\usepackage{enumitem}
+\usepackage{comment}
 
 \begin{document}
-\title{International Statistical Review - Response Letter of Manuscript ID ISR-OA-160-20}
+\title{Manuscript ID ISR-OA-160-20}
 
-\author{Eduarda~ T.~C.~Chagas,
-        Marcelo Queiroz,
-        Osvaldo A.\ Rosso,
-        Heitor S.\ Ramos,
-        Cristopher G.\ S. Freitas,
-        Leonardo V.\ Pereira,
-        Alejandro C.\ Frery}
+\author{Eduarda T.\ C.\ Chagas, Marcelo Queiroz-Oliveira, Osvaldo A.\ Rosso, Heitor S.\ Ramos, Cristopher G.\ S. Freitas, and Alejandro C.\ Frery}
 
+\papertype{Response Letter}
 \maketitle
-
-\IEEEpeerreviewmaketitle
 
@@
 \end{tcolorbox}
+
+We now state at the beginning of the Abstract that
+\begin{quote}
+	This article serves two purposes.
+	Firstly, it surveys the \citeauthor{PermutationEntropyBandtPompe} methodology for the statistical community, stressing topics that are open for research.
+	Secondly, it contributes towards a better understanding of the statistical properties of that approach for time series analysis.
+\end{quote}
 
@@
 
+We would like to stress the following paragraph from our Introduction:
+\begin{quote}
+	The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
+	Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+	There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
+	Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
+	two in the \textit{Journal of Time Series Analysis} and in 
+	\textit{Theory and Applications of Time Series Analysis},
+	and each of the remaining ten appeared in a different journal.
+	Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
+	It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
+	The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
+\end{quote}
+
 \section{Reviewer \#2}
@@
 
+\bibliography{References}
+
 \end{document}

### 2021-10-22 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex

@@
 
-\title{A Test for White Noise in the Entropy-Complexity Plane}
+\title{Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane}
 
@@
 \begin{abstract}
+This article serves two purposes.
+Firstly, it surveys the \citeauthor{PermutationEntropyBandtPompe} methodology for the statistical community, stressing topics that are open for research.
+Secondly, it contributes towards a better understanding of the statistical properties of that approach for time series analysis.
+%
 The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series. 
@@
 The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
+managing to assess sequences of true random samples as random (adequate test size), 
+rejecting correlated sequences (sound test power), and
 capturing the randomness of generators previously analyzed in the literature.

### 2021-10-22 Reports/Journal - Confidence Regions/Response-R1.tex
Response

@@
 
-We now state at the beginning of the Abstract that
+We wholeheartedly agree.
+Our initial version did not make a clear statement of the article's nature.
+In order to improve this issue, we have introduced two changes.
+The first is a new title, namely
+\begin{quote}
+Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane
+\end{quote}
+Second, we now state at the beginning of the Abstract that
 \begin{quote}
@@
 \end{quote}
+
+We hope these changes, which reflect our initial idea, make a clear point for the statistical community.
+
+We have made other changes to improve the manuscript readability and conciseness.
 

### 2021-10-23 Code/Container_function.R
Matei a charada!!!

@@ -136,7 +136,7 @@ calculate.p.value.samples(data.frame(H = hmix, C = cmix), N, D)
 
 ## Now begins the fun 2; let's add a sine
 
-xsin <- sin((1:1000)/1000 * 16*pi)
+xsin <- sin((1:1000)/1000 * 4*pi)
 
 alpha <- .2
 x.mix <- (1-alpha)*x+alpha*xsin
@@ -162,13 +162,37 @@ probs.patched = bandt.pompe(x.patched, D, tau)
 
 p + 
   geom_point(data=data.frame(h.patched, c.patched), 
-             aes(x=hmix, y=cmix), 
+             aes(x=h.patched, y=c.patched), 
              col="red", size=2) + 
   xlim(.91, .945) +
   ylim(.05, .25)
 #### Calcular o p-valor de x.patched
-calculate.p.value.samples(data.frame(H = h.logistic.map, C = c.logistic.map), N, D)
+calculate.p.value.samples(data.frame(H = h.patched, C = c.patched), N, D)
 
+### Now I will encapsulate things
 
+ExperimentPatched <- function(x, r, a, N, M, patch, plot.region) {
+  
+  x.logistic.map <- logistic.map(r, a, N, M)
+  n.tail <- round(patch*length(x))
+  x.patched <- c(x[1:(length(x)-n.tail)], 
+                 x.logistic.map[(length(x)-n.tail+1):length(x)])
+  
+  probs.patched = bandt.pompe(x.patched, 6, 1)
+  
+  print((h.patched = shannon.entropy.normalized(probs.patched)))
+  print((c.patched = Ccomplexity(probs.patched)))
+  
+  print(plot.region + 
+    geom_point(data=data.frame(h.patched, c.patched), 
+               aes(x=h.patched, y=c.patched), 
+               col="red", size=2) + 
+    xlim(.91, .945) +
+    ylim(.05, .25))
+  #### Calcular o p-valor de x.patched
+  (calculate.p.value.samples(data.frame(H = h.patched, C = c.patched), length(x), 6))
+}
 
+# patch in .01 to .06 !!!
+ExperimentPatched(x, 4, .5, 5000, 999, .06, p)
 

### 2021-10-23 Code/Container_function.R
Resolvido: função crescente

@@ -84,12 +84,12 @@ print(p)
 # Here begins the disaster by Alejandro
 
 ## New point 1: reverse the time series
-rev.ts <- rev(x)
-probs.rev.ts <- bandt.pompe(rev.ts, D, tau)
-(hrev = shannon.entropy.normalized(probs.rev.ts))
-(crev = Ccomplexity(probs.rev.ts))
-### The point did not change (that's good)
-calculate.p.value.samples(data.frame(H = hrev, C = crev), N, D)
+# rev.ts <- rev(x)
+# probs.rev.ts <- bandt.pompe(rev.ts, D, tau)
+# (hrev = shannon.entropy.normalized(probs.rev.ts))
+# (crev = Ccomplexity(probs.rev.ts))
+# ### The point did not change (that's good)
+# calculate.p.value.samples(data.frame(H = hrev, C = crev), N, D)
 
 ## New point 2: add logistic map
 
@@ -107,7 +107,7 @@ logistic.map <- function(r, x, N, M){
   z[c((N-M):N)]
 }
 
-x.logistic.map <- logistic.map(2.9, .5, 5000, 999)
+x.logistic.map <- logistic.map(3.999999999999999, .5, 5000, 999)
 
 p.logistic.map <- bandt.pompe(x.logistic.map, D, tau)
 (h.logistic.map = shannon.entropy.normalized(p.logistic.map))
@@ -195,4 +195,56 @@ ExperimentPatched <- function(x, r, a, N, M, patch, plot.region) {
 
 # patch in .01 to .06 !!!
 ExperimentPatched(x, 4, .5, 5000, 999, .06, p)
+
+# Six points for illustration
+x.logistic.map <- logistic.map(3.99999, .5, 5000, 999)
+percentage.patch <- seq(.01, .06, by=.01)
+Experiment.Logistic.Map <- data.frame(h.patched=rep(0, 6),
+                                      c.patched=rep(0, 6),
+                                      pvalue.patched=rep(0, 6))
+for(count in 1:6){
+  patch <- percentage.patch[count]
+  
+  n.tail <- round(patch*1000)
+  x.patched <- c(x[1:(1000-n.tail)], 
+                 x.logistic.map[(1000-n.tail+1):1000])
+  probs.patched <- bandt.pompe(x.patched, 6, 1)
+  Experiment.Logistic.Map$h.patched[count] <- shannon.entropy.normalized(probs.patched)
+  Experiment.Logistic.Map$c.patched[count] <- Ccomplexity(probs.patched)
[…]

### 2021-10-23 Code/Container_function.R
Update Container_function.R

@@ -239,12 +239,20 @@ for(count in 1:6){
     1000, 6)
 }
 
+Experiment.Increasing$percentage <- percentage.patch*100
+
 require(ggrepel)
 
 p +
-  geom_point(data=Experiment.Increasing, aes(x=h.patched, y=c.patched), 
+  geom_point(data=Experiment.Increasing, aes(x=h.patched, 
+                                             y=c.patched), 
              col="red", size=2) +
-  xlim(.905, .945)
+  geom_text_repel(data=Experiment.Increasing, aes(x=h.patched, 
+                                                  y=c.patched,
+                                                  label=paste0(as.character(percentage.patch*100), rep("%", 6))),
+                  direction = "y") +
+  xlim(.905, .945) +
+  ylim(0.05, 0.3)
 
 # Vamos reportar apenas o resultado de acrescentar ao final uma função crescente
 

### 2021-10-23 Code/Container_function.R
Align the labels

@@ -242,15 +242,18 @@ for(count in 1:6){
 Experiment.Increasing$percentage <- percentage.patch*100
 
 require(ggrepel)
+require("slowkow/ggrepel")
+devtools::install_github("slowkow/ggrepel")
+
 
 p +
   geom_point(data=Experiment.Increasing, aes(x=h.patched, 
                                              y=c.patched), 
              col="red", size=2) +
   geom_text_repel(data=Experiment.Increasing, aes(x=h.patched, 
-                                                  y=c.patched,
+                                                  y=c.patched, 
                                                   label=paste0(as.character(percentage.patch*100), rep("%", 6))),
-                  direction = "y") +
+                  direction = "y", nudge_y=-0.01, segment.size=0.25) +
   xlim(.905, .945) +
   ylim(0.05, 0.3)
 

### 2021-10-24 Reports/Journal - Confidence Regions/Response-R1.tex
Matei a charada!!!
Avancing R1

@@
 
-We hope these changes, which reflect our initial idea, make a clear point for the statistical community.
+We also updated the following paragraph from the Introduction:
+\begin{quote}
+	The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
+	Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+	There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
+	Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
+	two in the \textit{Journal of Time Series Analysis} and in 
+	\textit{Theory and Applications of Time Series Analysis},
+	and each of the remaining ten appeared in a different journal.
+	Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
+	It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
+	The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
+\end{quote}
+
+We hope these changes, which reflect our initial idea, make a clear point that this a contribution for the statistical community.
 
 We have made other changes to improve the manuscript readability and conciseness.
+For instance, we now provide explicit expressions for the normalized disequilibrium.
+In particular, as detailed below, we now illustrate the need of using the complexity.
 
@@
 
-We would like to stress the following paragraph from our Introduction:
+In fact, an infinitely large sample of white noise will produce a perfectly flat histogram of patterns which, in turn, becomes the point $(1,0)\in H\times C$.
+Nevertheless, the finite sample size properties are almost completely unknown, and starting their study is one of the purposes of this paper.
+
+\addtocounter{section}{2}
+\addtocounter{subsection}{1}
+\addtocounter{subsubsection}{1}
+\addtocounter{figure}{11}
+The reviewer rises a very relevant question: is the Statistical Complexity needed?
+Several researchers have addressed this question, and the unanimous answer is yes, it is needed.
+The discussion has been limited to the Physics literature, most markedly after the work by \citet{SimpleMeasureforComplexity} and the subsequent discussion \citep{CommentIonSimpleMeasureforComplexity,CommentIIonSimpleMeasureforComplexity} and rejoinder \citep{ReplytoCommentsonSimpleMeasureforComplexity} papers.
+
+Going further in this direction would require introducing several concepts which may seem unfamiliar to this journal's readership.
+Nevertheless, being an relevant point, we opted for illustrating the need of both descriptors, entropy and complexity, with an example in the discussion of the test power.
+
+We split the power subsection in two, and added another study which illustrates the need of considering the complexity:
 \begin{quote}
-	The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
-	Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
-	There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
-	Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
-	two in the \textit{Journal of Time Series Analysis} and in 
-	\textit{Theory and Applications of Time Series Analysis},
-	and each of the remaining ten appeared in a different journal.
-	Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
-	It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
-	The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
+	\subsubsection{$H_1$: Patch of Deterministic Function}
+
+	Consider the times series of length $T$ comprised of $T-[c100]$ white noise observations $x_1,x_2,\dots, x_{T-[c100]}$ followed by the signal $y_{T-[c100]+1}, y_{T-[c100]+2}, \dots, y_T$, in which $0\leq c \ll 1$ is the percentage of contamination.
+	We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
+	Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such a contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
+	The Figure also shows the confidence region at \SI{99}{\percent}.
+
+	\begin{figure}[hbt]
+		\centering
+		\includegraphics[width=.7\linewidth]{Figures/PointsPatchedIncreasingFunction}
+		\caption{Effect of patching an increasing function at different levels to a white noise sequence.}\label{Fig:PointsPatchedIncreasingFunction}
+	\end{figure}
+
+	The original point is displaced, at all levels of contamination, to a region with smaller entropy and larger complexity.
+	When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
+	The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.
+
+	It is worth noticing that a test based solely on the entropy would have less power.
+	In this case, the complexity component enables the test to reject the null hypothesis at small contamination percentages.
 \end{quote}
@@
 
+Thank you very much for your encouraging comments.
+
 \bibliography{References}

### 2021-10-24 Reports/Journal - Confidence Regions/Chapters/Background.tex
Avancing R1

@@
 The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$, and we chose to work with the uniform probability distribution function as the equilibrium law.
-\textcolor{red}{[Eduarda:] alguma referência (dentre as que já citamos) e algumas propriedades? Alguma simplificação quando u é a uniforme?}
+Under these conditions holds that
+$$
+\max\{Q'\} = -2\Big[
+\frac{D!+1}{D!} \log(D!+1) - 2 \log(2D!) + \log D!
+\Big].
+$$
 
 With this, they proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
+Notice that both $H$ and $Q$ are normalized quantities, so also is $C$. 
 A time series can then be mapped into a point in the $H\times C$ plane.
@@
 Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
+In particular, notice that the point associated to white noise is not at $(1,0)$, as consequence of being obtained from a finite rather than infinite length sequence.
 

### 2021-10-24 Reports/Journal - Confidence Regions/Chapters/Introduction.tex
Avancing R1

@@
 The time series is transformed into ordinal patterns, with which a histogram is formed.
-The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model and. 
-Thus, the approach can be applied to a variety of situations.
+The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model. 
+The approach can, thus, be applied to a variety of situations.
 
@@
 	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series.
+	\item We verify the test's power contrasting correlated noise time series, and white noise series patched with a deterministic signal.
 \end{itemize}

### 2021-10-24 Reports/Journal - Confidence Regions/Chapters/Methodology.tex
Avancing R1

@@
 
-We used \SI{54e6}{4\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
+We used \SI{54e6}{\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
 
@@
 
-We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \cite{ggplot2Wickman} for generating the plots.
+We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \citep{ggplot2Wickman} for generating the plots.
 

### 2021-10-24 Reports/Journal - Confidence Regions/Chapters/Results.tex
Avancing R1

--- 2021-10-10 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
-\documentclass[alpha-refs]{wiley-article}
+\section{Results}\label{Sec:Results}
 
-\usepackage[binary-units]{siunitx}
-\usepackage{bm,bbm}
-\usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{rotating}
-\graphicspath{{./Figures/}}
-\usepackage[linesnumbered,lined,boxed]{algorithm2e}
-\makeatletter
-\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
-\makeatother
-\usepackage{undertilde}
-\usepackage{todonotes}
-\usepackage{comment}
+\subsection{Empirical confidence regions}
 
-\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
-\DeclareSIUnit{\alphapercent}{\alpha\%}
+Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
+of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
+for $D=3,4,5,6$ and $N=1000,50000$, .
+The points are presented counterclockwise, starting with the one with the largest complexity.
 
-\newcommand{\Mycite}[1]{%
- (\citeauthor{#1},~\citeyear{#1})}
+\begin{comment}
+\begin{table}[hbt]
+\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
+\centering
+\begin{tabular}{rcllllllll}
+\toprule
+& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
+& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
+$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
+$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+\end{tabular}
+\end{table}
+\end{comment}
 
-\papertype{Original Article}
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 1000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
+		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
+		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
+		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
+		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
+		\midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
+		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
+		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
+		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
+		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
+		\midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
+		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
+		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
+		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
+		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
+		\midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
+		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
+		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
+		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
+		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
 
-\title{A Test for White Noise in the Entropy-Complexity Plane}
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 50000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
+		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
+		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
+		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
+		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+	\end{tabular}
+\end{table}
 
-\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}
+Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
+We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
 
-\author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
-\author[4]{Osvaldo A.\ Rosso}
-\author[1]{Heitor S.\ Ramos}
-\author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[5]{Alejandro C.\ Frery}
+\begin{figure}[hbt]
+	\centering
+	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
+	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
+	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
+	\label{fig:HC-PCA}
+\end{figure}
 
-\contrib[]{All authors contributed equally.}
+The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
 
-% Include full affiliation details for all authors
-\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
-\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
-\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
-\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
+Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
+They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
+As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
+Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
 
-\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
-\corremail{eduarda.chagas@dcc.ufmg.br}
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{PCA-hist-50k}
+	\caption{Histograms of the first principal component for $D=3,4,5,6$}
+	\label{fig:PCA-Hist}
+\end{figure}
 
-\fundinginfo{CNPq, Fapeal}
+\subsection{Test Size}
 
-% Include the name of the author that should appear in the running header
-\runningauthor{Eduarda T.\ C.\ Chagas et al.}
+We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
+Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
+show the results.
 
-\begin{document}
+On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
+On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
+In contrast, we expected \SI{1}{\percent} of rejection.
+This might be because, in this case, the condition $D!\ll T$ is not respected.
+Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
 
-% \begin{frontmatter}
-\maketitle
+%
+%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
+%
+%For short series, $T = 1000$, and $D = 3$ 
+%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
+%
+%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
+%A reasonable explanation for this event is given in the choice of the parameter itself.
+%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
 
-\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
-Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
-Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate size), 
-rejecting correlated sequences (sound power), and
-capturing the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
-\end{abstract}
+\begin{table}[hbt]
+	\centering
+	\caption{Empirical sizes of the test}
+	\label{tab:result1}
+	\begin{tabular}{*{3}rr}
+		\toprule
+		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
+		%& $p$-value\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		1000 & 3 & $0.98$ & $1.00$\\
+		& 4 & $0.98$ & $0.96$\\
+		& 5 & $1.00$ & $0.94$\\
+		& 6 & $0.97$ & $0.87$\\
+		\cmidrule(lr){1-4} 
+		50000 & 3 & $0.97$ & $0.96$\\
+		%& $0.47856$\\
+		& 4 & $0.94$ & $0.95$\\
+		%& $0.47555$\\ 
+		& 5 & $0.97$ & $0.96$\\ 
+		%& $0.48512$\\ 
+		& 6 & $0.98$ & $0.99$\\ 
+		%& $0.48058$\\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
-\input{Chapters/Introduction}
-\input{Chapters/Background}
-\input{Chapters/Methodology}
-\input{Chapters/Results}
-\input{Chapters/Conclusions}
-\input{Chapters/Source}
-\input{Chapters/acknowledgements}
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
+	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
+	\caption{New $100$ TRWNS and confidence regions.}
+	\label{fig:RNG}
+\end{figure}
 
-\printendnotes
+We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
 
-\bibliography{References}
+\subsection{Test Power}
 
-\end{document}
+\subsubsection{$H_1$: Correlated Noise}
+
+We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
+Several studies in the literature have used this approach for identifying and characterizing randomness.
+
+Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
+Recall that the emblematic time was chosen as the most representative of the data set.
+We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
+
+%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
+As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
+
+Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
+At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
+As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
+
+Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
+We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
+Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
+The same holds for all $k>3/10$.
+
+\begin{figure}
+	\centering
+	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
+	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
+	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
+	\label{fig:correlation}
+\end{figure}
+
+\subsubsection{$H_1$: Patch of Deterministic Function}
+
+Consider the times series of length $T$ comprised of $T-[c100]$ white noise observations $x_1,x_2,\dots, x_{T-[c100]}$ followed by the signal $y_{T-[c100]+1}, y_{T-[c100]+2}, \dots, y_T$, in which $0\leq c \ll 1$ is the percentage of contamination.
+We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
+Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such a contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
+The Figure also shows the confidence region at \SI{99}{\percent}.
+
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=.7\linewidth]{Figures/PointsPatchedIncreasingFunction}
+\caption{Effect of patching an increasing function at different levels to a white noise sequence.}\label{Fig:PointsPatchedIncreasingFunction}
+\end{figure}
+%%% The code that produces this figure starts at line 221, file "container_function.R"
+
+The original point is displaced, at all levels of contamination, to a region with smaller entropy and larger complexity.
+When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
+The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.
+
+It is worth noticing that a test based solely on the entropy would have less power.
+In this case, the complexity component enables the test to reject the null hypothesis at small contamination percentages.
+
+\subsection{Revisiting the White Noise Hypothesis in the Literature}
+
+In this section, we compare the performance of our test with that of 
+previous analyses that employ the Entropy-Complexity plane.
+To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
+Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
+We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
+
+\begin{table}
+	\caption{Results of the sequences generated by the main PRNGs in the literature. 
+		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+	\label{Tab:LiteratureComparations}
+	\centering
+	\begin{tabular}{cccc}
+		\toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		MOT & 3 & 0.305 & NR\\
+		& 4 & 0.572 & NR\\ 
+		& 5 & 0.455 & NR\\ 
+		& 6 & 0.508 & NR\\ 
+		\cmidrule(lr){1-4}
+		MWC & 3 & 0.501 & NR\\
+		& 4 & 0.477 & NR\\ 
+		& 5 & 0.496 & NR\\ 
+		& 6 & 0.496 & NR\\ 
+		\cmidrule(lr){1-4}
+		COM & 3 & 0.123 & NR\\
+		& 4 & 0.002 & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		\cmidrule(lr){1-4}
+		LEH & 3 & 0.531 & NR\\
+		& 4 & 0.515 & NR\\ 
+		\bottomrule
+	\end{tabular}
+	\begin{tabular}{|cccc}
+		\toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		LEH & 5 & 0.495 & NR\\ 
+		& 6 & 0.501 & NR\\ 
+		\cmidrule(lr){1-4}
+		fGn & 3 & 0.521 & NR\\
+		& 4 & 0.519 & NR\\ 
+		& 5 & 0.498 & NR\\ 
+		& 6 & 0.470 & NR\\
+		\cmidrule(lr){1-4}
+		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%\cmidrule(lr){1-4}
+		$f^{-k}$ & 3 & 0.482 & NR\\
+		& 4 & 0.520 & NR\\ 
+		& 5 & 0.513 & NR\\ 
+		& 6 & 0.508 & NR\\
+		\cmidrule(lr){1-4}
+		LCG & 3 & 0.009 & R\\ 
+		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
+
+It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
+In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.

### 2021-10-24 Code/Container_function.R

@@ -256,6 +256,7 @@ p +
                   direction = "y", nudge_y=-0.01, segment.size=0.25) +
   xlim(.905, .945) +
   ylim(0.05, 0.3)
+ggsave(file="../../Confidence Regions/Reports/JOURNAL - Confidence Regions/Figures/PointsPatchedIncreasingFunction.pdf", width=12, height = 10)
 
 # Vamos reportar apenas o resultado de acrescentar ao final uma função crescente
 

### 2021-10-24 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Avancing R1
Reorganized

@@
 %
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series. 
-It consists of computing
+The \citeauthor{PermutationEntropyBandtPompe} methodology 
+%has been used successfully in the analysis of time series. 
+%It 
+consists of computing
 Information Theory descriptors of the histogram of ordinal patterns. 
@@
 
-\input{Chapters/Introduction}
-\input{Chapters/Background}
-\input{Chapters/Methodology}
-\input{Chapters/Results}
-\input{Chapters/Conclusions}
-\input{Chapters/Source}
-\input{Chapters/acknowledgements}
+\section{Introduction}\label{Sec:Intro}
+
+Time Series carry valuable information about the system which produces the data.
+Their analysis is usually based on two approaches \citep{TimeSeriesAnalysisCryerChan}: 
+in the (natural) time and transformed domains (for instance, frequency and wavelet).
+In the context of time-domain analysis, \citet{PermutationEntropyBandtPompe} proposed a new methodology.
+Such an approach is non-parametric and based on descriptors of Information Theory.
+The time series is transformed into ordinal patterns, with which a histogram is formed.
+The resulting distribution is less sensitive to outliers than the original data, and the histogram does not depend on any model. 
+The approach can, thus, be applied to a variety of situations.
+
+The Bandt-Pompe methodology and its variants have been used successfully in the analysis of many types of dynamics, receiving so far more than \num{2,160} citations, according to the Web of Science\footnote{Checked on 23 October 2021}.
+We found works using this approach in several areas of scientific knowledge such as, for example:
+%
+distinguishing noise from chaos~\citep{rosso2007distinguishing};
+%
+the study of electroencephalography signals using wavelet decomposition~\citep{baravalle2018discriminating,baravalle2018rhythmic};
+%
+description of El Niño/Southern Oscillation during the Holocene~\citep{saco2010entropy};
+%
+the characterization of household appliances through their energy consumption~\citep{CharacterizationElectricLoadInformationTheoryQuantifiers};
+%
+detecting and quantifying stochastic and coherence resonance~\citep{rosso2009detectinga, rosso2009detectingb};
+%
+analysis and characterization of economic time series, e.g., stock market, sovereign bonds, credit rating, commodities, and cryptocurrencies~\citep{zunino2010complexity, zunino2012efficiency, bariviera2013efficiency, bariviera2018analysis, Araujo2019permutation};
+%
+online signature classification and verification~\citep{ClassificationVerificationOnlineHandwrittenSignatures}.
+\cite{InformationTheoryPerspectiveNetworkRobustness} verified the effect of attacks on complex networks by the displacement of points in the $H \times C$ plane.
+\citet{CharacterizationVehicleBehaviorInformationTheory} described vehicles' behavior depending on the topology of cities, and
+\citet{Chagas2020Characterization} succeeded in expanding the use of such techniques for analyzing textured images corrupted by speckle noise.
+\citet{LiborInvisibleHand} identified spurious interventions in the Libor market using the $H\times C$ plane representation.
+\citet{echegoyen2020permutation} were able to discriminate between individuals with mild cognitive impairment from those diagnosed with Alzheimer's disease using magnetoencephalography recordings.
+
+With the Bandt and Pompe methodology, a time series is described by a point in a manifold of $\mathbbm R^2$: the Entropy-Complexity plane $H\times C$.
+There are two well-known points in this plane: those of white noise and a completely deterministic sequence.
+Although the boundaries of the $H\times C$ plane are well-defined, its intrinsic topology's complete characterization is an open problem.
+In particular, the joint distribution of points in this plane under typical time series types, which would serve to build test statistics, is unknown.
+
+The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
+Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
+Five of these articles appeared in \textit{Stochastic Environmental Research and Risk Assessment}, 
+two in the \textit{Journal of Time Series Analysis} and in 
+\textit{Theory and Applications of Time Series Analysis},
+and each of the remaining ten appeared in a different journal.
+Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
+It is also noteworthy that, in this category of publications, \cite{DistributionsofOrderPatternsofIntervalMaps} provided a formal and more general proof of the structure of the boundary of the $H\times C$ manifold than that obtained by \cite{martin2006generalized}.
+The lack of attention that the Bandt and Pompe approach has received by the Probability \& Statistics community confirms that it is a fertile research avenue waiting to explore.
+
+Several works have used deterministic and pseudorandom sequences to understand the properties of the points they produce in the $H\times C$ plane.
+\cite{martin2006generalized} analyzed the chaotic logistic map and discussed the boundaries of the $H \times C$ plane.
+\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
+\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
+\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.
+
+With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
+Results in this direction can be found in the literature.
+\cite{RandomNumberGeneratorsCausality} showed that the Entropy-Complexity plane ($H\times C$) is a good indicator of Diehard tests' results on pseudorandom number generators.
+\cite{De_Micco_2008} assessed ways of improving pseudorandom sequences by their representation in this plane.
+
+Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
+In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
+We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
+Our contributions can be summarized as follows:
+\begin{itemize}
+	\item We provide the first contribution in constructing a test in the Entropy-Complexity Plane: we provide confidence regions and $p$-values.
+	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
+	\item We verify the test's power contrasting correlated noise time series, and white noise series patched with a deterministic signal.
+\end{itemize}
+
+The rest of this paper is structured as follows. 
+Section~\ref{Sec:BP} introduces the elements of the study:
+Section~\ref{Sec:BPMethodology} details the methodology,
+Section~\ref{Sec:HCPlane} describes the Entropy-Complexity plane,
+and Section~\ref{Sec:BPApplications} discusses applications of this approach.
+%
+Section~\ref{Sec:BPMethodology} describes our methodology:
+Section~\ref{Sec:OverallFramework} gives the overall framework.
+Section~\ref{Sec:TRNG} describes how we obtained true white noise random sequences from physical devices,
+Section~\ref{Sec:Parameters} lists the parameters of relevance for the study, and
+Section~\ref{confidenceRegions} describes how we obtained the confidence intervals and $p$-values.
+%
+Section~\ref{Sec:Results} assesses the proposed test by verifying its size and power, and its application to well-known pseudorandom number generators.
+Section~\ref{Sec:Conclusions} concludes the paper with a discussion of these results.
+
+\section{Bandt and Pompe Symbolization: A Background}\label{Sec:BP}
+
+In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
+Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
+We then obtain a test statistic, using confidence regions, that can discriminate among times series.
+
+\subsection{The Bandt and Pompe Methodology}\label{Sec:BPMethodology}
+
+Let ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ be a real-valued time series of length $T$, without ties. 
+As stated by \Mycite{PermutationEntropyBandtPompe} in their seminal work:  
+\begin{quote}
+	``If the $\{x_t\}_{t=1}^{T}$ attain infinitely many values, it is common to replace them by a symbol sequence 
+	$\Pi \equiv \{\pi_j\}$ with finitely many symbols, and calculate source entropy from it".
+\end{quote}
+Also, as stressed by these authors, 
+\begin{quote}
+	``The corresponding symbol sequence must come 
+	naturally from the $\{x_t\}_{t=1}^{T}$ without former model assumptions".
+\end{quote}
+
+Let ${\mathbbm A}_{D}$ (with $D \geq 2$ and $D \in {\mathbbm N}$) be the symmetric group of order $D!$ formed by all 
+possible permutation of order $D$, and the symbol component vector 
+${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
+($\pi_j \neq \pi_k~\forall~j \neq k$). 
+Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
+with embedding dimension $D \geq 2$ ($D \in {\mathbbm N}$) and time delay $\tau \geq 1$ ($\tau \in {\mathbbm N}$, also called ``embedding time''):
+\begin{equation} 
+	{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
+	\label{eq:time-delay}
+\end{equation} 
+for $t = 1,2,\dots,N$ with $N = T-(D-1) \tau$.
+Then, the vector ${\mathbf X}^{(D,\tau)}_t$ can be mapped to a symbol ${\bm \pi}^{(D)} \in {\mathbbm A}_{D}$. 
+This mapping should be defined in a way that preserves the desired relation between the elements 
+$x_t  \in {\mathbf X}^{(D,\tau)}_t$, and all $t \in T$ that share this pattern (also called ``motif'') are mapped to the same 
+${\bm \pi}^{(D)}$. 
+The two most frequent ways to define the mapping ${\mathbf X}^{(D,\tau)} \mapsto {\bm \pi}^{(D)}$ are:  
+\begin{enumerate}[label=\alph*)]
+	\item ordering the ranks of $x_t \in {\mathbf X}^{(D,\tau)}$ in chronological order 
+	(\textit{Rank Permutation}) or,
+	\item ordering the time indexes of $x_t \in {\mathbf X}^{(D,\tau)}$  
+	(\textit{Chronological Index Permutation}).
+\end{enumerate}
+See details in the work by \citet{BPRepeatedValuesChaos}.
+Without loss of generality, in the following, we will use the latter.
+
+Consider, for instance, the time series $\mathcal X = (2.8, 2.2, 4.2, 5.8, 5.2, 5.5, 3.3, 4.7, 2.2, 1.5)$ depicted in Fig.~\ref{Fig:IntroBP} as a light blue line.
+Assume we are using patterns of length $D=5$ with a unitary time lag $\tau=1$.
+The code associated to $\mathbf X_{3}^{(5,1)}=(x_3,\dots,x_7)=(4.2, 5.8, 5.2, 5.5, 3.3)$, shown in red, is formed by the indexes in $\bm\pi^{(5)}=(1,2,3,4,5)$ which sort the elements of $\mathbf X_{3}^{(5,1)}$ in increasing order: $51342$.
+With this, $\widetilde{\pi}^{(5)} = 51342$, and we increase the counting related to this motif in the histogram of all possible patterns of size $D=5$.
+
+The green line in Fig.~\ref{Fig:IntroBP} illustrates $\mathbf X_{1}^{(5,2)}$, i.e. the sequence of length $D=5$ starting at $x_1$ with lag $\tau=2$.
+In this case, $\mathbf X_{1}^{(5,2)}= (2.8, 4.2, 5.2, 3.3, 2.2)$, and the corresponding motif is $\widetilde{\pi}^{(5)}=51423$.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=.7\linewidth]{IntroBP}
+	\caption{Illustration of the Bandt and Pompe coding}
+	\label{Fig:IntroBP}
+\end{figure}
+
+After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
+Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
+The next step into the characterization of the time series is computing descriptors from this histogram.
+
+The first descriptor is a measure of the disorder of the system.
+The most frequently used feature for this is the Normalized Shannon entropy, defined as
+\begin{equation}
+	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
+\end{equation}
+with the convention that terms in the summation for which $h(j)=0$ are null.
+This quantity is bounded in the unit interval. 
+It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability function).
+
+Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
+In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
+To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
+They employed the Euclidean distance between $\bm h$ and the uniform probability function.
+
+The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as a more adequate measure of such a distance:
+\begin{equation}
+	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
+	u(\ell) \log\frac{u(\ell)}{h(\ell)}
+	\Big).
+	\label{eq:JensenShannon}
+\end{equation}
+This has been the preferred distance function since its proposal by \citet{Lamberti2004}.
+Most works consider the uniform distribution $\bm u = (1/D!, 1/D!, \dots, 1/D!)$ as the reference model.
+
+The quantity~\eqref{eq:JensenShannon} is also called ``disequilibrium.''
+The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$, and we chose to work with the uniform probability distribution function as the equilibrium law.
+Under these conditions holds that
+$$
+\max\{Q'\} = -2\Big[
+\frac{D!+1}{D!} \log(D!+1) - 2 \log(2D!) + \log D!
+\Big].
+$$
+
+With this, \citet{Lamberti2004} proposed $C=HQ$ as a measure of the Statistical Complexity of the underlying dynamics.
+Notice that both $H$ and $Q$ are normalized quantities, so also is $C$. 
+Moreover, $C$ is capable of discerning between different degrees of periodicity, among other relevant properties.
+
+A time series can then be mapped into a point in the $H\times C$ plane.
+
+\subsection{The Entropy-Complexity Plane}\label{Sec:HCPlane}
+
+The Entropy-Complexity plane is the set of all possible points $(h,c)$ that can be produced by arbitrary time series analyzed with embedding dimension $D$ that are mapped on histograms of $D!$ bins.
+The time delay is irrelevant, and we consider infinitely long series.
+
+Let us consider two extreme cases:
+\begin{enumerate}[label=Case~\Roman*., align=left, leftmargin=*]
+	\item 	Strictly monotonically increasing or decreasing series produce a single pattern, so the other $D!-1$ bins of the histogram are zero. 
+	The entropy is zero, and the distance to the uniform distribution is maximal. 
+	Therefore, the complexity is zero, and such series are mapped onto the point $(0,0)$.
+	\item 	White noise produces a histogram of equal proportions $1/D!$ and maximal entropy. 
+	The distance to the equilibrium distribution is zero. 
+	Thus, such series are mapped onto the point $(1,0)$.
+\end{enumerate}
+
+\citet{SomeFeaturesoftheLMCStatisticalComplexity} proved that, for a fixed value of entropy, there are two extreme values of complexity.
+\citet{martin2006generalized}, using geometrical arguments on the space of configurations, found expressions for such boundaries.
+The lower boundary $C_{\min}$ is smooth, while the upper $C_{\max}$ is defined by $D!-1$ pieces.
+The upper boundary converges to a smooth curve when $D\to\infty$.
+
+Fig.~\ref{fig:Boundaries} shows the boundaries of the $H\times C$ plane for the embedding dimensions $D=3$ (red) $D=4$ (green), and $D=5$ (blue).
+The inset plot highlights the fine structure of the upper boundary inside the rectangle.
+The jagged structure of $C_{\max}$ increases the difficulty of finding distributions for the points in the $H\times C$ plane.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=.7\linewidth]{Figures/BoundariesPlot}
+	\caption{Boundaries of the $H\times C$ plane for dimension embeddings $D=3,4,5$.}\label{fig:Boundaries}
+\end{figure}
+
+We illustrate the use of the Entropy-Complexity plane ($H\times C$) with the following time series:
+\begin{itemize}
+	\item Colored $k$-noise, or $f^{-k}$ noise: white ($k=0$), $k=1/2$, pink ($k=1$), $k=3/2$, red ($k=2$), $k=5/2$, and $k=3$;
+	\item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
+	\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
+\end{itemize}
+In all cases, we used $D=6$ and $\tau=1$.
+Fig.~\ref{fig:Histograms} shows nine of the histograms produced by these series using the Mersenne-Twister pseudorandom number generator;
+we omitted those corresponding to the deterministic series, as they produce one and two nonzero bins.
+
+\begin{figure}[hbt]
+	\includegraphics[width=\linewidth]{Figures/h.pdf}
+	\caption{Patterns histograms of selected time series  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
+	\label{fig:Histograms}
+\end{figure}
+
+Fig.~\ref{fig:AllSystems} shows the $H\times C$ plane with the bounds for $D=6$, the time series, and the points they were mapped onto.
+The points due to $f^{-k}$ noises appear joined by dotted segments.
+It is noticeable that deterministic patterns have more complexity than random ones.
+Also, points related to $f^{-k}$ noises tend to clutter for $k<1$, having the highest entropy values, as can be seen in Fig.~\ref{fig:RightMostCorner}.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{AllSystems}
+	\caption{Eleven systems and their points in the $H\times C$ plane for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
+	\label{fig:AllSystems}
+\end{figure}
+
+Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
+In particular, notice that the point associated to white noise is not at $(1,0)$, as consequence of being obtained from a finite rather than infinite length sequence.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{RightMostCorner}
+	\caption{Representations of white noise, $f^{-1/2}$, and $f^{-1}$ noise in the $H \times C$ plane  for dimension embedding $D = 6$, time delay $\tau = 1$, and sequence length $T = \num[scientific-notation=true]{e4}$.}
+	\label{fig:RightMostCorner}
+\end{figure}
+
+Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
+Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
+
+\subsection{The Entropy-Complexity Plane in the Literature}\label{Sec:BPApplications}
+
+Initial works on the characterization of white noises with permutation entropy arose from the need to discriminate between them and chaotic maps \citep{rosso2013characterization, xiong2020complexity}.
+Notice that the logistic map has been used for pseudorandom number generation; cf.
+\citet{AnalyzingLogisticMapPseudorandomNumberGeneratorsforPeriodicityInducedbyFinitePrecisionFloatingPointRepresentation} and the references therein.
+It was found that measures of statistical complexity were able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using Information Theory descriptors with the Bandt-Pompe symbolization \citep{larrondo2013statistical, gonzalez2005statistical}.
+
+Table~\ref{Tab:Literature} presents a summary of the main works in the literature that perform analysis of non-chaotic algorithmic generators, according to their features in the $H\times C$ plane.
+We also provide the length $T$ and embedding dimension $D$ of the time series under scrutiny.
+The following algorithmic generators were analyzed:
+\begin{itemize}
+	\item Mother RNG, available in Marsaglia's website \citep[MOT,][]{marsaglia1994yet};
+	\item Multiple with carry RNG \citep[MWC,][]{marsaglia1994yet};
+	\item Combo RNG \citep[COM,][]{marsaglia1994yet};
+	\item Lehmer RNG \citep[LEH,][]{payne1969coding};
+	\item Fractional Brownian motion (fBm) and fractional Gaussian noise (fGn); see \citet{bardet2003generators};
+	\item Colored noise with power spectrum $f^{-k}$ with $k \geq 0$~\citep{larrondo2012matlab};
+	\item Linear Congruential Generator \citep[LCG,][]{knuth1997sorting}.
+\end{itemize}
+
+\begin{table}[hbt]
+	\caption{Results of the main works of white noise sequences analysis in the $H \times C$ plane.}
+	\label{Tab:Literature}
+	\centering
+	\begin{tabular}{llcccc b{5.4em}}
+		\toprule
+		Reference & PRNG & $T$ & $D$ & $H$ & $C$ & Considered random? \\ 
+		\midrule
+		\citeauthor{larrondo2013statistical} (\citeyear{larrondo2013statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{RandomNumberGeneratorsCausality} (\citeyear{RandomNumberGeneratorsCausality}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes \\
+		&  MOT & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		&  MWC & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
+		& $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+None of these works provide $p$-values or hypothesis tests for their analysis.
+The focus of the articles is finding the set of descriptors that best discriminates chaos from noise.
+The authors make assessments about the randomness of sequence on ad hoc visual inspection of the point's location in the $H\times C$ plane.
+Our work fills such a gap for finite sequences of white noise and proposes a methodology that can be extended to any other situation.
+
+\section{Proposed Method}\label{Sec:Proposal}
+
+In this section, we formalize the task of building confidence regions in the Entropy-Complexity manifold.
+Then, we present our proposal to change space through the algorithm of the principal components analysis.
+Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
+Through this new representation of the data, we calculate empirical regions with different levels of confidence.
+Finally, after calculating these regions, we build a test statistic that determines the probability that a given sequence belongs to the distribution of the points provided.
+
+\subsection{Overall Framework}\label{Sec:OverallFramework}
+
+Our methodology consists of the following steps:
+\begin{enumerate}
+	\item\label{item:Methodology1} Observe a large number of true random white noise sequences (TRWNS).
+	\item\label{item:Methodology2} Map each TRWNS onto a point in the $H\times C$ plane.
+	\item\label{item:Methodology3} Obtain the principal components of these points.
+	\item\label{item:Methodology4} Compute enclosing boxes in the principal components space.
+	\item\label{item:Methodology5} Transform the coordinates of these boxes back to the $H\times C$ plane.
+\end{enumerate}
+
+\subsection{True Random Numbers}\label{Sec:TRNG}
+
+Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
+Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
+Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
+%In this study we used two sources of real random numbers. 
+%The first is based on vacuum states to generate random quantum numbers described by \citeauthor{RNGVacuumStates}~(\citeyear{RNGVacuumStates}), the second one is based on atmospheric noise captured by a cheap radio receiver presented at \url{www.random.org}.
+
+In this study, we used two sources of true random numbers, both from the observation and measurement of physical phenomena.
+The first uses vacuum states. 
+The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
+The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
+The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
+This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
+The history of this service and other information can be found at \citet{RandomOrg}.
+
+We used \SI{54e6}{\byte} words from each physical generator, which approximately amounts \SI{200}{\mega\byte} of data.
+
+%\textcolor{red}{Fornecer mais informações. Quantos dados em bits, ou bytes, ou outra unidade, foram empregados de cada fonte, e como foram armazenados. Precisão simples, certo?}
+
+\subsection{Parameters Settings and Dataset}\label{Sec:Parameters}
+
+We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
+We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
+On the other hand, we found two relevant variables: 
+the length of the sequence 
+and the embedding dimension.
+We, thus, employed the following factors:
+\begin{itemize}
+	\item Sequence length $T\in\mathcal T=\{ \num[scientific-notation=true]{e3}, \num[scientific-notation=true]{5 e4}\}$,
+	\item Embedding dimension $D\in\mathcal D=\{3, 4, 5, 6\}$.
+	%,and
+	%\item Time delay $\tau=\{1, 10, 30, 50\}$.
+\end{itemize}
+and kept $\tau=1$, which is the most frequently used option.
+The values of $D$ are within the range recommended in the literature~\citep{PermutationEntropyBandtPompe}.
+
+Using this parametric space, we analyzed the different degrees of information captured by the ordinal patterns formed.
+For the construction of the confidence regions presented, we used:
+\begin{itemize}
+	\item A set of \num{104596} points in the $H \times C$ plane, corresponding to sequences of length $T = 1000$, for each value of $D\in \mathcal D$, and
+	\item  a set of \num{2093} points in the $H \times C$ plane, corresponding to sequences of length $T = 50000$, for each value of $D \in \mathcal D$.
+\end{itemize}
+
+We used the \texttt R platform \citep[][v.~4.0.3]{Rmanual} for data generation and analyses, and the \texttt{ggplot2} library \citep{ggplot2Wickman} for generating the plots.
+
+\begin{comment}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{Figures/Points-PDF.png}
+\caption{White noise samples considered during the construction of the proposed confidence regions.}
+\label{fig:white-noise}
+\end{figure}
+
+\end{comment}
+
+\subsection{Empirical Confidence Regions and $p$-values}\label{confidenceRegions}
+
+%As we do not know the joint probability distribution of the pair $(h, c)$ for a sequence of random variables collectively independent and identically distributed according to a uniform law, studies involving classical bi-variate analysis, linear regression, and generalized linear models become unfeasible.
+
+Our first approaches to analyzing sequences of points in the $H\times C$ plane produced by TRWNS verified that they, and usual transformations, are far from bivariate Gaussian and generalized Hyperbolic distributions \Mycite{MultivariateDistributionModelswithGeneralizedHyperbolicMargins}.
+Different types of regression models of $C$ explained by $H$ did not produce acceptable results.
+Thus, we adopted a non-parametric approach and made an empirical analysis of the data obtained from physical sources for using them as our reference in the search for confidence regions and $p$-values.
+%Therefore, for the construction of our proposal, we adopted a non-parametric approach, making an empirical analysis of data obtained from physical sources and using them as our reference in the search for confidence regions.
+
+%The set of all feasible pairs in the $H \times C$ plane is found in a compact subset of $\mathbbm{R}^2$, which has limits with explicit expressions for the boundaries of this closed manifold, dependent only on the dimension of the probability space considered, that is $D!$ in the traditional Bandt-Pompe method~\citep{martin2006generalized}.
+%Due to such quotas, some limitations are generated, such as the absence of a representative distance metric and the difficulty of proposing confidence regions.
+%In view of this, it is necessary to apply an orthogonal projection in the data for a new two-dimensional coordinate system to solve these restrictions.
+%A classic proposal in these categories of problems is the principal component analysis algorithm~\citep{wold1987principal}.
+
+Let $\utilde{x} =(x_1, x_2, \dots, x_N)$ be $N$ times series of length $T$, and define an embedding dimension $D$.
+In the sequel, whenever possible, we will omit $T$ and $D$.
+For each $n=1,2,\dots, N$, the time series $x_n$ is mapped onto the point $(h_n,c_n)$ in the $H\times C$ plane, thus $\utilde{hc}=\big((h_1,c_n), (h_2,c_2), \dots, (h_N,c_N)\big)$ are the points that correspond to the $N$ time series.
+Fig.~\ref{fig:Methodology1} illustrates this step.
+We will obtain confidence regions and $p$-values from $\utilde{hc}$.
+
+The first step consists in finding and applying the principal components transformation to $\utilde{hc}$.
+With this, we obtain the set of uncorrelated points $\utilde{uv}=\big((u_1,v_1), (u_2,v_2),\dots,(u_N,v_N)\big)$, in which $u_n$ and $v_n$ are the first and second principal components of $h_n$ and $v_n$, respectively.
+This projection allows us to obtain a ``central'' point of the data set, around which we will build a rectangular box containing \SI{100}{\minusalphapercent} of the observations.
+Such box is a variation of the bagplot \citep{TheBagplotaBivariateBoxplot}.
+Notice that finding the smallest box that encloses $k$ out of $N$ points is difficult; cf.\ the work by \citet{SmallestKEnclosingRectangleRevisited}.
+
+For simplicity, and without loss of generality, assume $N$ is odd.
+\begin{enumerate}
+	\item Find the indexes that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order: $\bm r=(r_1,r_2,\dots,r_N)$, i.e., $u_{r_1}$ is the minimum value, and $u_{r_N}$ is the maximum value.
+	\item\label{item:Median} Find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$.
+Apply the inverse principal components transformation, and obtain $\bm P'=(h',v')$.
+Call the corresponding time series ``emblematic time series.''
+	\item\label{item:Point1} Find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$.
+	\item\label{item:Point2} Find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$.
+	\item\label{item:Point3} The values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively.
+	\item\label{item:Point4} The bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this values $v_{\min}$.
+	\item\label{item:Point5} The top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$.
+	\item The corners of the box are 
+	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
+	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
+	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
+	$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$.
+	\item\label{item:BoxHxC} Apply the inverse principal components transformation to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$.
+\end{enumerate}
+
+Fig.~\ref{fig:methodology} illustrates these steps.
+%
+Fig.~\ref{fig:Methodology1} shows the points produced by TRWNS in the $H\times C$ plane.
+The blue box includes a certain percentage of points, with sides parallel to the $H$ and $C$ axes.
+The area in the $H\times C$ plane overestimates the desired proportion and may include ``unacceptable'' points.
+%
+Fig.~\ref{fig:Methodology2} shows the previous points projected onto the principal components space (steps~\ref{item:Median} to~\ref{item:Point5}).
+The red box includes the same percentage of desired points, with axes parallel to the first and second principal components.
+We highlighted in red the point whose first principal component is the median of the observed values.
+%
+Fig.~\ref{fig:Methodology3} shows the result of projecting back the red box from the principal components space to the $H\times C$ plane (step~\ref{item:BoxHxC}).
+The comparison of the red and blue boxes shows that the area has been reduced, thus improving the test's power.
+
+\begin{figure}[hbt]
+	\centering
+	%    \includegraphics[width=\linewidth]{Figures/Methodology.pdf}
+	\subfloat[Mapping true white noise random sequences onto the $H\times C$ plane.\label{fig:Methodology1}]{\includegraphics[width=.33\linewidth]{step1}}
+	\subfloat[Transformation of the points in the $H\times C$ plane by Principal Components, and determination of minimal boxes.\label{fig:Methodology2}]{\includegraphics[width=.33\linewidth]{step2}}
+	\subfloat[Inverse transformation from the Principal Components plane to the $H\times C$ plane.\label{fig:Methodology3}]{\includegraphics[width=.33\linewidth]{step3}}
+	\caption{Outline of the methodology used for the construction of the confidence regions.}
+	\label{fig:methodology}
+\end{figure}
+
+Algorithm~\ref{Algo:ConfidenceRegions} provides details on how we obtain the confidence regions, defined by a set of points $\bm P_1, \bm P_2, \bm P_2, \bm P_4$, for each $D\in \mathcal D$, each $T\in \mathcal T$, and each significance level $\alpha$.
+We also obtain the ``emblematic point'' $\bm P'$, a kind of median point in the $H\times C$ plane for each situation.
+
+\begin{algorithm}[hbt]
+	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+	\Input{A data base of true random values}
+	\Input{The desired values of embedding dimension $\mathcal D$, sequence length $\mathcal T$, and confidence levels $\mathcal A$}
+	\Output{Confidence regions as points in the $H\times C$ plane}
+	\For{each $D\in \mathcal D$}{
+		\For{each $T\in \mathcal T$}{
+			\For{each $n=1,2,\dots,N$}{
+				build the time series $p_n$ with unused values from the data base\;
+				compute the point $(h_n,c_n)$ in the $H\times C$ plane that corresponds to $p_n$\; 
+			}
+			obtain $\text{PC}(D,T)$, the principal components transformation based on the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and its inverse $\text{PC}^{-1}(D,T)$\;
+			%
+			apply $\text{PC}(D,T)$ to the points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$, and obtain $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$\;
+			%
+			find the indexes $\bm r=(r_1,r_2,\dots,r_N)$ that sort the values of the first principal component $\bm u=(u_1,u_2,\dots,u_N)$ in ascending order\;
+			%
+			find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
+			%
+			apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to $(u,v)$, and obtain $\bm P'=(h',v')$; call the corresponding time series ``emblematic time series''\;
+			\Return{$\bm P'$}\;
+			%
+			\For{each confidence level $\alpha \in \mathcal A$}{
+				find the point $(u,v)$ whose first principal component is the quantile $\alpha/2$: $(u_{r_{[N\alpha/2]}}, \cdot)$\;
+				%
+				find the point $(u,v)$ whose first principal component is the quantile $1-\alpha/2$: $(u_{r_{[N(1-\alpha/2)]}}, \cdot)$\;
+				%
+				the values $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ are the rightmost and leftmost bounds of the box, respectively\;
+				%
+				the bottom bound of the box is the smallest second principal component value whose first principal component is at least $u_{r_{[N\alpha/2]}}$; denote this value $v_{\min}$\;
+				%
+				the top bound of the box is the largest second principal value whose first principal component is at most $u_{r_{[N(1-\alpha/2)]}}$; denote this value $v_{\max}$\;
+				%
+				the corners of the box are 
+				$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
+				$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
+				$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
+				$(u_{r_{[N(1-\alpha/2)]}},v_{\max})$\;
+				%
+				apply the inverse principal components transformation $\text{PC}^{-1}(D,T)$ to these corners obtaining $\bm P_1=(h_{v_1}, c_{v_1})$, $\bm P_2=(h_{v_2},h_{v_2})$, $\bm P_3=(h_{v_3}, c_{v_3})$ and $\bm P_4=(h_{v_4},c_{v_4})$\;
+				\Return{$\bm P_1$, $\bm P_2$, $\bm P_3$, $\bm P_4$}\;
+			}
+		}
+	}
+	\caption{Determination of confidence regions and emblematic time series}\label{Algo:ConfidenceRegions}
+\end{algorithm}
+
+%The visual representation of the proposed technique can be seen in Fig.~\ref{fig:methodology}.
+
+These confidence regions obtained provide a powerful tool to make binary assessments about the adequacy of a given time series $\bm x$ to the null hypothesis $\mathcal H_0$ that it is white noise.
+More generally, we are interested in obtaining the $p$-value of $\bm x$ under $\mathcal H_0$.
+We present a procedure to obtain an approximate $p$-value based on the evidence collected to build the confidence regions.
+
+The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
+We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
+We use $N$ TWNRS of size $T$, compute their points in the $H\times C$ plane, and project them to the corresponding principal components space.
+We then do the same with $\bm x$, and obtain a new point $(u_x,v_x)$.
+The closer $\bm x$ is to the emblematic time series, the larger its $p$-value.
+Assume that the emblematic time series is represented by $(u,v)$ in the principal components space.
+We measure this closeness by building a box around $(u_x,v_x)$ that contains $(u,v)$; assume that $u_x>u$, then:
+\begin{enumerate}
+	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
+By definition, $\eta_u\geq 1/2$.
+	%
+	\item the left side of the box is the $1-\eta_u$ quantile of $\utilde u$.
+	%
+	\item the top side of the box is the smallest $v_j$ which is larger that $v_x$; assume it corresponds to the quantile $\eta_v$ of $\utilde v = (v_1,v_2,\dots, v_N)$. By definition, $\eta_v\geq 1/2$.
+	%
+	\item the bottom side of the box is the $1-\eta_v$ quantile of $\utilde v$.
+\end{enumerate}
+Fig.~\ref{fig:methodologyPvalue} illustrates theses steps.
+
+The definition of the box for the case $u_x<u$ follows naturally, and is described in Algorithm~\ref{Algo:p-value}.
+With this approach, we obtain the smallest box that (i)~contains the new point, and (ii)~is defined by observed points from TRWNS.
+
+Such boxes are less prone to distortions in this space since the distribution of the points becomes less asymmetric than in the $H\times C$ plane; cf.\ Fig.~\ref{fig:HC-PCA}.
+Algorithm~\ref{Algo:p-value} shows the details.
+
+\begin{figure}[hbt]
+	\centering
+	\subfloat[Points produced by TRWNSs in the space of principal components.\label{fig:v1}]{\includegraphics[width=.33\linewidth]{PvalueStep1}}
+	\subfloat[Points whose first principal component is the median (red) and quantiles of order $\eta_u$ and $1-\eta_u$ (green).\label{fig:methodologyPvalue2}]{\includegraphics[width=.33\linewidth]{PvalueStep2}}
+	\subfloat[The $p$-value of the new point is the proportion of points outside the box.\label{fig:methodologyPvalue3}]{\includegraphics[width=.33\linewidth]{PvalueStep3}}
+	\caption{Outline of the methodology used to calculate the $p$-value. The new point is denoted as a crossed circle.}
+	\label{fig:methodologyPvalue}
+\end{figure}
+
+\begin{comment}
+The empirical $p$-value of $\bm x'$ for the null hypothesis is given by the percentage of points outside the lowest confidence region obtained by the reference points to which $\bm x'$ belongs.
+Therefore, it can be achieved by the following steps:
+\begin{enumerate}
+\item Compute $(h',c')$ the point in the $H\times C$ plane produced by $\bm x'$;
+\item Compute $b_{T,D}(\bm x')$: the smallest box which contains $(h',c')$ using the $M$ reference points;
+\item The empirical $p$-value of $\bm x'$ is obtained by the percentage of reference points outside $b_{T,D}(\bm x')$.
+\end{enumerate}
+Thus, we can verify that:
+\begin{itemize}
+\item the smallest $b_{T,D}(\bm x')$ is observed when $(h',c')$ ``coincides'' with the point produced by the emblematic sequence, in other words, point whose first principal component is the median of the $M$ reference points, and
+\item the largest box is any box associated to $(h',c')$ ``outside'' the largest box produced by the $M$ reference points.
+\end{itemize}
+Assuming the critical value $\alpha = 0.05$, we obtain:
+\begin{equation*}
+p-\text{value} \geq \alpha, \text{ the null hypothesis should not be rejected}.
+\end{equation*}
+\end{comment}
+
+\begin{algorithm}[hbt]
+	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+	\Input{The sequence $\bm x$ of length $T$ to be contrasted to the null hypothesis $\mathcal H_0$ that it is adherent to white noise}
+	\Input{The embedding dimension $D$}
+	\Input{$N$ points $(h_1,c_1),(h_2,c_2),\dots,(h_N,c_N)$ of true white noise series of length $T$;
+		the principal components tranformation $\text{PC}(D,T)$ induced by these points;	
+		the points projected onto the $H\times C$ plane: $(u_1,v_1),(u_2,v_2),\dots,(u_N,v_N)$}
+	\Output{An approximate $p$-value}
+	find the point $(u,v)$ whose first principal component is the median: $(u_{r_{(N+1)/2}}, \cdot)$\;
+	find the point $(h,c)$ of the sequence $\bm x$\;
+	find the projection $(u_x,v_x)$ of $(h,c)$ onto the principal components space using $\text{PC}(D,T)$\;	
+	\eIf{$u_x > u$}
+	{ $u_{r_{[N(1-\alpha/2)]}}$ is defined as the smallest element larger than $u_x$\;
+		$u_{r_{[N\alpha/2]}} \leftarrow 2u - u_{r_{[N(1-\alpha/2)]}}$\;
+	}
+	{
+		\eIf{$u_x < u$}
+		{ $u_{r_{[N\alpha/2]}}$ is the largest minor element of $u_x$\;
+			$u_{r_{[N(1-\alpha/2)]}} \leftarrow 2u - u_{r_{[N\alpha/2]}}$\;
+		}
+		{ $u_{r_{[N\alpha/2]}}$ and $u_{r_{[N(1-\alpha/2)]}}$ is equal to $u$, the median point of the first principal component\; 
+		}
+	}
+	obtain the maximum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\max}$\;
+	obtain the minimum values of the second component whose values of the first principal component are at least $u_{r_{[N\alpha/2]}}$ and at most $u_{r_{[N(1-\alpha/2)]}}$ and denote it $v_{\min}$\;
+	the corners of the box $b_{\alpha}(h,c)$ are 
+	$(u_{r_{[N\alpha/2]}}, v_{\min})$, 
+	$(u_{r_{[N\alpha/2]}}, v_{\max})$, 
+	$(u_{r_{[N(1-\alpha/2)]}}, v_{\min})$ and 
+	$(u_{r_{[N(1-\alpha/2)]}}, v_{\max})$\;
+	%find $b_{T,D}(h,c)$: the smallest box centered at $(h',c')$ which contains $\text{PC}(D,T)(h,c)$\;
+	count $n_{\bm x}$, the number of points out of the $N$ points which belong to $b_{\alpha}(h,c)$\;
+	\Return{$1-n_{\bm x}/N$}
+	\caption{Determination of the $p$-value of the sequence $\bm x$ under $\mathcal H_0$}\label{Algo:p-value}
+\end{algorithm}
+
+\section{Results}\label{Sec:Results}
+
+\subsection{Empirical confidence regions}
+
+Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
+of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent},
+for $D=3,4,5,6$ and $N=1000,50000$, .
+The points are presented counterclockwise, starting with the one with the largest complexity.
+
+\begin{comment}
+\begin{table}[hbt]
+\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
+\centering
+\begin{tabular}{rcllllllll}
+\toprule
+& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
+& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
+$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
+$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
+& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+\end{tabular}
+\end{table}
+\end{comment}
+
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 1000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
+		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
+		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
+		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
+		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
+		\midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
+		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
+		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
+		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
+		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
+		\midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
+		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
+		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
+		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
+		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
+		\midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
+		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
+		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
+		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
+		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}[hbt]
+	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
+	\centering
+	\begin{tabular}{rccccc}
+		\toprule
+		%& & \multicolumn{4}{c}{$N$}\\ 
+		%\cmidrule(lr){3-6}
+		& & \multicolumn{4}{c}{$N = 50000$}\\ 
+		\cmidrule(lr){3-6} 
+		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
+		\cmidrule(lr){3-3} 
+		\cmidrule(lr){4-4} 
+		\cmidrule(lr){5-5} 
+		\cmidrule(lr){6-6} 
+		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
+		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
+		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
+		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
+		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
+		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
+		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
+		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
+		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
+		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
+		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
+		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
+		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
+		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
+		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
+		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
+		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
+		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
+		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
+		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
+	\end{tabular}
+\end{table}
+
+Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
+We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
+
+\begin{figure}[hbt]
+	\centering
+	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
+	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
+	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
+	\label{fig:HC-PCA}
+\end{figure}
+
+The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.
+
+Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
+They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
+As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
+Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{PCA-hist-50k}
+	\caption{Histograms of the first principal component for $D=3,4,5,6$}
+	\label{fig:PCA-Hist}
+\end{figure}
+
+\subsection{Test Size}
+
+We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
+Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
+show the results.
+
+On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
+On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$.
+In contrast, we expected \SI{1}{\percent} of rejection.
+This might be because, in this case, the condition $D!\ll T$ is not respected.
+Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.
+
+%
+%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
+%
+%For short series, $T = 1000$, and $D = 3$ 
+%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
+%
+%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
+%A reasonable explanation for this event is given in the choice of the parameter itself.
+%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
+
+\begin{table}[hbt]
+	\centering
+	\caption{Empirical sizes of the test}
+	\label{tab:result1}
+	\begin{tabular}{*{3}rr}
+		\toprule
+		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
+		%& $p$-value\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		1000 & 3 & $0.98$ & $1.00$\\
+		& 4 & $0.98$ & $0.96$\\
+		& 5 & $1.00$ & $0.94$\\
+		& 6 & $0.97$ & $0.87$\\
+		\cmidrule(lr){1-4} 
+		50000 & 3 & $0.97$ & $0.96$\\
+		%& $0.47856$\\
+		& 4 & $0.94$ & $0.95$\\
+		%& $0.47555$\\ 
+		& 5 & $0.97$ & $0.96$\\ 
+		%& $0.48512$\\ 
+		& 6 & $0.98$ & $0.99$\\ 
+		%& $0.48058$\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
+	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
+	\caption{New $100$ TRWNS and confidence regions.}
+	\label{fig:RNG}
+\end{figure}
+
+We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.
+
+\subsection{Test Power}
+
+\subsubsection{$H_1$: Correlated Noise}
+
+We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
+Several studies in the literature have used this approach for identifying and characterizing randomness.
+
+Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
+Recall that the emblematic time was chosen as the most representative of the data set.
+We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.
+
+%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
+As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.
+
+Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
+At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
+As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
+
+Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
+We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
+Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
+The same holds for all $k>3/10$.
+
+\begin{figure}
+	\centering
+	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
+	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
+		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
+	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
+	\label{fig:correlation}
+\end{figure}
+
+\subsubsection{$H_1$: Patch of Deterministic Function}
+
+Consider the times series of length $T$ comprised of $T-[c100]$ white noise observations $x_1,x_2,\dots, x_{T-[c100]}$ followed by the signal $y_{T-[c100]+1}, y_{T-[c100]+2}, \dots, y_T$, in which $0\leq c \ll 1$ is the percentage of contamination.
+We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
+Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such a contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
+The Figure also shows the confidence region at \SI{99}{\percent}.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=.7\linewidth]{Figures/PointsPatchedIncreasingFunction}
+	\caption{Effect of patching an increasing function at different levels to a white noise sequence.}\label{Fig:PointsPatchedIncreasingFunction}
+\end{figure}
+%%% The code that produces this figure starts at line 221, file "container_function.R"
+
+The original point is displaced, at all levels of contamination, to a region with smaller entropy and larger complexity.
+When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
+The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.
+
+It is worth noticing that a test based solely on the entropy would have less power.
+In this case, the complexity component enables the test to reject the null hypothesis at small contamination percentages.
+
+\subsection{Revisiting the White Noise Hypothesis in the Literature}
+
+In this section, we compare the performance of our test with that of 
+previous analyses that employ the Entropy-Complexity plane.
+To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
+Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
+We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
+
+\begin{table}
+	\caption{Results of the sequences generated by the main PRNGs in the literature. 
+		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+	\label{Tab:LiteratureComparations}
+	\centering
+	\begin{tabular}{cccc}
+		\toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		MOT & 3 & 0.305 & NR\\
+		& 4 & 0.572 & NR\\ 
+		& 5 & 0.455 & NR\\ 
+		& 6 & 0.508 & NR\\ 
+		\cmidrule(lr){1-4}
+		MWC & 3 & 0.501 & NR\\
+		& 4 & 0.477 & NR\\ 
+		& 5 & 0.496 & NR\\ 
+		& 6 & 0.496 & NR\\ 
+		\cmidrule(lr){1-4}
+		COM & 3 & 0.123 & NR\\
+		& 4 & 0.002 & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		\cmidrule(lr){1-4}
+		LEH & 3 & 0.531 & NR\\
+		& 4 & 0.515 & NR\\ 
+		\bottomrule
+	\end{tabular}
+	\begin{tabular}{|cccc}
+		\toprule
+		Algorithm & 
+		\multicolumn{1}{c}{$D$} & 
+		$p$-value &
+		HC-PCA\\
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-2}
+		\cmidrule(lr){3-3}
+		\cmidrule(lr){4-4}
+		LEH & 5 & 0.495 & NR\\ 
+		& 6 & 0.501 & NR\\ 
+		\cmidrule(lr){1-4}
+		fGn & 3 & 0.521 & NR\\
+		& 4 & 0.519 & NR\\ 
+		& 5 & 0.498 & NR\\ 
+		& 6 & 0.470 & NR\\
+		\cmidrule(lr){1-4}
+		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		%\cmidrule(lr){1-4}
+		$f^{-k}$ & 3 & 0.482 & NR\\
+		& 4 & 0.520 & NR\\ 
+		& 5 & 0.513 & NR\\ 
+		& 6 & 0.508 & NR\\
+		\cmidrule(lr){1-4}
+		LCG & 3 & 0.009 & R\\ 
+		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+Comparing Tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we see that our test captures adequately the random dynamics of the sequences produced by most of the analyzed generators.
+
+It is noteworthy that the generator Combo RNG sequences only pass our white noise test for $D = 3$.
+In higher embedding dimensions, as we consider longer words, the sequences produced by this generator are not labeled as white noise.
+
+\section{Conclusions}\label{Sec:Conclusions}
+
+We presented and evaluated the first test for white noise in the  Entropy-Complexity plane.
+Our proposal is based on two stages:
+(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
+(2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
+We obtained the TWNRS with data from physical devices.
+
+Our test has a good size, mostly with long TWNRS.
+We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
+
+Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
+With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.
+
+\section{Reproducibility and Replicability}\label{Sec:code}
+
+Following the recommendations provided by \cite{ABadgingSystemforReproducibilityandReplicabilityinRemoteSensingResearch}, we make the text, source code, and data used in this study available at the \textit{Confidence-Regions} repository \url{https://github.com/EduardaChagas/ConfidenceRegions}.
+
+\section{Acknowledgements}\label{Sec:acknowledgements}
+
+This work was partially funded by the Coordination for the Improvement of Higher Education Personnel (CAPES) and National Council for Scientific and Technological Development (CNPq).
 

### 2021-10-24 Code/Container_function.R

@@ -260,3 +260,50 @@ ggsave(file="../../Confidence Regions/Reports/JOURNAL - Confidence Regions/Figur
 
 # Vamos reportar apenas o resultado de acrescentar ao final uma função crescente
 
+# Não sou gato, mas a curiosidade...
+
+x.increasing <- (1:1000)/1000
+percentage.patch <- seq(.01, 1, by=.01)
+Experiment.Increasing <- data.frame(h.patched=rep(0, 100),
+                                    c.patched=rep(0, 100),
+                                    pvalue.patched=rep(0, 100))
+for(count in 1:100){
+  patch <- percentage.patch[count]
+  
+  n.tail <- round(patch*1000)
+  x.patched <- c(x[1:(1000-n.tail)], 
+                 x.increasing[(1000-n.tail+1):1000])
+  probs.patched <- bandt.pompe(x.patched, 6, 1)
+  Experiment.Increasing$h.patched[count] <- shannon.entropy.normalized(probs.patched)
+  Experiment.Increasing$c.patched[count] <- Ccomplexity(probs.patched)
+  Experiment.Increasing$pvalue.patched[count] <- calculate.p.value.samples(
+    data.frame(H = Experiment.Increasing$h.patched[count], 
+               C = Experiment.Increasing$c.patched[count]), 
+    1000, 6)
+}
+
+Experiment.Increasing$percentage <- percentage.patch*100
+
+ggplot(Experiment.Increasing, aes(x=h.patched, y=c.patched)) +
+  geom_point() + 
+  theme_minimal()
+
+p +
+  geom_point(data=Experiment.Increasing, aes(x=h.patched, 
+                                             y=c.patched), col="red", size=2)
+### Normalization constant
+
+maxQprime <- function(D) {
+  dfactorial <- factorial(D)
+  return(
+    -2*(
+      (dfactorial+1)/dfactorial*log(dfactorial+1)-
+        2*log(2*dfactorial)+
+        log(dfactorial)
+    )
+  )
+}
+
+D <- 3:8
+
+plot(D, maxQprime(D))

### 2021-10-25 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Reinforces the importance of the HC-PCA column

@@
 Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
+We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR), given the p-value obtained by the HC-PCA test. 
+The aim of this experiment is to investigate the robustness of the confidence regions generated by TRWNS in samples from different randomness generators.
 
@@
 	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+		The sequences have length $T=\num[scientific-notation = true]{5 e4}$ and the HC-PCA column presents the test results considering the $\SI{5}{\percent}$ significance level.}
 	\label{Tab:LiteratureComparations}

### 2021-10-25 Code/Container_function.R
Pequeno teste com Q'max

@@ -291,7 +291,8 @@ ggplot(Experiment.Increasing, aes(x=h.patched, y=c.patched)) +
 p +
   geom_point(data=Experiment.Increasing, aes(x=h.patched, 
                                              y=c.patched), col="red", size=2)
-### Normalization constant
+
+### Normalization constant (just to check it makes sense)
 
 maxQprime <- function(D) {
   dfactorial <- factorial(D)

### 2021-10-25 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Update IT-ConfidenceRegionsR1.tex

--- 2021-10-24 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
@@
 	Our test is based on true white noise sequences obtained from physical devices.
-The proposed methodology provides consistent results, 
-managing to assess sequences of true random samples as random (adequate test size), 
-rejecting correlated sequences (sound test power), and
-capturing the randomness of generators previously analyzed in the literature.
+	The proposed methodology provides consistent results: 
+	it assesses sequences of true random samples as random (adequate test size), 
+	rejects correlated and contaminated sequences (sound test power), and
+	captures the randomness of generators previously analyzed in the literature.
 	\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
@@
 
-The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
-Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+The seminal paper has received \num{2,160} citations from articles published in \num{780} venues indexed by the Web of Science.
+Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the citing articles).
 There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
@@
 two in the \textit{Journal of Time Series Analysis} and in 
-\textit{Theory and Applications of Time Series Analysis},
-and each of the remaining ten appeared in a different journal.
+\textit{Theory and Applications of Time Series Analysis}.
+Furthermore, each of the remaining ten appeared in a different journal.
 Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
@@
 
-With the knowledge of the expected variability of such points, according to the underlying dynamics, we can make hypothesis tests for a wide variety of models.
+With the knowledge of the expected variability of such points, we can make hypotheses tests for a wide variety of models according to the underlying dynamics.
 Results in this direction can be found in the literature.
@@
 Motivated by previous works, in this paper, we advance the state-of-the-art providing the first test for white noise points in the $H\times C$ plane.
-In this proposal, the input is a sequence of true random observations generated by a physical-based procedure. 
-We obtain the confidence regions by performing an orthogonal projection of the data onto the space of principal components, thus eliminating the restrictions imposed by the bounded space of the Entropy-Complexity plane.
+We used sequences of true random observations generated by a physical-based procedure to produce clouds of points. 
+We then project these points onto their principal components, find the regions in this representation, and transform them back to the Entropy-Complexity plane.
+In this way, we circumvent the restrictions imposed by this 2D bounded manifold.
+We also provide an algorithm that, using geometrical arguments, computes the empirical $p$-value of a sequence under the white noise null hypothesis.
 Our contributions can be summarized as follows:
@@
 	\item We evaluate this test's size by analyzing random sequences generated by physical procedures and pseudorandom generators (PRNGs).
-	\item We verify the test's power contrasting correlated noise time series, and white noise series patched with a deterministic signal.
+	\item We verify the test's power contrasting (i)~correlated noise time series and (ii)~white noise series patched with a deterministic signal.
 \end{itemize}
@@
 
-In our work, we consider the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
+Our work considers the ordinal patterns formed from true white noise sequences (TWNS) using the Bandt and Pompe symbolization.
 Such sequences are then mapped in the two-dimensional plane of Information Theory descriptors, formed by the Permutation Entropy and the Statistical Complexity.
@@
 
-The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as a more adequate measure of such a distance:
+The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as an adequate measure of such a distance:
 \begin{equation}
@@
 Fig.~\ref{fig:RightMostCorner} shows the rightmost lower corner of the $H\times C$ plane, emphasizing the location of the white ($k=0$), $k=1/2$, and pink ($k=1$) noises.
-In particular, notice that the point associated to white noise is not at $(1,0)$, as consequence of being obtained from a finite rather than infinite length sequence.
+In particular, notice that the point associated with white noise is not at $(1,0)$, resulting from a finite rather than infinite length sequence.
 
@@
 
-Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high values of entropy and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
-Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
+Due to the infinitude of white noise sequences, although these sequences have the characteristic of presenting high entropy values and low statistical complexity, their points will not necessarily be located in $(1, 0)$, but in a surrounding region.
+Our study focuses on assessing pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
 
@@
 The focus of the articles is finding the set of descriptors that best discriminates chaos from noise.
-The authors make assessments about the randomness of sequence on ad hoc visual inspection of the point's location in the $H\times C$ plane.
+The authors assess the randomness of sequences by ad hoc visual inspection of the point's location in the $H\times C$ plane.
 Our work fills such a gap for finite sequences of white noise and proposes a methodology that can be extended to any other situation.
@@
 Then, we present our proposal to change space through the algorithm of the principal components analysis.
-Our goal is to find a latent space representative of the data without the restrictions of the $H\times C$ plane's boundaries.
+Our goal is to find a space to represent the data without the $H\times C$ plane's boundaries restrictions.
 Through this new representation of the data, we calculate empirical regions with different levels of confidence.
@@
 Random numbers are used in many fields, from gambling to cryptography, to guarantee a secure, realistic, or unpredictable behavior. 
-Pseudorandom results can be achieved by software in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
+Software can produce pseudorandom sequeces in a deterministic way, but some applications need actual random numbers (despite the somewhat elusive nature of actual randomness).
 Randomness can be observed in unpredictable real-world phenomena like cathodic radiation or atmospheric noise.
@@
 The first uses vacuum states. 
-The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors working together adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
+The setup consists of an ordinary laser source to generate a local oscillator (LO), a half-wave plate, a polarizing beamsplitter (BPS), and two balanced detectors, adding or subtracting the photocurrents results in a quadrature measurement of the LO or vacuum state.
 The distribution of the vacuum state is binned into $2^n$ equal parts (bins of the same size), assigning a fixed bit combination of length $n$ to each sample point in a given bin \citep{RNGVacuumStates}.
 The second one employs atmospheric noise captured by a cheap radio receiver with no filter for unwanted static sounds caused by atmospheric noise.
-This generator was implemented over a distributed setup with radios located at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
+This generator was implemented over a distributed setup with radios at different geographical locations sending random bits to a cloud server that processes data and hosts the values.
 The history of this service and other information can be found at \citet{RandomOrg}.
@@
 
-We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in the construction of empirical confidence regions.
-We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, in the sequel, we did no consider $\tau$ as a determining factor.
+We conducted an ablation study to identify the influence of the parameters $T$, $D$, and $\tau$ in constructing empirical confidence regions.
+We verified that the results involving the time delay parameter variation did not show significant differences in repeated experiments; therefore, we did not consider $\tau$ as a determining factor in the sequel.
 On the other hand, we found two relevant variables: 
@@
 
-The procedure operates on the principal components space and consists of measuring the closeness between the ``emblematic point'' and the observed point.
+The procedure operates on the principal components space and measures the closeness between the ``emblematic point'' and the observed point.
 We are given a time series $\bm x$ of size $T$, and we want its $p$-value when contrasted with TWNRS of the same size at embedding dimension $D$.
@@
 Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
-We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.
+We also show the projection of the $H \times C$ plane boundaries in this space and the median of each data set, the latter represented as red dots.
 
@@
 Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
-They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
+They tend to concentrate close to $(1,0)$ in the $H\times C$ plane.
 As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
@@
 
-We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
+We assessed the power of the test by contrasting time series with different correlation structures (under the $f^{-k}$ model) in the $H \times C$ plane.
 Several studies in the literature have used this approach for identifying and characterizing randomness.
@@
 At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
-As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.
+As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series becomes progressively more predictable.
 
@@
 We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
-Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such a contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
+Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
 The Figure also shows the confidence region at \SI{99}{\percent}.
@@
 
-The original point is displaced, at all levels of contamination, to a region with smaller entropy and larger complexity.
+At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
 When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
@@
 
-\subsection{Revisiting the White Noise Hypothesis in the Literature}
+\subsection{Revisiting the White Noise Hypothesis in the literature}
 
@@
 Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
-We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
+We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR), given the $p$-value obtained by our test. 
+This experiment investigates the robustness of the confidence regions generated by TRWNS in samples from different randomness generators.
 
@@
 	\caption{Results of the sequences generated by the main PRNGs in the literature. 
-		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
+		The sequences have length $T=\num[scientific-notation = true]{5 e4}$. 
+		The ``Decision'' of rejecting (R) or not (NR) is at the $\SI{5}{\percent}$ significance level.}
 	\label{Tab:LiteratureComparations}
@@
 		$p$-value &
-		HC-PCA\\
+		Decision\\
 		\cmidrule(lr){1-1}
@@
 Our proposal is based on two stages:
-(1)~building nonparametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
+(1)~building non-parametric empirical confidence regions in the principal components space and mapping these boxes back to the $H\times C$ plane.
 (2)~computing an approximate $p$-value for a given sample by comparing it with points produced by true white noise random sequences (TWNRS).
@@
 
-Our test has a good size, mostly with long TWNRS.
+Our test has good size, mostly with long TWNRS.
 We also determined the power of our test for the alternative hypothesis of correlated $f^{-k}$ noise and found that it rejects the null hypothesis ($k=0$) for $k>3/10$.
 
-Although our work focuses on the study of short sequences, we were able to capture the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
+Although our work focuses on the study of short sequences, we captured the random behavior of well-known pseudorandom number generators already analyzed in the literature. 
 With this, we verified the adequacy of our technique as it is capable of detecting correlation structures.

### 2021-10-25 Reports/Journal - Confidence Regions/Response-R1.tex
Ready for first round with authors

@@
 We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
-	Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such a contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
+Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
 The Figure also shows the confidence region at \SI{99}{\percent}.
@@
 
-	The original point is displaced, at all levels of contamination, to a region with smaller entropy and larger complexity.
-	When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
+At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
+When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{1}{\percent} level of significance; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
 The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.

### 2021-10-25 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Ready for first round with authors

@@
 At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
-When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
+When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{1}{\percent} level of significance; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
 The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.

### 2021-10-28 Reports/Journal - Confidence Regions/IT-ConfidenceRegions.tex
Reorganized
Update IT-ConfidenceRegions.tex

--- 2021-10-09 Reports/Journal - Confidence Regions/IT-ConfidenceRegions-V1.tex
@@
 \author[1]{Eduarda T.\ C.\ Chagas}
-\author[2,3]{Marcelo Queiroz}
+\author[2,3]{Marcelo Queiroz-Oliveira}
 \author[4]{Osvaldo A.\ Rosso}
@@
 \author[2]{Cristopher G.\ S. Freitas}
-\author[2]{Leonardo V.\ Pereira}
-\author[4]{Alejandro C.\ Frery}
+\author[5]{Alejandro C.\ Frery}
 
@@
 		\begin{abstract}
-The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
-by computing Information Theory descriptors of the histogram of ordinal patterns.
+			The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series.
+It consists of computing Information Theory descriptors of the histogram of ordinal patterns.
 			Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
-This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
+			This article proposes the first proposal of a test in the entropy-complexity plane for the white noise hypothesis.
 			Our test is based on true white noise sequences obtained from physical devices.
@@
 Our study's focus is to assess pure randomness by analyzing the empirical distribution of the points produced by true random sequences of finite size and obtaining regions of confidence in the $H \times C$ plane.
+
+\subsection{The Entropy-Complexity Plane in the Literature}\label{Sec:BPApplications}
+
+Initial works on the characterization of white noises with permutation entropy arose from the need to discriminate between them and chaotic maps \citep{rosso2013characterization, xiong2020complexity}.
+Notice that the logistic map has been used for pseudorandom number generation; cf.
+\citet{AnalyzingLogisticMapPseudorandomNumberGeneratorsforPeriodicityInducedbyFinitePrecisionFloatingPointRepresentation} and the references therein.
+It was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using Information Theory descriptors with the Bandt-Pompe symbolization \citep{larrondo2013statistical, gonzalez2005statistical}.
+
+Table~\ref{Tab:Literature} presents a summary of the main works in the literature that perform analysis of non-chaotic algorithmic generators, according to their features in the $H\times C$ plane.
+We also provide the length $T$ and embedding dimension $D$ of the time series under scrutiny.
+The following algorithmic generators were analyzed:
+\begin{itemize}
+	\item Mother RNG, available in Marsaglia's website \citep[MOT,][]{marsaglia1994yet};
+	\item Multiple with carry RNG \citep[MWC,][]{marsaglia1994yet};
+	\item Combo RNG \citep[COM,][]{marsaglia1994yet};
+	\item Lehmer RNG \citep[LEH,][]{payne1969coding};
+	\item Fractional Brownian motion (fBm) and fractional Gaussian noise (fGn); see \citet{bardet2003generators};
+	\item Colored noise with power spectrum $f^{-k}$ with $k \geq 0$~\citep{larrondo2012matlab};
+	\item Linear Congruential Generator \citep[LCG,][]{knuth1997sorting}.
+\end{itemize}
+
+\begin{table}[hbt]
+	\caption{Results of the main works of white noise sequences analysis in the $H \times C$ plane.}
+	\label{Tab:Literature}
+	\centering
+	\begin{tabular}{llcccc b{5.4em}}
+		\toprule
+		Reference & PRNG & $T$ & $D$ & $H$ & $C$ & Considered random? \\ 
+		\midrule
+		\citeauthor{larrondo2013statistical} (\citeyear{larrondo2013statistical}) &  MOT & NA & 6 & $\cong 0.9969$ & $\cong 0$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{gonzalez2005statistical} (\citeyear{gonzalez2005statistical})  &  MWC & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  MOT & 65536 & NA & $\cong 1$ & $0.3$ & yes \\
+		&  COM & 65536 & NA & $\cong 1$ & $0.05$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{RandomNumberGeneratorsCausality} (\citeyear{RandomNumberGeneratorsCausality}) &  LEH & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes \\
+		&  MOT & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		&  MWC & \num[scientific-notation=true]{5 e6} & 5 & $\cong 1$ & $10^{-4}$ & yes\\
+		\cmidrule(lr){1-7}
+		\citeauthor{rosso2013characterization} (\citeyear{rosso2013characterization}) &  LCG & \num[scientific-notation=true]{1 e7} & 6 & $0.997871$ & $0.005101$ & no\\
+		\cmidrule(lr){1-7}
+		\citeauthor{xiong2020complexity} (\citeyear{xiong2020complexity}) &  fGn & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
+		& $f^{-k}$ & \num[scientific-notation=true]{2 e17} & 6 & $\cong 1$ & $\cong 0$ & yes \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+None of these works provide $p$-values or hypothesis tests for their analysis.
+The focus of the articles is finding the set of descriptors that best discriminates chaos from noise.
+The authors make assessments about the randomness of sequence on ad hoc visual inspection of the point's location in the $H\times C$ plane.
+Our work fills such a gap for finite sequences of white noise and proposes a methodology that can be extended to any other situation.
 

### 2021-10-29 Reports/Journal - Confidence Regions/Response-R1.tex
Submitted verson

@@
 \usepackage{comment}   
+\usepackage{pdfpages}
 
@@
 Our initial version did not make a clear statement of the article's nature.
-In order to improve this issue, we have introduced two changes.
-The first is a new title, namely
+In order to improve this issue, we have introduced several changes.
+
+We propose a new title:
 \begin{quote}
@@
 \end{quote}
-Second, we now state at the beginning of the Abstract that
+
+We now state at the beginning of the Abstract that
 \begin{quote}
@@
 \begin{quote}
-	The \num{2,160} citations received by the seminal paper appeared in \num{780} venues indexed by the Web of Science.
-	Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the of citing articles).
+The seminal paper has received \num{2,160} citations from articles published in \num{780} venues indexed by the Web of Science.
+Among them, the journals belong to \num{127} categories, spanning from Multidisciplinary Physics (\SI{24}{\percent} of the publications) to Zoology (only one of the citing articles).
 There are \num{22} citing articles from journals that belong to the Statistics \& Probability category.
@@
 two in the \textit{Journal of Time Series Analysis} and in 
-	\textit{Theory and Applications of Time Series Analysis},
-	and each of the remaining ten appeared in a different journal.
+\textit{Theory and Applications of Time Series Analysis}.
+Furthermore, each of the remaining ten appeared in a different journal.
 Most of these articles relate successful applications of the Bandt and Pompe methodology, except \cite{OrdinalPatternProbabilities} that obtained the sample entropy's properties under zero-mean Gaussian processes.
@@
 \end{quote}
+
+Finally, in the Conclusions, we state that:
+\begin{quote}
+Although the Bandt and Pompe approach does not replace classical techniques, it is a valuable and widespread approach with an immediate graphical appeal.
+Making statistical inference in the Entropy-Complexity plane is challenging, but its potential impact is huge.
+\end{quote}
+
+We added a new study on the test power; cf. the response to Reviewer~\#1 below.
 
@@
 In particular, as detailed below, we now illustrate the need of using the complexity.
+
+In order to facilitate the revision, we have included at the end of this letter a version in which additions to the previous round are blue, and deletions in red.
 
@@
 
-We split the power subsection in two, and added another study which illustrates the need of considering the complexity:
+We split the test power subsection in two, and added another study which illustrates the need of considering the complexity:
 \begin{quote}
-	\subsubsection{$H_1$: Patch of Deterministic Function}
+	\subsubsection{$H_1$: Patch of a Deterministic Function}
 
@@
 We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
+This kind of contamination appears, for instance, when imputing missing data by linear interpolation~\citep{ImputationforConsecutiveMissingValuesinNonStationaryTimeSeriesData}.
+
 Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
@@
 
-It is worth noticing that a test based solely on the entropy would have less power.
-In this case, the complexity component enables the test to reject the null hypothesis at small contamination percentages.
+It is worth noticing that a test based solely on the entropy would have less power: it would only start rejecting when the contamination attains approximately \SI{6}{\percent} of the signal, or more.
+The complexity component enables the test to reject the null hypothesis at small contamination percentages.
 \end{quote}
@@
 
+\includepdf[pages=-]{diffR0R1.pdf}
+
 \end{document}

### 2021-10-29 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Submitted verson

@@
 \begin{enumerate}
-	\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$.
-By definition, $\eta_u\geq 1/2$.
+\item the right side of the box is the smallest $u_j$ which is larger that $u_x$; assume it corresponds to the quantile $\eta_u$ of $\utilde u = (u_1,u_2,\dots, u_N)$. By definition, $\eta_u\geq 1/2$.
 %
@@
 
-\subsubsection{$H_1$: Patch of Deterministic Function}
+\subsubsection{$H_1$: Patch of a Deterministic Function}\label{Sec:PatchDeterministic}
 
@@
 
-It is worth noticing that a test based solely on the entropy would have less power.
-In this case, the complexity component enables the test to reject the null hypothesis at small contamination percentages.
+It is worth noticing that a test based solely on the entropy would have less power: it would only start rejecting when the contamination attains approximately \SI{6}{\percent} of the signal, or more.
+The complexity component enables the test to reject the null hypothesis at small contamination percentages.
 
@@
 
+Although the Bandt and Pompe approach does not replace classical techniques, it is a valuable and widespread approach with an immediate graphical appeal.
+Making statistical inference in the Entropy-Complexity plane is challenging, but its potential impact is huge.
+
 \section{Reproducibility and Replicability}\label{Sec:code}

### 2021-10-29 Reports/Journal - Confidence Regions/ResearchProposal.tex
Submitted verson

@@
 \documentclass[12pt]{article}
+
+\newcommand\hmmax{0}
+\newcommand\bmmax{0}
 
@@
 	\end{equation}
+	{\color{magenta} ¿qué es $\psi$? }
 	which is a transformation of a bivariate Gaussian distribution.
@@
 
+	\textcolor{blue}{Si, y en principio no sería necesario pedir condiciones muy locas a la transformación; ver \citet{CasellaBergerStatisticalInference}}
+
 	\textcolor{red}{¿Cuál es la distribución conjuta asintótica de $(\widehat\alpha,\widehat\beta$)? Sabemos que la media es $(\alpha,\beta)$, pero ¿cuál es la matriz de covarianza?}
+
+	\textcolor{blue}{ Si $(\widehat\alpha,\widehat\beta)$ son los MLE de $(\alpha,\beta)$, entonces su distribución asintótica es $\mathcal{N}()$}
 
@@
 	Our proposal consists in approximating the distribution of $\mathfrak{C}$ by the distribution of $\widehat{C}(V,U)$.
+	So, finally, we will have the expression of ${C}(\widehat\alpha,\widehat\beta)$.
+
+	We will be in position to compute the joint distribution of 
+	\begin{equation}
+		\big( H (\widehat\alpha,\widehat\beta),
+		C(\widehat\alpha,\widehat\beta)
+		\big).    
+	\end{equation}
+	\textcolor{red}{¿Podremos usar resultados de distribución de permutaciones para tener el $p$-valor?}
+
+	\textcolor{magenta}{ Una cosa que creo que sí podemos usar para estimar la función de distribución, es aproximarla utilizando kernels.
+Según lo que estuve viendo, los kernels multivariados son simétricos y hay que estimar la matriz de covarianzas (lo cual parece que no es muy importante) y definir una matriz de anchos de banda.}
 
@@
 	\bibliographystyle{agsm}
-\bibliography{References}
+	\bibliography{references}
 

### 2021-12-19 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR2.tex
Version R2

--- 2021-10-29 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
@@
 
-\fundinginfo{CNPq, Fapeal}
+\fundinginfo{CNPq, Fapeal, and FAPESP (São Paulo Research Foundation) grant 2020/05121-4.}
 
@@
 ${\bm \pi}^{(D)} = (\pi_1, \pi_2, \dots, \pi_D)$ so every element ${\bm \pi}^{(D)}$ is unique 
-($\pi_j \neq \pi_k~\forall~j \neq k$). 
+($\pi_j \neq \pi_k$ for every $j \neq k$). 
 Consider for the time series ${\mathcal X} \equiv \{x_t\}_{t=1}^{T}$ its time delay embedding representation,
@@
 \begin{equation} 
-{\mathbf X}^{(D,\tau)}_t =( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} ) ,
+{\mathbf X}^{(D,\tau)}_t =\big( x_t,x_{t+\tau},\dots,x_{t+(D-1)\tau} \big) ,
 \label{eq:time-delay}
@@
 
-After computing all the symbols, one obtains the histogram of proportions $\bm h = (h(j))_{1\leq j\leq D!}$.
+After computing all the symbols, one obtains the histogram of proportions $\bm h = \big(h(j)\big)_{1\leq j\leq D!}$.
 Such histogram estimates the (unknown, in general) probability distribution function of these patterns.
@@
 
-The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as an adequate measure of such a distance:
+The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=\big(u(1), u(2), \dots, u(D!)\big)$ stems as an adequate measure of such a distance:
 \begin{equation}
@@
 Most works consider the uniform distribution $\bm u = (1/D!, 1/D!, \dots, 1/D!)$ as the reference model.
+In this case, \eqref{eq:JensenShannon} becomes
+\begin{equation}
+Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} h(\ell) \log h(\ell) - \frac{1}{D!} \sum_{\ell=1}^{D!} \log h(\ell).
+\label{eq:JS-Uniform}
+\end{equation}
+The usual assumption in~\eqref{eq:JensenShannon} and~\eqref{eq:JS-Uniform} is $0\log 0=0$.
 
@@
 \item Chaotic logistic series $x_t = r x_{t-1} (1 - x_{t-1})$, with $r=3.6$ and $4$;
-\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
+\item Deterministic series: monotonic increasing ($\log(x_t+0.1)$, $x_t=\{1,2,\dots,10^4\}$) and periodic ($\sin(2x_t)\cos(2x_t)$, with $0\leq x_t\leq 2\pi$ over ten thousand equally spaced points).
 \end{itemize}

### 2021-12-20 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR2.tex
Version R2

@@
+% !TeX TS-program = pdflatex
 \documentclass[alpha-refs]{wiley-article}
@@
 
-\title{Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane}
+\title{White Noise Test from Ordinal Patterns in the Entropy-Complexity Plane}
 
@@
 consists of computing
-Information Theory descriptors of the histogram of ordinal patterns. 
+Information Theory descriptors from the histogram of ordinal patterns. 
 Such descriptors lie in a 2D manifold: the Entropy-Complexity plane. 
@@
 captures the randomness of generators previously analyzed in the literature.
-\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
+\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Ordinal Patterns, Time Series, Information Theory}
 \end{abstract}
@@
 Most works consider the uniform distribution $\bm u = (1/D!, 1/D!, \dots, 1/D!)$ as the reference model.
-In this case, \eqref{eq:JensenShannon} becomes
-\begin{equation}
-Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} h(\ell) \log h(\ell) - \frac{1}{D!} \sum_{\ell=1}^{D!} \log h(\ell).
-\label{eq:JS-Uniform}
-\end{equation}
-The usual assumption in~\eqref{eq:JensenShannon} and~\eqref{eq:JS-Uniform} is $0\log 0=0$.
 
